### 2023-10-19 article/article.qmd
ss
asd

---
title: Quantile Regressions via Method of Moments with multiple fixed effects
author:
  - name: Fernando Rios-Avila
    email: friosavi@levy.org
    affiliations: 
        - id: levy
          name: Levy Economics Institute of Bard College          
    attributes:
        corresponding: true
  - name: Leonardo Siles
    email: leo@gmail.com
  - name: Gustavo Canavire-Bacarreza
    email: gcanavire@worldbank.org
    affiliations:
        - id: wb
          name: World Bank
abstract: |
  This paper proposes a new method to estimate quantile regressions with multiple fixed effects. The method expands on the strategy proposed by @mss2019, allowing for multiple fixed effects, and providing various alternatives for the estimation of Standard errors. We provide Monte Carlo simulations to show the finite sample properties of the proposed method in the presence of two sets of fixed effects. Finally, we apply the proposed method to estimate **something interesting**
keywords: 
  - Fixed effects
  - Linear heteroskedasticity
  - Location-scale model
  - Quantile regression

date: last-modified
bibliography: bibliography.bib
format:
  elsevier-pdf:
    keep-tex: true
    journal:
      name: Journal Name
      formatting: preprint
      model: 1p
      cite-style: authoryear
---

# Introduction

Quantile regression (QR), introduced by Koenker and Bassett (1978), is an estimation strategy used for modeling the relationships between explanatory variables X and the conditional quantiles of the dependent variable $q_\tau (y|x)$. Using QR one can obtain richer characterizations of the relationships between dependent and independent variables, by accounting for otherwise unobserved heterogeneity.

A relatively recent development in the literature has focused on extending quantile regressions analysis to include individual fixed effects in the framework of panel data. However, as described in Neyman and Scott (1948), and Lancaster (2000), when individual fixed effects are included in quantile regression analysis it generates an incident parameter problem. While many strategies have been proposed for estimating this type of model (see Galvão and Kato, 2018 for a brief review), neither has become standard because of their restrictive assumptions in regards to the individual effects, the computational complexity, and implementation.

More recently, @mss2019 (MSS hereafter) proposed a methodology based on a conditional location-scale model similar to the one described in @he1997, for the estimation of quantile regressions models for panel data via a method of moments. This method allows individual fixed effects allowing to have heterogeneous effects on the entire conditional distribution of the outcome, rather constraining their effect to be a location shift only as in Canay (2011), Koenker(2004), and Lancaster(2000).

In principle, under the assumption that data generating process behind the data is based on a multiplicative heteroskedastic process that is linear in parameters (Cameron and Trivedi, 2005; @mss2019; @he1997), the effect of a variable $X$ on the $q_th$ quantile can be derived as the combination of a location effect, and scale effect moderated by the quantile of an underlying i.i.d. error. For statistical inference, MSS derives the asymptotic distribution of the estimator, suggesting the use of bootstrap standard errors, as well.

While this methodology is not meant to substitute the use of standard quantile regression analysis, given the assumptions required for the identification of the model, it provides a simple and fast alternative for the estimation of quantile regression models with individual fixed effects.

In this framework, our paper expands on @mss2019, following some of the suggestions by the authors regarding further research. First, making use of the properties of GMM estimators, we derive various alternatives for the estimation of standard errors based on the empirical Influence functions of the estimators. Second, we reconsider the application of Frisch–Waugh–Lovell (FWL) theorem (Lovell (1963) and Frisch and Waugh’s (1933)) to extend the MSS estimator to allow for the inclusion of multiple fixed effects, for example, individual and year fixed effects.

The rest of the paper is restructured as follows. Section 2 presents the basic setup of the location-Scale model described in @he1997, tying the relationship between the standard quantile regression model, and the location and scale model. It also revisits MSS methodology, proposing alternative estimators for the standard errors based on the properties of GMM estimators and the empirical influence functions. It also shows that FWL theorem can be used to control for multiple fixed effects. Section 3 presents the results of a small simulation study and Section 4 illustrates the application of the proposed methods with two empirical examples. Seccion 5 concludes.

# Methodology
## Quantile Regression Location-Scale model @he1997

## Standard Errors: GLS, Robust, Clustered

## Multiple Fixed Effects: Expanding on @mss2019

# Monte Carlo Simulations

# Application: **Something interesting**

# Conclusions

# References {-}

# Appendix {-}

### 2023-10-19 article/article.tex
ss
asd

% Options for packages loaded elsewhere
\PassOptionsToPackage{unicode}{hyperref}
\PassOptionsToPackage{hyphens}{url}
\PassOptionsToPackage{dvipsnames,svgnames,x11names}{xcolor}
%
\documentclass[
  authoryear,
  preprint,
  1p]{elsarticle}

\usepackage{amsmath,amssymb}
\usepackage{iftex}
\ifPDFTeX
  \usepackage[T1]{fontenc}
  \usepackage[utf8]{inputenc}
  \usepackage{textcomp} % provide euro and other symbols
\else % if luatex or xetex
  \usepackage{unicode-math}
  \defaultfontfeatures{Scale=MatchLowercase}
  \defaultfontfeatures[\rmfamily]{Ligatures=TeX,Scale=1}
\fi
\usepackage{lmodern}
\ifPDFTeX\else  
    % xetex/luatex font selection
\fi
% Use upquote if available, for straight quotes in verbatim environments
\IfFileExists{upquote.sty}{\usepackage{upquote}}{}
\IfFileExists{microtype.sty}{% use microtype if available
  \usepackage[]{microtype}
  \UseMicrotypeSet[protrusion]{basicmath} % disable protrusion for tt fonts
}{}
\makeatletter
\@ifundefined{KOMAClassName}{% if non-KOMA class
  \IfFileExists{parskip.sty}{%
    \usepackage{parskip}
  }{% else
    \setlength{\parindent}{0pt}
    \setlength{\parskip}{6pt plus 2pt minus 1pt}}
}{% if KOMA class
  \KOMAoptions{parskip=half}}
\makeatother
\usepackage{xcolor}
\setlength{\emergencystretch}{3em} % prevent overfull lines
\setcounter{secnumdepth}{5}
% Make \paragraph and \subparagraph free-standing
\ifx\paragraph\undefined\else
  \let\oldparagraph\paragraph
  \renewcommand{\paragraph}[1]{\oldparagraph{#1}\mbox{}}
\fi
\ifx\subparagraph\undefined\else
  \let\oldsubparagraph\subparagraph
  \renewcommand{\subparagraph}[1]{\oldsubparagraph{#1}\mbox{}}
\fi

\providecommand{\tightlist}{%
  \setlength{\itemsep}{0pt}\setlength{\parskip}{0pt}}\usepackage{longtable,booktabs,array}
\usepackage{calc} % for calculating minipage widths
% Correct order of tables after \paragraph or \subparagraph
\usepackage{etoolbox}
\makeatletter
\patchcmd\longtable{\par}{\if@noskipsec\mbox{}\fi\par}{}{}
\makeatother
% Allow footnotes in longtable head/foot
\IfFileExists{footnotehyper.sty}{\usepackage{footnotehyper}}{\usepackage{footnote}}
\makesavenoteenv{longtable}
\usepackage{graphicx}
\makeatletter
\def\maxwidth{\ifdim\Gin@nat@width>\linewidth\linewidth\else\Gin@nat@width\fi}
\def\maxheight{\ifdim\Gin@nat@height>\textheight\textheight\else\Gin@nat@height\fi}
\makeatother
% Scale images if necessary, so that they will not overflow the page
% margins by default, and it is still possible to overwrite the defaults
% using explicit options in \includegraphics[width, height, ...]{}
\setkeys{Gin}{width=\maxwidth,height=\maxheight,keepaspectratio}
% Set default figure placement to htbp
\makeatletter
\def\fps@figure{htbp}
\makeatother

\makeatletter
\makeatother
\makeatletter
\makeatother
\makeatletter
\@ifpackageloaded{caption}{}{\usepackage{caption}}
\AtBeginDocument{%
\ifdefined\contentsname
  \renewcommand*\contentsname{Table of contents}
\else
  \newcommand\contentsname{Table of contents}
\fi
\ifdefined\listfigurename
  \renewcommand*\listfigurename{List of Figures}
\else
  \newcommand\listfigurename{List of Figures}
\fi
\ifdefined\listtablename
  \renewcommand*\listtablename{List of Tables}
\else
  \newcommand\listtablename{List of Tables}
\fi
\ifdefined\figurename
  \renewcommand*\figurename{Figure}
\else
  \newcommand\figurename{Figure}
\fi
\ifdefined\tablename
  \renewcommand*\tablename{Table}
\else
  \newcommand\tablename{Table}
\fi
}
\@ifpackageloaded{float}{}{\usepackage{float}}
\floatstyle{ruled}
\@ifundefined{c@chapter}{\newfloat{codelisting}{h}{lop}}{\newfloat{codelisting}{h}{lop}[chapter]}
\floatname{codelisting}{Listing}
\newcommand*\listoflistings{\listof{codelisting}{List of Listings}}
\makeatother
\makeatletter
\@ifpackageloaded{caption}{}{\usepackage{caption}}
\@ifpackageloaded{subcaption}{}{\usepackage{subcaption}}
\makeatother
\makeatletter
\@ifpackageloaded{tcolorbox}{}{\usepackage[skins,breakable]{tcolorbox}}
\makeatother
\makeatletter
\@ifundefined{shadecolor}{\definecolor{shadecolor}{rgb}{.97, .97, .97}}
\makeatother
\makeatletter
\makeatother
\makeatletter
\makeatother
\journal{Journal Name}
\ifLuaTeX
  \usepackage{selnolig}  % disable illegal ligatures
\fi
\usepackage[]{natbib}
\bibliographystyle{elsarticle-harv}
\IfFileExists{bookmark.sty}{\usepackage{bookmark}}{\usepackage{hyperref}}
\IfFileExists{xurl.sty}{\usepackage{xurl}}{} % add URL line breaks if available
\urlstyle{same} % disable monospaced font for URLs
\hypersetup{
  pdftitle={Quantile Regressions via Method of Moments with multiple fixed effects},
  pdfauthor={Fernando Rios-Avila; Leonardo Siles; Gustavo Canavire-Bacarreza},
  pdfkeywords={Fixed effects, Linear heteroskedasticity, Location-scale
model, Quantile regression},
  colorlinks=true,
  linkcolor={blue},
  filecolor={Maroon},
  citecolor={Blue},
  urlcolor={Blue},
  pdfcreator={LaTeX via pandoc}}

\setlength{\parindent}{6pt}
\begin{document}

\begin{frontmatter}
\title{Quantile Regressions via Method of Moments with multiple fixed
effects}
\author[1]{Fernando Rios-Avila%
\corref{cor1}%
}
 \ead{friosavi@levy.org} 
\author[]{Leonardo Siles%
%
}
 \ead{leo@gmail.com} 
\author[2]{Gustavo Canavire-Bacarreza%
%
}
 \ead{gcanavire@worldbank.org}

\affiliation[1]{organization={Levy Economics Institute of Bard
College},,postcodesep={}}
\affiliation[2]{organization={World Bank},,postcodesep={}}

\cortext[cor1]{Corresponding author}

\begin{abstract}
This paper proposes a new method to estimate quantile regressions with
multiple fixed effects. The method expands on the strategy proposed by
\citet{mss2019}, allowing for multiple fixed effects, and providing
various alternatives for the estimation of Standard errors. We provide
Monte Carlo simulations to show the finite sample properties of the
proposed method in the presence of two sets of fixed effects. Finally,
we apply the proposed method to estimate \textbf{something interesting}
\end{abstract}

\begin{keyword}
    Fixed effects \sep Linear heteroskedasticity \sep Location-scale
model \sep 
    Quantile regression
\end{keyword}
\end{frontmatter}
    \ifdefined\Shaded\renewenvironment{Shaded}{\begin{tcolorbox}[interior hidden, frame hidden, enhanced, sharp corners, breakable, borderline west={3pt}{0pt}{shadecolor}, boxrule=0pt]}{\end{tcolorbox}}\fi

\hypertarget{introduction}{%
\section{Introduction}\label{introduction}}

Quantile regression (QR), introduced by Koenker and Bassett (1978), is
an estimation strategy used for modeling the relationships between
explanatory variables X and the conditional quantiles of the dependent
variable \(q_\tau (y|x)\). Using QR one can obtain richer
characterizations of the relationships between dependent and independent
variables, by accounting for otherwise unobserved heterogeneity.

A relatively recent development in the literature has focused on
extending quantile regressions analysis to include individual fixed
effects in the framework of panel data. However, as described in Neyman
and Scott (1948), and Lancaster (2000), when individual fixed effects
are included in quantile regression analysis it generates an incident
parameter problem. While many strategies have been proposed for
estimating this type of model (see Galvão and Kato, 2018 for a brief
review), neither has become standard because of their restrictive
assumptions in regards to the individual effects, the computational
complexity, and implementation.

More recently, \citet{mss2019} (MSS hereafter) proposed a methodology
based on a conditional location-scale model similar to the one described
in \citet{he1997}, for the estimation of quantile regressions models for
panel data via a method of moments. This method allows individual fixed
effects allowing to have heterogeneous effects on the entire conditional
distribution of the outcome, rather constraining their effect to be a
location shift only as in Canay (2011), Koenker(2004), and
Lancaster(2000).

In principle, under the assumption that data generating process behind
the data is based on a multiplicative heteroskedastic process that is
linear in parameters (Cameron and Trivedi, 2005; \citet{mss2019};
\citet{he1997}), the effect of a variable \(X\) on the \(q_th\) quantile
can be derived as the combination of a location effect, and scale effect
moderated by the quantile of an underlying i.i.d. error. For statistical
inference, MSS derives the asymptotic distribution of the estimator,
suggesting the use of bootstrap standard errors, as well.

While this methodology is not meant to substitute the use of standard
quantile regression analysis, given the assumptions required for the
identification of the model, it provides a simple and fast alternative
for the estimation of quantile regression models with individual fixed
effects.

In this framework, our paper expands on \citet{mss2019}, following some
of the suggestions by the authors regarding further research. First,
making use of the properties of GMM estimators, we derive various
alternatives for the estimation of standard errors based on the
empirical Influence functions of the estimators. Second, we reconsider
the application of Frisch--Waugh--Lovell (FWL) theorem (Lovell (1963)
and Frisch and Waugh's (1933)) to extend the MSS estimator to allow for
the inclusion of multiple fixed effects, for example, individual and
year fixed effects.

The rest of the paper is restructured as follows. Section 2 presents the
basic setup of the location-Scale model described in \citet{he1997},
tying the relationship between the standard quantile regression model,
and the location and scale model. It also revisits MSS methodology,
proposing alternative estimators for the standard errors based on the
properties of GMM estimators and the empirical influence functions. It
also shows that FWL theorem can be used to control for multiple fixed
effects. Section 3 presents the results of a small simulation study and
Section 4 illustrates the application of the proposed methods with two
empirical examples. Seccion 5 concludes.

\hypertarget{methodology}{%
\section{Methodology}\label{methodology}}

\hypertarget{quantile-regression-location-scale-model-he1997}{%
\subsection{\texorpdfstring{Quantile Regression Location-Scale model
\citet{he1997}}{Quantile Regression Location-Scale model @he1997}}\label{quantile-regression-location-scale-model-he1997}}

\hypertarget{standard-errors-gls-robust-clustered}{%
\subsection{Standard Errors: GLS, Robust,
Clustered}\label{standard-errors-gls-robust-clustered}}

\hypertarget{multiple-fixed-effects-expanding-on-mss2019}{%
\subsection{\texorpdfstring{Multiple Fixed Effects: Expanding on
\citet{mss2019}}{Multiple Fixed Effects: Expanding on @mss2019}}\label{multiple-fixed-effects-expanding-on-mss2019}}

\hypertarget{monte-carlo-simulations}{%
\section{Monte Carlo Simulations}\label{monte-carlo-simulations}}

\hypertarget{application-something-interesting}{%
\section{\texorpdfstring{Application: \textbf{Something
interesting}}{Application: Something interesting}}\label{application-something-interesting}}

\hypertarget{conclusions}{%
\section{Conclusions}\label{conclusions}}

\hypertarget{references}{%
\section*{References}\label{references}}
\addcontentsline{toc}{section}{References}

\renewcommand\refname{Appendix}
  \bibliography{bibliography.bib}

\end{document}

### 2023-10-20 article/article.tex
s
s

@@
 \end{frontmatter}
-    \ifdefined\Shaded\renewenvironment{Shaded}{\begin{tcolorbox}[interior hidden, frame hidden, enhanced, sharp corners, breakable, borderline west={3pt}{0pt}{shadecolor}, boxrule=0pt]}{\end{tcolorbox}}\fi
+    \ifdefined\Shaded\renewenvironment{Shaded}{\begin{tcolorbox}[boxrule=0pt, sharp corners, interior hidden, breakable, frame hidden, borderline west={3pt}{0pt}{shadecolor}, enhanced]}{\end{tcolorbox}}\fi
 

### 2023-10-20 article/article.qmd
s
s
d
d

@@
 
-Quantile regression (QR), introduced by Koenker and Bassett (1978), is an estimation strategy used for modeling the relationships between explanatory variables X and the conditional quantiles of the dependent variable $q_\tau (y|x)$.
+Quantile regression (QR), introduced by @koenkerbasset1978, is an estimation strategy used for modeling the relationships between explanatory variables X and the conditional quantiles of the dependent variable $q_\tau (y|x)$.
 Using QR one can obtain richer characterizations of the relationships between dependent and independent variables, by accounting for otherwise unobserved heterogeneity.
@@
 A relatively recent development in the literature has focused on extending quantile regressions analysis to include individual fixed effects in the framework of panel data.
-However, as described in Neyman and Scott (1948), and Lancaster (2000), when individual fixed effects are included in quantile regression analysis it generates an incident parameter problem.
+However, as described in @neymanscott1948, and @lancaster2000, when individual fixed effects are included in quantile regression analysis it generates an incident parameter problem.
 While many strategies have been proposed for estimating this type of model (see Galvão and Kato, 2018 for a brief review), neither has become standard because of their restrictive assumptions in regards to the individual effects, the computational complexity, and implementation.
@@
 More recently, @mss2019 (MSS hereafter) proposed a methodology based on a conditional location-scale model similar to the one described in @he1997, for the estimation of quantile regressions models for panel data via a method of moments.
-This method allows individual fixed effects allowing to have heterogeneous effects on the entire conditional distribution of the outcome, rather constraining their effect to be a location shift only as in Canay (2011), Koenker(2004), and Lancaster(2000).
+This method allows individual fixed effects allowing to have heterogeneous effects on the entire conditional distribution of the outcome, rather constraining their effect to be a location shift only as in @canay2011, @koenker2004, and @lancaster2000.
 
-In principle, under the assumption that data generating process behind the data is based on a multiplicative heteroskedastic process that is linear in parameters (Cameron and Trivedi, 2005; @mss2019; @he1997), the effect of a variable $X$ on the $q_th$ quantile can be derived as the combination of a location effect, and scale effect moderated by the quantile of an underlying i.i.d.
+In principle, under the assumption that data generating process behind the data is based on a multiplicative heteroskedastic process that is linear in parameters (@cameron2005; @mss2019; @he1997), the effect of a variable $X$ on the $q_th$ quantile can be derived as the combination of a location effect, and scale effect moderated by the quantile of an underlying i.i.d.
 error.
@@
 First, making use of the properties of GMM estimators, we derive various alternatives for the estimation of standard errors based on the empirical Influence functions of the estimators.
-Second, we reconsider the application of Frisch–Waugh–Lovell (FWL) theorem (Lovell (1963) and Frisch and Waugh’s (1933)) to extend the MSS estimator to allow for the inclusion of multiple fixed effects, for example, individual and year fixed effects.
+Second, we reconsider the application of Frisch–Waugh–Lovell (FWL) theorem (@frishwaugh1933 and @lovell1963) to extend the MSS estimator to allow for the inclusion of multiple fixed effects, for example, individual and year fixed effects.
 
@@
 # Methodology
+
 ## Quantile Regression Location-Scale model @he1997
+
+Quantile regressions are used to identify relationships between the explanatory variables $x$ and the conditional quantiles of the dependent variable $q_\tau (y|x)$.
+One of the most common formulations to represent the need for quantile regression model is given by:
+
+$$Y=X\beta(\tau), \tau \sim uniform(0,1) $$
+
+Which allows for nonlinearities on the effect of $X$ on $Y$ along all values of $\tau$.
+This formulation , also known as a random coefficient model, can be re-written as a location-scale model, as described in @he1997:
+
+$$Y = X \beta + X \gamma(\tau)$$
+
+Here, $\beta$ represent the location effect, which represents the average effect $X$ has on $Y$ and can be estimated using e , and $\gamma(\tau)$ represents the scale effect, which can be interpreted as the effect of $X$ on the conditional variance of $Y$.
 
@@
 
+# Appendix {.appendix}
+
 # References {-}
-
-# Appendix {-}

### 2023-10-23 article/article.qmd
d
d

@@
 
-More recently, @mss2019 (MSS hereafter) proposed a methodology based on a conditional location-scale model similar to the one described in @he1997, for the estimation of quantile regressions models for panel data via a method of moments.
+More recently, @mss2019 (MSS hereafter) proposed a methodology based on a conditional location-scale model similar to the one described in @he1997 and @zhao2020, for the estimation of quantile regressions models for panel data via a method of moments.
 This method allows individual fixed effects allowing to have heterogeneous effects on the entire conditional distribution of the outcome, rather constraining their effect to be a location shift only as in @canay2011, @koenker2004, and @lancaster2000.
 
-In principle, under the assumption that data generating process behind the data is based on a multiplicative heteroskedastic process that is linear in parameters (@cameron2005; @mss2019; @he1997), the effect of a variable $X$ on the $q_th$ quantile can be derived as the combination of a location effect, and scale effect moderated by the quantile of an underlying i.i.d.
+In principle, under the assumption that data generating process behind the data is based on a multiplicative heteroskedastic process that is linear in parameters (@cameron2005; @mss2019; @he1997; @zhao2020), the effect of a variable $X$ on the $q_th$ quantile can be derived as the combination of a location effect, and scale effect moderated by the quantile of an underlying i.i.d.
 error.
@@
 The rest of the paper is restructured as follows.
-Section 2 presents the basic setup of the location-Scale model described in @he1997, tying the relationship between the standard quantile regression model, and the location and scale model.
+Section 2 presents the basic setup of the location-Scale model described in @he1997 and @zhao2020, tying the relationship between the standard quantile regression model, and the location and scale model.
 It also revisits MSS methodology, proposing alternative estimators for the standard errors based on the properties of GMM estimators and the empirical influence functions.
@@
 
-## Quantile Regression Location-Scale model @he1997
+## Quantile Regression: Location-Scale model
 
-Quantile regressions are used to identify relationships between the explanatory variables $x$ and the conditional quantiles of the dependent variable $q_\tau (y|x)$.
-One of the most common formulations to represent the need for quantile regression model is given by:
+Quantile regressions are used to identify relationships between the explanatory variables $x$ and the conditional quantiles of the dependent variable $Q(y|\tau,X)$.
+This relationship is commonly assumed to follow a linear functional form:
 
-$$Y=X\beta(\tau), \tau \sim uniform(0,1) $$
+$$Q(Y|X,\tau) =X\beta(\tau)
+$${#eq-eq1}
 
-Which allows for nonlinearities on the effect of $X$ on $Y$ along all values of $\tau$.
-This formulation , also known as a random coefficient model, can be re-written as a location-scale model, as described in @he1997:
+This allows for nonlinearities in the effect of $X$ on $Y$ across all values of $\tau$.
+This formulation can also be related to a random coefficient model, where all coefficients are assumed to be some nonlinear function of $\tau$, where $\tau$ follows a random uniform distribution.
 
-$$Y = X \beta + X \gamma(\tau)$$
+An alternative formulation of quantile regressions is the location-scale model.
+This approach assumes that the conditional quantile of $Y$ given $X$ and $\tau$ can be expressed as a combination of two models: the location model, which describes the central tendency of the conditional distribution, and the scale model, which describes deviations from the central tendency:
 
-Here, $\beta$ represent the location effect, which represents the average effect $X$ has on $Y$ and can be estimated using e , and $\gamma(\tau)$ represents the scale effect, which can be interpreted as the effect of $X$ on the conditional variance of $Y$.
+$$Q(Y|X,\tau) =X\beta+X\gamma(\tau)
+$${#eq-eq2}
+
+Here, the location parameters $\beta$ are typically identified using a linear regression model (as in @mss2019), or a median regression (as in @melly2005), and the scale parameters $\gamma(\tau)$ can be estimated using standard approaches.
+
+Both the standard quantile regression (@eq-eq1) and the location-scale specification (@eq-eq2) can be estimated as the solution to a weighted minimization problem:
+
+$$\hat{\beta}(\tau) = \underset{\beta}{\operatorname{argmin}}
+\left( \sum_{i\in y_i\geq x_i'\beta} \tau (y_i - x_i'\beta) - \sum_{i\in y_i<x_i'\beta} (1-\tau)(y_i - x_i'\beta) \right)
+$${#eq-eq3}
+
+One characteristic of this estimator is that the $\beta(\tau)$ coefficients are identified locally, and thus the estimated quantile coefficients will exhibit considerable variation when analyzed across $\tau$.
+It is also implicit that if one requires an analysis of the entire distribution, it would be necessary to estimate the model for each quantile.[^1]
+
+[^1]: There are other estimators that provide smoother estimates for the quantile regression coefficients using a kernel local weighted approach [@kaplan2017], as well as identifying the full set of quantile coefficients simultaneously assuming some parametric functional forms [@frumentobotai2016].
+
+One insightful extension to the location-scale parameterizations suggested by @he1997, @cameron2005, and @mss2019 is to assume that the data-generating process (DGP) can be written as a linear model with a multiplicative heteroskedastic process that is linear in parameters.[^2]
+
+$$y_i=x_i'\beta+\varepsilon_i \times x_i'\gamma(\tau)
+$${#eq-eq4}
+
+[^2]: @mss2019 also discuss a model where heteroskedasticity can be an arbitrary nonlinear function $\sigma(x_i'\gamma)$, but develop the estimator for the linear case, i.e., when $\sigma()$ is the identity function.
+
+Under the assumption that $\varepsilon$ is an independent and identically distributed (iid) unobserved random variable that is independent of $X$, the conditional quantile of $Y$ given $X$ and $\tau$ can be written as:
+
+$$Q(Y|X,\tau) =X\beta+X\gamma \times Q(\varepsilon|\tau)
+$${#eq-eq5}
+
+In this setup, the traditional quantile coefficients are identified as the location model coefficients, plus the scale model coefficients moderated by the $\tau_th$ unconditional quantile of the standardized error $\varepsilon$.
+
+$$\beta(\tau) = \beta + \gamma \times Q(\varepsilon|\tau)
+$${#eq-eq6}
+
+While this specification imposes a strong assumption on the DGP, it has two advantages over the standard quantile regression model.
+First, because the location and scale model can be identified globally, with only a single parmater ($Q(\varepsilon|\tau)$) requiring local estimation, this estimation approach would be more efficient than the standard quantile regression model (@zhao2000).
+Second, under the assumption that $X\gamma$ is strictly possitive, the model would produce quantile coefficients that do not cross.
+
+Following MSS, the quantile regression model defined by @eq-eq5 can be estimated using a method of moments approach.
+And while its possible to identify all coefficients ($\beta,\gamma, Q(\varepsilon|\tau)$) simultaneously, we describe and use the implementation approach advocated by MSS which identifies each set of coefficients separately.
+
+1.
+The location model can be estimated using a standard linear regression model, where the dependent variable is the outcome $Y$, and the independent variables are the explanatory variables $X$ (including a constant) with an error $u$, which is by definition heteroskedastic.
+In this case, the location model coefficients are identified under the following condition:
+$$\begin{aligned}
+  y_i &=x_i'\beta+u_i \\
+  E[u 'X ] &=0
+  \end{aligned}
+$${#eq-eq7}
+
+2.
+After the location model is estimated, the scale coefficients can be identified by modeling heteroskedasticity as a linear function of characteristics $X$.
+For this we use the absolute value of the errors from the location model $u$ as dependent variable, which would allow us to estimate the conditional standard deviation (rather than conditional variance) of the errors.
+In this case, the coefficients are identified under the following condition:
+
+$$\begin{aligned}
+  |u_i| &=x_i'\gamma+v_i \\
+  E[ (|u|-X \gamma) X ] &=0
+  \end{aligned}
+$${#eq-eq8}
+
+3. Finally, given the location and scale coefficients, the $\tau_{th}$ quantile of the error $e$ can be estimated using the following condition:
+
+$$\begin{aligned}
+  E\left[  \mathbb{1}\left(x_i' (\beta + \gamma Q(\varepsilon|\tau)) \geq y_i \right) - \tau \right] &=0  \\
+  E\left[  \mathbb{1}\left(   Q(\varepsilon|\tau)\geq \frac{y_i-x_i'\beta}{x_i'\gamma} \right) - \tau \right] &=0  \\
+  \end{aligned}
+$${#eq-eq9}
+
+Where one identifies the quantile of the error $\varepsilon$ using standardized errors $\frac{y_i-x_i'\beta}{x_i'\gamma}$, or by finding the values that identify the overall quantile coefficients $\beta(\tau)=\beta + \gamma Q(\varepsilon|\tau)$.
+Afterwords, the conditional quantile coefficients is simply defined as the combination of the location and scale coefficients.
 
 ## Standard Errors: GLS, Robust, Clustered
+
+As discussed in the previous section, the estimation of quantile regression coefficients using the location-scale model with heteroskedstic linear errors can be estimated using a the following set of moments, which fits in the Generalized Method of Moments framework:
+
+$$\begin{aligned}
+  E[u_i x_i ] &= E[h_{1,i}]=0 \\
+  E[ (|u_i|-x_i \gamma) x_i ] &=E[h_{2,i}]=0 \\
+  E\left[  \mathbb{1}\left(   Q(\varepsilon|\tau)\geq \frac{y_i-x_i'\beta}{x_i'\gamma} \right) - \tau \right] 
+  &=E[h_{3,i}]=0 
+  \end{aligned}
+$${#eq-eq10}
+
+Under the conditions described in @newey_chapter_1994 (see section 7), @cameron2005 (see chapter 6.3.9) or as shown in @mss2019, the location, scale and residual quantile coefficients are asymptotically normal.[^3]
+
+[^3]: @zhao2000 also shows that the quantile coefficients for the location-scale model also follows a normal distribution, but uses the assumption that the location model is derived using a least absolute deviation approach (median regression).
+
+Call $\theta=[ \beta' \ \ \gamma'  \ \ Q(\varepsilon|\tau)' ]'$ the set of coefficients that are identified in @eq-eq10, a just identified model.  And the functions $G_{k,l}$ and $S_{k.l}$ equal to:
+
+$$\begin{aligned}
+G_{k,l} &= N^{-1} \sum_{i=1}^N \frac{\partial h_{k,i}}{\partial \theta_l} \Big|_{\hat\theta} \ \forall k,l \in [1,2,3] \\
+S_{k,l} &= N^{-1} \sum_{i=1}^N h_{k,i} h_{l,i}' \Big|_{\hat\theta} \ \forall k,l \in [1,2,3]
+\end{aligned}
+$$
+
+where $\theta_1 = \beta$, $\theta_2 = \gamma$ and $\theta_3 = Q(\varepsilon,\tau)$.
+
+Then 
+$$
+\sqrt{N}(\hat\theta - \theta) \xrightarrow{d} N(0, G^{-1} S G^{-1})
+$$
+
+with, $G$ and $S$ defined as:
+
+$$\begin{aligned}
+G &= \begin{bmatrix}
+G_{1,1} &       0 & 0       \\
+G_{2,1} & G_{2,2} & 0       \\
+G_{3,1} & G_{3,2} & G_{3,3} 
+\end{bmatrix}  \text{ and }
+S &= \begin{bmatrix}
+S_{1,1} & S_{1,2} & S_{1,3}    \\
+S_{2,1} & S_{2,2} & S_{2,3}  \\
+S_{3,1} & S_{3,2} & S_{3,3} 
+\end{bmatrix}
+\end{aligned}
+$$
+
+Because
+
+$$
+Var(\hat\theta) = \frac{1}{N} \left(
+    \frac{1}{N} 
+    \sum_{i=1}^N  \lambda_i(\theta) \lambda_i(\theta)'  
+\right) = \frac{1}{N^2} 
+\lambda(\theta)'\lambda(\theta)
+$$
+
+$$
+\lambda_i(\theta) = \bar G(\theta)^{-1} h_i (x_i,\theta)
+$$
+
+Finally, the variance covariance of $\hat \beta(\tau)$ will be given by:
+
+$$Var(\hat\beta(\tau)) = \Xi Var(\hat\theta) \Xi'$$
+
+where $\Xi$ is a $k \times (2k+1)$ matrix defined as:
+
+$$
+\begin{aligned}
+    \Xi &= I(k), \hat q(\tau) I(k), \hat \gamma \\
+    \Xi &= \left[ \begin{array}{cccc|cccc|}
+           1 & 0 & \dots & 0 &\hat q_(\tau) & 0 & ... & 0  & \hat\gamma_0 \\
+           0 & 1 & \dots & 0 &0& \hat q_(\tau) & ... & 0 & \hat\gamma_1 \\
+          \vdots & \vdots & \dots & 0 &...&...& ... & 0             & ...\\
+           0 & 0 & \dots & 1 &0 & 0 & ... & \hat q(\tau)   & \hat\gamma_k
+        \end{array} \right]         
+\end{aligned}
+$$
 

### 2023-10-23 article/article.tex
d
d

@@
 \documentclass[
-  authoryear,
-  preprint,
-  1p]{elsarticle}
+  letterpaper,
+  DIV=11,
+  numbers=noendperiod]{scrartcl}
 
@@
 \setlength{\emergencystretch}{3em} % prevent overfull lines
-\setcounter{secnumdepth}{5}
+\setcounter{secnumdepth}{-\maxdimen} % remove section numbering
 % Make \paragraph and \subparagraph free-standing
@@
 \makeatother
+\newlength{\cslhangindent}
+\setlength{\cslhangindent}{1.5em}
+\newlength{\csllabelwidth}
+\setlength{\csllabelwidth}{3em}
+\newlength{\cslentryspacingunit} % times entry-spacing
+\setlength{\cslentryspacingunit}{\parskip}
+\newenvironment{CSLReferences}[2] % #1 hanging-ident, #2 entry spacing
+ {% don't indent paragraphs
+  \setlength{\parindent}{0pt}
+  % turn on hanging indent if param 1 is 1
+  \ifodd #1
+  \let\oldpar\par
+  \def\par{\hangindent=\cslhangindent\oldpar}
+  \fi
+  % set entry spacing
+  \setlength{\parskip}{#2\cslentryspacingunit}
+ }%
+ {}
+\usepackage{calc}
+\newcommand{\CSLBlock}[1]{#1\hfill\break}
+\newcommand{\CSLLeftMargin}[1]{\parbox[t]{\csllabelwidth}{#1}}
+\newcommand{\CSLRightInline}[1]{\parbox[t]{\linewidth - \csllabelwidth}{#1}\break}
+\newcommand{\CSLIndent}[1]{\hspace{\cslhangindent}#1}
 
+\KOMAoption{captions}{tableheading}
 \makeatletter
@@
 \makeatother
-\journal{Journal Name}
 \ifLuaTeX
@@
 \fi
-\usepackage[]{natbib}
-\bibliographystyle{elsarticle-harv}
 \IfFileExists{bookmark.sty}{\usepackage{bookmark}}{\usepackage{hyperref}}
@@
 
-\setlength{\parindent}{6pt}
-\begin{document}
-
-\begin{frontmatter}
 \title{Quantile Regressions via Method of Moments with multiple fixed
 effects}
-\author[1]{Fernando Rios-Avila%
-\corref{cor1}%
-}
- \ead{friosavi@levy.org} 
-\author[]{Leonardo Siles%
-%
-}
- \ead{leo@gmail.com} 
-\author[2]{Gustavo Canavire-Bacarreza%
-%
-}
- \ead{gcanavire@worldbank.org}
+\author{Fernando Rios-Avila \and Leonardo Siles \and Gustavo
+Canavire-Bacarreza}
+\date{2023-10-23}
 
-\affiliation[1]{organization={Levy Economics Institute of Bard
-College},,postcodesep={}}
-\affiliation[2]{organization={World Bank},,postcodesep={}}
-
-\cortext[cor1]{Corresponding author}
-
+\begin{document}
+\maketitle
 \begin{abstract}
@@
 multiple fixed effects. The method expands on the strategy proposed by
-\citet{mss2019}, allowing for multiple fixed effects, and providing
-various alternatives for the estimation of Standard errors. We provide
-Monte Carlo simulations to show the finite sample properties of the
-proposed method in the presence of two sets of fixed effects. Finally,
-we apply the proposed method to estimate \textbf{something interesting}
+Machado and Santos Silva (2019), allowing for multiple fixed effects,
+and providing various alternatives for the estimation of Standard
+errors. We provide Monte Carlo simulations to show the finite sample
+properties of the proposed method in the presence of two sets of fixed
+effects. Finally, we apply the proposed method to estimate
+\textbf{something interesting}
 \end{abstract}
-
-\begin{keyword}
-    Fixed effects \sep Linear heteroskedasticity \sep Location-scale
-model \sep 
-    Quantile regression
-\end{keyword}
-\end{frontmatter}
-    \ifdefined\Shaded\renewenvironment{Shaded}{\begin{tcolorbox}[boxrule=0pt, sharp corners, interior hidden, breakable, frame hidden, borderline west={3pt}{0pt}{shadecolor}, enhanced]}{\end{tcolorbox}}\fi
+\ifdefined\Shaded\renewenvironment{Shaded}{\begin{tcolorbox}[interior hidden, enhanced, sharp corners, borderline west={3pt}{0pt}{shadecolor}, frame hidden, breakable, boxrule=0pt]}{\end{tcolorbox}}\fi
 
@@
 
-More recently, \citet{mss2019} (MSS hereafter) proposed a methodology
-based on a conditional location-scale model similar to the one described
-in \citet{he1997}, for the estimation of quantile regressions models for
-panel data via a method of moments. This method allows individual fixed
-effects allowing to have heterogeneous effects on the entire conditional
-distribution of the outcome, rather constraining their effect to be a
-location shift only as in Canay (2011), Koenker(2004), and
-Lancaster(2000).
+More recently, Machado and Santos Silva (2019) (MSS hereafter) proposed
+a methodology based on a conditional location-scale model similar to the
+one described in He (1997) and (\textbf{zhao2020?}), for the estimation
+of quantile regressions models for panel data via a method of moments.
+This method allows individual fixed effects allowing to have
+heterogeneous effects on the entire conditional distribution of the
+outcome, rather constraining their effect to be a location shift only as
+in Canay (2011), Koenker (2004), and Lancaster (2000).
 
@@
 the data is based on a multiplicative heteroskedastic process that is
-linear in parameters (Cameron and Trivedi, 2005; \citet{mss2019};
-\citet{he1997}), the effect of a variable \(X\) on the \(q_th\) quantile
-can be derived as the combination of a location effect, and scale effect
-moderated by the quantile of an underlying i.i.d. error. For statistical
-inference, MSS derives the asymptotic distribution of the estimator,
-suggesting the use of bootstrap standard errors, as well.
+linear in parameters (Cameron and Trivedi (2005); Machado and Santos
+Silva (2019); He (1997); (\textbf{zhao2020?})), the effect of a variable
+\(X\) on the \(q_th\) quantile can be derived as the combination of a
+location effect, and scale effect moderated by the quantile of an
+underlying i.i.d. error. For statistical inference, MSS derives the
+asymptotic distribution of the estimator, suggesting the use of
+bootstrap standard errors, as well.
 
@@
 
-In this framework, our paper expands on \citet{mss2019}, following some
-of the suggestions by the authors regarding further research. First,
-making use of the properties of GMM estimators, we derive various
-alternatives for the estimation of standard errors based on the
-empirical Influence functions of the estimators. Second, we reconsider
-the application of Frisch--Waugh--Lovell (FWL) theorem (Lovell (1963)
-and Frisch and Waugh's (1933)) to extend the MSS estimator to allow for
-the inclusion of multiple fixed effects, for example, individual and
-year fixed effects.
+In this framework, our paper expands on Machado and Santos Silva (2019),
+following some of the suggestions by the authors regarding further
+research. First, making use of the properties of GMM estimators, we
+derive various alternatives for the estimation of standard errors based
+on the empirical Influence functions of the estimators. Second, we
+reconsider the application of Frisch--Waugh--Lovell (FWL) theorem
+(Frisch and Waugh (1933) and Lovell (1963)) to extend the MSS estimator
+to allow for the inclusion of multiple fixed effects, for example,
+individual and year fixed effects.
 
 The rest of the paper is restructured as follows. Section 2 presents the
-basic setup of the location-Scale model described in \citet{he1997},
-tying the relationship between the standard quantile regression model,
-and the location and scale model. It also revisits MSS methodology,
-proposing alternative estimators for the standard errors based on the
-properties of GMM estimators and the empirical influence functions. It
-also shows that FWL theorem can be used to control for multiple fixed
-effects. Section 3 presents the results of a small simulation study and
-Section 4 illustrates the application of the proposed methods with two
-empirical examples. Seccion 5 concludes.
+basic setup of the location-Scale model described in He (1997) and
+(\textbf{zhao2020?}), tying the relationship between the standard
+quantile regression model, and the location and scale model. It also
+revisits MSS methodology, proposing alternative estimators for the
+standard errors based on the properties of GMM estimators and the
+empirical influence functions. It also shows that FWL theorem can be
+used to control for multiple fixed effects. Section 3 presents the
+results of a small simulation study and Section 4 illustrates the
+application of the proposed methods with two empirical examples. Seccion
+5 concludes.
 
@@
 
-\hypertarget{quantile-regression-location-scale-model-he1997}{%
-\subsection{\texorpdfstring{Quantile Regression Location-Scale model
-\citet{he1997}}{Quantile Regression Location-Scale model @he1997}}\label{quantile-regression-location-scale-model-he1997}}
+\hypertarget{quantile-regression-location-scale-model}{%
+\subsection{Quantile Regression: Location-Scale
+model}\label{quantile-regression-location-scale-model}}
+
+Quantile regressions are used to identify relationships between the
+explanatory variables \(x\) and the conditional quantiles of the
+dependent variable \(Q(y|\tau,X)\). This relationship is commonly
+assumed to follow a linear functional form:
+
+\begin{equation}\protect\hypertarget{eq-eq1}{}{Q(Y|X,\tau) =X\beta(\tau)
+}\label{eq-eq1}\end{equation}
+
+This allows for nonlinearities in the effect of \(X\) on \(Y\) across
+all values of \(\tau\). This formulation can also be related to a random
+coefficient model, where all coefficients are assumed to be some
+nonlinear function of \(\tau\), where \(\tau\) follows a random uniform
+distribution.
+
+An alternative formulation of quantile regressions is the location-scale
+model. This approach assumes that the conditional quantile of \(Y\)
+given \(X\) and \(\tau\) can be expressed as a combination of two
+models: the location model, which describes the central tendency of the
+conditional distribution, and the scale model, which describes
+deviations from the central tendency:
+
+\begin{equation}\protect\hypertarget{eq-eq2}{}{Q(Y|X,\tau) =X\beta+X\gamma(\tau)
+}\label{eq-eq2}\end{equation}
+
+Here, the location parameters \(\beta\) are typically identified using a
+linear regression model (as in Machado and Santos Silva (2019)), or a
+median regression (as in Melly (2005)), and the scale parameters
+\(\gamma(\tau)\) can be estimated using standard approaches.
+
+Both the standard quantile regression (Equation~\ref{eq-eq1}) and the
+location-scale specification (Equation~\ref{eq-eq2}) can be estimated as
+the solution to a weighted minimization problem:
+
+\begin{equation}\protect\hypertarget{eq-eq3}{}{\hat{\beta}(\tau) = \underset{\beta}{\operatorname{argmin}}
+\left( \sum_{i\in y_i\geq x_i'\beta} \tau (y_i - x_i'\beta) - \sum_{i\in y_i<x_i'\beta} (1-\tau)(y_i - x_i'\beta) \right)
+}\label{eq-eq3}\end{equation}
+
+One characteristic of this estimator is that the \(\beta(\tau)\)
+coefficients are identified locally, and thus the estimated quantile
+coefficients will exhibit considerable variation when analyzed across
+\(\tau\). It is also implicit that if one requires an analysis of the
+entire distribution, it would be necessary to estimate the model for
+each quantile.\footnote{There are other estimators that provide smoother
+  estimates for the quantile regression coefficients using a kernel
+  local weighted approach (Kaplan and Sun 2017), as well as identifying
+  the full set of quantile coefficients simultaneously assuming some
+  parametric functional forms (Frumento and Bottai 2016).}
+
+One insightful extension to the location-scale parameterizations
+suggested by He (1997), Cameron and Trivedi (2005), and Machado and
+Santos Silva (2019) is to assume that the data-generating process (DGP)
+can be written as a linear model with a multiplicative heteroskedastic
+process that is linear in parameters.\footnote{Machado and Santos Silva
+  (2019) also discuss a model where heteroskedasticity can be an
+  arbitrary nonlinear function \(\sigma(x_i'\gamma)\), but develop the
+  estimator for the linear case, i.e., when \(\sigma()\) is the identity
+  function.}
+
+\begin{equation}\protect\hypertarget{eq-eq4}{}{y_i=x_i'\beta+\varepsilon_i \times x_i'\gamma(\tau)
+}\label{eq-eq4}\end{equation}
+
+Under the assumption that \(\varepsilon\) is an independent and
+identically distributed (iid) unobserved random variable that is
+independent of \(X\), the conditional quantile of \(Y\) given \(X\) and
+\(\tau\) can be written as:
+
+\begin{equation}\protect\hypertarget{eq-eq5}{}{Q(Y|X,\tau) =X\beta+X\gamma \times Q(\varepsilon|\tau)
+}\label{eq-eq5}\end{equation}
+
+In this setup, the traditional quantile coefficients are identified as
+the location model coefficients, plus the scale model coefficients
+moderated by the \(\tau_th\) unconditional quantile of the standardized
+error \(\varepsilon\).
+
+\begin{equation}\protect\hypertarget{eq-eq6}{}{\beta(\tau) = \beta + \gamma \times Q(\varepsilon|\tau)
+}\label{eq-eq6}\end{equation}
+
+While this specification imposes a strong assumption on the DGP, it has
+two advantages over the standard quantile regression model. First,
+because the location and scale model can be identified globally, with
+only a single parmater (\(Q(\varepsilon|\tau)\)) requiring local
+estimation, this estimation approach would be more efficient than the
+standard quantile regression model (Zhao (2000)). Second, under the
+assumption that \(X\gamma\) is strictly possitive, the model would
+produce quantile coefficients that do not cross.
+
+Following MSS, the quantile regression model defined by
+Equation~\ref{eq-eq5} can be estimated using a method of moments
+approach. And while its possible to identify all coefficients
+(\(\beta,\gamma, Q(\varepsilon|\tau)\)) simultaneously, we describe and
+use the implementation approach advocated by MSS which identifies each
+set of coefficients separately.
+
+\begin{enumerate}
+\def\labelenumi{\arabic{enumi}.}
+\item
+  The location model can be estimated using a standard linear regression
+  model, where the dependent variable is the outcome \(Y\), and the
+  independent variables are the explanatory variables \(X\) (including a
+  constant) with an error \(u\), which is by definition heteroskedastic.
+  In this case, the location model coefficients are identified under the
+  following condition:
+  \begin{equation}\protect\hypertarget{eq-eq7}{}{\begin{aligned}
+    y_i &=x_i'\beta+u_i \\
+    E[u 'X ] &=0
+    \end{aligned}
+  }\label{eq-eq7}\end{equation}
+\item
+  After the location model is estimated, the scale coefficients can be
+  identified by modeling heteroskedasticity as a linear function of
+  characteristics \(X\). For this we use the absolute value of the
+  errors from the location model \(u\) as dependent variable, which
+  would allow us to estimate the conditional standard deviation (rather
+  than conditional variance) of the errors. In this case, the
+  coefficients are identified under the following condition:
+\end{enumerate}
+
+\begin{equation}\protect\hypertarget{eq-eq8}{}{\begin{aligned}
+  |u_i| &=x_i'\gamma+v_i \\
+  E[ (|u|-X \gamma) X ] &=0
+  \end{aligned}
+}\label{eq-eq8}\end{equation}
+
+\begin{enumerate}
+\def\labelenumi{\arabic{enumi}.}
+\setcounter{enumi}{2}
+\tightlist
+\item
+  Finally, given the location and scale coefficients, the \(\tau_{th}\)
+  quantile of the error \(e\) can be estimated using the following
+  condition:
+\end{enumerate}
+
+\begin{equation}\protect\hypertarget{eq-eq9}{}{\begin{aligned}
+  E\left[  \mathbb{1}\left(x_i' (\beta + \gamma Q(\varepsilon|\tau)) \geq y_i \right) - \tau \right] &=0  \\
+  E\left[  \mathbb{1}\left(   Q(\varepsilon|\tau)\geq \frac{y_i-x_i'\beta}{x_i'\gamma} \right) - \tau \right] &=0  \\
+  \end{aligned}
+}\label{eq-eq9}\end{equation}
+
+Where one identifies the quantile of the error \(\varepsilon\) using
+standardized errors \(\frac{y_i-x_i'\beta}{x_i'\gamma}\), or by finding
+the values that identify the overall quantile coefficients
+\(\beta(\tau)=\beta + \gamma Q(\varepsilon|\tau)\). Afterwords, the
+conditional quantile coefficients is simply defined as the combination
+of the location and scale coefficients.
 
@@
 
+As discussed in the previous section, the estimation of quantile
+regression coefficients using the location-scale model with
+heteroskedstic linear errors can be estimated using a the following set
+of moments, which fits in the Generalized Method of Moments framework:
+
+\begin{equation}\protect\hypertarget{eq-eq10}{}{\begin{aligned}
+  E[u_i x_i ] &= E[h_{1,i}]=0 \\
+  E[ (|u_i|-x_i \gamma) x_i ] &=E[h_{2,i}]=0 \\
+  E\left[  \mathbb{1}\left(   Q(\varepsilon|\tau)\geq \frac{y_i-x_i'\beta}{x_i'\gamma} \right) - \tau \right] 
+  &=E[h_{3,i}]=0 
+  \end{aligned}
+}\label{eq-eq10}\end{equation}
+
+Under the conditions described in Newey and McFadden (1994) (see section
+7), Cameron and Trivedi (2005) (see chapter 6.3.9) or as shown in
+Machado and Santos Silva (2019), the location, scale and residual
+quantile coefficients are asymptotically normal.\footnote{Zhao (2000)
+  also shows that the quantile coefficients for the location-scale model
+  also follows a normal distribution, but uses the assumption that the
+  location model is derived using a least absolute deviation approach
+  (median regression).}
+
+Call \(\theta=[ \beta' \ \ \gamma' \ \ Q(\varepsilon|\tau)' ]'\) the set
+of coefficients that are identified in Equation~\ref{eq-eq10}, a just
+identified model. And the functions \(G_{k,l}\) and \(S_{k.l}\) equal
+to:
+
+\[\begin{aligned}
+G_{k,l} &= N^{-1} \sum_{i=1}^N \frac{\partial h_{k,i}}{\partial \theta_l} \Big|_{\hat\theta} \ \forall k,l \in [1,2,3] \\
+S_{k,l} &= N^{-1} \sum_{i=1}^N h_{k,i} h_{l,i}' \Big|_{\hat\theta} \ \forall k,l \in [1,2,3]
+\end{aligned}
+\]
+
+where \(\theta_1 = \beta\), \(\theta_2 = \gamma\) and
+\(\theta_3 = Q(\varepsilon,\tau)\).
+
+Then \[
+\sqrt{N}(\hat\theta - \theta) \xrightarrow{d} N(0, G^{-1} S G^{-1})
+\]
+
+with, \(G\) and \(S\) defined as:
+
+\[\begin{aligned}
+G &= \begin{bmatrix}
+G_{1,1} &       0 & 0       \\
+G_{2,1} & G_{2,2} & 0       \\
+G_{3,1} & G_{3,2} & G_{3,3} 
+\end{bmatrix}  \text{ and }
+S &= \begin{bmatrix}
+S_{1,1} & S_{1,2} & S_{1,3}    \\
+S_{2,1} & S_{2,2} & S_{2,3}  \\
+S_{3,1} & S_{3,2} & S_{3,3} 
+\end{bmatrix}
+\end{aligned}
+\]
+
+Because
+
+\[
+Var(\hat\theta) = \frac{1}{N} \left(
+    \frac{1}{N} 
+    \sum_{i=1}^N  \lambda_i(\theta) \lambda_i(\theta)'  
+\right) = \frac{1}{N^2} 
+\lambda(\theta)'\lambda(\theta)
+\]
+
+\[
+\lambda_i(\theta) = \bar G(\theta)^{-1} h_i (x_i,\theta)
+\]
+
+Finally, the variance covariance of \(\hat \beta(\tau)\) will be given
+by:
+
+\[Var(\hat\beta(\tau)) = \Xi Var(\hat\theta) \Xi'\]
+
+where \(\Xi\) is a \(k \times (2k+1)\) matrix defined as:
+
+\[
+\begin{aligned}
+    \Xi &= I(k), \hat q(\tau) I(k), \hat \gamma \\
+    \Xi &= \left[ \begin{array}{cccc|cccc|}
+           1 & 0 & \dots & 0 &\hat q_(\tau) & 0 & ... & 0  & \hat\gamma_0 \\
+           0 & 1 & \dots & 0 &0& \hat q_(\tau) & ... & 0 & \hat\gamma_1 \\
+          \vdots & \vdots & \dots & 0 &...&...& ... & 0             & ...\\
+           0 & 0 & \dots & 1 &0 & 0 & ... & \hat q(\tau)   & \hat\gamma_k
+        \end{array} \right]         
+\end{aligned}
+\]
+
 \hypertarget{multiple-fixed-effects-expanding-on-mss2019}{%
-\subsection{\texorpdfstring{Multiple Fixed Effects: Expanding on
-\citet{mss2019}}{Multiple Fixed Effects: Expanding on @mss2019}}\label{multiple-fixed-effects-expanding-on-mss2019}}
+\subsection{Multiple Fixed Effects: Expanding on Machado and Santos
+Silva (2019)}\label{multiple-fixed-effects-expanding-on-mss2019}}
 
@@
 
+\hypertarget{appendix}{%
+\section{Appendix}\label{appendix}}
+
 \hypertarget{references}{%
@@
 
-\renewcommand\refname{Appendix}
-  \bibliography{bibliography.bib}
+\hypertarget{refs}{}
+\begin{CSLReferences}{1}{0}
+\leavevmode\vadjust pre{\hypertarget{ref-cameron2005}{}}%
+Cameron, Adrian Colin, and Pravin K. Trivedi. 2005.
+\emph{Microeconometrics: Methods and Applications}. Cambridge ; New
+York: Cambridge University Press.
+
+\leavevmode\vadjust pre{\hypertarget{ref-canay2011}{}}%
+Canay, Ivan A. 2011. {``A Simple Approach to Quantile Regression for
+Panel Data.''} \emph{The Econometrics Journal} 14 (3): 368--86.
+https://doi.org/\url{https://doi.org/10.1111/j.1368-423X.2011.00349.x}.
+
+\leavevmode\vadjust pre{\hypertarget{ref-frishwaugh1933}{}}%
+Frisch, Ragnar, and Frederick V. Waugh. 1933. {``Partial Time
+Regressions as Compared with Individual Trends.''} \emph{Econometrica} 1
+(4): 387--401. \url{http://www.jstor.org/stable/1907330}.
+
+\leavevmode\vadjust pre{\hypertarget{ref-frumentobotai2016}{}}%
+Frumento, Paolo, and Matteo Bottai. 2016. {``Parametric Modeling of
+Quantile Regression Coefficient Functions.''} \emph{Biometrics} 72 (1):
+74--84. https://doi.org/\url{https://doi.org/10.1111/biom.12410}.
+
+\leavevmode\vadjust pre{\hypertarget{ref-he1997}{}}%
+He, Xuming. 1997. {``Quantile Curves Without Crossing.''} \emph{The
+American Statistician} 51 (2): 186--92.
+\url{https://doi.org/10.1080/00031305.1997.10473959}.
+
+\leavevmode\vadjust pre{\hypertarget{ref-kaplan2017}{}}%
+Kaplan, David M., and Yixiao Sun. 2017. {``Smoothed Estimating Equations
+for Instrumental Variables Quantile Regression.''} \emph{Econometric
+Theory} 33 (1): 105--57.
+\url{https://doi.org/10.1017/S0266466615000407}.
+
+\leavevmode\vadjust pre{\hypertarget{ref-koenker2004}{}}%
+Koenker, Roger. 2004. {``Quantile Regression for Longitudinal Data.''}
+\emph{Journal of Multivariate Analysis} 91 (1): 74--89.
+https://doi.org/\url{https://doi.org/10.1016/j.jmva.2004.05.006}.
+
+\leavevmode\vadjust pre{\hypertarget{ref-koenkerbasset1978}{}}%
+Koenker, Roger, and Gilbert Bassett. 1978. {``Regression Quantiles.''}
+\emph{Econometrica} 46 (1): 33--50.
+\url{http://www.jstor.org/stable/1913643}.
+
+\leavevmode\vadjust pre{\hypertarget{ref-lancaster2000}{}}%
+Lancaster, Tony. 2000. {``The Incidental Parameter Problem Since
+1948.''} \emph{Journal of Econometrics} 95 (2): 391--413.
+https://doi.org/\url{https://doi.org/10.1016/S0304-4076(99)00044-5}.
+
+\leavevmode\vadjust pre{\hypertarget{ref-lovell1963}{}}%
+Lovell, Michael C. 1963. {``Seasonal Adjustment of Economic Time Series
+and Multiple Regression Analysis.''} \emph{Journal of the American
+Statistical Association} 58 (304): 993--1010.
+\url{https://doi.org/10.1080/01621459.1963.10480682}.
+
+\leavevmode\vadjust pre{\hypertarget{ref-mss2019}{}}%
+Machado, José A. F., and J. M. C. Santos Silva. 2019. {``Quantiles via
+Moments.''} \emph{Journal of Econometrics} 213 (1): 145--73.
+\url{https://doi.org/10.1016/j.jeconom.2019.04.009}.
+
+\leavevmode\vadjust pre{\hypertarget{ref-melly2005}{}}%
+Melly, Blaise. 2005. {``Decomposition of Differences in Distribution
+Using Quantile Regression.''} \emph{Labour Economics} 12 (4): 577--90.
+https://doi.org/\url{https://doi.org/10.1016/j.labeco.2005.05.006}.
+
+\leavevmode\vadjust pre{\hypertarget{ref-newey_chapter_1994}{}}%
+Newey, Whitney K., and Daniel McFadden. 1994. {``Chapter 36 {Large}
+Sample Estimation and Hypothesis Testing.''} In \emph{Handbook of
+{Econometrics}}, 4:2111--2245. Elsevier.
+\url{https://doi.org/10.1016/S1573-4412(05)80005-4}.
+
+\leavevmode\vadjust pre{\hypertarget{ref-neymanscott1948}{}}%
+Neyman, J., and Elizabeth L. Scott. 1948. {``Consistent Estimates Based
+on Partially Consistent Observations.''} \emph{Econometrica} 16 (1):
+1--32. \url{http://www.jstor.org/stable/1914288}.
+
+\leavevmode\vadjust pre{\hypertarget{ref-zhao2000}{}}%
+Zhao, Quanshui. 2000. {``Restricted {Regression} {Quantiles}.''}
+\emph{Journal of Multivariate Analysis} 72 (1): 78--99.
+https://doi.org/\url{https://doi.org/10.1006/jmva.1999.1849}.
+
+\end{CSLReferences}
 

### 2023-10-24 article/article.qmd
s
s

@@
 
-More recently, @mss2019 (MSS hereafter) proposed a methodology based on a conditional location-scale model similar to the one described in @he1997 and @zhao2020, for the estimation of quantile regressions models for panel data via a method of moments.
+More recently, @mss2019 (MSS hereafter) proposed a methodology based on a conditional location-scale model similar to the one described in @he1997 and @zhao2000, for the estimation of quantile regressions models for panel data via a method of moments.
 This method allows individual fixed effects allowing to have heterogeneous effects on the entire conditional distribution of the outcome, rather constraining their effect to be a location shift only as in @canay2011, @koenker2004, and @lancaster2000.
 
-In principle, under the assumption that data generating process behind the data is based on a multiplicative heteroskedastic process that is linear in parameters (@cameron2005; @mss2019; @he1997; @zhao2020), the effect of a variable $X$ on the $q_th$ quantile can be derived as the combination of a location effect, and scale effect moderated by the quantile of an underlying i.i.d.
+In principle, under the assumption that data generating process behind the data is based on a multiplicative heteroskedastic process that is linear in parameters (@cameron2005, @mss2019, @he1997 and @zhao2000 ), the effect of a variable $X$ on the $q_th$ quantile can be derived as the combination of a location effect, and scale effect moderated by the quantile of an underlying i.i.d.
 error.
@@
 The rest of the paper is restructured as follows.
-Section 2 presents the basic setup of the location-Scale model described in @he1997 and @zhao2020, tying the relationship between the standard quantile regression model, and the location and scale model.
+Section 2 presents the basic setup of the location-Scale model described in @he1997 and @zhao2000, tying the relationship between the standard quantile regression model, and the location and scale model.
 It also revisits MSS methodology, proposing alternative estimators for the standard errors based on the properties of GMM estimators and the empirical influence functions.
@@
 
-Call $\theta=[ \beta' \ \ \gamma'  \ \ Q(\varepsilon|\tau)' ]'$ the set of coefficients that are identified in @eq-eq10, a just identified model.  And the functions $G_{k,l}$ and $S_{k.l}$ equal to:
-
-$$\begin{aligned}
-G_{k,l} &= N^{-1} \sum_{i=1}^N \frac{\partial h_{k,i}}{\partial \theta_l} \Big|_{\hat\theta} \ \forall k,l \in [1,2,3] \\
-S_{k,l} &= N^{-1} \sum_{i=1}^N h_{k,i} h_{l,i}' \Big|_{\hat\theta} \ \forall k,l \in [1,2,3]
-\end{aligned}
+Call $\theta=[ \beta' \ \ \gamma'  \ \ Q(\varepsilon|\tau)' ]'$ the set of coefficients that are identified in @eq-eq10, a just identified model.
+And the function $h_i$ is a vector function that stacks all the moments at the individual level described in @eq-eq10.
+Then $\hat\theta$ follows a normal distribution with mean $\theta$ and variance-covariance matrix $V(\theta)$ that is estimated as:
+$$
+\hat{V}(\hat\theta)=\frac{1}{N} 
+\bar G(\hat\theta)^{-1} 
+\left( \frac{1}{N} \sum_{i=1}^N h_i h_i'  \Big|_{\theta=\hat\theta} \right) 
+\bar G(\hat\theta)^{-1} 
 $$
 
-where $\theta_1 = \beta$, $\theta_2 = \gamma$ and $\theta_3 = Q(\varepsilon,\tau)$.
+where the inner product is the moment covariance matrix, and $\bar{G}(\theta)$ is the Jacobian matrix of the moment equations (@eq-eq10) evaluated at $\hat\theta$.
 
-Then 
+$$\bar{G}(\theta) =-\frac{1}{N} \sum_{i=1} \frac{\partial h_i}{\partial \theta'} \Big|_{\theta=\hat\theta}$$
+
+This is equivalent to the Eicker-White Heteroskedastic-Consistent estimator for least-squares estimators.
+
+In this framework, the quantile regression coefficients, a combination of the location-scale-quantile estimates, will follow a normal distribution with mean $\beta(\tau) = \beta+Q(\varepsilon,\tau)\gamma$ and variance-covariance matrix equal to:
+
+$$\hat{V}(\beta(\tau)) = \Xi \hat{V}(\hat\theta) \Xi'
 $$
-\sqrt{N}(\hat\theta - \theta) \xrightarrow{d} N(0, G^{-1} S G^{-1})
-$$
-
-with, $G$ and $S$ defined as:
-
-$$\begin{aligned}
-G &= \begin{bmatrix}
-G_{1,1} &       0 & 0       \\
-G_{2,1} & G_{2,2} & 0       \\
-G_{3,1} & G_{3,2} & G_{3,3} 
-\end{bmatrix}  \text{ and }
-S &= \begin{bmatrix}
-S_{1,1} & S_{1,2} & S_{1,3}    \\
-S_{2,1} & S_{2,2} & S_{2,3}  \\
-S_{3,1} & S_{3,2} & S_{3,3} 
-\end{bmatrix}
-\end{aligned}
-$$
-
-Because
-
-$$
-Var(\hat\theta) = \frac{1}{N} \left(
-    \frac{1}{N} 
-    \sum_{i=1}^N  \lambda_i(\theta) \lambda_i(\theta)'  
-\right) = \frac{1}{N^2} 
-\lambda(\theta)'\lambda(\theta)
-$$
-
-$$
-\lambda_i(\theta) = \bar G(\theta)^{-1} h_i (x_i,\theta)
-$$
-
-Finally, the variance covariance of $\hat \beta(\tau)$ will be given by:
-
-$$Var(\hat\beta(\tau)) = \Xi Var(\hat\theta) \Xi'$$
 
@@
 
+$$\Xi = [ I(k), \hat Q(\varepsilon|\tau) \cdot I(k), \hat \gamma ]
 $$
-\begin{aligned}
-    \Xi &= I(k), \hat q(\tau) I(k), \hat \gamma \\
-    \Xi &= \left[ \begin{array}{cccc|cccc|}
-           1 & 0 & \dots & 0 &\hat q_(\tau) & 0 & ... & 0  & \hat\gamma_0 \\
-           0 & 1 & \dots & 0 &0& \hat q_(\tau) & ... & 0 & \hat\gamma_1 \\
-          \vdots & \vdots & \dots & 0 &...&...& ... & 0             & ...\\
-           0 & 0 & \dots & 1 &0 & 0 & ... & \hat q(\tau)   & \hat\gamma_k
-        \end{array} \right]         
-\end{aligned}
-$$
+
+with $I(k)$ being an identity matrix of dimension $k$ (number of explanatory variables in $X$ including the constant).
+
+The different types of Standard errors estimation, thus, depend on the assumptions imposed for the estimation of $V(\theta)$.
 

### 2023-10-24 article/article.tex
s
s

@@
 Canavire-Bacarreza}
-\date{2023-10-23}
+\date{2023-10-24}
 
@@
 \end{abstract}
-\ifdefined\Shaded\renewenvironment{Shaded}{\begin{tcolorbox}[interior hidden, enhanced, sharp corners, borderline west={3pt}{0pt}{shadecolor}, frame hidden, breakable, boxrule=0pt]}{\end{tcolorbox}}\fi
+\ifdefined\Shaded\renewenvironment{Shaded}{\begin{tcolorbox}[frame hidden, enhanced, borderline west={3pt}{0pt}{shadecolor}, interior hidden, breakable, boxrule=0pt, sharp corners]}{\end{tcolorbox}}\fi
 
@@
 a methodology based on a conditional location-scale model similar to the
-one described in He (1997) and (\textbf{zhao2020?}), for the estimation
-of quantile regressions models for panel data via a method of moments.
-This method allows individual fixed effects allowing to have
-heterogeneous effects on the entire conditional distribution of the
-outcome, rather constraining their effect to be a location shift only as
-in Canay (2011), Koenker (2004), and Lancaster (2000).
+one described in He (1997) and Zhao (2000), for the estimation of
+quantile regressions models for panel data via a method of moments. This
+method allows individual fixed effects allowing to have heterogeneous
+effects on the entire conditional distribution of the outcome, rather
+constraining their effect to be a location shift only as in Canay
+(2011), Koenker (2004), and Lancaster (2000).
 
@@
 the data is based on a multiplicative heteroskedastic process that is
-linear in parameters (Cameron and Trivedi (2005); Machado and Santos
-Silva (2019); He (1997); (\textbf{zhao2020?})), the effect of a variable
+linear in parameters (Cameron and Trivedi (2005), Machado and Santos
+Silva (2019), He (1997) and Zhao (2000) ), the effect of a variable
 \(X\) on the \(q_th\) quantile can be derived as the combination of a
@@
 The rest of the paper is restructured as follows. Section 2 presents the
-basic setup of the location-Scale model described in He (1997) and
-(\textbf{zhao2020?}), tying the relationship between the standard
-quantile regression model, and the location and scale model. It also
-revisits MSS methodology, proposing alternative estimators for the
-standard errors based on the properties of GMM estimators and the
-empirical influence functions. It also shows that FWL theorem can be
-used to control for multiple fixed effects. Section 3 presents the
-results of a small simulation study and Section 4 illustrates the
-application of the proposed methods with two empirical examples. Seccion
-5 concludes.
+basic setup of the location-Scale model described in He (1997) and Zhao
+(2000), tying the relationship between the standard quantile regression
+model, and the location and scale model. It also revisits MSS
+methodology, proposing alternative estimators for the standard errors
+based on the properties of GMM estimators and the empirical influence
+functions. It also shows that FWL theorem can be used to control for
+multiple fixed effects. Section 3 presents the results of a small
+simulation study and Section 4 illustrates the application of the
+proposed methods with two empirical examples. Seccion 5 concludes.
 
@@
 of coefficients that are identified in Equation~\ref{eq-eq10}, a just
-identified model. And the functions \(G_{k,l}\) and \(S_{k.l}\) equal
-to:
-
-\[\begin{aligned}
-G_{k,l} &= N^{-1} \sum_{i=1}^N \frac{\partial h_{k,i}}{\partial \theta_l} \Big|_{\hat\theta} \ \forall k,l \in [1,2,3] \\
-S_{k,l} &= N^{-1} \sum_{i=1}^N h_{k,i} h_{l,i}' \Big|_{\hat\theta} \ \forall k,l \in [1,2,3]
-\end{aligned}
+identified model. And the function \(h_i\) is a vector function that
+stacks all the moments at the individual level described in
+Equation~\ref{eq-eq10}. Then \(\hat\theta\) follows a normal
+distribution with mean \(\theta\) and variance-covariance matrix
+\(V(\theta)\) that is estimated as: \[
+\hat{V}(\hat\theta)=\frac{1}{N} 
+\bar G(\hat\theta)^{-1} 
+\left( \frac{1}{N} \sum_{i=1}^N h_i h_i'  \Big|_{\theta=\hat\theta} \right) 
+\bar G(\hat\theta)^{-1} 
 \]
 
-where \(\theta_1 = \beta\), \(\theta_2 = \gamma\) and
-\(\theta_3 = Q(\varepsilon,\tau)\).
+where the inner product is the moment covariance matrix, and
+\(\bar{G}(\theta)\) is the Jacobian matrix of the moment equations
+(Equation~\ref{eq-eq10}) evaluated at \(\hat\theta\).
 
-Then \[
-\sqrt{N}(\hat\theta - \theta) \xrightarrow{d} N(0, G^{-1} S G^{-1})
+\[\bar{G}(\theta) =-\frac{1}{N} \sum_{i=1} \frac{\partial h_i}{\partial \theta'} \Big|_{\theta=\hat\theta}\]
+
+This is equivalent to the Eicker-White Heteroskedastic-Consistent
+estimator for least-squares estimators.
+
+In this framework, the quantile regression coefficients, a combination
+of the location-scale-quantile estimates, will follow a normal
+distribution with mean \(\beta(\tau) = \beta+Q(\varepsilon,\tau)\gamma\)
+and variance-covariance matrix equal to:
+
+\[\hat{V}(\beta(\tau)) = \Xi \hat{V}(\hat\theta) \Xi'
 \]
-
-with, \(G\) and \(S\) defined as:
-
-\[\begin{aligned}
-G &= \begin{bmatrix}
-G_{1,1} &       0 & 0       \\
-G_{2,1} & G_{2,2} & 0       \\
-G_{3,1} & G_{3,2} & G_{3,3} 
-\end{bmatrix}  \text{ and }
-S &= \begin{bmatrix}
-S_{1,1} & S_{1,2} & S_{1,3}    \\
-S_{2,1} & S_{2,2} & S_{2,3}  \\
-S_{3,1} & S_{3,2} & S_{3,3} 
-\end{bmatrix}
-\end{aligned}
-\]
-
-Because
-
-\[
-Var(\hat\theta) = \frac{1}{N} \left(
-    \frac{1}{N} 
-    \sum_{i=1}^N  \lambda_i(\theta) \lambda_i(\theta)'  
-\right) = \frac{1}{N^2} 
-\lambda(\theta)'\lambda(\theta)
-\]
-
-\[
-\lambda_i(\theta) = \bar G(\theta)^{-1} h_i (x_i,\theta)
-\]
-
-Finally, the variance covariance of \(\hat \beta(\tau)\) will be given
-by:
-
-\[Var(\hat\beta(\tau)) = \Xi Var(\hat\theta) \Xi'\]
 
@@
 
-\[
-\begin{aligned}
-    \Xi &= I(k), \hat q(\tau) I(k), \hat \gamma \\
-    \Xi &= \left[ \begin{array}{cccc|cccc|}
-           1 & 0 & \dots & 0 &\hat q_(\tau) & 0 & ... & 0  & \hat\gamma_0 \\
-           0 & 1 & \dots & 0 &0& \hat q_(\tau) & ... & 0 & \hat\gamma_1 \\
-          \vdots & \vdots & \dots & 0 &...&...& ... & 0             & ...\\
-           0 & 0 & \dots & 1 &0 & 0 & ... & \hat q(\tau)   & \hat\gamma_k
-        \end{array} \right]         
-\end{aligned}
+\[\Xi = [ I(k), \hat Q(\varepsilon|\tau) \cdot I(k), \hat \gamma ]
 \]
+
+with \(I(k)\) being an identity matrix of dimension \(k\) (number of
+explanatory variables in \(X\) including the constant).
+
+The different types of Standard errors estimation, thus, depend on the
+assumptions imposed for the estimation of \(V(\theta)\).
 

### 2023-10-26 article/article.qmd
s
s

@@
 
-## Quantile Regression: Location-Scale model
+## Quantile Regression: Location-Scale model {#sec-betas}
 
@@
 
-## Standard Errors: GLS, Robust, Clustered
+## Standard Errors: GLS, Robust, Clustered {#sec-se}
 
@@
 
+Using the setup described in the previous section, @mss2019 proposes an extension to the model proposed by @he1997 that would allow for the estimation of quantile regression models with panel data, allowing for the inclusion of individual fixed effects.
+However, as the authors suggest, the methodology can be generalized to allow for the inclusion of multiple fixed effects.
+This type of analysis may be useful when considering data such as employer-employee linked data [@abowed2006], or teacher-student linked data [@harrissass2011].
+Or, in the most common case, allowing to control for both individual and time fixed effects.
+
+Reconsider the original model, and assume there are sets of unobserved heterogeneity that are assumed to be constant across observations, if they belong to common groups.
+In panel data, the groups would be the individual fixed effects and the time fixed effects.
+Without loss of generality, we can assume that the data generating process is as follows:
+
+$$\begin{aligned}
+  y_{i} &= x_{i}' \beta + \delta_{g1} + \delta_{g2} + \nu_i \\
+  \nu_i &= \varepsilon_i \times (x_{i}' \gamma + \zeta_{g1} + \zeta_{g2})   
+  \end{aligned}
+$$
+
+where we assume $x_{i}$ vary across groups $g_1$ and $g_2$, thus are not collinear, and that $\delta's$ and $\zeta's$ are the location and scale effects associated with groups fixed effects.[^4]
+
+[^4]: We could just as well consider multiple sets of fixed effects
+
+If the dimension of groups $g_k$ is low, this model could be estimated using a dummy inclussion approach following @sec-betas, and standard errors obtained as discussed in @sec-se.
+However, if the dimensionality of $g_k$ is high, the dummy inclusion approach may not be feasible.
+Instead, a more feasible approach is to apply the Frisch-Waugh-Lovell (FWL) theorem, and partial out the impact of the group fixed effects on the control variables $x_{i}$, the outcome of interest $y_{i}$, with a similar approach for the identification of $\sigma(x)$.
+In the case of unbalanced setups, with multiple groups, the estimation involves iterative processes for which various approaches have been suggested and implemented (see @correia_feasible_nodate, @gaure2013, @rios2015, among others).
+
+When applying the partialing out approach, some modifications to the approach described in @sec-betas are needed.
+
+1. For all dependent and independent variables in the model ($w=y,x$), we partial out the group fixed effects, and obtain the centered-residualized variables:
+
+$$\begin{aligned}
+w_{i} &= \delta_{g1}^w + \delta_{g2}^w + u_{i}^w \\
+w_{i}^{rc} &= E(w_{i}) + \hat{u}_{i}^w
+\end{aligned}
+$$
+
+2. We estimate the location model using the centered-residualized variables:
+
+$$y_{i}^{rc} = x_{i}^{rc'} \beta + nu_{i}
+$$
+
+3. Since $|\hat \nu_i|$ is the dependent variable for the scale model, we apply the partialling out and recentering to this expression ($|\hat \nu_i|^{rc}$), and use that to estimate the model:
+
+$$|\hat\nu_{i}|^{rc} = x_{i}^{rc'} \gamma + e_{i}$$
+
+4. Finally the standardized residuals $\varepsilon_i$ can be obtained as follows
+
+$$\hat{\varepsilon}_{i} = \frac{\nu_{i}}{|\hat\nu_{i}|- \hat e_{i}}$$
+
+where $|\hat\nu_{i}|- \hat e_{i}$ is the prediction for the conditional standard deviation $\sigma(x_i)=x_{i}' \gamma + \zeta_{g1} + \zeta_{g2}$
+
+The $\tau_{th}$ quantile of the error $\varepsilon$ can be estimated as usual, and the variance-covariance matrices obtained in the same way as before (see @sec-se), but using  $x_{i}^{rc}$ instead of $x_{i}$ when estimating the influence functions for all estimated coefficients.
+
 # Monte Carlo Simulations
@@
 
+The estimation of quantile regression via moments assumes that the DGP is linear in parameters, with an heteroskedastic error term that is also linear function of parameters:
+
+$$\begin{aligned}
+y = x\beta + \nu \\
+\nu = \varepsilon \times x\gamma
+\end{aligned}
+$$
+
+where $\varepsilon$ is an unobserved i.i.d. random variable that is independent of $x$, and such that $x\gamma$ is larger than zero for any $x$.
+
+In this case, the $\tau_{th}$ conditional quantile model can be written as:
+
+$$q(y|\tau,X) = x(\beta + q(e|\tau) \times \gamma)$$
+
+This model is identified under the following conditions:
+
+$$\begin{aligned}
+  E[(y_i-x_i'\beta)x_i ]  &= E[h_{1,i}]=0 \\
+  E[ (|y_i-x_i'\beta|-x_i' \gamma) x_i ] &=E[h_{2,i}]=0 \\
+  E\left[  \mathbb{1}\left( q(\varepsilon|\tau) x_i'\gamma +x_i'\beta\geq  y_i  \right) - \tau \right] 
+   &=E[h_{3,i}]=0 
+\end{aligned}
+$$
+
+In this model, to estimate the variance-covariance matrix the set of coefficients $\theta'=[\beta' \ \gamma' \ q(\varepsilon|\tau)']$, we need to obtain the influence functions of all coefficients, which are defined as:
+
+$$\lambda_i = \bar G(\theta)^{-1}
+\begin{bmatrix}
+h_{1,i} \\
+h_{2,i} \\
+h_{3,i}
+\end{bmatrix}
+$$
+
+where the Jacobian matrix $\bar G(\theta)$ is defined as:
+
+$$\bar G(\theta) = \begin{bmatrix}
+\bar G_{11} & G_{12} & G_{13} \\
+\bar G_{21} & \bar G_{22} & G_{23} \\
+\bar G_{31} & \bar G_{32} & \bar G_{13} \\
+\end{bmatrix}
+$$
+
+with
+
+$$\bar G_{j,k} = - \frac 1 N \sum_{i=1}^N \frac{\partial h_{j,i}}{\partial \theta_k'} \ \forall j,k \in 1,2,3
+$$
+
+### First Moment Condition: Location Model
+
+$$h_{1,i}=x_i(y_i-x_i'\beta)$$
+
+$$\begin{aligned}
+\bar G_{1,1} &=- \frac{1}{N} \sum_{i=1}^N \frac{\partial h_{1,i}}{\partial \beta'} \\
+             &=- \frac{1}{N} \sum_{i=1}^N (-x_i x_i') \\
+             &= N^{-1} X'X
+\end{aligned}
+$$
+
+$$
+\bar G_{1,2} = \bar G_{1,3} = 0
+$$
+
+### Second Moment Condition: Scale model
+
+$$h_{2,i}=x_i(|y_i-x_i'\beta|-x_i'\gamma)$$
+
+$$\begin{aligned}
+\bar G_{2,1} &= -\frac{1}{N} \sum \frac{\partial h_{2,i}}{\partial \beta'} \\
+             &=  \frac{1}{N} \sum x_i x_i' \frac{y_i-x_i'\beta}{|y_i-x_i'\beta|} \\
+\frac{y_i-x_i'\beta}{|y_i-x_i'\beta|} &= sign(y_i-x_i'\beta) \\            
+\end{aligned}
+$$
+
+Under the assumption $\varepsilon_i \times x\gamma$, or in this case $y_i-x_i'\beta$, is uncorrelated with $x$, we can simplify the expression as:
+
+$$\begin{aligned}
+\bar G_{2,1} &= N^{-1} \left(N^{-1}\sum sign(y_i-x_i'\beta)\right) \sum x_i x_i' \\
+&= N^{-1} E[sign(y_i-x_i'\beta)] X'X
+\end{aligned}
+$$
+
+$$\begin{aligned}
+\bar G_{2,2} &= -\frac{1}{N} \sum \frac{\partial h_{2,i}}{\partial \gamma'} \\
+             &=  \frac{1}{N} \sum x_i x_i' 
+             &= N^{-1} X'X
+\end{aligned}
+$$
+
+$$\bar G_{2,3}=0$$
+
+### Third Moment Condition: Quantile of Standardized Residual
+
+$$h_{3,i} = \mathbb{1}\left( q(\varepsilon|\tau) x_i'\gamma +x_i'\beta - y_i \geq 0 \right) - \tau$$
+
+Because the indicator function $\mathbb{1}()$ is not differentiable, we impose some smoothing assumptions:
+
+First:
+
+$$\begin{aligned}
+E[h_{3,i}] -\tau &= E[\mathbb{1}\left( q(\varepsilon|\tau) x_i'\gamma +x_i'\beta - y_i \geq 0 \right)] - \tau \\
+                &= E\left[E[\mathbb{1}\left( q(\varepsilon|\tau) x_i'\gamma +x_i'\beta - y_i \geq 0 \right)|x]\right] - \tau
+\end{aligned}
+$$
+
+Because we are aiming to identify the conditional quantile function of $y$, and under the assumption of the DGP it follows that:
+
+$$\begin{aligned}
+q(y|\tau) &= q(\varepsilon|\tau) x_i'\gamma +x_i'\beta \\
+E[\mathbb{1}\left( q(y|\tau) - y_i \geq 0 \right)|x] &= \tau 
+\end{aligned}
+$$
+
+and asymptotically, we expect that
+
+$$E[\mathbb{1}\left( q(y|\tau) - y_i \geq 0 \right)|x]=
+E[\mathbb{1}\left( q(y|\tau) \geq  y_i \right)|x] = \tau = F_{y |X} \big( q(y|\tau) \big) 
+$$
+
+but also that
+
+$$F_{y|X} \big( q(y|\tau)) = \tau = F_{\varepsilon}( q(\varepsilon|\tau) )
+$$
+
+where $F_{y|X}$ is the conditional cumulative distribution function (CDF) of $y$, and $F_{\varepsilon}$ is the unconditonal CDF of the iid error $\varepsilon$.
+
+Second, based on non-parametric estimation of the CDF, we can approximate $F_{y|X} \big( q(y|\tau))$ as:
+
+$$F_{y|X} \big( q(y|\tau) ) \approx \frac{\sum_{i=1}^N F_{y|X) ( q(y|\tau) - y_i)
+
 # References {-}

### 2023-10-26 article/article.tex
s
s

@@
 Canavire-Bacarreza}
-\date{2023-10-24}
+\date{2023-10-26}
 
@@
 \end{abstract}
-\ifdefined\Shaded\renewenvironment{Shaded}{\begin{tcolorbox}[frame hidden, enhanced, borderline west={3pt}{0pt}{shadecolor}, interior hidden, breakable, boxrule=0pt, sharp corners]}{\end{tcolorbox}}\fi
+\ifdefined\Shaded\renewenvironment{Shaded}{\begin{tcolorbox}[sharp corners, enhanced, boxrule=0pt, borderline west={3pt}{0pt}{shadecolor}, frame hidden, interior hidden, breakable]}{\end{tcolorbox}}\fi
 
@@
 
-\hypertarget{quantile-regression-location-scale-model}{%
-\subsection{Quantile Regression: Location-Scale
-model}\label{quantile-regression-location-scale-model}}
+\hypertarget{sec-betas}{%
+\subsection{Quantile Regression: Location-Scale model}\label{sec-betas}}
 
@@
 
-\hypertarget{standard-errors-gls-robust-clustered}{%
-\subsection{Standard Errors: GLS, Robust,
-Clustered}\label{standard-errors-gls-robust-clustered}}
+\hypertarget{sec-se}{%
+\subsection{Standard Errors: GLS, Robust, Clustered}\label{sec-se}}
 
@@
 
+Using the setup describe in the previous section, Machado and Santos
+Silva (2019) proposes an extension to the model proposed by He (1997)
+that would allow for the estimation of quantile regression models with
+panel data, allowing for the inclussion of individual fixed effects.
+However, as the authors suggest, the methodology can be generalized to
+allow for the inclusion of multiple fixed effects. This type of analysis
+may be useful when considering data such as employer-employee linked
+data (Abowd, Kramarz, and Roux 2006), or teacher-student linked data
+(Harris and Sass 2011). Or, in the most common case, allowing to control
+for both individual and time fixed effects.
+
+Reconsider the original model, and assume there are sets of unobserved
+heterogeneity that are assumed to be constant across observations, if
+they belong to common groups. In panel data, the groups would be the
+individual fixed effects and the time fixed effects. Without loss of
+generality, we can assume that the data generating process is as
+follows:
+
+\[\begin{aligned}
+  y_{i} &= x_{i}' \beta + \delta_{g1} + \delta_{g2} + \nu_i \\
+  \nu_i &= \varepsilon_i \times (x_{i}' \gamma + \zeta_{g1} + \zeta_{g2})   
+  \end{aligned}
+\]
+
+where we assume \(x_{i}\) vary across groups \(g_1\) and \(g_2\), thus
+are not collinear, and that \(\delta's\) and \(\zeta's\) are the
+location and scale effects associated with groups fixed
+effects.\footnote{We could just as well consider multiple sets of fixed
+  effects}
+
+If the dimension of groups \(g_k\) is low, this model could be estimated
+using a dummy inclussion approach following Section~\ref{sec-betas}, and
+standard errors obtained as discussed in Section~\ref{sec-se}. However,
+if the dimensionsionality of \(g_k\) is high, dummy inclussion approach
+may not be feasible. Instead, a more feasible approach is to apply the
+Frisch-Waugh-Lovell (FWL) theorem, and partial out the impact of the
+group fixed effects on the control variables \(x_{i}\), the outcome of
+interest \(y_{i}\), with a similar approach for the identification of
+\(\sigma(x)\). In the case of unbalanced setups, with multiple groups,
+the estimation involves iterative processes for which various approaches
+have been sugested and implemented (see Correia (2016), Gaure (2013),
+Rios-Avila (2015), among others).
+
+When applying the partialing out approach, some modifications to the
+approach described in Section~\ref{sec-betas} is needed.
+
+\begin{enumerate}
+\def\labelenumi{\arabic{enumi}.}
+\tightlist
+\item
+  For all dependent and independent variables in the model (\(w=y,x\)),
+  we partial out the group fixed effects, and obtain the
+  centered-residualized variables:
+\end{enumerate}
+
+\[\begin{aligned}
+w_{i} &= \delta_{g1}^w + \delta_{g2}^w + u_{i}^w \\
+w_{i}^{rc} &= E(w_{i}) + \hat{u}_{i}^w
+\end{aligned}
+\]
+
+\begin{enumerate}
+\def\labelenumi{\arabic{enumi}.}
+\setcounter{enumi}{1}
+\tightlist
+\item
+  We estimate the location model using the centered-residualized
+  variables:
+\end{enumerate}
+
+\[y_{i}^{rc} = x_{i}^{rc'} \beta + nu_{i}
+\]
+
+\begin{enumerate}
+\def\labelenumi{\arabic{enumi}.}
+\setcounter{enumi}{2}
+\tightlist
+\item
+  Since \(|\hat \nu_i|\) is the dependent variable for the scale model,
+  we apply the partialling out and recentering to this expression
+  (\(|\hat \nu_i|^{rc}\)), and use that to estimate the model:
+\end{enumerate}
+
+\[|\hat\nu_{i}|^{rc} = x_{i}^{rc'} \gamma + e_{i}\]
+
+\begin{enumerate}
+\def\labelenumi{\arabic{enumi}.}
+\setcounter{enumi}{3}
+\tightlist
+\item
+  Finally the standardized residuals \(\varepsilon_i\) can be obtained
+  as follows
+\end{enumerate}
+
+\[\hat{\varepsilon}_{i} = \frac{\nu_{i}}{|\hat\nu_{i}|- \hat e_{i}}\]
+
+where \(|\hat\nu_{i}|- \hat e_{i}\) is the prediction for the
+conditional standard deviation
+\(\sigma(x_i)=x_{i}' \gamma + \zeta_{g1} + \zeta_{g2}\)
+
+The \(\tau_{th}\) quantile of the error \(\varepsilon\) can be estimated
+as usual, and the variance-covariance matrices obtained in the same way
+as before (see Section~\ref{sec-se}), but using \(x_{i}^{rc}\) instead
+of \(x_{i}\) when estimating the influence functions for all estimated
+coefficients.
+
 \hypertarget{monte-carlo-simulations}{%
@@
 
+The estimation of quantile regression via moments assumes that the DGP
+is linear in parameters, with an heteroskedastic error term that is also
+linear function of parameters:
+
+\[y = x\beta + e_i \times x\gamma\]
+
+where \(e_i\) is an unobserved i.i.d. random variable that is
+independent of \(x\), and such that \(x\gamma\) is larger than zero for
+any \(x\).
+
+In this case, the \(\tau_{th}\)conditional quantile model can be written
+as:
+
+\[q(y|\tau,X) = x(\beta + q(e|\tau) \times \gamma)\]
+
+This model is identified under the following conditions:
+
+\[\begin{aligned}
+  E[(y_i-x_i'\beta)x_i ]  &= E[h_{1,i}]=0 \\
+  E[ (|y_i-x_i'\beta|-x_i' \gamma) x_i ] &=E[h_{2,i}]=0 \\
+  E\left[  \mathbb{1}\left( q(\varepsilon|\tau) x_i'\gamma +x_i'\beta\geq  y_i  \right) - \tau \right] 
+   &=E[h_{3,i}]=0 
+\end{aligned}
+\]
+
+In this model, to estimate the variance-covariance matrix the set of
+coefficients \(\theta'=[\beta' \ \gamma' \ q(\varepsilon|\tau)']\), we
+need to obtain the influence functions of all coefficients, which are
+defined as:
+
+\[\lambda_i = \bar G(\theta)^{-1}
+\begin{bmatrix}
+h_{1,i} \\
+h_{2,i} \\
+h_{3,i}
+\end{bmatrix}
+\]
+
+where the Jacobian matrix \(\bar G(\theta)\) is defined as:
+
+\[\bar G(\theta) = \begin{bmatrix}
+\bar G_{11} & G_{12} & G_{13} \\
+\bar G_{21} & \bar G_{22} & G_{23} \\
+\bar G_{31} & \bar G_{32} & \bar G_{13} \\
+\end{bmatrix}
+\]
+
+with
+
+\[\bar G_{j,k} = - \frac 1 N \sum_{i=1}^N \frac{\partial h_{j,i}}{\partial \theta_k'} \ \forall j,k \in 1,2,3
+\]
+
+\hypertarget{first-moment-condition-location-model}{%
+\subsubsection{First Moment Condition: Location
+Model}\label{first-moment-condition-location-model}}
+
+\[h_{1,i}=x_i(y_i-x_i'\beta)\]
+
+\[\begin{aligned}
+\bar G_{1,1} &=- \frac{1}{N} \sum_{i=1}^N \frac{\partial h_{j,i}}{\partial \beta'} \\
+             &=- \frac{1}{N} \sum_{i=1}^N (-x_i x_i') \\
+             &= N^{-1} X'X
+\end{aligned}
+\]
+
+\[\begin{aligned}
+\bar G_{1,2} = \bar G_{1,3} = 0
+\]
+
+\hypertarget{second-moment-condition-scale-model}{%
+\subsubsection{Second Moment Condition: Scale
+model}\label{second-moment-condition-scale-model}}
+
 \hypertarget{references}{%
@@
 \begin{CSLReferences}{1}{0}
+\leavevmode\vadjust pre{\hypertarget{ref-abowed2006}{}}%
+Abowd, John M., Francis Kramarz, and Sébastien Roux. 2006. {``Wages,
+Mobility and Firm Performance: Advantages and Insights from Using
+Matched Worker--Firm Data*.''} \emph{The Economic Journal} 116 (512):
+F245--85.
+https://doi.org/\url{https://doi.org/10.1111/j.1468-0297.2006.01099.x}.
+
 \leavevmode\vadjust pre{\hypertarget{ref-cameron2005}{}}%
@@
 
+\leavevmode\vadjust pre{\hypertarget{ref-correia_feasible_nodate}{}}%
+Correia, Sergio. 2016. {``A {Feasible} {Estimator} for {Linear} {Models}
+with {Multi}-{Way} {Fixed} {Effects}.''}
+\url{http://scorreia.com/research/hdfe.pdf}.
+
 \leavevmode\vadjust pre{\hypertarget{ref-frishwaugh1933}{}}%
@@
 74--84. https://doi.org/\url{https://doi.org/10.1111/biom.12410}.
+
+\leavevmode\vadjust pre{\hypertarget{ref-gaure2013}{}}%
+Gaure, Simen. 2013. {``{OLS} with Multiple High Dimensional Category
+Variables.''} \emph{Computational Statistics \& Data Analysis} 66:
+8--18. https://doi.org/\url{https://doi.org/10.1016/j.csda.2013.03.024}.
+
+\leavevmode\vadjust pre{\hypertarget{ref-harrissass2011}{}}%
+Harris, Douglas N., and Tim R. Sass. 2011. {``Teacher Training, Teacher
+Quality and Student Achievement.''} \emph{Journal of Public Economics}
+95 (7): 798--812.
+https://doi.org/\url{https://doi.org/10.1016/j.jpubeco.2010.11.009}.
 
@@
 
+\leavevmode\vadjust pre{\hypertarget{ref-rios2015}{}}%
+Rios-Avila, Fernando. 2015. {``Feasible {Fitting} of {Linear} {Models}
+with {N} {Fixed} {Effects}.''} \emph{The Stata Journal} 15 (3): 881--98.
+\url{https://doi.org/10.1177/1536867X1501500318}.
+
 \leavevmode\vadjust pre{\hypertarget{ref-zhao2000}{}}%

### 2023-10-27 article/article.qmd
s
s

@@
 
-Because the indicator function $\mathbb{1}()$ is not differentiable, we impose some smoothing assumptions:
+Because the indicator function $\mathbb{1}()$ is not differentiable, we borrow from the non-parametric literature, and approximate the indicator function with the integral of a kernel density function $I()$.
+This function $I()$, is monotonic and symetrical function around zero, with a domain over the real numbers, and a range between 0 and 1.
 
-First:
+With an arbirarily small bandwidth $h$, this function will approximate the indicator function:
+
+$$
+\lim_{h\rightarrow 0} I\left(\frac{z}{h}\right) \approx \mathbb{1}(z\geq 0)
+$$
+
+Thus the function $h_{3,i}$ can be approximated as:
+
+$$h_{3,i} \approx I\left( q(\varepsilon|\tau) x_i'\gamma +x_i'\beta - y_i  \right) - \tau$$
+
+Now, we can obtain the Jacobian matrix $\bar G_{3,1}$ as:
 
 $$\begin{aligned}
-E[h_{3,i}] -\tau &= E[\mathbb{1}\left( q(\varepsilon|\tau) x_i'\gamma +x_i'\beta - y_i \geq 0 \right)] - \tau \\
-                &= E\left[E[\mathbb{1}\left( q(\varepsilon|\tau) x_i'\gamma +x_i'\beta - y_i \geq 0 \right)|x]\right] - \tau
+\bar G_{3,1} &= -\frac{1}{N} \sum \frac{\partial h_{3,i}}{\partial \beta'} \\
+             &= -N^{-1} \sum K_h(q(\varepsilon|\tau) x_i'\gamma +x_i'\beta - y_i ) x_i'
 \end{aligned}
@@
 
-Because we are aiming to identify the conditional quantile function of $y$, and under the assumption of the DGP it follows that:
+Under the assumption that we have enough observations within each combination of $x$, and of multiplicative heteroskedasticity, we have:
 
 $$\begin{aligned}
-q(y|\tau) &= q(\varepsilon|\tau) x_i'\gamma +x_i'\beta \\
-E[\mathbb{1}\left( q(y|\tau) - y_i \geq 0 \right)|x] &= \tau 
+E(K_h(q(\varepsilon|\tau) x_i'\gamma +x_i'\beta - y_i )|X) &= f_{y|X}(q(\varepsilon|\tau) x_i'\gamma +x_i'\beta) \\
+&=\frac{1}{x_i'\gamma} f_{\varepsilon}(q(\varepsilon|\tau)) \\
 \end{aligned}
@@
 
-and asymptotically, we expect that
+where $f_{y|X}$ is the conditional probability density function of $y$ given $X$, and $f_\varepsilon$ is the unconditional distribution of the standardized error.
+With this, we can rewrite the Jacobian matrix as:
 
-$$E[\mathbb{1}\left( q(y|\tau) - y_i \geq 0 \right)|x]=
-E[\mathbb{1}\left( q(y|\tau) \geq  y_i \right)|x] = \tau = F_{y |X} \big( q(y|\tau) \big) 
+$$\bar G_{3,1} &= -N^{-1} f_{\varepsilon}\big(q(\varepsilon|\tau)\big) \sum  \frac{x_i'}{x_i'\gamma} 
 $$
 
-but also that
+Asymptotically, however, the expression $\sum\frac{a_i}{b_i}$ can be approximated using taylor expansions by $N\frac{\bar a}{\bar b}$.[^6] Thus, we can rewrite the last term as:
 
-$$F_{y|X} \big( q(y|\tau)) = \tau = F_{\varepsilon}( q(\varepsilon|\tau) )
+[^6:] This approximation will be useful when we consider the estimation of the influence functions.
+$$\bar G_{3,1} = - f_{\varepsilon}\big(q(\varepsilon|\tau)\big) \frac{\bar x_i'}{\bar x_i'\gamma} 
 $$
 
-where $F_{y|X}$ is the conditional cumulative distribution function (CDF) of $y$, and $F_{\varepsilon}$ is the unconditonal CDF of the iid error $\varepsilon$.
+The Jacobian for the second matrix $\bar G_{3,2}$ can be derived similarly:
 
-Second, based on non-parametric estimation of the CDF, we can approximate $F_{y|X} \big( q(y|\tau))$ as:
+$$\begin{aligned}
+\bar G_{3,2} &= -\frac{1}{N} \sum \frac{\partial h_{3,i}}{\partial \gamma'} \\
+             &= -N^{-1} \sum K_h(q(\varepsilon|\tau) x_i'\gamma +x_i'\beta - y_i ) q(\varepsilon,\tau) x_i' \\
+             &=-N^{-1} \sum f_{y|x}(q(\varepsilon|\tau) x_i'\gamma +x_i'\beta ) q(\varepsilon,\tau) x_i' \\
+             &=-N^{-1} f_{\varepsilon}(q(\varepsilon|\tau)) q(\varepsilon,\tau) \sum \frac{x_i'}{x_i'\gamma} \\
+             &=- f_{\varepsilon}(q(\varepsilon|\tau)) q(\varepsilon,\tau) \frac{\bar x_i'}{\bar x_i'\gamma}
+\end{aligned}
+$$
 
-$$F_{y|X} \big( q(y|\tau) ) \approx \frac{\sum_{i=1}^N F_{y|X) ( q(y|\tau) - y_i)
+and the Jacobian for the third matrix $\bar G_{3,3}$ is:
+
+$$\begin{aligned}
+\bar G_{3,3} &= -\frac{1}{N} \sum \frac{\partial h_{3,i}}{\partial q(\varepsilon|\tau)} \\
+ &= -\frac{1}{N} \sum K_h(q(\varepsilon|\tau) x_i'\gamma +x_i'\beta - y_i ) x_i'\gamma \\
+ &= -\frac{1}{N} \sum f_{y|X}(q(\varepsilon|\tau) x_i'\gamma +x_i'\beta) x_i'\gamma \\
+ &= -\frac{1}{N} \sum f_{\varepsilon}(q(\varepsilon|\tau)) \frac{x_i'\gamma}{ x_i'\gamma} \\
+ &= - f_{\varepsilon}(q(\varepsilon|\tau)) 
+\end{aligned}
+$$
+
+### Influence functions
+
+**Location coefficients**:
+
+$$\lambda_i(\beta) = \bar G^{-1}_{1,1} h_{1,i} = N (X'X)^{-1}(x_i (y_i-x_i'\beta)) = N (X'X)^{-1}(x_i \nu_i)
+$$
+
+**Scale Coefficients coefficients**:
+
+$$\begin{aligned}
+\lambda_i(\gamma)&=\bar G_{22}^{-1}\Big(h_{2i}-\bar G_{21} \lambda_i(\beta)\big) \\
+&=N (X'X)^{-1}(x_i(|\nu_i|-x_i' \gamma))
+-  N E(sign(\nu_i))  (X'X)^{-1} x_i R_i \\
+&= N(X'X)^{-1} x_i \Big(2 R_i \big[1(R_i \geq 0) - E(1(R_i \geq 0)) \big]  -x_i'\gamma \Big) \\
+&= N(X'X)^{-1} x_i (\tilde R_i  -x_i'\gamma )
+\end{aligned}
+$$
 

### 2023-10-27 article/article.tex
s
s

@@
 \documentclass[
-  letterpaper,
-  DIV=11,
-  numbers=noendperiod]{scrartcl}
+  authoryear,
+  preprint,
+  1p]{elsarticle}
 
@@
 \setlength{\emergencystretch}{3em} % prevent overfull lines
-\setcounter{secnumdepth}{-\maxdimen} % remove section numbering
+\setcounter{secnumdepth}{5}
 % Make \paragraph and \subparagraph free-standing
@@
 \makeatother
-\newlength{\cslhangindent}
-\setlength{\cslhangindent}{1.5em}
-\newlength{\csllabelwidth}
-\setlength{\csllabelwidth}{3em}
-\newlength{\cslentryspacingunit} % times entry-spacing
-\setlength{\cslentryspacingunit}{\parskip}
-\newenvironment{CSLReferences}[2] % #1 hanging-ident, #2 entry spacing
- {% don't indent paragraphs
-  \setlength{\parindent}{0pt}
-  % turn on hanging indent if param 1 is 1
-  \ifodd #1
-  \let\oldpar\par
-  \def\par{\hangindent=\cslhangindent\oldpar}
-  \fi
-  % set entry spacing
-  \setlength{\parskip}{#2\cslentryspacingunit}
- }%
- {}
-\usepackage{calc}
-\newcommand{\CSLBlock}[1]{#1\hfill\break}
-\newcommand{\CSLLeftMargin}[1]{\parbox[t]{\csllabelwidth}{#1}}
-\newcommand{\CSLRightInline}[1]{\parbox[t]{\linewidth - \csllabelwidth}{#1}\break}
-\newcommand{\CSLIndent}[1]{\hspace{\cslhangindent}#1}
 
-\KOMAoption{captions}{tableheading}
 \makeatletter
@@
 \makeatother
+\journal{Journal Name}
 \ifLuaTeX
@@
 \fi
+\usepackage[]{natbib}
+\bibliographystyle{elsarticle-harv}
 \IfFileExists{bookmark.sty}{\usepackage{bookmark}}{\usepackage{hyperref}}
@@
 
+\setlength{\parindent}{6pt}
+\begin{document}
+
+\begin{frontmatter}
 \title{Quantile Regressions via Method of Moments with multiple fixed
 effects}
-\author{Fernando Rios-Avila \and Leonardo Siles \and Gustavo
-Canavire-Bacarreza}
-\date{2023-10-26}
+\author[1]{Fernando Rios-Avila%
+\corref{cor1}%
+}
+ \ead{friosavi@levy.org} 
+\author[]{Leonardo Siles%
+%
+}
+ \ead{leo@gmail.com} 
+\author[2]{Gustavo Canavire-Bacarreza%
+%
+}
+ \ead{gcanavire@worldbank.org}
 
-\begin{document}
-\maketitle
+\affiliation[1]{organization={Levy Economics Institute of Bard
+College},,postcodesep={}}
+\affiliation[2]{organization={World Bank},,postcodesep={}}
+
+\cortext[cor1]{Corresponding author}
+
 \begin{abstract}
@@
 multiple fixed effects. The method expands on the strategy proposed by
-Machado and Santos Silva (2019), allowing for multiple fixed effects,
-and providing various alternatives for the estimation of Standard
-errors. We provide Monte Carlo simulations to show the finite sample
-properties of the proposed method in the presence of two sets of fixed
-effects. Finally, we apply the proposed method to estimate
-\textbf{something interesting}
+\citet{mss2019}, allowing for multiple fixed effects, and providing
+various alternatives for the estimation of Standard errors. We provide
+Monte Carlo simulations to show the finite sample properties of the
+proposed method in the presence of two sets of fixed effects. Finally,
+we apply the proposed method to estimate \textbf{something interesting}
 \end{abstract}
-\ifdefined\Shaded\renewenvironment{Shaded}{\begin{tcolorbox}[sharp corners, enhanced, boxrule=0pt, borderline west={3pt}{0pt}{shadecolor}, frame hidden, interior hidden, breakable]}{\end{tcolorbox}}\fi
+
+\begin{keyword}
+    Fixed effects \sep Linear heteroskedasticity \sep Location-scale
+model \sep 
+    Quantile regression
+\end{keyword}
+\end{frontmatter}
+    \ifdefined\Shaded\renewenvironment{Shaded}{\begin{tcolorbox}[frame hidden, interior hidden, borderline west={3pt}{0pt}{shadecolor}, boxrule=0pt, enhanced, sharp corners, breakable]}{\end{tcolorbox}}\fi
 
@@
 
-Quantile regression (QR), introduced by Koenker and Bassett (1978), is
-an estimation strategy used for modeling the relationships between
+Quantile regression (QR), introduced by \citet{koenkerbasset1978}, is an
+estimation strategy used for modeling the relationships between
 explanatory variables X and the conditional quantiles of the dependent
@@
 extending quantile regressions analysis to include individual fixed
-effects in the framework of panel data. However, as described in Neyman
-and Scott (1948), and Lancaster (2000), when individual fixed effects
-are included in quantile regression analysis it generates an incident
-parameter problem. While many strategies have been proposed for
-estimating this type of model (see Galvão and Kato, 2018 for a brief
+effects in the framework of panel data. However, as described in
+\citet{neymanscott1948}, and \citet{lancaster2000}, when individual
+fixed effects are included in quantile regression analysis it generates
+an incident parameter problem. While many strategies have been proposed
+for estimating this type of model (see Galvão and Kato, 2018 for a brief
 review), neither has become standard because of their restrictive
@@
 
-More recently, Machado and Santos Silva (2019) (MSS hereafter) proposed
-a methodology based on a conditional location-scale model similar to the
-one described in He (1997) and Zhao (2000), for the estimation of
-quantile regressions models for panel data via a method of moments. This
-method allows individual fixed effects allowing to have heterogeneous
-effects on the entire conditional distribution of the outcome, rather
-constraining their effect to be a location shift only as in Canay
-(2011), Koenker (2004), and Lancaster (2000).
+More recently, \citet{mss2019} (MSS hereafter) proposed a methodology
+based on a conditional location-scale model similar to the one described
+in \citet{he1997} and \citet{zhao2000}, for the estimation of quantile
+regressions models for panel data via a method of moments. This method
+allows individual fixed effects allowing to have heterogeneous effects
+on the entire conditional distribution of the outcome, rather
+constraining their effect to be a location shift only as in
+\citet{canay2011}, \citet{koenker2004}, and \citet{lancaster2000}.
 
@@
 the data is based on a multiplicative heteroskedastic process that is
-linear in parameters (Cameron and Trivedi (2005), Machado and Santos
-Silva (2019), He (1997) and Zhao (2000) ), the effect of a variable
-\(X\) on the \(q_th\) quantile can be derived as the combination of a
-location effect, and scale effect moderated by the quantile of an
-underlying i.i.d. error. For statistical inference, MSS derives the
-asymptotic distribution of the estimator, suggesting the use of
-bootstrap standard errors, as well.
+linear in parameters (\citet{cameron2005}, \citet{mss2019},
+\citet{he1997} and \citet{zhao2000} ), the effect of a variable \(X\) on
+the \(q_th\) quantile can be derived as the combination of a location
+effect, and scale effect moderated by the quantile of an underlying
+i.i.d. error. For statistical inference, MSS derives the asymptotic
+distribution of the estimator, suggesting the use of bootstrap standard
+errors, as well.
 
@@
 
-In this framework, our paper expands on Machado and Santos Silva (2019),
-following some of the suggestions by the authors regarding further
-research. First, making use of the properties of GMM estimators, we
-derive various alternatives for the estimation of standard errors based
-on the empirical Influence functions of the estimators. Second, we
-reconsider the application of Frisch--Waugh--Lovell (FWL) theorem
-(Frisch and Waugh (1933) and Lovell (1963)) to extend the MSS estimator
-to allow for the inclusion of multiple fixed effects, for example,
-individual and year fixed effects.
+In this framework, our paper expands on \citet{mss2019}, following some
+of the suggestions by the authors regarding further research. First,
+making use of the properties of GMM estimators, we derive various
+alternatives for the estimation of standard errors based on the
+empirical Influence functions of the estimators. Second, we reconsider
+the application of Frisch--Waugh--Lovell (FWL) theorem
+(\citet{frishwaugh1933} and \citet{lovell1963}) to extend the MSS
+estimator to allow for the inclusion of multiple fixed effects, for
+example, individual and year fixed effects.
 
 The rest of the paper is restructured as follows. Section 2 presents the
-basic setup of the location-Scale model described in He (1997) and Zhao
-(2000), tying the relationship between the standard quantile regression
-model, and the location and scale model. It also revisits MSS
+basic setup of the location-Scale model described in \citet{he1997} and
+\citet{zhao2000}, tying the relationship between the standard quantile
+regression model, and the location and scale model. It also revisits MSS
 methodology, proposing alternative estimators for the standard errors
@@
 Here, the location parameters \(\beta\) are typically identified using a
-linear regression model (as in Machado and Santos Silva (2019)), or a
-median regression (as in Melly (2005)), and the scale parameters
-\(\gamma(\tau)\) can be estimated using standard approaches.
+linear regression model (as in \citet{mss2019}), or a median regression
+(as in \citet{melly2005}), and the scale parameters \(\gamma(\tau)\) can
+be estimated using standard approaches.
 
@@
   estimates for the quantile regression coefficients using a kernel
-  local weighted approach (Kaplan and Sun 2017), as well as identifying
-  the full set of quantile coefficients simultaneously assuming some
-  parametric functional forms (Frumento and Bottai 2016).}
+  local weighted approach \citep{kaplan2017}, as well as identifying the
+  full set of quantile coefficients simultaneously assuming some
+  parametric functional forms \citep{frumentobotai2016}.}
 
 One insightful extension to the location-scale parameterizations
-suggested by He (1997), Cameron and Trivedi (2005), and Machado and
-Santos Silva (2019) is to assume that the data-generating process (DGP)
-can be written as a linear model with a multiplicative heteroskedastic
-process that is linear in parameters.\footnote{Machado and Santos Silva
-  (2019) also discuss a model where heteroskedasticity can be an
-  arbitrary nonlinear function \(\sigma(x_i'\gamma)\), but develop the
-  estimator for the linear case, i.e., when \(\sigma()\) is the identity
-  function.}
+suggested by \citet{he1997}, \citet{cameron2005}, and \citet{mss2019} is
+to assume that the data-generating process (DGP) can be written as a
+linear model with a multiplicative heteroskedastic process that is
+linear in parameters.\footnote{\citet{mss2019} also discuss a model
+  where heteroskedasticity can be an arbitrary nonlinear function
+  \(\sigma(x_i'\gamma)\), but develop the estimator for the linear case,
+  i.e., when \(\sigma()\) is the identity function.}
 
@@
 estimation, this estimation approach would be more efficient than the
-standard quantile regression model (Zhao (2000)). Second, under the
+standard quantile regression model (\citet{zhao2000}). Second, under the
 assumption that \(X\gamma\) is strictly possitive, the model would
@@
 
-Under the conditions described in Newey and McFadden (1994) (see section
-7), Cameron and Trivedi (2005) (see chapter 6.3.9) or as shown in
-Machado and Santos Silva (2019), the location, scale and residual
-quantile coefficients are asymptotically normal.\footnote{Zhao (2000)
-  also shows that the quantile coefficients for the location-scale model
-  also follows a normal distribution, but uses the assumption that the
-  location model is derived using a least absolute deviation approach
-  (median regression).}
+Under the conditions described in \citet{newey_chapter_1994} (see
+section 7), \citet{cameron2005} (see chapter 6.3.9) or as shown in
+\citet{mss2019}, the location, scale and residual quantile coefficients
+are asymptotically normal.\footnote{\citet{zhao2000} also shows that the
+  quantile coefficients for the location-scale model also follows a
+  normal distribution, but uses the assumption that the location model
+  is derived using a least absolute deviation approach (median
+  regression).}
 
@@
 \hypertarget{multiple-fixed-effects-expanding-on-mss2019}{%
-\subsection{Multiple Fixed Effects: Expanding on Machado and Santos
-Silva (2019)}\label{multiple-fixed-effects-expanding-on-mss2019}}
+\subsection{\texorpdfstring{Multiple Fixed Effects: Expanding on
+\citet{mss2019}}{Multiple Fixed Effects: Expanding on @mss2019}}\label{multiple-fixed-effects-expanding-on-mss2019}}
 
-Using the setup describe in the previous section, Machado and Santos
-Silva (2019) proposes an extension to the model proposed by He (1997)
-that would allow for the estimation of quantile regression models with
-panel data, allowing for the inclussion of individual fixed effects.
-However, as the authors suggest, the methodology can be generalized to
-allow for the inclusion of multiple fixed effects. This type of analysis
-may be useful when considering data such as employer-employee linked
-data (Abowd, Kramarz, and Roux 2006), or teacher-student linked data
-(Harris and Sass 2011). Or, in the most common case, allowing to control
+Using the setup described in the previous section, \citet{mss2019}
+proposes an extension to the model proposed by \citet{he1997} that would
+allow for the estimation of quantile regression models with panel data,
+allowing for the inclusion of individual fixed effects. However, as the
+authors suggest, the methodology can be generalized to allow for the
+inclusion of multiple fixed effects. This type of analysis may be useful
+when considering data such as employer-employee linked data
+\citep{abowed2006}, or teacher-student linked data
+\citep{harrissass2011}. Or, in the most common case, allowing to control
 for both individual and time fixed effects.
@@
 standard errors obtained as discussed in Section~\ref{sec-se}. However,
-if the dimensionsionality of \(g_k\) is high, dummy inclussion approach
+if the dimensionality of \(g_k\) is high, the dummy inclusion approach
 may not be feasible. Instead, a more feasible approach is to apply the
@@
 the estimation involves iterative processes for which various approaches
-have been sugested and implemented (see Correia (2016), Gaure (2013),
-Rios-Avila (2015), among others).
+have been suggested and implemented (see
+\citet{correia_feasible_nodate}, \citet{gaure2013}, \citet{rios2015},
+among others).
 
 When applying the partialing out approach, some modifications to the
-approach described in Section~\ref{sec-betas} is needed.
+approach described in Section~\ref{sec-betas} are needed.
 
@@
 
-\[y = x\beta + e_i \times x\gamma\]
+\[\begin{aligned}
+y = x\beta + \nu \\
+\nu = \varepsilon \times x\gamma
+\end{aligned}
+\]
 
-where \(e_i\) is an unobserved i.i.d. random variable that is
+where \(\varepsilon\) is an unobserved i.i.d. random variable that is
 independent of \(x\), and such that \(x\gamma\) is larger than zero for
@@
 
-In this case, the \(\tau_{th}\)conditional quantile model can be written
-as:
+In this case, the \(\tau_{th}\) conditional quantile model can be
+written as:
 
@@
 \[\begin{aligned}
-\bar G_{1,1} &=- \frac{1}{N} \sum_{i=1}^N \frac{\partial h_{j,i}}{\partial \beta'} \\
+\bar G_{1,1} &=- \frac{1}{N} \sum_{i=1}^N \frac{\partial h_{1,i}}{\partial \beta'} \\
              &=- \frac{1}{N} \sum_{i=1}^N (-x_i x_i') \\
@@
 
-\[\begin{aligned}
+\[
 \bar G_{1,2} = \bar G_{1,3} = 0
@@
 
-\hypertarget{references}{%
-\section*{References}\label{references}}
-\addcontentsline{toc}{section}{References}
+\[h_{2,i}=x_i(|y_i-x_i'\beta|-x_i'\gamma)\]
 
-\hypertarget{refs}{}
-\begin{CSLReferences}{1}{0}
-\leavevmode\vadjust pre{\hypertarget{ref-abowed2006}{}}%
-Abowd, John M., Francis Kramarz, and Sébastien Roux. 2006. {``Wages,
-Mobility and Firm Performance: Advantages and Insights from Using
-Matched Worker--Firm Data*.''} \emph{The Economic Journal} 116 (512):
-F245--85.
-https://doi.org/\url{https://doi.org/10.1111/j.1468-0297.2006.01099.x}.
+\[\begin{aligned}
+\bar G_{2,1} &= -\frac{1}{N} \sum \frac{\partial h_{2,i}}{\partial \beta'} \\
+             &=  \frac{1}{N} \sum x_i x_i' \frac{y_i-x_i'\beta}{|y_i-x_i'\beta|} \\
+\frac{y_i-x_i'\beta}{|y_i-x_i'\beta|} &= sign(y_i-x_i'\beta) \\            
+\end{aligned}
+\]
 
-\leavevmode\vadjust pre{\hypertarget{ref-cameron2005}{}}%
-Cameron, Adrian Colin, and Pravin K. Trivedi. 2005.
-\emph{Microeconometrics: Methods and Applications}. Cambridge ; New
-York: Cambridge University Press.
+Under the assumption \(\varepsilon_i \times x\gamma\), or in this case
+\(y_i-x_i'\beta\), is uncorrelated with \(x\), we can simplify the
+expression as:
 
-\leavevmode\vadjust pre{\hypertarget{ref-canay2011}{}}%
-Canay, Ivan A. 2011. {``A Simple Approach to Quantile Regression for
-Panel Data.''} \emph{The Econometrics Journal} 14 (3): 368--86.
-https://doi.org/\url{https://doi.org/10.1111/j.1368-423X.2011.00349.x}.
+\[\begin{aligned}
+\bar G_{2,1} &= N^{-1} \left(N^{-1}\sum sign(y_i-x_i'\beta)\right) \sum x_i x_i' \\
+&= N^{-1} E[sign(y_i-x_i'\beta)] X'X
+\end{aligned}
+\]
 
-\leavevmode\vadjust pre{\hypertarget{ref-correia_feasible_nodate}{}}%
-Correia, Sergio. 2016. {``A {Feasible} {Estimator} for {Linear} {Models}
-with {Multi}-{Way} {Fixed} {Effects}.''}
-\url{http://scorreia.com/research/hdfe.pdf}.
+\[\begin{aligned}
+\bar G_{2,2} &= -\frac{1}{N} \sum \frac{\partial h_{2,i}}{\partial \gamma'} \\
+             &=  \frac{1}{N} \sum x_i x_i' 
+             &= N^{-1} X'X
+\end{aligned}
+\]
 
-\leavevmode\vadjust pre{\hypertarget{ref-frishwaugh1933}{}}%
-Frisch, Ragnar, and Frederick V. Waugh. 1933. {``Partial Time
-Regressions as Compared with Individual Trends.''} \emph{Econometrica} 1
-(4): 387--401. \url{http://www.jstor.org/stable/1907330}.
+\[\bar G_{2,3}=0\]
 
-\leavevmode\vadjust pre{\hypertarget{ref-frumentobotai2016}{}}%
-Frumento, Paolo, and Matteo Bottai. 2016. {``Parametric Modeling of
-Quantile Regression Coefficient Functions.''} \emph{Biometrics} 72 (1):
-74--84. https://doi.org/\url{https://doi.org/10.1111/biom.12410}.
+\hypertarget{third-moment-condition-quantile-of-standardized-residual}{%
+\subsubsection{Third Moment Condition: Quantile of Standardized
+Residual}\label{third-moment-condition-quantile-of-standardized-residual}}
 
-\leavevmode\vadjust pre{\hypertarget{ref-gaure2013}{}}%
-Gaure, Simen. 2013. {``{OLS} with Multiple High Dimensional Category
-Variables.''} \emph{Computational Statistics \& Data Analysis} 66:
-8--18. https://doi.org/\url{https://doi.org/10.1016/j.csda.2013.03.024}.
+\[h_{3,i} = \mathbb{1}\left( q(\varepsilon|\tau) x_i'\gamma +x_i'\beta - y_i \geq 0 \right) - \tau\]
 
-\leavevmode\vadjust pre{\hypertarget{ref-harrissass2011}{}}%
-Harris, Douglas N., and Tim R. Sass. 2011. {``Teacher Training, Teacher
-Quality and Student Achievement.''} \emph{Journal of Public Economics}
-95 (7): 798--812.
-https://doi.org/\url{https://doi.org/10.1016/j.jpubeco.2010.11.009}.
+Because the indicator function \(\mathbb{1}()\) is not differentiable,
+we borrow from the non-parametric literature, and approximate the
+indicator function with the integral of a kernel density function
+\(I()\). This function \(I()\), is monotonic and symetrical function
+around zero, with a domain over the real numbers, and a range between 0
+and 1.
 
-\leavevmode\vadjust pre{\hypertarget{ref-he1997}{}}%
-He, Xuming. 1997. {``Quantile Curves Without Crossing.''} \emph{The
-American Statistician} 51 (2): 186--92.
-\url{https://doi.org/10.1080/00031305.1997.10473959}.
+With an arbirarily small bandwidth \(h\), this function will approximate
+the indicator function:
 
-\leavevmode\vadjust pre{\hypertarget{ref-kaplan2017}{}}%
-Kaplan, David M., and Yixiao Sun. 2017. {``Smoothed Estimating Equations
-for Instrumental Variables Quantile Regression.''} \emph{Econometric
-Theory} 33 (1): 105--57.
-\url{https://doi.org/10.1017/S0266466615000407}.
+\[
+\lim_{h\rightarrow 0} I\left(\frac{z}{h}\right) \approx \mathbb{1}(z\geq 0)
+\]
 
-\leavevmode\vadjust pre{\hypertarget{ref-koenker2004}{}}%
-Koenker, Roger. 2004. {``Quantile Regression for Longitudinal Data.''}
-\emph{Journal of Multivariate Analysis} 91 (1): 74--89.
-https://doi.org/\url{https://doi.org/10.1016/j.jmva.2004.05.006}.
+Thus the function \(h_{3,i}\) can be approximated as:
 
-\leavevmode\vadjust pre{\hypertarget{ref-koenkerbasset1978}{}}%
-Koenker, Roger, and Gilbert Bassett. 1978. {``Regression Quantiles.''}
-\emph{Econometrica} 46 (1): 33--50.
-\url{http://www.jstor.org/stable/1913643}.
+\[h_{3,i} \approx I\left( q(\varepsilon|\tau) x_i'\gamma +x_i'\beta - y_i  \right) - \tau\]
 
-\leavevmode\vadjust pre{\hypertarget{ref-lancaster2000}{}}%
-Lancaster, Tony. 2000. {``The Incidental Parameter Problem Since
-1948.''} \emph{Journal of Econometrics} 95 (2): 391--413.
-https://doi.org/\url{https://doi.org/10.1016/S0304-4076(99)00044-5}.
+Now, we can obtain the Jacobian matrix \(\bar G_{3,1}\) as:
 
-\leavevmode\vadjust pre{\hypertarget{ref-lovell1963}{}}%
-Lovell, Michael C. 1963. {``Seasonal Adjustment of Economic Time Series
-and Multiple Regression Analysis.''} \emph{Journal of the American
-Statistical Association} 58 (304): 993--1010.
-\url{https://doi.org/10.1080/01621459.1963.10480682}.
+\[\begin{aligned}
+\bar G_{3,1} &= -\frac{1}{N} \sum \frac{\partial h_{3,i}}{\partial \beta'} \\
+             &= -N^{-1} \sum K_h(q(\varepsilon|\tau) x_i'\gamma +x_i'\beta - y_i ) x_i'
+\end{aligned}
+\]
 
-\leavevmode\vadjust pre{\hypertarget{ref-mss2019}{}}%
-Machado, José A. F., and J. M. C. Santos Silva. 2019. {``Quantiles via
-Moments.''} \emph{Journal of Econometrics} 213 (1): 145--73.
-\url{https://doi.org/10.1016/j.jeconom.2019.04.009}.
+Under the assumption that we have enough observations within each
+combination of \(x\), and of multiplicative heteroskedasticity, we have:
+\[\begin{aligned}
+E(K_h(q(\varepsilon|\tau) x_i'\gamma +x_i'\beta - y_i )|X) &= f_{y|X}(q(\varepsilon|\tau) x_i'\gamma +x_i'\beta) \\
+f_{y|X}(q(\varepsilon|\tau) x_i'\gamma +x_i'\beta) &= f_{\frac{y-x_i'\beta}{x_i\gamma|X}(q(\varepsilon|\tau))
+\end{aligned}
+\]
 
-\leavevmode\vadjust pre{\hypertarget{ref-melly2005}{}}%
-Melly, Blaise. 2005. {``Decomposition of Differences in Distribution
-Using Quantile Regression.''} \emph{Labour Economics} 12 (4): 577--90.
-https://doi.org/\url{https://doi.org/10.1016/j.labeco.2005.05.006}.
+where \(f_{y|X}\) is the conditional probability density function of
+\(y\) given \(X\). With this, we can rewrite the Jacobian matrix as:
 
-\leavevmode\vadjust pre{\hypertarget{ref-newey_chapter_1994}{}}%
-Newey, Whitney K., and Daniel McFadden. 1994. {``Chapter 36 {Large}
-Sample Estimation and Hypothesis Testing.''} In \emph{Handbook of
-{Econometrics}}, 4:2111--2245. Elsevier.
-\url{https://doi.org/10.1016/S1573-4412(05)80005-4}.
+\[\begin{aligned}
+\bar G_{3,1} &= -N^{-1} \sum f_{y|X}(q(\varepsilon|\tau) x_i'\gamma +x_i'\beta ) x_i'
+\end{aligned}
+\]
 
-\leavevmode\vadjust pre{\hypertarget{ref-neymanscott1948}{}}%
-Neyman, J., and Elizabeth L. Scott. 1948. {``Consistent Estimates Based
-on Partially Consistent Observations.''} \emph{Econometrica} 16 (1):
-1--32. \url{http://www.jstor.org/stable/1914288}.
-
-\leavevmode\vadjust pre{\hypertarget{ref-rios2015}{}}%
-Rios-Avila, Fernando. 2015. {``Feasible {Fitting} of {Linear} {Models}
-with {N} {Fixed} {Effects}.''} \emph{The Stata Journal} 15 (3): 881--98.
-\url{https://doi.org/10.1177/1536867X1501500318}.
-
-\leavevmode\vadjust pre{\hypertarget{ref-zhao2000}{}}%
-Zhao, Quanshui. 2000. {``Restricted {Regression} {Quantiles}.''}
-\emph{Journal of Multivariate Analysis} 72 (1): 78--99.
-https://doi.org/\url{https://doi.org/10.1006/jmva.1999.1849}.
-
-\end{CSLReferences}
+\renewcommand\refname{References}
+  \bibliography{bibliography.bib}
 

### 2023-10-27 article/article.qmd
update
article

@@
 
+<!--
+How to Render this?
+Lik this:
+quarto render article.qmd --to elsevier-pdf
+
+-->
+
 # Introduction
@@
 First, making use of the properties of GMM estimators, we derive various alternatives for the estimation of standard errors based on the empirical Influence functions of the estimators.
-Second, we reconsider the application of Frisch–Waugh–Lovell (FWL) theorem (@frishwaugh1933 and @lovell1963) to extend the MSS estimator to allow for the inclusion of multiple fixed effects, for example, individual and year fixed effects.
+Second, we reconsider the application of Frisch--Waugh--Lovell (FWL) theorem (@frishwaugh1933 and @lovell1963) to extend the MSS estimator to allow for the inclusion of multiple fixed effects, for example, individual and year fixed effects.
 
@@
 
-$$Q(Y|X,\tau) =X\beta(\tau)
-$${#eq-eq1}
+$$q(Y|X,\tau) =X\beta(\tau)
+$$ {#eq-eq1}
 
@@
 
-$$Q(Y|X,\tau) =X\beta+X\gamma(\tau)
+$$q(Y|X,\tau) =X\beta+X\gamma(\tau)
 $${#eq-eq2}
@@
 \left( \sum_{i\in y_i\geq x_i'\beta} \tau (y_i - x_i'\beta) - \sum_{i\in y_i<x_i'\beta} (1-\tau)(y_i - x_i'\beta) \right)
-$${#eq-eq3}
+$$ {#eq-eq3}
 
@@
 
-$$y_i=x_i'\beta+\varepsilon_i \times x_i'\gamma(\tau)
-$${#eq-eq4}
+[^2]: @mss2019 also discuss a model where heteroskedasticity can be an arbitrary nonlinear function $\sigma(x_i'\gamma)$, but develop the estimator for the linear case, i.e., when $\sigma()$ is the identity function.
 
-[^2]: @mss2019 also discuss a model where heteroskedasticity can be an arbitrary nonlinear function $\sigma(x_i'\gamma)$, but develop the estimator for the linear case, i.e., when $\sigma()$ is the identity function.
+$$\begin{aligned}
+y_i &=x_i'\beta+\nu_i \\
+\nu_i &=\varepsilon_i \times x_i'\gamma 
+\end{aligned}
+$$ {#eq-eq4}
 
@@
 
-$$Q(Y|X,\tau) =X\beta+X\gamma \times Q(\varepsilon|\tau)
-$${#eq-eq5}
+$$q(Y|X,\tau) =X\beta+q(\varepsilon|\tau) \times X\gamma 
+$$ {#eq-eq5}
 
@@
 
-$$\beta(\tau) = \beta + \gamma \times Q(\varepsilon|\tau)
-$${#eq-eq6}
+$$\beta(\tau) = \beta + q(\varepsilon|\tau) \times \gamma 
+$$ {#eq-eq6}
 
 While this specification imposes a strong assumption on the DGP, it has two advantages over the standard quantile regression model.
-First, because the location and scale model can be identified globally, with only a single parmater ($Q(\varepsilon|\tau)$) requiring local estimation, this estimation approach would be more efficient than the standard quantile regression model (@zhao2000).
+First, because the location and scale model can be identified globally, with only a single parmater ($q(\varepsilon|\tau)$) requiring local estimation, this estimation approach would be more efficient than the standard quantile regression model (@zhao2000).
 Second, under the assumption that $X\gamma$ is strictly possitive, the model would produce quantile coefficients that do not cross.
@@
 Following MSS, the quantile regression model defined by @eq-eq5 can be estimated using a method of moments approach.
-And while its possible to identify all coefficients ($\beta,\gamma, Q(\varepsilon|\tau)$) simultaneously, we describe and use the implementation approach advocated by MSS which identifies each set of coefficients separately.
+And while its possible to identify all coefficients ($\beta,\gamma, q(\varepsilon|\tau)$) simultaneously, we describe and use the implementation approach advocated by MSS which identifies each set of coefficients separately.
 
@@
 In this case, the location model coefficients are identified under the following condition:
+
 $$\begin{aligned}
-  y_i &=x_i'\beta+u_i \\
-  E[u 'X ] &=0
+      y_i &=x_i'\beta+\nu_i \\
+      E\big[ x_i \nu_i\big] &=0
       \end{aligned}
-$${#eq-eq7}
+$$ {#eq-eq7}
 
@@
 $$\begin{aligned}
-  |u_i| &=x_i'\gamma+v_i \\
-  E[ (|u|-X \gamma) X ] &=0
+  |\nu_i| &=x_i'\gamma+\omega_i \\
+  E\big[ x_i \omega_i \big] &=0 \\
+  E\big[ x_i (|\nu_i| -x_i'\gamma ) \big] &=0
   \end{aligned}
-$${#eq-eq8}
+$$ {#eq-eq8}
 
@@
 $$\begin{aligned}
-  E\left[  \mathbb{1}\left(x_i' (\beta + \gamma Q(\varepsilon|\tau)) \geq y_i \right) - \tau \right] &=0  \\
-  E\left[  \mathbb{1}\left(   Q(\varepsilon|\tau)\geq \frac{y_i-x_i'\beta}{x_i'\gamma} \right) - \tau \right] &=0  \\
+  E\left[  \mathbb{1}\left(x_i' (\beta + \gamma q(\varepsilon|\tau)) \geq y_i \right) - \tau \right] &=0  \\
+  E\left[  \mathbb{1}\left(   q(\varepsilon|\tau)\geq \frac{y_i-x_i'\beta}{x_i'\gamma} \right) - \tau \right] &=0  \\
   \end{aligned}
-$${#eq-eq9}
+$$ {#eq-eq9}
 
-Where one identifies the quantile of the error $\varepsilon$ using standardized errors $\frac{y_i-x_i'\beta}{x_i'\gamma}$, or by finding the values that identify the overall quantile coefficients $\beta(\tau)=\beta + \gamma Q(\varepsilon|\tau)$.
+Where one identifies the quantile of the error $\varepsilon$ using standardized errors $\frac{y_i-x_i'\beta}{x_i'\gamma}$, or by finding the values that identify the overall quantile coefficients $\beta(\tau)=\beta + \gamma q(\varepsilon|\tau)$.
 Afterwords, the conditional quantile coefficients is simply defined as the combination of the location and scale coefficients.
@@
 $$\begin{aligned}
-  E[u_i x_i ] &= E[h_{1,i}]=0 \\
-  E[ (|u_i|-x_i \gamma) x_i ] &=E[h_{2,i}]=0 \\
-  E\left[  \mathbb{1}\left(   Q(\varepsilon|\tau)\geq \frac{y_i-x_i'\beta}{x_i'\gamma} \right) - \tau \right] 
+  E[x_i \nu_i  ] &= E[h_{1,i}]=0 \\
+  E[x_i  (|\nu_i|-x_i \gamma) ] &=E[h_{2,i}]=0 \\
+  E\left[  \mathbb{1}\left(   q(\varepsilon|\tau)\geq \frac{y_i-x_i'\beta}{x_i'\gamma} \right) - \tau \right] 
   &=E[h_{3,i}]=0 
   \end{aligned}
-$${#eq-eq10}
+$$ {#eq-eq10}
 
@@
 
-Call $\theta=[ \beta' \ \ \gamma'  \ \ Q(\varepsilon|\tau)' ]'$ the set of coefficients that are identified in @eq-eq10, a just identified model.
+Call $\theta=[ \beta' \ \ \gamma' \ \ q(\varepsilon|\tau)' ]'$ the set of coefficients that are identified by the modement conditions in @eq-eq10, a just identified model.
 And the function $h_i$ is a vector function that stacks all the moments at the individual level described in @eq-eq10.
 Then $\hat\theta$ follows a normal distribution with mean $\theta$ and variance-covariance matrix $V(\theta)$ that is estimated as:
+
 $$
@@
 
-where the inner product is the moment covariance matrix, and $\bar{G}(\theta)$ is the Jacobian matrix of the moment equations (@eq-eq10) evaluated at $\hat\theta$.
+Which is equivalent to the Eicker-White Heteroskedastic-Consistent estimator for least-squares estimators.
+
+Here, the inner product is the moment covariance matrix, and $\bar{G}(\theta)$ is the Jacobian matrix of the moment equations (@eq-eq10) evaluated at $\hat\theta$.
 
@@
 
-This is equivalent to the Eicker-White Heteroskedastic-Consistent estimator for least-squares estimators.
-
-In this framework, the quantile regression coefficients, a combination of the location-scale-quantile estimates, will follow a normal distribution with mean $\beta(\tau) = \beta+Q(\varepsilon,\tau)\gamma$ and variance-covariance matrix equal to:
+In this framework, the quantile regression coefficients, a combination of the location-scale-quantile estimates, will follow a normal distribution with mean $\beta(\tau) = \beta+q(\varepsilon|\tau)\gamma$ and variance-covariance matrix equal to:
 
@@
 
-$$\Xi = [ I(k), \hat Q(\varepsilon|\tau) \cdot I(k), \hat \gamma ]
+$$\Xi = [ I(k), \hat q(\varepsilon|\tau) \times I(k), \hat \gamma ]
 $$
@@
 
+While it is possible to estimate the variance-covariance matrix using simultaneous model estimation, for a just identified model, it is more efficient to estimate each set of coefficients separately.
+The variance-covariance matrix can be estimated using the empirical influence functions of the estimators (see @jann_2020 for an overview of the application, and @hampel2005 for an in-depth review).
+
+1. Need to add the general condition Var=(inf (theta) * inf(theta))
+
+Thatn inf(theta) = inf beta gamma and q)tay
+
+and finally define what the IFs are (see appendix)
+
 The different types of Standard errors estimation, thus, depend on the assumptions imposed for the estimation of $V(\theta)$.
+
+### Robust Standard Errors
+
+Cross product of IFs
+
+### Clustered Standard Errors
+
+Sun then cross product
+
+### GLS Standard Errors
+
+Original paper;
 
@@
 
+## Model Identification
+
 The estimation of quantile regression via moments assumes that the DGP is linear in parameters, with an heteroskedastic error term that is also linear function of parameters:
@@
 
-$$q(y|\tau,X) = x(\beta + q(e|\tau) \times \gamma)$$
+$$q(y|\tau,X) = x(\beta + q(\varepsilon |\tau) \times \gamma)$$
 
@@
 
-In this model, to estimate the variance-covariance matrix the set of coefficients $\theta'=[\beta' \ \gamma' \ q(\varepsilon|\tau)']$, we need to obtain the influence functions of all coefficients, which are defined as:
+For simplicity, for the rest of the appendix, I will use $q^\varepsilon_\tau$ to represent $q(\varepsilon |\tau)$.
+
+## Estimation of the variance-covariance matrix
+
+In this model, to estimate the variance-covariance matrix the set of coefficients $\theta'=[\beta' \ \gamma' \ q^\varepsilon_\tau]$, we need to obtain the influence functions of all coefficients, which are defined as:
 
@@
 
-$$h_{3,i} = \mathbb{1}\left( q(\varepsilon|\tau) x_i'\gamma +x_i'\beta - y_i \geq 0 \right) - \tau$$
+$$\begin{aligned}
+h_{3,i} &= \mathbb{1}\left( q^\varepsilon_\tau x_i'\gamma +x_i'\beta - y_i \geq 0 \right) - \tau \text{ or}\\
+h_{3,i} &= \mathbb{1}\left( q^\varepsilon_\tau  \geq \frac{y_i- x_i'\beta}{x_i'\gamma}  \right) - \tau = \mathbb{1}\big( q^\varepsilon_\tau  \geq \varepsilon  \big) - \tau \\
+\end{aligned}
+$$
 
@@
 
-$$h_{3,i} \approx I\left( q(\varepsilon|\tau) x_i'\gamma +x_i'\beta - y_i  \right) - \tau$$
+$$h_{3,i} \approx I\left( q^\varepsilon_\tau x_i'\gamma +x_i'\beta - y_i  \right) - \tau$$
 
@@
 \bar G_{3,1} &= -\frac{1}{N} \sum \frac{\partial h_{3,i}}{\partial \beta'} \\
-             &= -N^{-1} \sum K_h(q(\varepsilon|\tau) x_i'\gamma +x_i'\beta - y_i ) x_i'
+             &= -N^{-1} \sum K_h(q^\varepsilon_\tau x_i'\gamma +x_i'\beta - y_i ) x_i'
 \end{aligned}
@@
 $$\begin{aligned}
-E(K_h(q(\varepsilon|\tau) x_i'\gamma +x_i'\beta - y_i )|X) &= f_{y|X}(q(\varepsilon|\tau) x_i'\gamma +x_i'\beta) \\
-&=\frac{1}{x_i'\gamma} f_{\varepsilon}(q(\varepsilon|\tau)) \\
+E(K_h(q^\varepsilon_\tau x_i'\gamma +x_i'\beta - y_i )|X) &= f_{y|X}(q^\varepsilon_\tau x_i'\gamma +x_i'\beta) \\
+&=\frac{1}{x_i'\gamma} f_{\varepsilon}(q^\varepsilon_\tau) \\
 \end{aligned}
@@
 
-$$\bar G_{3,1} &= -N^{-1} f_{\varepsilon}\big(q(\varepsilon|\tau)\big) \sum  \frac{x_i'}{x_i'\gamma} 
+$$\bar G_{3,1} = -N^{-1} f_{\varepsilon}\big(q^\varepsilon_\tau\big) \sum  \frac{x_i'}{x_i'\gamma} 
 $$
 
-Asymptotically, however, the expression $\sum\frac{a_i}{b_i}$ can be approximated using taylor expansions by $N\frac{\bar a}{\bar b}$.[^6] Thus, we can rewrite the last term as:
+Asymptotically, however, the expression $\sum\frac{a_i}{b_i}$ can be approximated using taylor expansions by $N\frac{\bar a}{\bar b}$. [^6] Thus, we can rewrite the last term as:
 
-[^6:] This approximation will be useful when we consider the estimation of the influence functions.
-$$\bar G_{3,1} = - f_{\varepsilon}\big(q(\varepsilon|\tau)\big) \frac{\bar x_i'}{\bar x_i'\gamma} 
+$$\bar G_{3,1} = - f_{\varepsilon}\big(q^\varepsilon_\tau\big) \frac{\bar x_i'}{\bar x_i'\gamma} 
 $$
+
+[^6]: This approximation will be useful when we consider the estimation of the influence functions.
 
@@
 \bar G_{3,2} &= -\frac{1}{N} \sum \frac{\partial h_{3,i}}{\partial \gamma'} \\
-             &= -N^{-1} \sum K_h(q(\varepsilon|\tau) x_i'\gamma +x_i'\beta - y_i ) q(\varepsilon,\tau) x_i' \\
-             &=-N^{-1} \sum f_{y|x}(q(\varepsilon|\tau) x_i'\gamma +x_i'\beta ) q(\varepsilon,\tau) x_i' \\
-             &=-N^{-1} f_{\varepsilon}(q(\varepsilon|\tau)) q(\varepsilon,\tau) \sum \frac{x_i'}{x_i'\gamma} \\
-             &=- f_{\varepsilon}(q(\varepsilon|\tau)) q(\varepsilon,\tau) \frac{\bar x_i'}{\bar x_i'\gamma}
+             &= -N^{-1} \sum K_h(q^\varepsilon_\tau x_i'\gamma +x_i'\beta - y_i ) q^\varepsilon_\tau x_i' \\
+             &=-N^{-1} \sum f_{y|x}(q^\varepsilon_\tau x_i'\gamma +x_i'\beta ) q^\varepsilon_\tau x_i' \\
+             &=-N^{-1} f_{\varepsilon}(q^\varepsilon_\tau) q^\varepsilon_\tau \sum \frac{x_i'}{x_i'\gamma} \\
+             &=- f_{\varepsilon}(q^\varepsilon_\tau) q^\varepsilon_\tau \frac{\bar x_i'}{\bar x_i'\gamma}
 \end{aligned}
@@
 $$\begin{aligned}
-\bar G_{3,3} &= -\frac{1}{N} \sum \frac{\partial h_{3,i}}{\partial q(\varepsilon|\tau)} \\
- &= -\frac{1}{N} \sum K_h(q(\varepsilon|\tau) x_i'\gamma +x_i'\beta - y_i ) x_i'\gamma \\
- &= -\frac{1}{N} \sum f_{y|X}(q(\varepsilon|\tau) x_i'\gamma +x_i'\beta) x_i'\gamma \\
- &= -\frac{1}{N} \sum f_{\varepsilon}(q(\varepsilon|\tau)) \frac{x_i'\gamma}{ x_i'\gamma} \\
- &= - f_{\varepsilon}(q(\varepsilon|\tau)) 
+\bar G_{3,3} &= -\frac{1}{N} \sum \frac{\partial h_{3,i}}{\partial q^\varepsilon_\tau} \\
+ &= -\frac{1}{N} \sum K_h(q^\varepsilon_\tau x_i'\gamma +x_i'\beta - y_i ) x_i'\gamma \\
+ &= -\frac{1}{N} \sum f_{y|X}(q^\varepsilon_\tau x_i'\gamma +x_i'\beta) x_i'\gamma \\
+ &= -\frac{1}{N} \sum f_{\varepsilon}(q^\varepsilon_\tau) \frac{x_i'\gamma}{ x_i'\gamma} \\
+ &= - f_{\varepsilon}(q^\varepsilon_\tau) 
 \end{aligned}
@@
 
-### Influence functions
+## Influence functions
 
-**Location coefficients**:
+### Location coefficients
 
@@
 
-**Scale Coefficients coefficients**:
+Which can also be written as a function of the standardized residuals:
+
+$$\lambda_i(\beta) = \bar G^{-1}_{1,1} h_{1,i} = N (X'X)^{-1}(x_i (y_i-x_i'\beta)) = N (X'X)^{-1}(x_i ( x_i'\gamma \times \varepsilon))
+$$
+
+### Scale Coefficients coefficients**
 
 $$\begin{aligned}
-\lambda_i(\gamma)&=\bar G_{22}^{-1}\Big(h_{2i}-\bar G_{21} \lambda_i(\beta)\big) \\
-&=N (X'X)^{-1}(x_i(|\nu_i|-x_i' \gamma))
--  N E(sign(\nu_i))  (X'X)^{-1} x_i R_i \\
-&= N(X'X)^{-1} x_i \Big(2 R_i \big[1(R_i \geq 0) - E(1(R_i \geq 0)) \big]  -x_i'\gamma \Big) \\
-&= N(X'X)^{-1} x_i (\tilde R_i  -x_i'\gamma )
+\lambda_i(\gamma)&=\bar G_{2,2}^{-1}\Big(h_{2,i}-\bar G_{2,1} \lambda_i(\beta)\Big) \\
+&=N (X'X)^{-1} \Big(x_i(|\nu_i|-x_i' \gamma) 
+- N^{-1} E[sign(\nu_i)] X'X \big[ N (X'X)^{-1}(x_i \nu_i) \big] \Big) \\
+&=N (X'X)^{-1} \Big(x_i(|\nu_i|-x_i' \gamma) - E[sign(\nu_i)] (x_i \nu_i)  \Big) \\
+&=N (X'X)^{-1} x_i \Big( |\nu_i| - E[sign(\nu_i)] \nu_i -x_i' \gamma \Big) 
 \end{aligned}
@@
 
-# References {-}
+However,
+
+$$\begin{aligned}
+|\nu_i| &= \nu_i \times \mathbb{1}(\nu_i \geq 0) - \nu_i \times \mathbb{1}(\nu_i < 0) \\
+|\nu_i| &= \nu_i \times \mathbb{1}(\nu_i \geq 0) - \nu_i \times [1-\mathbb{1}(\nu_i \geq 0)] \\
+|\nu_i| &= 2 \nu_i \times \mathbb{1}(\nu_i \geq 0) - \nu_i  
+\end{aligned}
+$$
+
+And
+$$\begin{aligned}
+E[sign(\nu_i)] &= E[\mathbb{1}(\nu_i \geq 0)] - E[\mathbb{1}(\nu_i < 0)] \\
+E[sign(\nu_i)] &= E[\mathbb{1}(\nu_i \geq 0)] - E[(1-\mathbb{1}(\nu_i \geq 0))] \\
+E[sign(\nu_i)] &= 2 E[\mathbb{1}(\nu_i \geq 0)] - 1
+\end{aligned}
+$$
+
+Thus,
+
+$$\begin{aligned}
+\lambda_i(\gamma) &= N(X'X)^{-1} x_i   \Big( 2 \nu_i \times \mathbb{1}(\nu_i \geq 0) - \nu_i  - ( 2 E[\mathbb{1}(\nu_i \geq 0)] - 1) \nu_i -x_i' \gamma \Big) \\
+  &= N(X'X)^{-1} x_i   \Big( 2 \nu_i \times \mathbb{1}(\nu_i \geq 0) -  2 E[\mathbb{1}(\nu_i \geq 0)] \nu_i -x_i' \gamma \Big) \\
+  &= N(X'X)^{-1} x_i   \Big( 2 \nu_i \times \big[ \mathbb{1}(\nu_i \geq 0) -  E[\mathbb{1}(\nu_i \geq 0)] \big] -x_i'\gamma \Big) \\
+  &= N(X'X)^{-1} x_i   \Big( \tilde \nu_i -x_i' 
+  \gamma \Big)
+\end{aligned}
+$$
+
+This last expression is the equivalent simplification used in @mss2019 and @im2000.
+If the scale function is strictly possitive, it also follows that $\mathbb{1}(\nu_i \geq 0)= \mathbb{1}(\varepsilon_i \geq 0)$.
+Thus, it can be simplified as:
+
+$$\begin{aligned}
+\lambda_i(\gamma) &= N(X'X)^{-1} x_i ( x_i' \gamma ) \times (\tilde \varepsilon_i -1\big)
+\end{aligned}
+$$
+
+### Quantile of standardized residual
+
+$$\begin{aligned}
+\lambda_i(q^\varepsilon_\tau)&=\bar G_{3,3}^{-1}
+\Big(
+ h_{3,i}-\bar G_{3,1} \lambda_i(\beta)-\bar G_{3,2} \lambda_i(\gamma)
+\Big) \\
+&=-\frac{1}{f_{\varepsilon}(q^\varepsilon_\tau)} \times \Bigg( \Big(\mathbb{1} ( q^\varepsilon_\tau  \geq \varepsilon  ) - \tau \Big)  \\
+&+ f_{\varepsilon} (q^\varepsilon_\tau) \frac{\bar x_i'}{\bar x_i'\gamma} 
+N (X'X)^{-1} x_i  ( x_i'\gamma \times \varepsilon) \\
+&+ f_{\varepsilon}(q^\varepsilon_\tau) q^\varepsilon_\tau \frac{\bar x_i'}{\bar x_i'\gamma} N(X'X)^{-1} x_i   \big( \tilde \nu_i -x_i' 
+  \gamma \big) 
+\Bigg) \\
+&=\frac{\tau-\mathbb{1}\big( q^\varepsilon_\tau  \geq \varepsilon  \big) }{f_{\varepsilon}(q^\varepsilon_\tau)}
+- \frac{ x_i'\gamma \times \varepsilon_i }{\bar x_i'\gamma} 
+-  q^\varepsilon_\tau \frac{ \tilde \nu_i -x_i' 
+  \gamma }{\bar x_i'\gamma} 
+\end{aligned}
+$$
+
+# References {.unnumbered}

### 2023-10-27 article/article.tex
update
article

@@
 \end{frontmatter}
-    \ifdefined\Shaded\renewenvironment{Shaded}{\begin{tcolorbox}[frame hidden, interior hidden, borderline west={3pt}{0pt}{shadecolor}, boxrule=0pt, enhanced, sharp corners, breakable]}{\end{tcolorbox}}\fi
+    \ifdefined\Shaded\renewenvironment{Shaded}{\begin{tcolorbox}[sharp corners, frame hidden, boxrule=0pt, interior hidden, borderline west={3pt}{0pt}{shadecolor}, enhanced, breakable]}{\end{tcolorbox}}\fi
 
@@
 
-\begin{equation}\protect\hypertarget{eq-eq1}{}{Q(Y|X,\tau) =X\beta(\tau)
+\begin{equation}\protect\hypertarget{eq-eq1}{}{q(Y|X,\tau) =X\beta(\tau)
 }\label{eq-eq1}\end{equation}
@@
 
-\begin{equation}\protect\hypertarget{eq-eq2}{}{Q(Y|X,\tau) =X\beta+X\gamma(\tau)
+\begin{equation}\protect\hypertarget{eq-eq2}{}{q(Y|X,\tau) =X\beta+X\gamma(\tau)
 }\label{eq-eq2}\end{equation}
@@
 
-\begin{equation}\protect\hypertarget{eq-eq4}{}{y_i=x_i'\beta+\varepsilon_i \times x_i'\gamma(\tau)
+\begin{equation}\protect\hypertarget{eq-eq4}{}{\begin{aligned}
+y_i &=x_i'\beta+\nu_i \\
+\nu_i &=\varepsilon_i \times x_i'\gamma 
+\end{aligned}
 }\label{eq-eq4}\end{equation}
@@
 
-\begin{equation}\protect\hypertarget{eq-eq5}{}{Q(Y|X,\tau) =X\beta+X\gamma \times Q(\varepsilon|\tau)
+\begin{equation}\protect\hypertarget{eq-eq5}{}{q(Y|X,\tau) =X\beta+q(\varepsilon|\tau) \times X\gamma 
 }\label{eq-eq5}\end{equation}
@@
 
-\begin{equation}\protect\hypertarget{eq-eq6}{}{\beta(\tau) = \beta + \gamma \times Q(\varepsilon|\tau)
+\begin{equation}\protect\hypertarget{eq-eq6}{}{\beta(\tau) = \beta + q(\varepsilon|\tau) \times \gamma 
 }\label{eq-eq6}\end{equation}
@@
 because the location and scale model can be identified globally, with
-only a single parmater (\(Q(\varepsilon|\tau)\)) requiring local
+only a single parmater (\(q(\varepsilon|\tau)\)) requiring local
 estimation, this estimation approach would be more efficient than the
@@
 approach. And while its possible to identify all coefficients
-(\(\beta,\gamma, Q(\varepsilon|\tau)\)) simultaneously, we describe and
+(\(\beta,\gamma, q(\varepsilon|\tau)\)) simultaneously, we describe and
 use the implementation approach advocated by MSS which identifies each
@@
 \def\labelenumi{\arabic{enumi}.}
+\tightlist
 \item
@@
   following condition:
+\end{enumerate}
+
 \begin{equation}\protect\hypertarget{eq-eq7}{}{\begin{aligned}
-    y_i &=x_i'\beta+u_i \\
-    E[u 'X ] &=0
+      y_i &=x_i'\beta+\nu_i \\
+      E\big[ x_i \nu_i\big] &=0
       \end{aligned}
 }\label{eq-eq7}\end{equation}
+
+\begin{enumerate}
+\def\labelenumi{\arabic{enumi}.}
+\setcounter{enumi}{1}
+\tightlist
 \item
@@
 \begin{equation}\protect\hypertarget{eq-eq8}{}{\begin{aligned}
-  |u_i| &=x_i'\gamma+v_i \\
-  E[ (|u|-X \gamma) X ] &=0
+  |\nu_i| &=x_i'\gamma+\omega_i \\
+  E\big[ x_i \omega_i \big] &=0 \\
+  E\big[ x_i (|\nu_i| -x_i'\gamma ) \big] &=0
   \end{aligned}
@@
 \begin{equation}\protect\hypertarget{eq-eq9}{}{\begin{aligned}
-  E\left[  \mathbb{1}\left(x_i' (\beta + \gamma Q(\varepsilon|\tau)) \geq y_i \right) - \tau \right] &=0  \\
-  E\left[  \mathbb{1}\left(   Q(\varepsilon|\tau)\geq \frac{y_i-x_i'\beta}{x_i'\gamma} \right) - \tau \right] &=0  \\
+  E\left[  \mathbb{1}\left(x_i' (\beta + \gamma q(\varepsilon|\tau)) \geq y_i \right) - \tau \right] &=0  \\
+  E\left[  \mathbb{1}\left(   q(\varepsilon|\tau)\geq \frac{y_i-x_i'\beta}{x_i'\gamma} \right) - \tau \right] &=0  \\
   \end{aligned}
@@
 the values that identify the overall quantile coefficients
-\(\beta(\tau)=\beta + \gamma Q(\varepsilon|\tau)\). Afterwords, the
+\(\beta(\tau)=\beta + \gamma q(\varepsilon|\tau)\). Afterwords, the
 conditional quantile coefficients is simply defined as the combination
@@
 \begin{equation}\protect\hypertarget{eq-eq10}{}{\begin{aligned}
-  E[u_i x_i ] &= E[h_{1,i}]=0 \\
-  E[ (|u_i|-x_i \gamma) x_i ] &=E[h_{2,i}]=0 \\
-  E\left[  \mathbb{1}\left(   Q(\varepsilon|\tau)\geq \frac{y_i-x_i'\beta}{x_i'\gamma} \right) - \tau \right] 
+  E[x_i \nu_i  ] &= E[h_{1,i}]=0 \\
+  E[x_i  (|\nu_i|-x_i \gamma) ] &=E[h_{2,i}]=0 \\
+  E\left[  \mathbb{1}\left(   q(\varepsilon|\tau)\geq \frac{y_i-x_i'\beta}{x_i'\gamma} \right) - \tau \right] 
   &=E[h_{3,i}]=0 
@@
 
-Call \(\theta=[ \beta' \ \ \gamma' \ \ Q(\varepsilon|\tau)' ]'\) the set
-of coefficients that are identified in Equation~\ref{eq-eq10}, a just
-identified model. And the function \(h_i\) is a vector function that
-stacks all the moments at the individual level described in
-Equation~\ref{eq-eq10}. Then \(\hat\theta\) follows a normal
-distribution with mean \(\theta\) and variance-covariance matrix
-\(V(\theta)\) that is estimated as: \[
+Call \(\theta=[ \beta' \ \ \gamma' \ \ q(\varepsilon|\tau)' ]'\) the set
+of coefficients that are identified by the modement conditions in
+Equation~\ref{eq-eq10}, a just identified model. And the function
+\(h_i\) is a vector function that stacks all the moments at the
+individual level described in Equation~\ref{eq-eq10}. Then
+\(\hat\theta\) follows a normal distribution with mean \(\theta\) and
+variance-covariance matrix \(V(\theta)\) that is estimated as:
+
+\[
 \hat{V}(\hat\theta)=\frac{1}{N} 
@@
 
-where the inner product is the moment covariance matrix, and
+Which is equivalent to the Eicker-White Heteroskedastic-Consistent
+estimator for least-squares estimators.
+
+Here, the inner product is the moment covariance matrix, and
 \(\bar{G}(\theta)\) is the Jacobian matrix of the moment equations
@@
 
-This is equivalent to the Eicker-White Heteroskedastic-Consistent
-estimator for least-squares estimators.
-
 In this framework, the quantile regression coefficients, a combination
 of the location-scale-quantile estimates, will follow a normal
-distribution with mean \(\beta(\tau) = \beta+Q(\varepsilon,\tau)\gamma\)
+distribution with mean \(\beta(\tau) = \beta+q(\varepsilon|\tau)\gamma\)
 and variance-covariance matrix equal to:
@@
 
-\[\Xi = [ I(k), \hat Q(\varepsilon|\tau) \cdot I(k), \hat \gamma ]
+\[\Xi = [ I(k), \hat q(\varepsilon|\tau) \times I(k), \hat \gamma ]
 \]
@@
 
+While it is possible to estimate the variance-covariance matrix using
+simultaneous model estimation, for a just identified model, it is more
+efficient to estimate each set of coefficients separately. The
+variance-covariance matrix can be estimated using the empirical
+influence functions of the estimators (see \citet{jann_2020} for an
+overview of the application, and \citet{hampel2005} for an in-depth
+review).
+
+\begin{enumerate}
+\def\labelenumi{\arabic{enumi}.}
+\tightlist
+\item
+  Need to add the general condition Var=(inf (theta) * inf(theta))
+\end{enumerate}
+
+Thatn inf(theta) = inf beta gamma and q)tay
+
+and finally define what the IFs are (see appendix)
+
 The different types of Standard errors estimation, thus, depend on the
 assumptions imposed for the estimation of \(V(\theta)\).
+
+\hypertarget{robust-standard-errors}{%
+\subsubsection{Robust Standard Errors}\label{robust-standard-errors}}
+
+Cross product of IFs
+
+\hypertarget{clustered-standard-errors}{%
+\subsubsection{Clustered Standard
+Errors}\label{clustered-standard-errors}}
+
+Sun then cross product
+
+\hypertarget{gls-standard-errors}{%
+\subsubsection{GLS Standard Errors}\label{gls-standard-errors}}
+
+Original paper;
 
@@
 
+\hypertarget{model-identification}{%
+\subsection{Model Identification}\label{model-identification}}
+
 The estimation of quantile regression via moments assumes that the DGP
@@
 
-\[q(y|\tau,X) = x(\beta + q(e|\tau) \times \gamma)\]
+\[q(y|\tau,X) = x(\beta + q(\varepsilon |\tau) \times \gamma)\]
 
@@
 
+For simplicity, for the rest of the appendix, I will use
+\(q^\varepsilon_\tau\) to represent \(q(\varepsilon |\tau)\).
+
+\hypertarget{estimation-of-the-variance-covariance-matrix}{%
+\subsection{Estimation of the variance-covariance
+matrix}\label{estimation-of-the-variance-covariance-matrix}}
+
 In this model, to estimate the variance-covariance matrix the set of
-coefficients \(\theta'=[\beta' \ \gamma' \ q(\varepsilon|\tau)']\), we
+coefficients \(\theta'=[\beta' \ \gamma' \ q^\varepsilon_\tau]\), we
 need to obtain the influence functions of all coefficients, which are
@@
 
-\[h_{3,i} = \mathbb{1}\left( q(\varepsilon|\tau) x_i'\gamma +x_i'\beta - y_i \geq 0 \right) - \tau\]
+\[\begin{aligned}
+h_{3,i} &= \mathbb{1}\left( q^\varepsilon_\tau x_i'\gamma +x_i'\beta - y_i \geq 0 \right) - \tau \text{ or}\\
+h_{3,i} &= \mathbb{1}\left( q^\varepsilon_\tau  \geq \frac{y_i- x_i'\beta}{x_i'\gamma}  \right) - \tau = \mathbb{1}\big( q^\varepsilon_\tau  \geq \varepsilon  \big) - \tau \\
+\end{aligned}
+\]
 
@@
 
-\[h_{3,i} \approx I\left( q(\varepsilon|\tau) x_i'\gamma +x_i'\beta - y_i  \right) - \tau\]
+\[h_{3,i} \approx I\left( q^\varepsilon_\tau x_i'\gamma +x_i'\beta - y_i  \right) - \tau\]
 
@@
 combination of \(x\), and of multiplicative heteroskedasticity, we have:
+
 \[\begin{aligned}
-E(K_h(q(\varepsilon|\tau) x_i'\gamma +x_i'\beta - y_i )|X) &= f_{y|X}(q(\varepsilon|\tau) x_i'\gamma +x_i'\beta) \\
-f_{y|X}(q(\varepsilon|\tau) x_i'\gamma +x_i'\beta) &= f_{\frac{y-x_i'\beta}{x_i\gamma|X}(q(\varepsilon|\tau))
+E(K_h(q^\varepsilon_\tau x_i'\gamma +x_i'\beta - y_i )|X) &= f_{y|X}(q^\varepsilon_\tau x_i'\gamma +x_i'\beta) \\
+&=\frac{1}{x_i'\gamma} f_{\varepsilon}(q^\varepsilon_\tau) \\
 \end{aligned}
@@
 where \(f_{y|X}\) is the conditional probability density function of
-\(y\) given \(X\). With this, we can rewrite the Jacobian matrix as:
+\(y\) given \(X\), and \(f_\varepsilon\) is the unconditional
+distribution of the standardized error. With this, we can rewrite the
+Jacobian matrix as:
+
+\[\bar G_{3,1} = -N^{-1} f_{\varepsilon}\big(q^\varepsilon_\tau\big) \sum  \frac{x_i'}{x_i'\gamma} 
+\]
+
+Asymptotically, however, the expression \(\sum\frac{a_i}{b_i}\) can be
+approximated using taylor expansions by \(N\frac{\bar a}{\bar b}\).
+\footnote{This approximation will be useful when we consider the
+  estimation of the influence functions.} Thus, we can rewrite the last
+term as:
+
+\[\bar G_{3,1} = - f_{\varepsilon}\big(q^\varepsilon_\tau\big) \frac{\bar x_i'}{\bar x_i'\gamma} 
+\]
+
+The Jacobian for the second matrix \(\bar G_{3,2}\) can be derived
+similarly:
 
 \[\begin{aligned}
-\bar G_{3,1} &= -N^{-1} \sum f_{y|X}(q(\varepsilon|\tau) x_i'\gamma +x_i'\beta ) x_i'
+\bar G_{3,2} &= -\frac{1}{N} \sum \frac{\partial h_{3,i}}{\partial \gamma'} \\
+             &= -N^{-1} \sum K_h(q^\varepsilon_\tau x_i'\gamma +x_i'\beta - y_i ) q^\varepsilon_\tau x_i' \\
+             &=-N^{-1} \sum f_{y|x}(q^\varepsilon_\tau x_i'\gamma +x_i'\beta ) q^\varepsilon_\tau x_i' \\
+             &=-N^{-1} f_{\varepsilon}(q^\varepsilon_\tau) q^\varepsilon_\tau \sum \frac{x_i'}{x_i'\gamma} \\
+             &=- f_{\varepsilon}(q^\varepsilon_\tau) q^\varepsilon_\tau \frac{\bar x_i'}{\bar x_i'\gamma}
+\end{aligned}
+\]
+
+and the Jacobian for the third matrix \(\bar G_{3,3}\) is:
+
+\[\begin{aligned}
+\bar G_{3,3} &= -\frac{1}{N} \sum \frac{\partial h_{3,i}}{\partial q^\varepsilon_\tau} \\
+ &= -\frac{1}{N} \sum K_h(q^\varepsilon_\tau x_i'\gamma +x_i'\beta - y_i ) x_i'\gamma \\
+ &= -\frac{1}{N} \sum f_{y|X}(q^\varepsilon_\tau x_i'\gamma +x_i'\beta) x_i'\gamma \\
+ &= -\frac{1}{N} \sum f_{\varepsilon}(q^\varepsilon_\tau) \frac{x_i'\gamma}{ x_i'\gamma} \\
+ &= - f_{\varepsilon}(q^\varepsilon_\tau) 
+\end{aligned}
+\]
+
+\hypertarget{influence-functions}{%
+\subsection{Influence functions}\label{influence-functions}}
+
+\hypertarget{location-coefficients}{%
+\subsubsection{Location coefficients}\label{location-coefficients}}
+
+\[\lambda_i(\beta) = \bar G^{-1}_{1,1} h_{1,i} = N (X'X)^{-1}(x_i (y_i-x_i'\beta)) = N (X'X)^{-1}(x_i \nu_i)
+\]
+
+Which can also be written as a function of the standardized residuals:
+
+\[\lambda_i(\beta) = \bar G^{-1}_{1,1} h_{1,i} = N (X'X)^{-1}(x_i (y_i-x_i'\beta)) = N (X'X)^{-1}(x_i ( x_i'\gamma \times \varepsilon))
+\]
+
+\hypertarget{scale-coefficients-coefficients}{%
+\subsubsection{Scale Coefficients
+coefficients**}\label{scale-coefficients-coefficients}}
+
+\[\begin{aligned}
+\lambda_i(\gamma)&=\bar G_{2,2}^{-1}\Big(h_{2,i}-\bar G_{2,1} \lambda_i(\beta)\Big) \\
+&=N (X'X)^{-1} \Big(x_i(|\nu_i|-x_i' \gamma) 
+- N^{-1} E[sign(\nu_i)] X'X \big[ N (X'X)^{-1}(x_i \nu_i) \big] \Big) \\
+&=N (X'X)^{-1} \Big(x_i(|\nu_i|-x_i' \gamma) - E[sign(\nu_i)] (x_i \nu_i)  \Big) \\
+&=N (X'X)^{-1} x_i \Big( |\nu_i| - E[sign(\nu_i)] \nu_i -x_i' \gamma \Big) 
+\end{aligned}
+\]
+
+However,
+
+\[\begin{aligned}
+|\nu_i| &= \nu_i \times \mathbb{1}(\nu_i \geq 0) - \nu_i \times \mathbb{1}(\nu_i < 0) \\
+|\nu_i| &= \nu_i \times \mathbb{1}(\nu_i \geq 0) - \nu_i \times [1-\mathbb{1}(\nu_i \geq 0)] \\
+|\nu_i| &= 2 \nu_i \times \mathbb{1}(\nu_i \geq 0) - \nu_i  
+\end{aligned}
+\]
+
+And \[\begin{aligned}
+E[sign(\nu_i)] &= E[\mathbb{1}(\nu_i \geq 0)] - E[\mathbb{1}(\nu_i < 0)] \\
+E[sign(\nu_i)] &= E[\mathbb{1}(\nu_i \geq 0)] - E[(1-\mathbb{1}(\nu_i \geq 0))] \\
+E[sign(\nu_i)] &= 2 E[\mathbb{1}(\nu_i \geq 0)] - 1
+\end{aligned}
+\]
+
+Thus,
+
+\[\begin{aligned}
+\lambda_i(\gamma) &= N(X'X)^{-1} x_i   \Big( 2 \nu_i \times \mathbb{1}(\nu_i \geq 0) - \nu_i  - ( 2 E[\mathbb{1}(\nu_i \geq 0)] - 1) \nu_i -x_i' \gamma \Big) \\
+  &= N(X'X)^{-1} x_i   \Big( 2 \nu_i \times \mathbb{1}(\nu_i \geq 0) -  2 E[\mathbb{1}(\nu_i \geq 0)] \nu_i -x_i' \gamma \Big) \\
+  &= N(X'X)^{-1} x_i   \Big( 2 \nu_i \times \big[ \mathbb{1}(\nu_i \geq 0) -  E[\mathbb{1}(\nu_i \geq 0)] \big] -x_i'\gamma \Big) \\
+  &= N(X'X)^{-1} x_i   \Big( \tilde \nu_i -x_i' 
+  \gamma \Big)
+\end{aligned}
+\]
+
+This last expression is the equivalent simplification used in
+\citet{mss2019} and \citet{im2000}. If the scale function is strictly
+possitive, it also follows that
+\(\mathbb{1}(\nu_i \geq 0)= \mathbb{1}(\varepsilon_i \geq 0)\). Thus, it
+can be simplified as:
+
+\[\begin{aligned}
+\lambda_i(\gamma) &= N(X'X)^{-1} x_i ( x_i' \gamma ) \times (\tilde \varepsilon_i -1\big)
+\end{aligned}
+\]
+
+\hypertarget{quantile-of-standardized-residual}{%
+\subsubsection{Quantile of standardized
+residual}\label{quantile-of-standardized-residual}}
+
+\[\begin{aligned}
+\lambda_i(q^\varepsilon_\tau)&=\bar G_{3,3}^{-1}
+\Big(
+ h_{3,i}-\bar G_{3,1} \lambda_i(\beta)-\bar G_{3,2} \lambda_i(\gamma)
+\Big) \\
+&=-\frac{1}{f_{\varepsilon}(q^\varepsilon_\tau)} \times \Bigg( \Big(\mathbb{1} ( q^\varepsilon_\tau  \geq \varepsilon  ) - \tau \Big)  \\
+&+ f_{\varepsilon} (q^\varepsilon_\tau) \frac{\bar x_i'}{\bar x_i'\gamma} 
+N (X'X)^{-1} x_i  ( x_i'\gamma \times \varepsilon) \\
+&+ f_{\varepsilon}(q^\varepsilon_\tau) q^\varepsilon_\tau \frac{\bar x_i'}{\bar x_i'\gamma} N(X'X)^{-1} x_i   \big( \tilde \nu_i -x_i' 
+  \gamma \big) 
+\Bigg) \\
+&=\frac{\tau-\mathbb{1}\big( q^\varepsilon_\tau  \geq \varepsilon  \big) }{f_{\varepsilon}(q^\varepsilon_\tau)}
+- \frac{ x_i'\gamma \times \varepsilon_i }{\bar x_i'\gamma} 
+-  q^\varepsilon_\tau \frac{ \tilde \nu_i -x_i' 
+  \gamma }{\bar x_i'\gamma} 
 \end{aligned}

### 2023-10-30 article/article.qmd
mmqreg
update

@@
       cite-style: authoryear
+      number-depth: 2
+
 ---
@@
 However, as described in @neymanscott1948, and @lancaster2000, when individual fixed effects are included in quantile regression analysis it generates an incident parameter problem.
-While many strategies have been proposed for estimating this type of model (see Galvão and Kato, 2018 for a brief review), neither has become standard because of their restrictive assumptions in regards to the individual effects, the computational complexity, and implementation.
+While many strategies have been proposed for estimating this type of model (see @galvao2017quantile for a brief review), neither has become standard because of their restrictive assumptions in regards to the individual effects, the computational complexity, and implementation.
 
@@
 
-In principle, under the assumption that data generating process behind the data is based on a multiplicative heteroskedastic process that is linear in parameters (@cameron2005, @mss2019, @he1997 and @zhao2000 ), the effect of a variable $X$ on the $q_th$ quantile can be derived as the combination of a location effect, and scale effect moderated by the quantile of an underlying i.i.d.
+In principle, under the assumption that data generating process behind the data is based on a multiplicative heteroskedastic process that is linear in parameters [@cameron2005, @mss2019, @he1997,  @zhao2000], the effect of a variable $X$ on the $q_{th}$ quantile can be derived as the combination of a location effect, and scale effect moderated by the quantile of an underlying i.i.d.
 error.
@@
 \left( \sum_{i\in y_i\geq x_i'\beta} \tau (y_i - x_i'\beta) - \sum_{i\in y_i<x_i'\beta} (1-\tau)(y_i - x_i'\beta) \right)
-$$ {#eq-eq3}
+$${#eq-eq3}
 
@@
 
-In this setup, the traditional quantile coefficients are identified as the location model coefficients, plus the scale model coefficients moderated by the $\tau_th$ unconditional quantile of the standardized error $\varepsilon$.
+In this setup, the traditional quantile coefficients are identified as the location model coefficients, plus the scale model coefficients moderated by the $\tau_{th}$ unconditional quantile of the standardized error $\varepsilon$.
 
@@
 While this specification imposes a strong assumption on the DGP, it has two advantages over the standard quantile regression model.
-First, because the location and scale model can be identified globally, with only a single parmater ($q(\varepsilon|\tau)$) requiring local estimation, this estimation approach would be more efficient than the standard quantile regression model (@zhao2000).
+First, because the location and scale model can be identified globally, with only a single paramater ($q(\varepsilon|\tau)$) requiring local estimation, this estimation approach would be more efficient than the standard quantile regression model (@zhao2000).
 Second, under the assumption that $X\gamma$ is strictly possitive, the model would produce quantile coefficients that do not cross.
@@
 
-3.  Finally, given the location and scale coefficients, the $\tau_{th}$ quantile of the error $e$ can be estimated using the following condition:
+3.  Finally, given the location and scale coefficients, the $\tau_{th}$ quantile of the error $\varepsilon$ can be estimated using the following condition:
 
@@
 
-Here, the inner product is the moment covariance matrix, and $\bar{G}(\theta)$ is the Jacobian matrix of the moment equations (@eq-eq10) evaluated at $\hat\theta$.
+Here, the inner product is the moment covariance matrix, and $\bar{G}(\theta)$ is the Jacobian matrix of the moment equations evaluated at $\hat\theta$.
 
@@
 $$\Xi = [ I(k), \hat q(\varepsilon|\tau) \times I(k), \hat \gamma ]
-$$
+$${#eq-eqqtile}
 
@@
 While it is possible to estimate the variance-covariance matrix using simultaneous model estimation, for a just identified model, it is more efficient to estimate each set of coefficients separately.
-The variance-covariance matrix can be estimated using the empirical influence functions of the estimators (see @jann_2020 for an overview of the application, and @hampel2005 for an in-depth review).
+Afterwards, the variance-covariance matrix can be estimated using the empirical influence functions of the estimators (see @jann_2020 for an overview of the application, and @hampel2005 for an in-depth review).
 
-1. Need to add the general condition Var=(inf (theta) * inf(theta))
+Specifically, given an arbitrary vector of empirical influence functions $\lambda_i(\theta)$, the variance-covariance matrix can be estimated as:
+$$\hat{V}(\theta) = \frac{1}{N^2} \sum_{i=1}^N \lambda_i(\theta) \lambda_i(\theta)'
+$${#eq-eqvcv}
 
-Thatn inf(theta) = inf beta gamma and q)tay
+where the influence functions are defined as:
 
-and finally define what the IFs are (see appendix)
+$$\lambda_i(\theta) = \bar G(\theta)^{-1} h_i(\theta)$$
+
+For the specific case of quantile regressions via momoments, the influence functions for the location, scale and quantile coefficients are:[^7]
+
+[^7]: The derivation of the influence functions can be found in @sec-appendix.
+
+$$\begin{aligned}
+\lambda_i(\theta)&=
+  \begin{bmatrix}
+  \lambda_{i}(\beta) \\
+  \lambda_{i}(\gamma) \\
+  \lambda_{i}(q(\varepsilon|\tau)) 
+  \end{bmatrix} \\
+\lambda_{i}(\beta)&=N (X'X)^{-1}  x_i ( x_i'\gamma) \times \varepsilon_i \\
+\lambda_{i}(\gamma)&= N(X'X)^{-1} x_i ( x_i' \gamma ) \times (\tilde \varepsilon_i -1\big)\\
+\lambda_{i}(q(\varepsilon|\tau))&=\frac{\tau-\mathbb{1}\big( q(\varepsilon|\tau)  \geq \varepsilon_i  \big) }{f_{\varepsilon}(q(\varepsilon|\tau))}
+- \frac{ x_i'\gamma \times \varepsilon_i }{\bar x_i'\gamma} 
+-  q(\varepsilon|\tau) \frac{  x_i' \gamma  \times (\tilde \varepsilon_i -1\big)}{\bar x_i'\gamma}
+\end{aligned}
+$${#eq-ifs}
 
@@
 
-Cross product of IFs
+The first, and most natural standard error estimator is given by equation @eq-eqvcv.
+This is equivalent to the Eicker-White Heteroskedastic-Consistent estimator for least-squares estimators.
+Considering the location-scale model, the variance-covariance matrix for the quantile coefficients can be estimated as:
+
+$$\hat{V}_{robust}
+  \begin{pmatrix}
+  \hat\beta \\
+  \hat\gamma \\
+  \hat q(\varepsilon|\tau)
+  \end{pmatrix}
+ = \frac{1}{N^2} 
+ \begin{pmatrix}
+ \sum \lambda_i(\beta) \lambda_i(\beta)' & \sum \lambda_i(\beta) \lambda_i(\gamma)' & \sum \lambda_i(\beta) \lambda_i(q(\varepsilon|\tau))' \\
+ \sum \lambda_i(\gamma) \lambda_i(\beta)' & \sum \lambda_i(\gamma) \lambda_i(\gamma)' & \sum \lambda_i(\gamma) \lambda_i(q(\varepsilon|\tau))' \\
+ \sum \lambda_i(q(\varepsilon|\tau) \lambda_i(\beta)' & \sum \lambda_i(q(\varepsilon|\tau))\lambda_i(\gamma)' & \sum \lambda_i(q(\varepsilon|\tau)) \lambda_i(q(\varepsilon|\tau))' 
+  \end{pmatrix}
+$$
+
+This estimator of Standard errors should be robust to arbitrary heteroskedasticity.
+However, because the location-scale specification relies on the correct specification of the model heteroskedasticity, large differences in Standard errors compared to GLS-standard errors may be an indication of misspecification of the model.
 
@@
 
-Sun then cross product
+Because one of the typical applications of quantile regressions is the analysis of panel data, allowing for clustered standard errors at the individual level is important.
+If the unobserved error $\varepsilon$ is correlated within clusters, GLS-Standard errors could be severily biased.
+The standard recommendation has been to report block-bootstrap standard errors, clustering at the individual level.
+
+Since we have access to the influence functions, it is straight forward to estimate one-way clustered standard errors.
+
+Call $N_G$ to be the total number of clusteres g, where $g=1\dots N_G$. The clustered variance covariance matrix is given by:[^10]
+
+[^10]: It should be noted that one could just as well apply the insights of @cameron_robust_2011, allowing for multiway clustering.
+
+$$\hat{V}_{clustered}
+  \begin{pmatrix}
+  \hat\beta \\
+  \hat\gamma \\
+  \hat q(\varepsilon|\tau)
+  \end{pmatrix}
+ = \frac{1}{N^2} 
+ \begin{pmatrix}
+ \sum_{g=1}^{N_G} S\lambda_i(\theta) S\lambda_i(\theta)'
+  \end{pmatrix}
+$$
+
+Where $S\lambda_i(\theta)$ is the sum of the influence functions over all observations within a given cluster $g$.
+
+$$S\lambda_i(\theta) = \sum_{i\in g} \lambda_i(\theta)
+$$
 
@@
 
-Original paper;
+The standard errors proposed by MSS can be understood as an application of generalized least squares (GLS), which will be valid as long as the model for heteroskedasticity is correctly specified.[^15] To estimate the GLS-Standard errors, we make use of the following property:
+
+[^15]: As discussed in most econometric textbooks, like @cameron2005, one approach to correct for heteroskedasticity, when the heteroskedasticity functional form is known, or can be estimated, is to use weighted least squares.
+While feasible, however, this approach would defeat the purpose of identifying quantile effects exploiting the heteroskedasticity of the model.
+
+Consider the influence functions and robust variance-covariance matrix for the location coefficients:
+
+$$\begin{aligned}
+\hat V(\hat \beta) &= \frac{1}{N} \sum_i^N \lambda_{i}(\beta) \lambda_{i}(\beta)' \\
+&= \frac{1}{N}  (X'X)^{-1}  \sum_i^N x_i x_i' ( x_i'\gamma \times \varepsilon_i)^2 (X'X)^{-1} \\
+\end{aligned}
+$$
+
+Under the assumption that the model for heteroskedasticity is correctly specified, we can apply the law of iterated expectations and rewrite the variance-covariance matrix as:
+
+$$\begin{aligned}
+\hat V(\hat \beta) &= \frac{1}{N} \sum_i^N \lambda_{i}(\beta) \lambda_{i}(\beta)' \\
+&= E(\varepsilon_i^2) \frac{1}{N}  (X'X)^{-1}  \sum_i^N x_i x_i' ( x_i'\gamma)^2 (X'X)^{-1} \\
+&= \sigma^2_{\varepsilon} \frac{1}{N}  (X'X)^{-1}  \hat\Omega_{\beta\beta} (X'X)^{-1}  
+\end{aligned}
+$$
+
+This standard error estimator is an application of GLS that accounts for the heteroskedasticity the model uses to identify the quantile coefficients.
+We can apply the same principle to find the GLS-Standard errors for the system of location-scale and quantile coefficients.
+To do this, define the following modified influence functions:
+
+$$\begin{aligned}
+\tilde \lambda_{1,i}&=\tilde \lambda_{2,i}=N (X'X)^{-1}  x_i ( x_i'\gamma) \\  
+\tilde \lambda_{3,i}&=x_i' \gamma  \\
+\tilde \psi_1 &= \varepsilon_i \\
+\tilde \psi_2 &= \tilde \varepsilon_i -1 \\
+\tilde \psi_3 &= \frac{1}{ x_i' \gamma }\frac{\tau-\mathbb{1}\big( q(\varepsilon|\tau)  \geq \varepsilon_i  \big) }{ f_{\varepsilon}(q(\varepsilon|\tau))} - \frac{\varepsilon_i }{\bar x_i'\gamma} 
+-  q(\varepsilon|\tau) \frac{(\tilde \varepsilon_i -1\big)}{\bar x_i'\gamma}
+\end{aligned}
+$$
+
+Then, the GLS-Standard errors for the location-scale and quantile coefficients can be estimated as:
+
+$$\hat{V}_{gls}
+  \begin{pmatrix}
+  \hat\beta \\
+  \hat\gamma \\
+  \hat q(\varepsilon|\tau)
+  \end{pmatrix}
+ = \frac{1}{N^2} 
+ \begin{pmatrix}
+ \hat\sigma_{11} \hat\Omega_{11} & \hat\sigma_{12} \hat\Omega_{12} & \hat\sigma_{11} \hat\Omega_{13} \\
+ \hat\sigma_{21} \hat\Omega_{21} & \hat\sigma_{22} \hat\Omega_{22} & \hat\sigma_{21} \hat\Omega_{23} \\
+ \hat\sigma_{31} \hat\Omega_{31} & \hat\sigma_{32} \hat\Omega_{32} & \hat\sigma_{33} \hat\Omega_{33}
+  \end{pmatrix}
+$$
+
+where
+
+$$\begin{aligned}
+\hat\Omega_{ij} &= \frac{1}{N} \sum_i^N \tilde \lambda_{i}(\theta) \tilde \lambda_{j}(\theta)' \\
+\hat\sigma_{ij} &= \frac{1}{N} \sum_i^N \phi_{i} \phi_{j}
+\end{aligned}
+$$
+
+This estimator of Standard errors is equivalent to the one derived by MSS by Theorem 3.
 
@@
 
-2.  We estimate the location model using the centered-residualized variables:
+2.  We estimate the location model using the centered-residualized variables:[^rc]
 
-$$y_{i}^{rc} = x_{i}^{rc'} \beta + nu_{i}
+$$y_{i}^{rc} = x_{i}^{rc'} \beta + \nu_{i}
 $$
+
+[^rc]: Using centered-residualized variables allow us to include a constant in the model specification, which simplifies the derivation of the influence functions.
+However, as with other fixed effects models, the constant is not identified, and thus should not be interpreted.
 
@@
 
-$$|\hat\nu_{i}|^{rc} = x_{i}^{rc'} \gamma + e_{i}$$
+$$|\hat\nu_{i}|^{rc} = x_{i}^{rc'} \gamma + \omega_{i}$$
 
@@
 
-$$\hat{\varepsilon}_{i} = \frac{\nu_{i}}{|\hat\nu_{i}|- \hat e_{i}}$$
+$$\hat{\varepsilon}_{i} = \frac{\nu_{i}}{|\hat\nu_{i}|- \hat \omega_{i}}$$
 
-where $|\hat\nu_{i}|- \hat e_{i}$ is the prediction for the conditional standard deviation $\sigma(x_i)=x_{i}' \gamma + \zeta_{g1} + \zeta_{g2}$
+where $|\hat\nu_{i}|- \hat \omega_{i}$ is the prediction for the conditional standard deviation $\sigma(x_i)=x_{i}' \gamma + \zeta_{g1} + \zeta_{g2}$
 
@@
 
-# Monte Carlo Simulations
+# Simulation Evidence
 
-# Application: **Something interesting**
+To show the performance of the extended strategy, we implement the results of a small simulation study.
+We consider a simple model with a single explanatory variable $x$, and a single fixed effect $g$.
+The data generating process is as follows:
+
+# Illustrative application
+
+In this section we replicate one of the excercises from MSS, allowing for time and individual fixed effects, as well as for different standard errors estimations.
+We use data from @persson_economic_2005, to estimate the relationship between surplus of goverment as share of GDP, and a measure of quality of democracy (POLITY); log of real income per capita (LYP); trade volume as share of GDP (TRADE), Share of population between 15-65 uears of age (P1564), the share of the population 65 years or older (P65); one-year lag of the dependent variable (LSP); oil prices in US dollars differntiating importer and exported countries (OILIM and OILEX); and the output gap (YGAP).
+In addition to country fixed effects (as illustrated in MSS), we also show results allowing for time fixed effects.
+@tbl-tb1 and  @tbl-tb2 provide the results for the model with and without time fixed effects, respectively.
+It show cases the location and scale coefficients, as well as the quantile coefficients for the 25th, 50th and 75th quantiles.
+We also report GLS-Standard errors, Robust standard errors (brackets) and clustered standard errors at the country level.
+
+|            | polityt |       lyp |     trade |   p1564 |     p65 |      lspl |    oil\_im |    oil\_ex |      ygap |
+| ---------- | :-------: | :-------: | :-------: | :-------: | :-------: | :-------: | :-------: | :-------: | :-------: |
+| Location   |           |           |           |           |           |           |           |           |           |
+| \ coeff      |     0.116 |    -0.715 |     0.030 |     0.121 |     0.028 |     0.691 |    -0.047 |    -0.006 |     0.010 |
+| \ se\_gls     |     0.046 |     0.540 |     0.008 |     0.033 |     0.070 |     0.035 |     0.008 |     0.022 |     0.028 |
+| \ se\_r       |     0.047 |     0.597 |     0.008 |     0.031 |     0.070 |     0.037 |     0.007 |     0.017 |     0.021 |
+| \ se\_cl      |     0.046 |     0.465 |     0.007 |     0.032 |     0.071 |     0.035 |     0.010 |     0.020 |     0.023 |
+| Scale      |           |           |           |           |           |           |           |           |           |
+| \ coeff      |    -0.097 |    -0.616 |     0.003 |     0.036 |     0.087 |    -0.085 |     0.013 |     0.016 |    -0.004 |
+| \ se\_gls     |     0.032 |     0.371 |     0.005 |     0.023 |     0.048 |     0.024 |     0.006 |     0.015 |     0.019 |
+| \ se\_r       |     0.031 |     0.398 |     0.005 |     0.020 |     0.049 |     0.025 |     0.005 |     0.010 |     0.015 |
+| \ se\_cl      |     0.048 |     0.800 |     0.008 |     0.031 |     0.067 |     0.029 |     0.004 |     0.010 |     0.012 |
+| Q25        |           |           |           |           |           |           |           |           |           |
+| \ coeff      |     0.191 |    -0.239 |     0.028 |     0.093 |    -0.039 |     0.756 |    -0.057 |    -0.018 |     0.013 |
+| \ se\_gls     |     0.059 |     0.684 |     0.010 |     0.042 |     0.088 |     0.045 |     0.010 |     0.027 |     0.035 |
+| \ se\_r       |     0.056 |     0.656 |     0.008 |     0.036 |     0.086 |     0.040 |     0.010 |     0.020 |     0.025 |
+| \ se\_cl      |     0.073 |     0.687 |     0.006 |     0.041 |     0.098 |     0.023 |     0.010 |     0.021 |     0.029 |
+| Q50        |           |           |           |           |           |           |           |           |           |
+| \ coeff      |     0.108 |    -0.765 |     0.030 |     0.124 |     0.035 |     0.684 |    -0.046 |    -0.005 |     0.009 |
+| \ se\_gls     |     0.046 |     0.535 |     0.007 |     0.033 |     0.069 |     0.035 |     0.008 |     0.022 |     0.027 |
+| \ se\_r       |     0.046 |     0.593 |     0.008 |     0.031 |     0.069 |     0.036 |     0.007 |     0.017 |     0.021 |
+| \ se\_cl      |     0.043 |     0.484 |     0.008 |     0.032 |     0.070 |     0.036 |     0.010 |     0.020 |     0.023 |
+| Q75        |           |           |           |           |           |           |           |           |           |
+| \ coeff      |     0.031 |    -1.258 |     0.033 |     0.153 |     0.104 |     0.616 |    -0.036 |     0.008 |     0.006 |
+| \ se\_gls     |     0.048 |     0.551 |     0.008 |     0.034 |     0.071 |     0.036 |     0.008 |     0.022 |     0.028 |
+| \ se\_r       |     0.049 |     0.696 |     0.009 |     0.034 |     0.075 |     0.043 |     0.007 |     0.018 |     0.023 |
+| \ se\_cl      |     0.039 |     0.919 |     0.012 |     0.041 |     0.079 |     0.055 |     0.010 |     0.022 |     0.020 |
+
+: The determinants of government surpluses: Individual Fixed effects {#tbl-tb1}
+
+As expected, @tbl-tb1 shows that point estimates for the point estimates for the quantile regressions are identical to the ones reported in @mss2019 (table 6), including analytical standard errors (GLS).
+With our estimator, however, we are able to also produce both robust and clustered standard errors for location and scale coefficients.
+Except for few cases, Robust and Clustered standard errors are larger than GLS standard errors, which may be an indication of misspecification of the model.
+The GLS standard errors we report differ from the ones in MSS, because they use panel standard errors, equivalent to our clustered standard errors, instead of the analytical standard errors we derive.
+
+Considering the estimated effects across quantiles, we observe few differences in the reported GLS standard errors compared to the analytical standard errors reported MSS.
+Our clustered standard errors, however, are closer to the bootstrap based standard errors the authors report.[^20]
+
+[^20]: There are two possible reasons that may explain the differences in the GLS standard errors.
+On the one hand, in our derivation, the influence function of the standardized $\tau_{th}$ quantile (see #eq-infs) does not have the same leading term as the one reported in MSS (see theorem 3, and the definition of $W$).
+
+In @tbl-tb2, we report the results including both individual and year fixed effects.
+Because Oil prices only vary across years, the variableis excluded from the model specification.
+Accounting for time fixed effects, does not change the general conclusions one could make based no the results from @tbl-tb1.
+The two largest differences are that the log of income percapita has a positive effect on Goverment Surpluses, but only for the 25th quantile, because of the largest impact on the Scale component.
+Similarly, we observe that the income gap now has an impact on Goverment surplus that is always negative, but increasing across quantiles.
+In both instances, the effects are not statistically significant.
+
+|            | polity |       lyp |     trade |  prop1564 |    prop65 |      lspl |      ygap |
+| ---------- | :-------: | :-------: | :-------: | :-------: | :-------: | :-------: | :-------: |
+| Location   |           |           |           |           |           |           |           |
+| \ coeff      |     0.126 |    -0.418 |     0.028 |     0.108 |     0.042 |     0.693 |    -0.014 |
+| \ se\_gls     |     0.087 |     1.157 |     0.015 |     0.072 |     0.136 |     0.066 |     0.053 |
+| \ se\_r       |     0.047 |     0.703 |     0.008 |     0.038 |     0.068 |     0.038 |     0.022 |
+| \ se\_cl      |     0.048 |     0.506 |     0.008 |     0.044 |     0.077 |     0.037 |     0.022 |
+| Scale      |           |           |           |           |           |           |           |
+| \ coeff      |    -0.095 |    -1.255 |     0.005 |     0.033 |     0.040 |    -0.081 |     0.008 |
+| \ se\_gls     |     0.081 |     1.073 |     0.014 |     0.067 |     0.126 |     0.061 |     0.049 |
+| \ se\_r       |     0.031 |     0.452 |     0.005 |     0.025 |     0.045 |     0.025 |     0.017 |
+| \ se\_cl      |     0.041 |     0.848 |     0.006 |     0.030 |     0.048 |     0.033 |     0.013 |
+| Q25        |           |           |           |           |           |           |           |
+| \ coeff      |     0.201 |     0.576 |     0.025 |     0.082 |     0.010 |     0.757 |    -0.020 |
+| \ se\_gls     |     0.154 |     2.070 |     0.024 |     0.118 |     0.219 |     0.121 |     0.085 |
+| \ se\_r       |     0.058 |     0.751 |     0.008 |     0.049 |     0.080 |     0.040 |     0.026 |
+| \ se\_cl      |     0.073 |     0.761 |     0.006 |     0.052 |     0.087 |     0.023 |     0.027 |
+| Q50        |           |           |           |           |           |           |           |
+| \ coeff      |     0.119 |    -0.512 |     0.029 |     0.111 |     0.045 |     0.687 |    -0.013 |
+| \ se\_gls     |     0.091 |     1.230 |     0.014 |     0.070 |     0.130 |     0.072 |     0.051 |
+| \ se\_r       |     0.046 |     0.695 |     0.008 |     0.037 |     0.068 |     0.038 |     0.022 |
+| \ se\_cl      |     0.045 |     0.529 |     0.008 |     0.044 |     0.077 |     0.039 |     0.021 |
+| Q75        |           |           |           |           |           |           |           |
+| \ coeff      |     0.041 |    -1.555 |     0.033 |     0.138 |     0.078 |     0.619 |    -0.007 |
+| \ se\_gls     |     0.067 |     0.898 |     0.011 |     0.053 |     0.098 |     0.052 |     0.038 |
+| \ se\_r       |     0.048 |     0.827 |     0.009 |     0.037 |     0.075 |     0.046 |     0.026 |
+| \ se\_cl      |     0.038 |     0.980 |     0.012 |     0.050 |     0.086 |     0.063 |     0.020 |
+: The determinants of government surpluses: Individual and Time Fixed effects {#tbl-tb2}
 
@@
 
-# Appendix {.appendix}
+# Appendix {.appendix}{#sec-appendix}
 

### 2023-10-30 article/article.tex
mmqreg
update

@@
 \end{frontmatter}
-    \ifdefined\Shaded\renewenvironment{Shaded}{\begin{tcolorbox}[sharp corners, frame hidden, boxrule=0pt, interior hidden, borderline west={3pt}{0pt}{shadecolor}, enhanced, breakable]}{\end{tcolorbox}}\fi
+    \ifdefined\Shaded\renewenvironment{Shaded}{\begin{tcolorbox}[breakable, boxrule=0pt, borderline west={3pt}{0pt}{shadecolor}, frame hidden, interior hidden, enhanced, sharp corners]}{\end{tcolorbox}}\fi
 
@@
 an incident parameter problem. While many strategies have been proposed
-for estimating this type of model (see Galvão and Kato, 2018 for a brief
-review), neither has become standard because of their restrictive
+for estimating this type of model (see \citet{galvao2017quantile} for a
+brief review), neither has become standard because of their restrictive
 assumptions in regards to the individual effects, the computational
@@
 the data is based on a multiplicative heteroskedastic process that is
-linear in parameters (\citet{cameron2005}, \citet{mss2019},
-\citet{he1997} and \citet{zhao2000} ), the effect of a variable \(X\) on
-the \(q_th\) quantile can be derived as the combination of a location
+linear in parameters \citep[\citet{mss2019}, \citet{he1997},
+\citet{zhao2000}]{cameron2005}, the effect of a variable \(X\) on the
+\(q_{th}\) quantile can be derived as the combination of a location
 effect, and scale effect moderated by the quantile of an underlying
@@
 the location model coefficients, plus the scale model coefficients
-moderated by the \(\tau_th\) unconditional quantile of the standardized
-error \(\varepsilon\).
+moderated by the \(\tau_{th}\) unconditional quantile of the
+standardized error \(\varepsilon\).
 
@@
 because the location and scale model can be identified globally, with
-only a single parmater (\(q(\varepsilon|\tau)\)) requiring local
+only a single paramater (\(q(\varepsilon|\tau)\)) requiring local
 estimation, this estimation approach would be more efficient than the
@@
   Finally, given the location and scale coefficients, the \(\tau_{th}\)
-  quantile of the error \(e\) can be estimated using the following
-  condition:
+  quantile of the error \(\varepsilon\) can be estimated using the
+  following condition:
 \end{enumerate}
@@
 \(\bar{G}(\theta)\) is the Jacobian matrix of the moment equations
-(Equation~\ref{eq-eq10}) evaluated at \(\hat\theta\).
+evaluated at \(\hat\theta\).
 
@@
 
-\[\Xi = [ I(k), \hat q(\varepsilon|\tau) \times I(k), \hat \gamma ]
-\]
+\begin{equation}\protect\hypertarget{eq-eqqtile}{}{\Xi = [ I(k), \hat q(\varepsilon|\tau) \times I(k), \hat \gamma ]
+}\label{eq-eqqtile}\end{equation}
 
@@
 simultaneous model estimation, for a just identified model, it is more
-efficient to estimate each set of coefficients separately. The
-variance-covariance matrix can be estimated using the empirical
+efficient to estimate each set of coefficients separately. Afterwards,
+the variance-covariance matrix can be estimated using the empirical
 influence functions of the estimators (see \citet{jann_2020} for an
@@
 
-\begin{enumerate}
-\def\labelenumi{\arabic{enumi}.}
-\tightlist
-\item
-  Need to add the general condition Var=(inf (theta) * inf(theta))
-\end{enumerate}
-
-Thatn inf(theta) = inf beta gamma and q)tay
-
-and finally define what the IFs are (see appendix)
+Specifically, given an arbitrary vector of empirical influence functions
+\(\lambda_i(\theta)\), the variance-covariance matrix can be estimated
+as:
+\begin{equation}\protect\hypertarget{eq-eqvcv}{}{\hat{V}(\theta) = \frac{1}{N^2} \sum_{i=1}^N \lambda_i(\theta) \lambda_i(\theta)'
+}\label{eq-eqvcv}\end{equation}
+
+where the influence functions are defined as:
+
+\[\lambda_i(\theta) = \bar G(\theta)^{-1} h_i(\theta)\]
+
+For the specific case of quantile regressions via momoments, the
+influence functions for the location, scale and quantile coefficients
+are:\footnote{The derivation of the influence functions can be found in
+  Section~\ref{sec-appendix}.}
+
+\begin{equation}\protect\hypertarget{eq-ifs}{}{\begin{aligned}
+\lambda_i(\theta)&=
+  \begin{bmatrix}
+  \lambda_{i}(\beta) \\
+  \lambda_{i}(\gamma) \\
+  \lambda_{i}(q(\varepsilon|\tau)) 
+  \end{bmatrix} \\
+\lambda_{i}(\beta)&=N (X'X)^{-1}  x_i ( x_i'\gamma) \times \varepsilon_i \\
+\lambda_{i}(\gamma)&= N(X'X)^{-1} x_i ( x_i' \gamma ) \times (\tilde \varepsilon_i -1\big)\\
+\lambda_{i}(q(\varepsilon|\tau))&=\frac{\tau-\mathbb{1}\big( q(\varepsilon|\tau)  \geq \varepsilon_i  \big) }{f_{\varepsilon}(q(\varepsilon|\tau))}
+- \frac{ x_i'\gamma \times \varepsilon_i }{\bar x_i'\gamma} 
+-  q(\varepsilon|\tau) \frac{  x_i' \gamma  \times (\tilde \varepsilon_i -1\big)}{\bar x_i'\gamma}
+\end{aligned}
+}\label{eq-ifs}\end{equation}
 
@@
 
-Cross product of IFs
+The first, and most natural standard error estimator is given by
+equation Equation~\ref{eq-eqvcv}. This is equivalent to the Eicker-White
+Heteroskedastic-Consistent estimator for least-squares estimators.
+Considering the location-scale model, the variance-covariance matrix for
+the quantile coefficients can be estimated as:
+
+\[\hat{V}_{robust}
+  \begin{pmatrix}
+  \hat\beta \\
+  \hat\gamma \\
+  \hat q(\varepsilon|\tau)
+  \end{pmatrix}
+ = \frac{1}{N^2} 
+ \begin{pmatrix}
+ \sum \lambda_i(\beta) \lambda_i(\beta)' & \sum \lambda_i(\beta) \lambda_i(\gamma)' & \sum \lambda_i(\beta) \lambda_i(q(\varepsilon|\tau))' \\
+ \sum \lambda_i(\gamma) \lambda_i(\beta)' & \sum \lambda_i(\gamma) \lambda_i(\gamma)' & \sum \lambda_i(\gamma) \lambda_i(q(\varepsilon|\tau))' \\
+ \sum \lambda_i(q(\varepsilon|\tau) \lambda_i(\beta)' & \sum \lambda_i(q(\varepsilon|\tau))\lambda_i(\gamma)' & \sum \lambda_i(q(\varepsilon|\tau)) \lambda_i(q(\varepsilon|\tau))' 
+  \end{pmatrix}
+\]
+
+This estimator of Standard errors should be robust to arbitrary
+heteroskedasticity. However, because the location-scale specification
+relies on the correct specification of the model heteroskedasticity,
+large differences in Standard errors compared to GLS-standard errors may
+be an indication of misspecification of the model.
 
@@
 
-Sun then cross product
+Because one of the typical applications of quantile regressions is the
+analysis of panel data, allowing for clustered standard errors at the
+individual level is important. If the unobserved error \(\varepsilon\)
+is correlated within clusters, GLS-Standard errors could be severily
+biased. The standard recommendation has been to report block-bootstrap
+standard errors, clustering at the individual level.
+
+Since we have access to the influence functions, it is straight forward
+to estimate one-way clustered standard errors.
+
+Call \(N_G\) to be the total number of clusteres g, where
+\(g=1\dots N_G\). The clustered variance covariance matrix is given
+by:\footnote{It should be noted that one could just as well apply the
+  insights of \citet{cameron_robust_2011}, allowing for multiway
+  clustering.}
+
+\[\hat{V}_{clustered}
+  \begin{pmatrix}
+  \hat\beta \\
+  \hat\gamma \\
+  \hat q(\varepsilon|\tau)
+  \end{pmatrix}
+ = \frac{1}{N^2} 
+ \begin{pmatrix}
+ \sum_{g=1}^{N_G} S\lambda_i(\theta) S\lambda_i(\theta)'
+  \end{pmatrix}
+\]
+
+Where \(S\lambda_i(\theta)\) is the sum of the influence functions over
+all observations within a given cluster \(g\).
+
+\[S\lambda_i(\theta) = \sum_{i\in g} \lambda_i(\theta)
+\]
 
@@
 
-Original paper;
+The standard errors proposed by MSS can be understood as an application
+of generalized least squares (GLS), which will be valid as long as the
+model for heteroskedasticity is correctly specified.\footnote{As
+  discussed in most econometric textbooks, like \citet{cameron2005}, one
+  approach to correct for heteroskedasticity, when the
+  heteroskedasticity functional form is known, or can be estimated, is
+  to use weighted least squares. While feasible, however, this approach
+  would defeat the purpose of identifying quantile effects exploiting
+  the heteroskedasticity of the model.} To estimate the GLS-Standard
+errors, we make use of the following property:
+
+Consider the influence functions and robust variance-covariance matrix
+for the location coefficients:
+
+\[\begin{aligned}
+\hat V(\hat \beta) &= \frac{1}{N} \sum_i^N \lambda_{i}(\beta) \lambda_{i}(\beta)' \\
+&= \frac{1}{N}  (X'X)^{-1}  \sum_i^N x_i x_i' ( x_i'\gamma \times \varepsilon_i)^2 (X'X)^{-1} \\
+\end{aligned}
+\]
+
+Under the assumption that the model for heteroskedasticity is correctly
+specified, we can apply the law of iterated expectations and rewrite the
+variance-covariance matrix as:
+
+\[\begin{aligned}
+\hat V(\hat \beta) &= \frac{1}{N} \sum_i^N \lambda_{i}(\beta) \lambda_{i}(\beta)' \\
+&= E(\varepsilon_i^2) \frac{1}{N}  (X'X)^{-1}  \sum_i^N x_i x_i' ( x_i'\gamma)^2 (X'X)^{-1} \\
+&= \sigma^2_{\varepsilon} \frac{1}{N}  (X'X)^{-1}  \hat\Omega_{\beta\beta} (X'X)^{-1}  
+\end{aligned}
+\]
+
+This standard error estimator is an application of GLS that accounts for
+the heteroskedasticity the model uses to identify the quantile
+coefficients. We can apply the same principle to find the GLS-Standard
+errors for the system of location-scale and quantile coefficients. To do
+this, define the following modified influence functions:
+
+\[\begin{aligned}
+\tilde \lambda_{1,i}&=\tilde \lambda_{2,i}=N (X'X)^{-1}  x_i ( x_i'\gamma) \\  
+\tilde \lambda_{3,i}&=x_i' \gamma  \\
+\tilde \psi_1 &= \varepsilon_i \\
+\tilde \psi_2 &= \tilde \varepsilon_i -1 \\
+\tilde \psi_3 &= \frac{1}{ x_i' \gamma }\frac{\tau-\mathbb{1}\big( q(\varepsilon|\tau)  \geq \varepsilon_i  \big) }{ f_{\varepsilon}(q(\varepsilon|\tau))} - \frac{\varepsilon_i }{\bar x_i'\gamma} 
+-  q(\varepsilon|\tau) \frac{(\tilde \varepsilon_i -1\big)}{\bar x_i'\gamma}
+\end{aligned}
+\]
+
+Then, the GLS-Standard errors for the location-scale and quantile
+coefficients can be estimated as:
+
+\[\hat{V}_{gls}
+  \begin{pmatrix}
+  \hat\beta \\
+  \hat\gamma \\
+  \hat q(\varepsilon|\tau)
+  \end{pmatrix}
+ = \frac{1}{N^2} 
+ \begin{pmatrix}
+ \hat\sigma_{11} \hat\Omega_{11} & \hat\sigma_{12} \hat\Omega_{12} & \hat\sigma_{11} \hat\Omega_{13} \\
+ \hat\sigma_{21} \hat\Omega_{21} & \hat\sigma_{22} \hat\Omega_{22} & \hat\sigma_{21} \hat\Omega_{23} \\
+ \hat\sigma_{31} \hat\Omega_{31} & \hat\sigma_{32} \hat\Omega_{32} & \hat\sigma_{33} \hat\Omega_{33}
+  \end{pmatrix}
+\]
+
+where
+
+\[\begin{aligned}
+\hat\Omega_{ij} &= \frac{1}{N} \sum_i^N \tilde \lambda_{i}(\theta) \tilde \lambda_{j}(\theta)' \\
+\hat\sigma_{ij} &= \frac{1}{N} \sum_i^N \phi_{i} \phi_{j}
+\end{aligned}
+\]
+
+This estimator of Standard errors is equivalent to the one derived by
+MSS by Theorem 3.
 
@@
   We estimate the location model using the centered-residualized
-  variables:
+  variables:\footnote{Using centered-residualized variables allow us to
+    include a constant in the model specification, which simplifies the
+    derivation of the influence functions. However, as with other fixed
+    effects models, the constant is not identified, and thus should not
+    be interpreted.}
 \end{enumerate}
 
-\[y_{i}^{rc} = x_{i}^{rc'} \beta + nu_{i}
+\[y_{i}^{rc} = x_{i}^{rc'} \beta + \nu_{i}
 \]
@@
 
-\[|\hat\nu_{i}|^{rc} = x_{i}^{rc'} \gamma + e_{i}\]
+\[|\hat\nu_{i}|^{rc} = x_{i}^{rc'} \gamma + \omega_{i}\]
 
@@
 
-\[\hat{\varepsilon}_{i} = \frac{\nu_{i}}{|\hat\nu_{i}|- \hat e_{i}}\]
-
-where \(|\hat\nu_{i}|- \hat e_{i}\) is the prediction for the
+\[\hat{\varepsilon}_{i} = \frac{\nu_{i}}{|\hat\nu_{i}|- \hat \omega_{i}}\]
+
+where \(|\hat\nu_{i}|- \hat \omega_{i}\) is the prediction for the
 conditional standard deviation
@@
 
-\hypertarget{monte-carlo-simulations}{%
-\section{Monte Carlo Simulations}\label{monte-carlo-simulations}}
-
-\hypertarget{application-something-interesting}{%
-\section{\texorpdfstring{Application: \textbf{Something
-interesting}}{Application: Something interesting}}\label{application-something-interesting}}
+\hypertarget{simulation-evidence}{%
+\section{Simulation Evidence}\label{simulation-evidence}}
+
+To show the performance of the extended strategy, we implement the
+results of a small simulation study. We consider a simple model with a
+single explanatory variable \(x\), and a single fixed effect \(g\). The
+data generating process is as follows:
+
+\hypertarget{illustrative-application}{%
+\section{Illustrative application}\label{illustrative-application}}
+
+In this section we replicate one of the excercises from MSS, allowing
+for time and individual fixed effects, as well as for different standard
+errors estimations. We use data from \citet{persson_economic_2005}, to
+estimate the relationship between surplus of goverment as share of GDP,
+and a measure of quality of democracy (POLITY); log of real income per
+capita (LYP); trade volume as share of GDP (TRADE), Share of population
+between 15-65 uears of age (P1564), the share of the population 65 years
+or older (P65); one-year lag of the dependent variable (LSP); oil prices
+in US dollars differntiating importer and exported countries (OILIM and
+OILEX); and the output gap (YGAP). In addition to country fixed effects
+(as illustrated in MSS), we also show results allowing for time fixed
+effects. Table~\ref{tbl-tb1} and Table~\ref{tbl-tb2} provide the results
+for the model with and without time fixed effects, respectively. It show
+cases the location and scale coefficients, as well as the quantile
+coefficients for the 25th, 50th and 75th quantiles. We also report
+GLS-Standard errors, Robust standard errors (brackets) and clustered
+standard errors at the country level.
+
+\hypertarget{tbl-tb1}{}
+\begin{longtable}[]{@{}
+  >{\raggedright\arraybackslash}p{(\columnwidth - 18\tabcolsep) * \real{0.1099}}
+  >{\centering\arraybackslash}p{(\columnwidth - 18\tabcolsep) * \real{0.0989}}
+  >{\centering\arraybackslash}p{(\columnwidth - 18\tabcolsep) * \real{0.0989}}
+  >{\centering\arraybackslash}p{(\columnwidth - 18\tabcolsep) * \real{0.0989}}
+  >{\centering\arraybackslash}p{(\columnwidth - 18\tabcolsep) * \real{0.0989}}
+  >{\centering\arraybackslash}p{(\columnwidth - 18\tabcolsep) * \real{0.0989}}
+  >{\centering\arraybackslash}p{(\columnwidth - 18\tabcolsep) * \real{0.0989}}
+  >{\centering\arraybackslash}p{(\columnwidth - 18\tabcolsep) * \real{0.0989}}
+  >{\centering\arraybackslash}p{(\columnwidth - 18\tabcolsep) * \real{0.0989}}
+  >{\centering\arraybackslash}p{(\columnwidth - 18\tabcolsep) * \real{0.0989}}@{}}
+\caption{\label{tbl-tb1}The determinants of government surpluses:
+Individual Fixed effects}\tabularnewline
+\toprule\noalign{}
+\begin{minipage}[b]{\linewidth}\raggedright
+\end{minipage} & \begin{minipage}[b]{\linewidth}\centering
+polityt
+\end{minipage} & \begin{minipage}[b]{\linewidth}\centering
+lyp
+\end{minipage} & \begin{minipage}[b]{\linewidth}\centering
+trade
+\end{minipage} & \begin{minipage}[b]{\linewidth}\centering
+p1564
+\end{minipage} & \begin{minipage}[b]{\linewidth}\centering
+p65
+\end{minipage} & \begin{minipage}[b]{\linewidth}\centering
+lspl
+\end{minipage} & \begin{minipage}[b]{\linewidth}\centering
+oil\_im
+\end{minipage} & \begin{minipage}[b]{\linewidth}\centering
+oil\_ex
+\end{minipage} & \begin{minipage}[b]{\linewidth}\centering
+ygap
+\end{minipage} \\
+\midrule\noalign{}
+\endfirsthead
+\toprule\noalign{}
+\begin{minipage}[b]{\linewidth}\raggedright
+\end{minipage} & \begin{minipage}[b]{\linewidth}\centering
+polityt
+\end{minipage} & \begin{minipage}[b]{\linewidth}\centering
+lyp
+\end{minipage} & \begin{minipage}[b]{\linewidth}\centering
+trade
+\end{minipage} & \begin{minipage}[b]{\linewidth}\centering
+p1564
+\end{minipage} & \begin{minipage}[b]{\linewidth}\centering
+p65
+\end{minipage} & \begin{minipage}[b]{\linewidth}\centering
+lspl
+\end{minipage} & \begin{minipage}[b]{\linewidth}\centering
+oil\_im
+\end{minipage} & \begin{minipage}[b]{\linewidth}\centering
+oil\_ex
+\end{minipage} & \begin{minipage}[b]{\linewidth}\centering
+ygap
+\end{minipage} \\
+\midrule\noalign{}
+\endhead
+\bottomrule\noalign{}
+\endlastfoot
+Location & & & & & & & & & \\
+~coeff & 0.116 & -0.715 & 0.030 & 0.121 & 0.028 & 0.691 & -0.047 &
+-0.006 & 0.010 \\
+~se\_gls & 0.046 & 0.540 & 0.008 & 0.033 & 0.070 & 0.035 & 0.008 & 0.022
+& 0.028 \\
+~se\_r & 0.047 & 0.597 & 0.008 & 0.031 & 0.070 & 0.037 & 0.007 & 0.017 &
+0.021 \\
+~se\_cl & 0.046 & 0.465 & 0.007 & 0.032 & 0.071 & 0.035 & 0.010 & 0.020
+& 0.023 \\
+Scale & & & & & & & & & \\
+~coeff & -0.097 & -0.616 & 0.003 & 0.036 & 0.087 & -0.085 & 0.013 &
+0.016 & -0.004 \\
+~se\_gls & 0.032 & 0.371 & 0.005 & 0.023 & 0.048 & 0.024 & 0.006 & 0.015
+& 0.019 \\
+~se\_r & 0.031 & 0.398 & 0.005 & 0.020 & 0.049 & 0.025 & 0.005 & 0.010 &
+0.015 \\
+~se\_cl & 0.048 & 0.800 & 0.008 & 0.031 & 0.067 & 0.029 & 0.004 & 0.010
+& 0.012 \\
+Q25 & & & & & & & & & \\
+~coeff & 0.191 & -0.239 & 0.028 & 0.093 & -0.039 & 0.756 & -0.057 &
+-0.018 & 0.013 \\
+~se\_gls & 0.059 & 0.684 & 0.010 & 0.042 & 0.088 & 0.045 & 0.010 & 0.027
+& 0.035 \\
+~se\_r & 0.056 & 0.656 & 0.008 & 0.036 & 0.086 & 0.040 & 0.010 & 0.020 &
+0.025 \\
+~se\_cl & 0.073 & 0.687 & 0.006 & 0.041 & 0.098 & 0.023 & 0.010 & 0.021
+& 0.029 \\
+Q50 & & & & & & & & & \\
+~coeff & 0.108 & -0.765 & 0.030 & 0.124 & 0.035 & 0.684 & -0.046 &
+-0.005 & 0.009 \\
+~se\_gls & 0.046 & 0.535 & 0.007 & 0.033 & 0.069 & 0.035 & 0.008 & 0.022
+& 0.027 \\
+~se\_r & 0.046 & 0.593 & 0.008 & 0.031 & 0.069 & 0.036 & 0.007 & 0.017 &
+0.021 \\
+~se\_cl & 0.043 & 0.484 & 0.008 & 0.032 & 0.070 & 0.036 & 0.010 & 0.020
+& 0.023 \\
+Q75 & & & & & & & & & \\
+~coeff & 0.031 & -1.258 & 0.033 & 0.153 & 0.104 & 0.616 & -0.036 & 0.008
+& 0.006 \\
+~se\_gls & 0.048 & 0.551 & 0.008 & 0.034 & 0.071 & 0.036 & 0.008 & 0.022
+& 0.028 \\
+~se\_r & 0.049 & 0.696 & 0.009 & 0.034 & 0.075 & 0.043 & 0.007 & 0.018 &
+0.023 \\
+~se\_cl & 0.039 & 0.919 & 0.012 & 0.041 & 0.079 & 0.055 & 0.010 & 0.022
+& 0.020 \\
+\end{longtable}
+
+As expected, Table~\ref{tbl-tb1} shows that point estimates for the
+point estimates for the quantile regressions are identical to the ones
+reported in \citet{mss2019} (table 6), including analytical standard
+errors (GLS). With our estimator, however, we are able to also produce
+both robust and clustered standard errors for location and scale
+coefficients. Except for few cases, Robust and Clustered standard errors
+are larger than GLS standard errors, which may be an indication of
+misspecification of the model. The GLS standard errors we report differ
+from the ones in MSS, because they use panel standard errors, equivalent
+to our clustered standard errors, instead of the analytical standard
+errors we derive.
+
+Considering the estimated effects across quantiles, we observe few
+differences in the reported GLS standard errors compared to the
+analytical standard errors reported MSS. Our clustered standard errors,
+however, are closer to the bootstrap based standard errors the authors
+report.\footnote{There are two possible reasons that may explain the
+  differences in the GLS standard errors. On the one hand, in our
+  derivation, the influence function of the standardized \(\tau_{th}\)
+  quantile (see \#eq-infs) does not have the same leading term as the
+  one reported in MSS (see theorem 3, and the definition of \(W\)).}
+
+In Table~\ref{tbl-tb2}, we report the results including both individual
+and year fixed effects. Because Oil prices only vary across years, the
+variableis excluded from the model specification. Accounting for time
+fixed effects, does not change the general conclusions one could make
+based no the results from Table~\ref{tbl-tb1}. The two largest
+differences are that the log of income percapita has a positive effect
+on Goverment Surpluses, but only for the 25th quantile, because of the
+largest impact on the Scale component. Similarly, we observe that the
+income gap now has an impact on Goverment surplus that is always
+negative, but increasing across quantiles. In both instances, the
+effects are not statistically significant.
+
+\hypertarget{tbl-tb2}{}
+\begin{longtable}[]{@{}
+  >{\raggedright\arraybackslash}p{(\columnwidth - 14\tabcolsep) * \real{0.1370}}
+  >{\centering\arraybackslash}p{(\columnwidth - 14\tabcolsep) * \real{0.1233}}
+  >{\centering\arraybackslash}p{(\columnwidth - 14\tabcolsep) * \real{0.1233}}
+  >{\centering\arraybackslash}p{(\columnwidth - 14\tabcolsep) * \real{0.1233}}
+  >{\centering\arraybackslash}p{(\columnwidth - 14\tabcolsep) * \real{0.1233}}
+  >{\centering\arraybackslash}p{(\columnwidth - 14\tabcolsep) * \real{0.1233}}
+  >{\centering\arraybackslash}p{(\columnwidth - 14\tabcolsep) * \real{0.1233}}
+  >{\centering\arraybackslash}p{(\columnwidth - 14\tabcolsep) * \real{0.1233}}@{}}
+\caption{\label{tbl-tb2}The determinants of government surpluses:
+Individual and Time Fixed effects}\tabularnewline
+\toprule\noalign{}
+\begin{minipage}[b]{\linewidth}\raggedright
+\end{minipage} & \begin{minipage}[b]{\linewidth}\centering
+polity
+\end{minipage} & \begin{minipage}[b]{\linewidth}\centering
+lyp
+\end{minipage} & \begin{minipage}[b]{\linewidth}\centering
+trade
+\end{minipage} & \begin{minipage}[b]{\linewidth}\centering
+prop1564
+\end{minipage} & \begin{minipage}[b]{\linewidth}\centering
+prop65
+\end{minipage} & \begin{minipage}[b]{\linewidth}\centering
+lspl
+\end{minipage} & \begin{minipage}[b]{\linewidth}\centering
+ygap
+\end{minipage} \\
+\midrule\noalign{}
+\endfirsthead
+\toprule\noalign{}
+\begin{minipage}[b]{\linewidth}\raggedright
+\end{minipage} & \begin{minipage}[b]{\linewidth}\centering
+polity
+\end{minipage} & \begin{minipage}[b]{\linewidth}\centering
+lyp
+\end{minipage} & \begin{minipage}[b]{\linewidth}\centering
+trade
+\end{minipage} & \begin{minipage}[b]{\linewidth}\centering
+prop1564
+\end{minipage} & \begin{minipage}[b]{\linewidth}\centering
+prop65
+\end{minipage} & \begin{minipage}[b]{\linewidth}\centering
+lspl
+\end{minipage} & \begin{minipage}[b]{\linewidth}\centering
+ygap
+\end{minipage} \\
+\midrule\noalign{}
+\endhead
+\bottomrule\noalign{}
+\endlastfoot
+Location & & & & & & & \\
+~coeff & 0.126 & -0.418 & 0.028 & 0.108 & 0.042 & 0.693 & -0.014 \\
+~se\_gls & 0.087 & 1.157 & 0.015 & 0.072 & 0.136 & 0.066 & 0.053 \\
+~se\_r & 0.047 & 0.703 & 0.008 & 0.038 & 0.068 & 0.038 & 0.022 \\
+~se\_cl & 0.048 & 0.506 & 0.008 & 0.044 & 0.077 & 0.037 & 0.022 \\
+Scale & & & & & & & \\
+~coeff & -0.095 & -1.255 & 0.005 & 0.033 & 0.040 & -0.081 & 0.008 \\
+~se\_gls & 0.081 & 1.073 & 0.014 & 0.067 & 0.126 & 0.061 & 0.049 \\
+~se\_r & 0.031 & 0.452 & 0.005 & 0.025 & 0.045 & 0.025 & 0.017 \\
+~se\_cl & 0.041 & 0.848 & 0.006 & 0.030 & 0.048 & 0.033 & 0.013 \\
+Q25 & & & & & & & \\
+~coeff & 0.201 & 0.576 & 0.025 & 0.082 & 0.010 & 0.757 & -0.020 \\
+~se\_gls & 0.154 & 2.070 & 0.024 & 0.118 & 0.219 & 0.121 & 0.085 \\
+~se\_r & 0.058 & 0.751 & 0.008 & 0.049 & 0.080 & 0.040 & 0.026 \\
+~se\_cl & 0.073 & 0.761 & 0.006 & 0.052 & 0.087 & 0.023 & 0.027 \\
+Q50 & & & & & & & \\
+~coeff & 0.119 & -0.512 & 0.029 & 0.111 & 0.045 & 0.687 & -0.013 \\
+~se\_gls & 0.091 & 1.230 & 0.014 & 0.070 & 0.130 & 0.072 & 0.051 \\
+~se\_r & 0.046 & 0.695 & 0.008 & 0.037 & 0.068 & 0.038 & 0.022 \\
+~se\_cl & 0.045 & 0.529 & 0.008 & 0.044 & 0.077 & 0.039 & 0.021 \\
+Q75 & & & & & & & \\
+~coeff & 0.041 & -1.555 & 0.033 & 0.138 & 0.078 & 0.619 & -0.007 \\
+~se\_gls & 0.067 & 0.898 & 0.011 & 0.053 & 0.098 & 0.052 & 0.038 \\
+~se\_r & 0.048 & 0.827 & 0.009 & 0.037 & 0.075 & 0.046 & 0.026 \\
+~se\_cl & 0.038 & 0.980 & 0.012 & 0.050 & 0.086 & 0.063 & 0.020 \\
+\end{longtable}
 
@@
 
-\hypertarget{appendix}{%
-\section{Appendix}\label{appendix}}
+\hypertarget{sec-appendix}{%
+\section{Appendix \{.appendix\}}\label{sec-appendix}}
 

### 2023-10-31 article/article.qmd
Update article.qmd

@@
 We provide Monte Carlo simulations to show the finite sample properties of the proposed method in the presence of two sets of fixed effects.
-Finally, we apply the proposed method to estimate **something interesting**
+Finally, we apply the proposed method to estimate the determinants of the surplus of government as a share of GDP allowing for both time and country fixed effects.
 keywords: 

### 2023-10-31 article/article.qmd
update
First Draft except conclusions

@@
       name: Journal Name
-      formatting: preprint
+      formatting: review
       model: 1p
@@
 
-# Methodology
+# Methodology {#sec-method}
 
@@
 Specifically, given an arbitrary vector of empirical influence functions $\lambda_i(\theta)$, the variance-covariance matrix can be estimated as:
+
 $$\hat{V}(\theta) = \frac{1}{N^2} \sum_{i=1}^N \lambda_i(\theta) \lambda_i(\theta)'
@@
 
-To show the performance of the extended strategy, we implement the results of a small simulation study.
-We consider a simple model with a single explanatory variable $x$, and a single fixed effect $g$.
-The data generating process is as follows:
+To show the performance of the extended strategy, we implement a small simulation study.
+We consider a simple model with a single explanatory variable $x$.
+In contrast with MSS, we consider a two-way fixed effect structure that is more general than the panel structure used in by the authors.
+For this excercise, we consider the following data generating process:
+
+$$y_i = \alpha_{1i} + \alpha_{2i} + x_i + (1+x_i + \alpha_{1i} + \alpha_{2i} ) \varepsilon_i
+$$
+
+where $\alpha_{1i}\sim \chi^2(1)$, $\alpha_{2i} \sim \chi^2(1)$ and $x_i = 0.5 * (\chi_i +0.5(\alpha_{1i}+\alpha_{2i}))$ with $\chi_i \sim \chi^2(1)$.
+We only consider the case when the error term $\varepsilon_i$ is assumed to be normally distributed with mean zero and standard deviation 0.5.
+We assume that there are 50 mutually exclusive fixed effect groups for each set of fixed effects.
+Observations are assigned to each subgroup randomly, using a uniform distribution between 1 and 50.
+We consider a sample sizes of 500, 1000, 2000 and 4000 observations, which implies an average of 10, 20, 40 and 80 observations per group.
+The model is estimated using the location-scale model with heteroskedastic linear errors, and we report the coefficients for the 25th and 75th quantiles.
+We run this excercise 5000 times.
+@tbl-sim1 reports the bias, simulated standard error and mean squared error.
+We also report the results obtained using an adaptation bias-corrected estimator based on the split-panel jackknife estimator proposed by @dhaene2015.[^jk] These results are labeled JKC.
+
+[^jk]: For the implementation, we estimate the model using the full sample, then, randomly assign each observation into one of two groups, and re-estimate the quantile coefficients for each group.
+The bias-corrected estimator is then obtained as $\hat\beta(\tau)_{jkc}=2*\hat\beta(\tau)_{full}-0.5*\big(\hat\beta(\tau)_{s1}+\hat\beta(\tau)_{s1}\big)$.
+
+Similar to the findings in MSS, we find that the estimator presents a bias when the sample is small ($N=500$), but this bias shrinks as the sample sizes increases.
+As MSS describes, the bias seems to be proportional to the sample size, or more precisely to $N/N_{g1}$ and $N/N_{g2}$, where $N_{g1}$ and $N_{g2}$ are the average number of observations per group.
+Interestingly, the bias-corrected estimator presents an almost zero bias, even when the samples are is small (about 10 observations per sub-group).
+Also replicating the results of MSS, despite bias reduction obtained using the JKC estimator, the standard errors and mean squared error (MSE) are larger than without correction.
+
+::: {#tbl-sim1 layout-nrow=2 layout-ncol=2}
+
+| N = 500      |         Bias | Sim SE       |         MSE  |
+| ------------ | :----------: | :----------: | :----------: |
+| q25          |              |              |              |
+| \ mmqreg       |        0.104 |        0.247 |        0.072 |
+| \ jkc          |        0.008 |        0.297 |        0.088 |
+| q75          |              |              |              |
+| \ mmqreg       |       -0.091 |        0.251 |        0.071 |
+| \ jkc          |        0.002 |        0.303 |        0.092 |
+
+| N = 1000     |         Bias | Sim SE       |         MSE  |
+| ------------ | :----------: | :----------: | :----------: |
+| q25          |              |              |              |
+| \ mmqreg       |        0.050 |        0.173 |        0.032 |
+| \ jkc          |       -0.001 |        0.191 |        0.036 |
+| q75          |              |              |              |
+| \ mmqreg       |       -0.044 |        0.176 |        0.033 |
+| \ jkc          |        0.006 |        0.195 |        0.038 |
+
+| N = 1000      |         Bias | Sim SE       |         MSE  |
+| ------------ | :----------: | :----------: | :----------: |
+| q25          |              |              |              |
+| \ mmqreg       |        0.025 |        0.122 |        0.016 |
+| \ jkc          |        0.003 |        0.129 |        0.017 |
+| q75          |              |              |              |
+| \ mmqreg       |       -0.023 |        0.124 |        0.016 |
+| \ jkc          |        0.001 |        0.131 |        0.017 |
+
+| N = 2000      |         Bias | Sim SE       |         MSE  |
+| ------------ | :----------: | :----------: | :----------: |
+| q25          |              |              |              |
+| \ mmqreg       |        0.012 |        0.087 |        0.008 |
+| \ jkc          |        0.000 |        0.089 |        0.008 |
+| q75          |              |              |              |
+| \ mmqreg       |       -0.011 |        0.087 |        0.008 |
+| \ jkc          |        0.000 |        0.089 |        0.008 |
+
+Bias, Simulated Standard error, and Mean Squared Error
+
+:::
+
+As described in section @sec-se, GLS-Standard errors may not be appropriate if heteroskedasticity in the model is misspecified.
+This could happen if the heteroskedasticity is not linear in parameters, or if there is correlations within groups.
+To show the performance of the GLS-Standard errors, we consider two additional simulations.
+To see the impact of heteroskedasticity misspecification, we assume the DGP is given by:
+
+$$y_i = \alpha_{1i} + \alpha_{2i} + x_i + (1+x_i + \sqrt{x_i} +\alpha_{1i} + \alpha_{2i} ) \varepsilon_i
+$$
+
+To show the impact of ignoring correlation within groups, we consider the case where the error $\varepsilon$ is correlated within groups defined by the first fixed effect. Specifically:
+
+$$\varepsilon_i =0.5*(\sqrt{0.5} z_i + \sqrt{0.5} w_g)$$
+
+where $z_i~N(0,1)$ and $w_g~N(0,1)$, with $g$ being the $g_{th}$ group defined by the first fixed effect.
+
+For the simulation, we run the excercise 5000 times, using a sample of size $N=2000$.
+The results from both simulations are reported in the @tbl-sim2.
+We report the average coefficient, simulation based Standard errors, and the standard errors using GLS, robust and clustered estimations.
+
+|              |      Het:q25 |      Het:q75 |    Clust:q25 |    Clust:q75 |
+| ------------ | :----------: | :----------: | :----------: | :----------: |
+| Coefficient  |        0.550 |        1.442 |        0.775 |        1.229 |
+| SIM\_SE       |        0.154 |        0.155 |        0.109 |        0.107 |
+| GLS\_SE       |        0.476 |        0.451 |        0.288 |        0.221 |
+| Robust       |        0.140 |        0.139 |        0.087 |        0.088 |
+| Cluster      |         |         |        0.097 |        0.097 |
+: Heteroskedasticity misspecification and clustered errors {#tbl-sim2}
+
+One of the conclusions from the results in @tbl-sim2 is that the results for the 25th and 75th quantiles are mostly identical, because of the symmetric error we used in the simulation.
+On the one hand, because the error structure is misspecified, we should expect to see a large bias in the estimated coefficients, especially in cases of misspecified heteroskedasticity.
+However, the purpose of this exercise is not to demonstrate the unbiasedness of the coefficients, but rather to assess the performance of the standard error estimation.
+
+As expected, the GLS-standard errors are biased, and the bias is larger in the case of misspecified heteroskedasticity.
+In fact, with heteroskedastic misspecification, the average GLS-SE (.476) is almost three times as large as the simulation-based standard error (0.154).
+In this first case, robust standard errors perform better, but with a small difference (0.14 to 0.154).
+In the case of clustered correlation, GLS-SE also performs poorly.
+Robust standard errors perform better, but seem to underestimate the magnitude of the true standard errors.
+Finally, cluster standard errors perform the best, with a small difference between the simulation-based standard errors (0.097 to 0.109).
 
@@
 
-As expected, @tbl-tb1 shows that point estimates for the point estimates for the quantile regressions are identical to the ones reported in @mss2019 (table 6), including analytical standard errors (GLS).
+As expected, @tbl-tb1 shows that point estimates for the point estimates are identical to the ones reported in @mss2019 (Table 6), including analytical standard errors (GLS).
 With our estimator, however, we are able to also produce both robust and clustered standard errors for location and scale coefficients.
-Except for few cases, Robust and Clustered standard errors are larger than GLS standard errors, which may be an indication of misspecification of the model.
-The GLS standard errors we report differ from the ones in MSS, because they use panel standard errors, equivalent to our clustered standard errors, instead of the analytical standard errors we derive.
+Except for a few cases, robust and clustered standard errors are larger than GLS standard errors, which may be an indication of misspecification of the model.
+The GLS standard errors we report differ from the ones in MSS because they use panel standard errors, which are equivalent to our clustered standard errors, instead of the analytical standard errors we derive.
 
@@
 In @tbl-tb2, we report the results including both individual and year fixed effects.
-Because Oil prices only vary across years, the variableis excluded from the model specification.
-Accounting for time fixed effects, does not change the general conclusions one could make based no the results from @tbl-tb1.
-The two largest differences are that the log of income percapita has a positive effect on Goverment Surpluses, but only for the 25th quantile, because of the largest impact on the Scale component.
-Similarly, we observe that the income gap now has an impact on Goverment surplus that is always negative, but increasing across quantiles.
+Because oil prices only vary across years, the variable is excluded from the model specification.
+Accounting for time fixed effects does not change the general conclusions one could make based on the results from @tbl-tb1.
+The two largest differences are that the log of income per capita has a positive effect on Government Surpluses, but only for the 25th quantile, because of the largest impact on the Scale component.
+Similarly, we observe that the income gap now has an impact on Government surplus that is always negative, but increasing across quantiles.
 In both instances, the effects are not statistically significant.
@@
 
-# Appendix {.appendix}{#sec-appendix}
+# Appendix {#sec-appendix}
 
-## Model Identification
+## Derivation of the influence functions
+
+### Model Identification
 
@@
 $$\begin{aligned}
-y = x\beta + \nu \\
-\nu = \varepsilon \times x\gamma
+y_i = x_i'\beta + \nu_i \\
+\nu_i = \varepsilon_i \times x_i'\gamma
 \end{aligned}
@@
 
-$$q(y|\tau,X) = x(\beta + q(\varepsilon |\tau) \times \gamma)$$
+$$q(y|\tau,x) = x'(\beta + q(\varepsilon |\tau) \times \gamma)$$
 
@@
 
-## Estimation of the variance-covariance matrix
+### Estimation of the variance-covariance matrix
 
@@
 
-### First Moment Condition: Location Model
+#### First Moment Condition: Location Model
 
@@
 
-### Second Moment Condition: Scale model
+#### Second Moment Condition: Scale model
 
@@
 
-### Third Moment Condition: Quantile of Standardized Residual
+#### Third Moment Condition: Quantile of Standardized Residual
 
@@
 
-## Influence functions
+### Influence functions
 
-### Location coefficients
+#### Location coefficients
 
@@
 
-### Scale Coefficients coefficients**
+#### Scale Coefficients
 
@@
 
-### Quantile of standardized residual
+#### Quantile of standardized residual
 
@@
 
+## Implementation
+
+The method described here can be implemented using any of the following packages
+
+- `mmqreg` in Stata: Installed from Github
+- `mmqreg` in R: Programs Available in Github
+- `mmqreg` in Python: 
+- `mmqreg` in julia:
+
 # References {.unnumbered}

### 2023-10-31 article/article.tex
update
First Draft except conclusions

@@
   authoryear,
-  preprint,
+  review,
   1p]{elsarticle}
@@
 \makeatletter
-\makeatother
-\makeatletter
-\makeatother
-\makeatletter
 \@ifpackageloaded{caption}{}{\usepackage{caption}}
@@
 \makeatletter
+\makeatother
+\makeatletter
 \@ifpackageloaded{caption}{}{\usepackage{caption}}
 \@ifpackageloaded{subcaption}{}{\usepackage{subcaption}}
-\makeatother
-\makeatletter
-\@ifpackageloaded{tcolorbox}{}{\usepackage[skins,breakable]{tcolorbox}}
-\makeatother
-\makeatletter
-\@ifundefined{shadecolor}{\definecolor{shadecolor}{rgb}{.97, .97, .97}}
-\makeatother
-\makeatletter
-\makeatother
-\makeatletter
 \makeatother
@@
 proposed method in the presence of two sets of fixed effects. Finally,
-we apply the proposed method to estimate \textbf{something interesting}
+we apply the proposed method to estimate the determinants of the surplus
+of government as a share of GDP allowing for both time and country fixed
+effects.
 \end{abstract}
@@
 \end{frontmatter}
-    \ifdefined\Shaded\renewenvironment{Shaded}{\begin{tcolorbox}[breakable, boxrule=0pt, borderline west={3pt}{0pt}{shadecolor}, frame hidden, interior hidden, enhanced, sharp corners]}{\end{tcolorbox}}\fi
-
-\hypertarget{introduction}{%
-\section{Introduction}\label{introduction}}
+    \section{Introduction}\label{introduction}
 
@@
 
-\hypertarget{methodology}{%
-\section{Methodology}\label{methodology}}
-
-\hypertarget{sec-betas}{%
-\subsection{Quantile Regression: Location-Scale model}\label{sec-betas}}
+\section{Methodology}\label{sec-method}
+
+\subsection{Quantile Regression: Location-Scale model}\label{sec-betas}
 
@@
 
-\begin{equation}\protect\hypertarget{eq-eq1}{}{q(Y|X,\tau) =X\beta(\tau)
-}\label{eq-eq1}\end{equation}
+\begin{equation}\phantomsection\label{eq-eq1}{q(Y|X,\tau) =X\beta(\tau)
+}\end{equation}
 
@@
 
-\begin{equation}\protect\hypertarget{eq-eq2}{}{q(Y|X,\tau) =X\beta+X\gamma(\tau)
-}\label{eq-eq2}\end{equation}
+\begin{equation}\phantomsection\label{eq-eq2}{q(Y|X,\tau) =X\beta+X\gamma(\tau)
+}\end{equation}
 
@@
 
-\begin{equation}\protect\hypertarget{eq-eq3}{}{\hat{\beta}(\tau) = \underset{\beta}{\operatorname{argmin}}
+\begin{equation}\phantomsection\label{eq-eq3}{\hat{\beta}(\tau) = \underset{\beta}{\operatorname{argmin}}
 \left( \sum_{i\in y_i\geq x_i'\beta} \tau (y_i - x_i'\beta) - \sum_{i\in y_i<x_i'\beta} (1-\tau)(y_i - x_i'\beta) \right)
-}\label{eq-eq3}\end{equation}
+}\end{equation}
 
@@
 
-\begin{equation}\protect\hypertarget{eq-eq4}{}{\begin{aligned}
+\begin{equation}\phantomsection\label{eq-eq4}{\begin{aligned}
 y_i &=x_i'\beta+\nu_i \\
@@
 \end{aligned}
-}\label{eq-eq4}\end{equation}
+}\end{equation}
 
@@
 
-\begin{equation}\protect\hypertarget{eq-eq5}{}{q(Y|X,\tau) =X\beta+q(\varepsilon|\tau) \times X\gamma 
-}\label{eq-eq5}\end{equation}
+\begin{equation}\phantomsection\label{eq-eq5}{q(Y|X,\tau) =X\beta+q(\varepsilon|\tau) \times X\gamma 
+}\end{equation}
 
@@
 
-\begin{equation}\protect\hypertarget{eq-eq6}{}{\beta(\tau) = \beta + q(\varepsilon|\tau) \times \gamma 
-}\label{eq-eq6}\end{equation}
+\begin{equation}\phantomsection\label{eq-eq6}{\beta(\tau) = \beta + q(\varepsilon|\tau) \times \gamma 
+}\end{equation}
 
@@
 
-\begin{equation}\protect\hypertarget{eq-eq7}{}{\begin{aligned}
+\begin{equation}\phantomsection\label{eq-eq7}{\begin{aligned}
       y_i &=x_i'\beta+\nu_i \\
@@
       \end{aligned}
-}\label{eq-eq7}\end{equation}
+}\end{equation}
 
@@
 
-\begin{equation}\protect\hypertarget{eq-eq8}{}{\begin{aligned}
+\begin{equation}\phantomsection\label{eq-eq8}{\begin{aligned}
   |\nu_i| &=x_i'\gamma+\omega_i \\
@@
   \end{aligned}
-}\label{eq-eq8}\end{equation}
+}\end{equation}
 
@@
 
-\begin{equation}\protect\hypertarget{eq-eq9}{}{\begin{aligned}
+\begin{equation}\phantomsection\label{eq-eq9}{\begin{aligned}
   E\left[  \mathbb{1}\left(x_i' (\beta + \gamma q(\varepsilon|\tau)) \geq y_i \right) - \tau \right] &=0  \\
@@
   \end{aligned}
-}\label{eq-eq9}\end{equation}
+}\end{equation}
 
@@
 
-\hypertarget{sec-se}{%
-\subsection{Standard Errors: GLS, Robust, Clustered}\label{sec-se}}
+\subsection{Standard Errors: GLS, Robust, Clustered}\label{sec-se}
 
@@
 
-\begin{equation}\protect\hypertarget{eq-eq10}{}{\begin{aligned}
+\begin{equation}\phantomsection\label{eq-eq10}{\begin{aligned}
   E[x_i \nu_i  ] &= E[h_{1,i}]=0 \\
@@
   \end{aligned}
-}\label{eq-eq10}\end{equation}
+}\end{equation}
 
@@
 
-\begin{equation}\protect\hypertarget{eq-eqqtile}{}{\Xi = [ I(k), \hat q(\varepsilon|\tau) \times I(k), \hat \gamma ]
-}\label{eq-eqqtile}\end{equation}
+\begin{equation}\phantomsection\label{eq-eqqtile}{\Xi = [ I(k), \hat q(\varepsilon|\tau) \times I(k), \hat \gamma ]
+}\end{equation}
 
@@
 as:
-\begin{equation}\protect\hypertarget{eq-eqvcv}{}{\hat{V}(\theta) = \frac{1}{N^2} \sum_{i=1}^N \lambda_i(\theta) \lambda_i(\theta)'
-}\label{eq-eqvcv}\end{equation}
+
+\begin{equation}\phantomsection\label{eq-eqvcv}{\hat{V}(\theta) = \frac{1}{N^2} \sum_{i=1}^N \lambda_i(\theta) \lambda_i(\theta)'
+}\end{equation}
 
@@
 
-\begin{equation}\protect\hypertarget{eq-ifs}{}{\begin{aligned}
+\begin{equation}\phantomsection\label{eq-ifs}{\begin{aligned}
 \lambda_i(\theta)&=
@@
 \end{aligned}
-}\label{eq-ifs}\end{equation}
+}\end{equation}
 
@@
 
-\hypertarget{robust-standard-errors}{%
-\subsubsection{Robust Standard Errors}\label{robust-standard-errors}}
+\subsubsection{Robust Standard Errors}\label{robust-standard-errors}
 
@@
 
-\hypertarget{clustered-standard-errors}{%
 \subsubsection{Clustered Standard
-Errors}\label{clustered-standard-errors}}
+Errors}\label{clustered-standard-errors}
 
@@
 
-\hypertarget{gls-standard-errors}{%
-\subsubsection{GLS Standard Errors}\label{gls-standard-errors}}
+\subsubsection{GLS Standard Errors}\label{gls-standard-errors}
 
@@
 
-\hypertarget{multiple-fixed-effects-expanding-on-mss2019}{%
 \subsection{\texorpdfstring{Multiple Fixed Effects: Expanding on
-\citet{mss2019}}{Multiple Fixed Effects: Expanding on @mss2019}}\label{multiple-fixed-effects-expanding-on-mss2019}}
+\citet{mss2019}}{Multiple Fixed Effects: Expanding on @mss2019}}\label{multiple-fixed-effects-expanding-on-mss2019}
 
@@
 
-\hypertarget{simulation-evidence}{%
-\section{Simulation Evidence}\label{simulation-evidence}}
-
-To show the performance of the extended strategy, we implement the
-results of a small simulation study. We consider a simple model with a
-single explanatory variable \(x\), and a single fixed effect \(g\). The
-data generating process is as follows:
-
-\hypertarget{illustrative-application}{%
-\section{Illustrative application}\label{illustrative-application}}
+\section{Simulation Evidence}\label{simulation-evidence}
+
+To show the performance of the extended strategy, we implement a small
+simulation study. We consider a simple model with a single explanatory
+variable \(x\). In contrast with MSS, we consider a two-way fixed effect
+structure that is more general than the panel structure used in by the
+authors. For this excercise, we consider the following data generating
+process:
+
+\[y_i = \alpha_{1i} + \alpha_{2i} + x_i + (1+x_i + \alpha_{1i} + \alpha_{2i} ) \varepsilon_i
+\]
+
+where \(\alpha_{1i}\sim \chi^2(1)\), \(\alpha_{2i} \sim \chi^2(1)\) and
+\(x_i = 0.5 * (\chi_i +0.5(\alpha_{1i}+\alpha_{2i}))\) with
+\(\chi_i \sim \chi^2(1)\). We only consider the case when the error term
+\(\varepsilon_i\) is assumed to be normally distributed with mean zero
+and standard deviation 0.5. We assume that there are 50 mutually
+exclusive fixed effect groups for each set of fixed effects.
+Observations are assigned to each subgroup randomly, using a uniform
+distribution between 1 and 50. We consider a sample sizes of 500, 1000,
+2000 and 4000 observations, which implies an average of 10, 20, 40 and
+80 observations per group. The model is estimated using the
+location-scale model with heteroskedastic linear errors, and we report
+the coefficients for the 25th and 75th quantiles. We run this excercise
+5000 times. Table~\ref{tbl-sim1} reports the bias, simulated standard
+error and mean squared error. We also report the results obtained using
+an adaptation bias-corrected estimator based on the split-panel
+jackknife estimator proposed by \citet{dhaene2015}.\footnote{For the
+  implementation, we estimate the model using the full sample, then,
+  randomly assign each observation into one of two groups, and
+  re-estimate the quantile coefficients for each group. The
+  bias-corrected estimator is then obtained as
+  \(\hat\beta(\tau)_{jkc}=2*\hat\beta(\tau)_{full}-0.5*\big(\hat\beta(\tau)_{s1}+\hat\beta(\tau)_{s1}\big)\).}
+These results are labeled JKC.
+
+Similar to the findings in MSS, we find that the estimator presents a
+bias when the sample is small (\(N=500\)), but this bias shrinks as the
+sample sizes increases. As MSS describes, the bias seems to be
+proportional to the sample size, or more precisely to \(N/N_{g1}\) and
+\(N/N_{g2}\), where \(N_{g1}\) and \(N_{g2}\) are the average number of
+observations per group. Interestingly, the bias-corrected estimator
+presents an almost zero bias, even when the samples are is small (about
+10 observations per sub-group). Also replicating the results of MSS,
+despite bias reduction obtained using the JKC estimator, the standard
+errors and mean squared error (MSE) are larger than without correction.
+
+\begin{table}
+
+\caption{\label{tbl-sim1}Bias, Simulated Standard error, and Mean
+Squared Error}
+
+\begin{minipage}[t]{0.50\linewidth}
+
+\begin{longtable}[]{@{}lccc@{}}
+\toprule\noalign{}
+N = 500 & Bias & Sim SE & MSE \\
+\midrule\noalign{}
+\endhead
+\bottomrule\noalign{}
+\endlastfoot
+q25 & & & \\
+~mmqreg & 0.104 & 0.247 & 0.072 \\
+~jkc & 0.008 & 0.297 & 0.088 \\
+q75 & & & \\
+~mmqreg & -0.091 & 0.251 & 0.071 \\
+~jkc & 0.002 & 0.303 & 0.092 \\
+\end{longtable}
+
+\end{minipage}%
+%
+\begin{minipage}[t]{0.50\linewidth}
+
+\begin{longtable}[]{@{}lccc@{}}
+\toprule\noalign{}
+N = 1000 & Bias & Sim SE & MSE \\
+\midrule\noalign{}
+\endhead
+\bottomrule\noalign{}
+\endlastfoot
+q25 & & & \\
+~mmqreg & 0.050 & 0.173 & 0.032 \\
+~jkc & -0.001 & 0.191 & 0.036 \\
+q75 & & & \\
+~mmqreg & -0.044 & 0.176 & 0.033 \\
+~jkc & 0.006 & 0.195 & 0.038 \\
+\end{longtable}
+
+\end{minipage}%
+\newline
+\begin{minipage}[t]{0.50\linewidth}
+
+\begin{longtable}[]{@{}lccc@{}}
+\toprule\noalign{}
+N = 1000 & Bias & Sim SE & MSE \\
+\midrule\noalign{}
+\endhead
+\bottomrule\noalign{}
+\endlastfoot
+q25 & & & \\
+~mmqreg & 0.025 & 0.122 & 0.016 \\
+~jkc & 0.003 & 0.129 & 0.017 \\
+q75 & & & \\
+~mmqreg & -0.023 & 0.124 & 0.016 \\
+~jkc & 0.001 & 0.131 & 0.017 \\
+\end{longtable}
+
+\end{minipage}%
+%
+\begin{minipage}[t]{0.50\linewidth}
+
+\begin{longtable}[]{@{}lccc@{}}
+\toprule\noalign{}
+N = 2000 & Bias & Sim SE & MSE \\
+\midrule\noalign{}
+\endhead
+\bottomrule\noalign{}
+\endlastfoot
+q25 & & & \\
+~mmqreg & 0.012 & 0.087 & 0.008 \\
+~jkc & 0.000 & 0.089 & 0.008 \\
+q75 & & & \\
+~mmqreg & -0.011 & 0.087 & 0.008 \\
+~jkc & 0.000 & 0.089 & 0.008 \\
+\end{longtable}
+
+\end{minipage}%
+
+\end{table}%
+
+As described in section Section~\ref{sec-se}, GLS-Standard errors may
+not be appropriate if heteroskedasticity in the model is misspecified.
+This could happen if the heteroskedasticity is not linear in parameters,
+or if there is correlations within groups. To show the performance of
+the GLS-Standard errors, we consider two additional simulations. To see
+the impact of heteroskedasticity misspecification, we assume the DGP is
+given by:
+
+\[y_i = \alpha_{1i} + \alpha_{2i} + x_i + (1+x_i + \sqrt{x_i} +\alpha_{1i} + \alpha_{2i} ) \varepsilon_i
+\]
+
+To show the impact of ignoring correlation within groups, we consider
+the case where the error \(\varepsilon\) is correlated within groups
+defined by the first fixed effect. Specifically:
+
+\[\varepsilon_i =0.5*(\sqrt{0.5} z_i + \sqrt{0.5} w_g)\]
+
+where \(z_i~N(0,1)\) and \(w_g~N(0,1)\), with \(g\) being the \(g_{th}\)
+group defined by the first fixed effect.
+
+For the simulation, we run the excercise 5000 times, using a sample of
+size \(N=2000\). The results from both simulations are reported in the
+Table~\ref{tbl-sim2}. We report the average coefficient, simulation
+based Standard errors, and the standard errors using GLS, robust and
+clustered estimations.
+
+\begin{longtable}[]{@{}
+  >{\raggedright\arraybackslash}p{(\columnwidth - 8\tabcolsep) * \real{0.2000}}
+  >{\centering\arraybackslash}p{(\columnwidth - 8\tabcolsep) * \real{0.2000}}
+  >{\centering\arraybackslash}p{(\columnwidth - 8\tabcolsep) * \real{0.2000}}
+  >{\centering\arraybackslash}p{(\columnwidth - 8\tabcolsep) * \real{0.2000}}
+  >{\centering\arraybackslash}p{(\columnwidth - 8\tabcolsep) * \real{0.2000}}@{}}
+\caption{Heteroskedasticity misspecification and clustered
+errors}\label{tbl-sim2}\tabularnewline
+\toprule\noalign{}
+\begin{minipage}[b]{\linewidth}\raggedright
+\end{minipage} & \begin{minipage}[b]{\linewidth}\centering
+Het:q25
+\end{minipage} & \begin{minipage}[b]{\linewidth}\centering
+Het:q75
+\end{minipage} & \begin{minipage}[b]{\linewidth}\centering
+Clust:q25
+\end{minipage} & \begin{minipage}[b]{\linewidth}\centering
+Clust:q75
+\end{minipage} \\
+\midrule\noalign{}
+\endfirsthead
+\toprule\noalign{}
+\begin{minipage}[b]{\linewidth}\raggedright
+\end{minipage} & \begin{minipage}[b]{\linewidth}\centering
+Het:q25
+\end{minipage} & \begin{minipage}[b]{\linewidth}\centering
+Het:q75
+\end{minipage} & \begin{minipage}[b]{\linewidth}\centering
+Clust:q25
+\end{minipage} & \begin{minipage}[b]{\linewidth}\centering
+Clust:q75
+\end{minipage} \\
+\midrule\noalign{}
+\endhead
+\bottomrule\noalign{}
+\endlastfoot
+Coefficient & 0.550 & 1.442 & 0.775 & 1.229 \\
+SIM\_SE & 0.154 & 0.155 & 0.109 & 0.107 \\
+GLS\_SE & 0.476 & 0.451 & 0.288 & 0.221 \\
+Robust & 0.140 & 0.139 & 0.087 & 0.088 \\
+Cluster & & & 0.097 & 0.097 \\
+\end{longtable}
+
+One of the conclusions from the results in Table~\ref{tbl-sim2} is that
+the results for the 25th and 75th quantiles are mostly identical,
+because of the symmetric error we used in the simulation. On the one
+hand, because the error structure is misspecified, we should expect to
+see a large bias in the estimated coefficients, especially in cases of
+misspecified heteroskedasticity. However, the purpose of this exercise
+is not to demonstrate the unbiasedness of the coefficients, but rather
+to assess the performance of the standard error estimation.
+
+As expected, the GLS-standard errors are biased, and the bias is larger
+in the case of misspecified heteroskedasticity. In fact, with
+heteroskedastic misspecification, the average GLS-SE (.476) is almost
+three times as large as the simulation-based standard error (0.154). In
+this first case, robust standard errors perform better, but with a small
+difference (0.14 to 0.154). In the case of clustered correlation, GLS-SE
+also performs poorly. Robust standard errors perform better, but seem to
+underestimate the magnitude of the true standard errors. Finally,
+cluster standard errors perform the best, with a small difference
+between the simulation-based standard errors (0.097 to 0.109).
+
+\section{Illustrative application}\label{illustrative-application}
 
@@
 
-\hypertarget{tbl-tb1}{}
 \begin{longtable}[]{@{}
@@
   >{\centering\arraybackslash}p{(\columnwidth - 18\tabcolsep) * \real{0.0989}}@{}}
-\caption{\label{tbl-tb1}The determinants of government surpluses:
-Individual Fixed effects}\tabularnewline
+\caption{The determinants of government surpluses: Individual Fixed
+effects}\label{tbl-tb1}\tabularnewline
 \toprule\noalign{}
@@
 As expected, Table~\ref{tbl-tb1} shows that point estimates for the
-point estimates for the quantile regressions are identical to the ones
-reported in \citet{mss2019} (table 6), including analytical standard
-errors (GLS). With our estimator, however, we are able to also produce
-both robust and clustered standard errors for location and scale
-coefficients. Except for few cases, Robust and Clustered standard errors
-are larger than GLS standard errors, which may be an indication of
-misspecification of the model. The GLS standard errors we report differ
-from the ones in MSS, because they use panel standard errors, equivalent
-to our clustered standard errors, instead of the analytical standard
-errors we derive.
+point estimates are identical to the ones reported in \citet{mss2019}
+(Table 6), including analytical standard errors (GLS). With our
+estimator, however, we are able to also produce both robust and
+clustered standard errors for location and scale coefficients. Except
+for a few cases, robust and clustered standard errors are larger than
+GLS standard errors, which may be an indication of misspecification of
+the model. The GLS standard errors we report differ from the ones in MSS
+because they use panel standard errors, which are equivalent to our
+clustered standard errors, instead of the analytical standard errors we
+derive.
 
@@
 In Table~\ref{tbl-tb2}, we report the results including both individual
-and year fixed effects. Because Oil prices only vary across years, the
-variableis excluded from the model specification. Accounting for time
-fixed effects, does not change the general conclusions one could make
-based no the results from Table~\ref{tbl-tb1}. The two largest
-differences are that the log of income percapita has a positive effect
-on Goverment Surpluses, but only for the 25th quantile, because of the
+and year fixed effects. Because oil prices only vary across years, the
+variable is excluded from the model specification. Accounting for time
+fixed effects does not change the general conclusions one could make
+based on the results from Table~\ref{tbl-tb1}. The two largest
+differences are that the log of income per capita has a positive effect
+on Government Surpluses, but only for the 25th quantile, because of the
 largest impact on the Scale component. Similarly, we observe that the
-income gap now has an impact on Goverment surplus that is always
+income gap now has an impact on Government surplus that is always
 negative, but increasing across quantiles. In both instances, the
@@
 
-\hypertarget{tbl-tb2}{}
 \begin{longtable}[]{@{}
@@
   >{\centering\arraybackslash}p{(\columnwidth - 14\tabcolsep) * \real{0.1233}}@{}}
-\caption{\label{tbl-tb2}The determinants of government surpluses:
-Individual and Time Fixed effects}\tabularnewline
+\caption{The determinants of government surpluses: Individual and Time
+Fixed effects}\label{tbl-tb2}\tabularnewline
 \toprule\noalign{}
@@
 
-\hypertarget{conclusions}{%
-\section{Conclusions}\label{conclusions}}
-
-\hypertarget{sec-appendix}{%
-\section{Appendix \{.appendix\}}\label{sec-appendix}}
-
-\hypertarget{model-identification}{%
-\subsection{Model Identification}\label{model-identification}}
+\section{Conclusions}\label{conclusions}
+
+\section{Appendix}\label{sec-appendix}
+
+\subsection{Derivation of the influence
+functions}\label{derivation-of-the-influence-functions}
+
+\subsubsection{Model Identification}\label{model-identification}
 
@@
 \[\begin{aligned}
-y = x\beta + \nu \\
-\nu = \varepsilon \times x\gamma
+y_i = x_i'\beta + \nu_i \\
+\nu_i = \varepsilon_i \times x_i'\gamma
 \end{aligned}
@@
 
-\[q(y|\tau,X) = x(\beta + q(\varepsilon |\tau) \times \gamma)\]
+\[q(y|\tau,x) = x'(\beta + q(\varepsilon |\tau) \times \gamma)\]
 
@@
 
-\hypertarget{estimation-of-the-variance-covariance-matrix}{%
-\subsection{Estimation of the variance-covariance
-matrix}\label{estimation-of-the-variance-covariance-matrix}}
+\subsubsection{Estimation of the variance-covariance
+matrix}\label{estimation-of-the-variance-covariance-matrix}
 
@@
 
-\hypertarget{first-moment-condition-location-model}{%
-\subsubsection{First Moment Condition: Location
-Model}\label{first-moment-condition-location-model}}
+\paragraph{First Moment Condition: Location
+Model}\label{first-moment-condition-location-model}
 
@@
 
-\hypertarget{second-moment-condition-scale-model}{%
-\subsubsection{Second Moment Condition: Scale
-model}\label{second-moment-condition-scale-model}}
+\paragraph{Second Moment Condition: Scale
+model}\label{second-moment-condition-scale-model}
 
@@
 
-\hypertarget{third-moment-condition-quantile-of-standardized-residual}{%
-\subsubsection{Third Moment Condition: Quantile of Standardized
-Residual}\label{third-moment-condition-quantile-of-standardized-residual}}
+\paragraph{Third Moment Condition: Quantile of Standardized
+Residual}\label{third-moment-condition-quantile-of-standardized-residual}
 
@@
 
-\hypertarget{influence-functions}{%
-\subsection{Influence functions}\label{influence-functions}}
-
-\hypertarget{location-coefficients}{%
-\subsubsection{Location coefficients}\label{location-coefficients}}
+\subsubsection{Influence functions}\label{influence-functions}
+
+\paragraph{Location coefficients}\label{location-coefficients}
 
@@
 
-\hypertarget{scale-coefficients-coefficients}{%
-\subsubsection{Scale Coefficients
-coefficients**}\label{scale-coefficients-coefficients}}
+\paragraph{Scale Coefficients}\label{scale-coefficients}
 
@@
 
-\hypertarget{quantile-of-standardized-residual}{%
-\subsubsection{Quantile of standardized
-residual}\label{quantile-of-standardized-residual}}
+\paragraph{Quantile of standardized
+residual}\label{quantile-of-standardized-residual}
 
@@
 
+\subsection{Implementation}\label{implementation}
+
+The method described here can be implemented using any of the following
+packages
+
+\begin{itemize}
+\tightlist
+\item
+  \texttt{mmqreg} in Stata: Installed from Github
+\item
+  \texttt{mmqreg} in R: Programs Available in Github
+\item
+  \texttt{mmqreg} in Python:
+\item
+  \texttt{mmqreg} in julia:
+\end{itemize}
+
 \renewcommand\refname{References}

### 2023-11-01 article/article.qmd
1
1

@@
     email: leo@gmail.com
+    affiliations:
+        - name: Universidad Catolica Boliviana
+          id: ucb
   - name: Gustavo Canavire-Bacarreza
@@
           name: World Bank
+    note: |
+      The opinions expressed in this paper are those of the authors and do not necessarily reflect the views of the World Bank, its Board of Directors, or the countries it represents         
 abstract: |
@@
 
-1.
-The location model can be estimated using a standard linear regression model, where the dependent variable is the outcome $Y$, and the independent variables are the explanatory variables $X$ (including a constant) with an error $u$, which is by definition heteroskedastic.
+First, the location model can be estimated using a standard linear regression model, where the dependent variable is the outcome $Y$, and the independent variables are the explanatory variables $X$ (including a constant) with an error $u$, which is by definition heteroskedastic.
 In this case, the location model coefficients are identified under the following condition:
@@
 
-2.
-After the location model is estimated, the scale coefficients can be identified by modeling heteroskedasticity as a linear function of characteristics $X$.
+Second, after the location model is estimated, the scale coefficients can be identified by modeling heteroskedasticity as a linear function of characteristics $X$.
 For this we use the absolute value of the errors from the location model $u$ as dependent variable, which would allow us to estimate the conditional standard deviation (rather than conditional variance) of the errors.
@@
 
-3.  Finally, given the location and scale coefficients, the $\tau_{th}$ quantile of the error $\varepsilon$ can be estimated using the following condition:
+Thurd, given the location and scale coefficients, the $\tau_{th}$ quantile of the error $\varepsilon$ can be estimated using the following condition:
 
@@
 
-[^7]: The derivation of the influence functions can be found in @sec-appendix.
+[^7]: The derivation of the influence functions can be found in the appendix.
 
@@
 
-1.  For all dependent and independent variables in the model ($w=y,x$), we partial out the group fixed effects, and obtain the centered-residualized variables:
+First, for all dependent and independent variables in the model ($w=y,x$), we partial out the group fixed effects, and obtain the centered-residualized variables:
 
@@
 
-2.  We estimate the location model using the centered-residualized variables:[^rc]
+Afterwards, we estimate the location model using the centered-residualized variables:[^rc]
 
@@
 
-3.  Since $|\hat \nu_i|$ is the dependent variable for the scale model, we apply the partialling out and recentering to this expression ($|\hat \nu_i|^{rc}$), and use that to estimate the model:
+Since $|\hat \nu_i|$ is the dependent variable for the scale model, we apply the partialling out and recentering to this expression ($|\hat \nu_i|^{rc}$), and use that to estimate the model:
 
@@
 
-4.  Finally the standardized residuals $\varepsilon_i$ can be obtained as follows
+Finally the standardized residuals $\varepsilon_i$ can be obtained as follows
 
@@
 We consider a simple model with a single explanatory variable $x$.
-In contrast with MSS, we consider a two-way fixed effect structure that is more general than the panel structure used in by the authors.
+In contrast with MSS, we consider a two-way fixed effect structure that is more general than the panel structure.
 For this excercise, we consider the following data generating process:
@@
 where $\alpha_{1i}\sim \chi^2(1)$, $\alpha_{2i} \sim \chi^2(1)$ and $x_i = 0.5 * (\chi_i +0.5(\alpha_{1i}+\alpha_{2i}))$ with $\chi_i \sim \chi^2(1)$.
-We only consider the case when the error term $\varepsilon_i$ is assumed to be normally distributed with mean zero and standard deviation 0.5.
+We only consider the case when the error term $\varepsilon_i$ is assumed to be normally distributed with mean zero and standard deviation of 0.5.
 We assume that there are 50 mutually exclusive fixed effect groups for each set of fixed effects.
@@
 
-# Appendix {#sec-appendix}
+In this paper, we have extended the methodology proposed by @mss2019, allowing for the estimation of quantile regression models with multiple sets of fixed effects, as well as alternative Standard Errors estimations.
+This methodology would allow researchers to implement more comprehensive analysis of datasets characterized by complex hierarchies and unobserved heterogeneity.
+This extension is particularly valuable in contexts where group specific effects vary across the conditional distribution of the outcome of interest.
 
-## Derivation of the influence functions
+Using a small simulation study, we show that our extended approach is as effective in identifying the parameters of interest as @mss2019 indicated, even in contexts with two sets of fixed effects.
+Notably, the bias-corrected estimator based on the split-panel jackknife estimator exhibits promising results, mitigating biases when samples are small, but increasing standard errors.
 
-### Model Identification
+Furthermore, we have assessed the impact of misspecified heteroskedasticity and intra-cluster correlation on the performance of standard error estimations.
+Our findings emphasize the importance of using appropriate standard error estimators to ensure accurate inference.
+In particular, we find that GLS standard errors are biased when the model heteroskedasticity is misspecified, and that robust and clustered standard errors perform better in these cases.
+This may also suggest a venue for future research, testing the validity of the location-scale model assumption.
+
+# References {.unnumbered}
+
+::: {#refs}
+:::
+
+{{< pagebreak >}}
+
+\appendix
+
+# Derivation of the influence functions
+
+## Model Identification
 
@@
 
-### Estimation of the variance-covariance matrix
+## Estimation of the variance-covariance matrix
 
@@
 
-#### First Moment Condition: Location Model
+**First Moment Condition: Location Model**
 
@@
 
-#### Second Moment Condition: Scale model
+**Second Moment Condition: Scale model**
 
@@
 
-#### Third Moment Condition: Quantile of Standardized Residual
+**Third Moment Condition: Quantile of Standardized Residual**
 
@@
 
-### Influence functions
+## Influence functions
 
-#### Location coefficients
+**Location coefficients**
 
@@
 
-#### Scale Coefficients
+**Scale Coefficients**
 
@@
 
-#### Quantile of standardized residual
+**Quantile of standardized residual**
 
@@
 
-## Implementation
+# Implementation
 
@@
 
-- `mmqreg` in Stata: Installed from Github
+- `mmqreg` in Stata: `net install mmqre, from(https://friosavila.github.io/stpackages)
 - `mmqreg` in R: Programs Available in Github
@@
 - `mmqreg` in julia:
-
-# References {.unnumbered}

### 2023-11-01 article/article.tex
1
1

@@
  \ead{friosavi@levy.org} 
-\author[]{Leonardo Siles%
+\author[2]{Leonardo Siles%
 %
@@
  \ead{leo@gmail.com} 
-\author[2]{Gustavo Canavire-Bacarreza%
+\author[3]{Gustavo Canavire-Bacarreza%
 %
-}
+\fnref{fn1}}
  \ead{gcanavire@worldbank.org}
@@
 College},,postcodesep={}}
-\affiliation[2]{organization={World Bank},,postcodesep={}}
+\affiliation[2]{organization={Universidad Catolica
+Boliviana},,postcodesep={}}
+\affiliation[3]{organization={World Bank},,postcodesep={}}
 
 \cortext[cor1]{Corresponding author}
+
+\fntext[fn1]{The opinions expressed in this paper are those of the
+authors and do not necessarily reflect the views of the World Bank, its
+Board of Directors, or the countries it represents}
 
@@
 
-\begin{enumerate}
-\def\labelenumi{\arabic{enumi}.}
-\tightlist
-\item
-  The location model can be estimated using a standard linear regression
-  model, where the dependent variable is the outcome \(Y\), and the
-  independent variables are the explanatory variables \(X\) (including a
-  constant) with an error \(u\), which is by definition heteroskedastic.
+First, the location model can be estimated using a standard linear
+regression model, where the dependent variable is the outcome \(Y\), and
+the independent variables are the explanatory variables \(X\) (including
+a constant) with an error \(u\), which is by definition heteroskedastic.
 In this case, the location model coefficients are identified under the
 following condition:
-\end{enumerate}
 
@@
 
-\begin{enumerate}
-\def\labelenumi{\arabic{enumi}.}
-\setcounter{enumi}{1}
-\tightlist
-\item
-  After the location model is estimated, the scale coefficients can be
-  identified by modeling heteroskedasticity as a linear function of
-  characteristics \(X\). For this we use the absolute value of the
-  errors from the location model \(u\) as dependent variable, which
-  would allow us to estimate the conditional standard deviation (rather
-  than conditional variance) of the errors. In this case, the
-  coefficients are identified under the following condition:
-\end{enumerate}
+Second, after the location model is estimated, the scale coefficients
+can be identified by modeling heteroskedasticity as a linear function of
+characteristics \(X\). For this we use the absolute value of the errors
+from the location model \(u\) as dependent variable, which would allow
+us to estimate the conditional standard deviation (rather than
+conditional variance) of the errors. In this case, the coefficients are
+identified under the following condition:
 
@@
 
-\begin{enumerate}
-\def\labelenumi{\arabic{enumi}.}
-\setcounter{enumi}{2}
-\tightlist
-\item
-  Finally, given the location and scale coefficients, the \(\tau_{th}\)
+Thurd, given the location and scale coefficients, the \(\tau_{th}\)
 quantile of the error \(\varepsilon\) can be estimated using the
 following condition:
-\end{enumerate}
 
@@
 are:\footnote{The derivation of the influence functions can be found in
-  Section~\ref{sec-appendix}.}
+  the appendix.}
 
@@
 
-\begin{enumerate}
-\def\labelenumi{\arabic{enumi}.}
-\tightlist
-\item
-  For all dependent and independent variables in the model (\(w=y,x\)),
-  we partial out the group fixed effects, and obtain the
+First, for all dependent and independent variables in the model
+(\(w=y,x\)), we partial out the group fixed effects, and obtain the
 centered-residualized variables:
-\end{enumerate}
 
@@
 
-\begin{enumerate}
-\def\labelenumi{\arabic{enumi}.}
-\setcounter{enumi}{1}
-\tightlist
-\item
-  We estimate the location model using the centered-residualized
-  variables:\footnote{Using centered-residualized variables allow us to
-    include a constant in the model specification, which simplifies the
-    derivation of the influence functions. However, as with other fixed
-    effects models, the constant is not identified, and thus should not
-    be interpreted.}
-\end{enumerate}
+Afterwards, we estimate the location model using the
+centered-residualized variables:\footnote{Using centered-residualized
+  variables allow us to include a constant in the model specification,
+  which simplifies the derivation of the influence functions. However,
+  as with other fixed effects models, the constant is not identified,
+  and thus should not be interpreted.}
 
@@
 
-\begin{enumerate}
-\def\labelenumi{\arabic{enumi}.}
-\setcounter{enumi}{2}
-\tightlist
-\item
-  Since \(|\hat \nu_i|\) is the dependent variable for the scale model,
-  we apply the partialling out and recentering to this expression
+Since \(|\hat \nu_i|\) is the dependent variable for the scale model, we
+apply the partialling out and recentering to this expression
 (\(|\hat \nu_i|^{rc}\)), and use that to estimate the model:
-\end{enumerate}
 
@@
 
-\begin{enumerate}
-\def\labelenumi{\arabic{enumi}.}
-\setcounter{enumi}{3}
-\tightlist
-\item
-  Finally the standardized residuals \(\varepsilon_i\) can be obtained
-  as follows
-\end{enumerate}
+Finally the standardized residuals \(\varepsilon_i\) can be obtained as
+follows
 
@@
 variable \(x\). In contrast with MSS, we consider a two-way fixed effect
-structure that is more general than the panel structure used in by the
-authors. For this excercise, we consider the following data generating
-process:
+structure that is more general than the panel structure. For this
+excercise, we consider the following data generating process:
 
@@
 \(\varepsilon_i\) is assumed to be normally distributed with mean zero
-and standard deviation 0.5. We assume that there are 50 mutually
+and standard deviation of 0.5. We assume that there are 50 mutually
 exclusive fixed effect groups for each set of fixed effects.
@@
 
-\section{Appendix}\label{sec-appendix}
-
-\subsection{Derivation of the influence
+In this paper, we have extended the methodology proposed by
+\citet{mss2019}, allowing for the estimation of quantile regression
+models with multiple sets of fixed effects, as well as alternative
+Standard Errors estimations. This methodology would allow researchers to
+implement more comprehensive analysis of datasets characterized by
+complex hierarchies and unobserved heterogeneity. This extension is
+particularly valuable in contexts where group specific effects vary
+across the conditional distribution of the outcome of interest.
+
+Using a small simulation study, we show that our extended approach is as
+effective in identifying the parameters of interest as \citet{mss2019}
+indicated, even in contexts with two sets of fixed effects. Notably, the
+bias-corrected estimator based on the split-panel jackknife estimator
+exhibits promising results, mitigating biases when samples are small,
+but increasing standard errors.
+
+Furthermore, we have assessed the impact of misspecified
+heteroskedasticity and intra-cluster correlation on the performance of
+standard error estimations. Our findings emphasize the importance of
+using appropriate standard error estimators to ensure accurate
+inference. In particular, we find that GLS standard errors are biased
+when the model heteroskedasticity is misspecified, and that robust and
+clustered standard errors perform better in these cases. This may also
+suggest a venue for future research, testing the validity of the
+location-scale model assumption.
+
+\section*{References}\label{references}
+\addcontentsline{toc}{section}{References}
+
+\renewcommand{\bibsection}{}
+\bibliography{bibliography.bib}
+
+\newpage{}
+
+\appendix
+
+\section{Derivation of the influence
 functions}\label{derivation-of-the-influence-functions}
 
-\subsubsection{Model Identification}\label{model-identification}
+\subsection{Model Identification}\label{model-identification}
 
@@
 
-\subsubsection{Estimation of the variance-covariance
+\subsection{Estimation of the variance-covariance
 matrix}\label{estimation-of-the-variance-covariance-matrix}
@@
 
-\paragraph{First Moment Condition: Location
-Model}\label{first-moment-condition-location-model}
+\textbf{First Moment Condition: Location Model}
 
@@
 
-\paragraph{Second Moment Condition: Scale
-model}\label{second-moment-condition-scale-model}
+\textbf{Second Moment Condition: Scale model}
 
@@
 
-\paragraph{Third Moment Condition: Quantile of Standardized
-Residual}\label{third-moment-condition-quantile-of-standardized-residual}
+\textbf{Third Moment Condition: Quantile of Standardized Residual}
 
@@
 
-\subsubsection{Influence functions}\label{influence-functions}
-
-\paragraph{Location coefficients}\label{location-coefficients}
+\subsection{Influence functions}\label{influence-functions}
+
+\textbf{Location coefficients}
 
@@
 
-\paragraph{Scale Coefficients}\label{scale-coefficients}
+\textbf{Scale Coefficients}
 
@@
 
-\paragraph{Quantile of standardized
-residual}\label{quantile-of-standardized-residual}
+\textbf{Quantile of standardized residual}
 
@@
 
-\subsection{Implementation}\label{implementation}
+\section{Implementation}\label{implementation}
 
@@
 \item
-  \texttt{mmqreg} in Stata: Installed from Github
+  \texttt{mmqreg} in Stata: `net install mmqre,
+  from(https://friosavila.github.io/stpackages)
 \item
@@
 
-\renewcommand\refname{References}
-  \bibliography{bibliography.bib}
-
 \end{document}

### 2023-11-01 software/R/v1.1.R
Add files via upload

@@ -1,0 +1,305 @@
+# Version 1.1
+# Output has to be more 'user friendly'
+
+
+mmqreg <- function(formula, data, tau = 0.5, absorb = NULL, weights = NULL,
+                   vcov = "gls"){
+
+  # Input
+  yx <- model.frame(formula, data)
+  y <- as.matrix(yx[, 1])
+  x <- cbind(as.matrix(yx[, 2:ncol(yx)]), 1)
+  n <- nrow(x)
+  k <- ncol(x)
+
+  if (is.null(weights)) {
+    # No weights provided
+
+    if (is.null(absorb)) {
+      # Simple model, no weights
+
+      xx <- crossprod(x)
+      ixx <- solve(xx)
+
+      # Location
+      b <- ixx %*% crossprod(x, y)
+      e <- y - x %*% b
+
+      # Scale
+
+      g <- ixx %*% crossprod(x, abs(e))
+      xg <-  x %*% g
+      se <- e/xg
+
+      # Quantile regression
+
+      se_qr <- quantreg::rq(se ~ 1, tau)
+      qt <- se_qr[["coefficients"]]
+      se_qr <- summary(se_qr, se = "iid", cov = T)
+      f <- c()
+      for (i in 1:length(tau)) {
+        f[i] <- se_qr[[i]][["scale"]]
+      }
+
+    } else {
+      # FE model, no weights
+
+      fe <- model.frame(absorb, data)
+
+      # Centered residualized vars
+      y <- fixest::demean(X = y, f = fe) + colMeans(y)
+      x <- fixest::demean(X = x, f = fe) + matrix(colMeans(x), n, k, T)
+
+      # Location HDFE
+      xx <- crossprod(x)
+      ixx <- solve(xx)
+      b <- ixx %*% crossprod(x, y)
+      e <- y - x %*% b
+
+      # Scale HDFE
+      erc <- fixest::demean(X = abs(e), f = fe) + colMeans(abs(e))
+      g <- ixx %*% crossprod(x, erc)
+      xg <- abs(e) - (erc - x %*% g)
+      se <- e/xg
+
+      # Quantile regression HDFE
+      se_qr <- quantreg::rq(se ~ 1, tau)
+      qt <- se_qr[["coefficients"]]
[…]

### 2023-11-01 article/article.qmd
update
updated my email address and the link to this repository so that others can find the R code for mmqreg.

@@
   - name: Leonardo Siles
-    email: leo@gmail.com
+    email: leonardosiles@hotmail.com
     affiliations:
-        - name: Universidad Catolica Boliviana
+        - name: Universidad Católica Boliviana
           id: ucb
@@
 - `mmqreg` in Stata: `net install mmqre, from(https://friosavila.github.io/stpackages)
-- `mmqreg` in R: Programs Available in Github
+- `mmqreg` in R: Program Available in mmqreg repository in GitHub (https://github.com/friosavila/mmqreg)
 - `mmqreg` in Python: 

### 2023-11-01 article/article.qmd
s
s

@@
 A relatively recent development in the literature has focused on extending quantile regressions analysis to include individual fixed effects in the framework of panel data.
-However, as described in @neymanscott1948, and @lancaster2000, when individual fixed effects are included in quantile regression analysis it generates an incident parameter problem.
+However, as described in @neymanscott1948, and @lancaster2000, when individual fixed effects are included in quantile regression analysis it generates an incidental parameter problem.
 While many strategies have been proposed for estimating this type of model (see @galvao2017quantile for a brief review), neither has become standard because of their restrictive assumptions in regards to the individual effects, the computational complexity, and implementation.
@@
 
-Thurd, given the location and scale coefficients, the $\tau_{th}$ quantile of the error $\varepsilon$ can be estimated using the following condition:
+Third, given the location and scale coefficients, the $\tau_{th}$ quantile of the error $\varepsilon$ can be estimated using the following condition:
 
@@
 As MSS describes, the bias seems to be proportional to the sample size, or more precisely to $N/N_{g1}$ and $N/N_{g2}$, where $N_{g1}$ and $N_{g2}$ are the average number of observations per group.
-Interestingly, the bias-corrected estimator presents an almost zero bias, even when the samples are is small (about 10 observations per sub-group).
+Interestingly, the bias-corrected estimator presents an almost zero bias, even when the samples are small (about 10 observations per sub-group).
 Also replicating the results of MSS, despite bias reduction obtained using the JKC estimator, the standard errors and mean squared error (MSE) are larger than without correction.
@@
 
-As expected, @tbl-tb1 shows that point estimates for the point estimates are identical to the ones reported in @mss2019 (Table 6), including analytical standard errors (GLS).
+As expected, @tbl-tb1 shows that point estimates are identical to the ones reported in @mss2019 (Table 6), including analytical standard errors (GLS).
 With our estimator, however, we are able to also produce both robust and clustered standard errors for location and scale coefficients.

### 2023-11-01 article/article.tex
s
s

@@
 \makeatletter
+\makeatother
+\makeatletter
+\makeatother
+\makeatletter
 \@ifpackageloaded{caption}{}{\usepackage{caption}}
@@
 \makeatletter
+\@ifpackageloaded{caption}{}{\usepackage{caption}}
+\@ifpackageloaded{subcaption}{}{\usepackage{subcaption}}
 \makeatother
 \makeatletter
-\@ifpackageloaded{caption}{}{\usepackage{caption}}
-\@ifpackageloaded{subcaption}{}{\usepackage{subcaption}}
+\@ifpackageloaded{tcolorbox}{}{\usepackage[skins,breakable]{tcolorbox}}
+\makeatother
+\makeatletter
+\@ifundefined{shadecolor}{\definecolor{shadecolor}{rgb}{.97, .97, .97}}
+\makeatother
+\makeatletter
+\makeatother
+\makeatletter
 \makeatother
@@
 }
- \ead{leo@gmail.com} 
+ \ead{leonardosiles@hotmail.com} 
 \author[3]{Gustavo Canavire-Bacarreza%
@@
 College},,postcodesep={}}
-\affiliation[2]{organization={Universidad Catolica
+\affiliation[2]{organization={Universidad Católica
 Boliviana},,postcodesep={}}
@@
 \end{frontmatter}
-    \section{Introduction}\label{introduction}
+    \ifdefined\Shaded\renewenvironment{Shaded}{\begin{tcolorbox}[interior hidden, borderline west={3pt}{0pt}{shadecolor}, boxrule=0pt, sharp corners, enhanced, breakable, frame hidden]}{\end{tcolorbox}}\fi
+
+\hypertarget{introduction}{%
+\section{Introduction}\label{introduction}}
 
@@
 fixed effects are included in quantile regression analysis it generates
-an incident parameter problem. While many strategies have been proposed
-for estimating this type of model (see \citet{galvao2017quantile} for a
-brief review), neither has become standard because of their restrictive
-assumptions in regards to the individual effects, the computational
-complexity, and implementation.
+an incidental parameter problem. While many strategies have been
+proposed for estimating this type of model (see
+\citet{galvao2017quantile} for a brief review), neither has become
+standard because of their restrictive assumptions in regards to the
+individual effects, the computational complexity, and implementation.
 
@@
 
-\section{Methodology}\label{sec-method}
-
-\subsection{Quantile Regression: Location-Scale model}\label{sec-betas}
+\hypertarget{sec-method}{%
+\section{Methodology}\label{sec-method}}
+
+\hypertarget{sec-betas}{%
+\subsection{Quantile Regression: Location-Scale model}\label{sec-betas}}
 
@@
 
-\begin{equation}\phantomsection\label{eq-eq1}{q(Y|X,\tau) =X\beta(\tau)
-}\end{equation}
+\begin{equation}\protect\hypertarget{eq-eq1}{}{q(Y|X,\tau) =X\beta(\tau)
+}\label{eq-eq1}\end{equation}
 
@@
 
-\begin{equation}\phantomsection\label{eq-eq2}{q(Y|X,\tau) =X\beta+X\gamma(\tau)
-}\end{equation}
+\begin{equation}\protect\hypertarget{eq-eq2}{}{q(Y|X,\tau) =X\beta+X\gamma(\tau)
+}\label{eq-eq2}\end{equation}
 
@@
 
-\begin{equation}\phantomsection\label{eq-eq3}{\hat{\beta}(\tau) = \underset{\beta}{\operatorname{argmin}}
+\begin{equation}\protect\hypertarget{eq-eq3}{}{\hat{\beta}(\tau) = \underset{\beta}{\operatorname{argmin}}
 \left( \sum_{i\in y_i\geq x_i'\beta} \tau (y_i - x_i'\beta) - \sum_{i\in y_i<x_i'\beta} (1-\tau)(y_i - x_i'\beta) \right)
-}\end{equation}
+}\label{eq-eq3}\end{equation}
 
@@
 
-\begin{equation}\phantomsection\label{eq-eq4}{\begin{aligned}
+\begin{equation}\protect\hypertarget{eq-eq4}{}{\begin{aligned}
 y_i &=x_i'\beta+\nu_i \\
@@
 \end{aligned}
-}\end{equation}
+}\label{eq-eq4}\end{equation}
 
@@
 
-\begin{equation}\phantomsection\label{eq-eq5}{q(Y|X,\tau) =X\beta+q(\varepsilon|\tau) \times X\gamma 
-}\end{equation}
+\begin{equation}\protect\hypertarget{eq-eq5}{}{q(Y|X,\tau) =X\beta+q(\varepsilon|\tau) \times X\gamma 
+}\label{eq-eq5}\end{equation}
 
@@
 
-\begin{equation}\phantomsection\label{eq-eq6}{\beta(\tau) = \beta + q(\varepsilon|\tau) \times \gamma 
-}\end{equation}
+\begin{equation}\protect\hypertarget{eq-eq6}{}{\beta(\tau) = \beta + q(\varepsilon|\tau) \times \gamma 
+}\label{eq-eq6}\end{equation}
 
@@
 
-\begin{equation}\phantomsection\label{eq-eq7}{\begin{aligned}
+\begin{equation}\protect\hypertarget{eq-eq7}{}{\begin{aligned}
       y_i &=x_i'\beta+\nu_i \\
@@
       \end{aligned}
-}\end{equation}
+}\label{eq-eq7}\end{equation}
 
@@
 
-\begin{equation}\phantomsection\label{eq-eq8}{\begin{aligned}
+\begin{equation}\protect\hypertarget{eq-eq8}{}{\begin{aligned}
   |\nu_i| &=x_i'\gamma+\omega_i \\
@@
   \end{aligned}
-}\end{equation}
-
-Thurd, given the location and scale coefficients, the \(\tau_{th}\)
+}\label{eq-eq8}\end{equation}
+
+Third, given the location and scale coefficients, the \(\tau_{th}\)
 quantile of the error \(\varepsilon\) can be estimated using the
@@
 
-\begin{equation}\phantomsection\label{eq-eq9}{\begin{aligned}
+\begin{equation}\protect\hypertarget{eq-eq9}{}{\begin{aligned}
   E\left[  \mathbb{1}\left(x_i' (\beta + \gamma q(\varepsilon|\tau)) \geq y_i \right) - \tau \right] &=0  \\
@@
   \end{aligned}
-}\end{equation}
+}\label{eq-eq9}\end{equation}
 
@@
 
-\subsection{Standard Errors: GLS, Robust, Clustered}\label{sec-se}
+\hypertarget{sec-se}{%
+\subsection{Standard Errors: GLS, Robust, Clustered}\label{sec-se}}
 
@@
 
-\begin{equation}\phantomsection\label{eq-eq10}{\begin{aligned}
+\begin{equation}\protect\hypertarget{eq-eq10}{}{\begin{aligned}
   E[x_i \nu_i  ] &= E[h_{1,i}]=0 \\
@@
   \end{aligned}
-}\end{equation}
+}\label{eq-eq10}\end{equation}
 
@@
 
-\begin{equation}\phantomsection\label{eq-eqqtile}{\Xi = [ I(k), \hat q(\varepsilon|\tau) \times I(k), \hat \gamma ]
-}\end{equation}
+\begin{equation}\protect\hypertarget{eq-eqqtile}{}{\Xi = [ I(k), \hat q(\varepsilon|\tau) \times I(k), \hat \gamma ]
+}\label{eq-eqqtile}\end{equation}
 
@@
 
-\begin{equation}\phantomsection\label{eq-eqvcv}{\hat{V}(\theta) = \frac{1}{N^2} \sum_{i=1}^N \lambda_i(\theta) \lambda_i(\theta)'
-}\end{equation}
+\begin{equation}\protect\hypertarget{eq-eqvcv}{}{\hat{V}(\theta) = \frac{1}{N^2} \sum_{i=1}^N \lambda_i(\theta) \lambda_i(\theta)'
+}\label{eq-eqvcv}\end{equation}
 
@@
 
-\begin{equation}\phantomsection\label{eq-ifs}{\begin{aligned}
+\begin{equation}\protect\hypertarget{eq-ifs}{}{\begin{aligned}
 \lambda_i(\theta)&=
@@
 \end{aligned}
-}\end{equation}
+}\label{eq-ifs}\end{equation}
 
@@
 
-\subsubsection{Robust Standard Errors}\label{robust-standard-errors}
+\hypertarget{robust-standard-errors}{%
+\subsubsection{Robust Standard Errors}\label{robust-standard-errors}}
 
@@
 
+\hypertarget{clustered-standard-errors}{%
 \subsubsection{Clustered Standard
-Errors}\label{clustered-standard-errors}
+Errors}\label{clustered-standard-errors}}
 
@@
 
-\subsubsection{GLS Standard Errors}\label{gls-standard-errors}
+\hypertarget{gls-standard-errors}{%
+\subsubsection{GLS Standard Errors}\label{gls-standard-errors}}
 
@@
 
+\hypertarget{multiple-fixed-effects-expanding-on-mss2019}{%
 \subsection{\texorpdfstring{Multiple Fixed Effects: Expanding on
-\citet{mss2019}}{Multiple Fixed Effects: Expanding on @mss2019}}\label{multiple-fixed-effects-expanding-on-mss2019}
+\citet{mss2019}}{Multiple Fixed Effects: Expanding on @mss2019}}\label{multiple-fixed-effects-expanding-on-mss2019}}
 
@@
 
-\section{Simulation Evidence}\label{simulation-evidence}
+\hypertarget{simulation-evidence}{%
+\section{Simulation Evidence}\label{simulation-evidence}}
 
@@
 the coefficients for the 25th and 75th quantiles. We run this excercise
-5000 times. Table~\ref{tbl-sim1} reports the bias, simulated standard
+5000 times. \textbf{?@tbl-sim1} reports the bias, simulated standard
 error and mean squared error. We also report the results obtained using
@@
 observations per group. Interestingly, the bias-corrected estimator
-presents an almost zero bias, even when the samples are is small (about
-10 observations per sub-group). Also replicating the results of MSS,
+presents an almost zero bias, even when the samples are small (about 10
+observations per sub-group). Also replicating the results of MSS,
 despite bias reduction obtained using the JKC estimator, the standard
@@
 
-\caption{\label{tbl-sim1}Bias, Simulated Standard error, and Mean
-Squared Error}
-
-\begin{minipage}[t]{0.50\linewidth}
+\caption{Bias, Simulated Standard error, and Mean Squared
+Error}\begin{minipage}[t]{0.50\linewidth}
+
+{\centering
 
@@
 
+}
+
 \end{minipage}%
@@
 \begin{minipage}[t]{0.50\linewidth}
+
+{\centering
 
@@
 
+}
+
 \end{minipage}%
 
-\end{table}%
+\end{table}
 
@@
 
+\hypertarget{tbl-sim2}{}
 \begin{longtable}[]{@{}
@@
   >{\centering\arraybackslash}p{(\columnwidth - 8\tabcolsep) * \real{0.2000}}@{}}
-\caption{Heteroskedasticity misspecification and clustered
-errors}\label{tbl-sim2}\tabularnewline
+\caption{\label{tbl-sim2}Heteroskedasticity misspecification and
+clustered errors}\tabularnewline
 \toprule\noalign{}
@@
 
-\section{Illustrative application}\label{illustrative-application}
+\hypertarget{illustrative-application}{%
+\section{Illustrative application}\label{illustrative-application}}
 
@@
 
+\hypertarget{tbl-tb1}{}
 \begin{longtable}[]{@{}
@@
   >{\centering\arraybackslash}p{(\columnwidth - 18\tabcolsep) * \real{0.0989}}@{}}
-\caption{The determinants of government surpluses: Individual Fixed
-effects}\label{tbl-tb1}\tabularnewline
+\caption{\label{tbl-tb1}The determinants of government surpluses:
+Individual Fixed effects}\tabularnewline
 \toprule\noalign{}
@@
 
-As expected, Table~\ref{tbl-tb1} shows that point estimates for the
-point estimates are identical to the ones reported in \citet{mss2019}
-(Table 6), including analytical standard errors (GLS). With our
-estimator, however, we are able to also produce both robust and
-clustered standard errors for location and scale coefficients. Except
-for a few cases, robust and clustered standard errors are larger than
-GLS standard errors, which may be an indication of misspecification of
-the model. The GLS standard errors we report differ from the ones in MSS
-because they use panel standard errors, which are equivalent to our
-clustered standard errors, instead of the analytical standard errors we
-derive.
+As expected, Table~\ref{tbl-tb1} shows that point estimates are
+identical to the ones reported in \citet{mss2019} (Table 6), including
+analytical standard errors (GLS). With our estimator, however, we are
+able to also produce both robust and clustered standard errors for
+location and scale coefficients. Except for a few cases, robust and
+clustered standard errors are larger than GLS standard errors, which may
+be an indication of misspecification of the model. The GLS standard
+errors we report differ from the ones in MSS because they use panel
+standard errors, which are equivalent to our clustered standard errors,
+instead of the analytical standard errors we derive.
 
@@
 
+\hypertarget{tbl-tb2}{}
 \begin{longtable}[]{@{}
@@
   >{\centering\arraybackslash}p{(\columnwidth - 14\tabcolsep) * \real{0.1233}}@{}}
-\caption{The determinants of government surpluses: Individual and Time
-Fixed effects}\label{tbl-tb2}\tabularnewline
+\caption{\label{tbl-tb2}The determinants of government surpluses:
+Individual and Time Fixed effects}\tabularnewline
 \toprule\noalign{}
@@
 
-\section{Conclusions}\label{conclusions}
+\hypertarget{conclusions}{%
+\section{Conclusions}\label{conclusions}}
 
@@
 
-\section*{References}\label{references}
+\hypertarget{references}{%
+\section*{References}\label{references}}
 \addcontentsline{toc}{section}{References}
@@
 
+\hypertarget{derivation-of-the-influence-functions}{%
 \section{Derivation of the influence
-functions}\label{derivation-of-the-influence-functions}
-
-\subsection{Model Identification}\label{model-identification}
+functions}\label{derivation-of-the-influence-functions}}
+
+\hypertarget{model-identification}{%
+\subsection{Model Identification}\label{model-identification}}
 
@@
 
+\hypertarget{estimation-of-the-variance-covariance-matrix}{%
 \subsection{Estimation of the variance-covariance
-matrix}\label{estimation-of-the-variance-covariance-matrix}
+matrix}\label{estimation-of-the-variance-covariance-matrix}}
 
@@
 
-\subsection{Influence functions}\label{influence-functions}
+\hypertarget{influence-functions}{%
+\subsection{Influence functions}\label{influence-functions}}
 
@@
 
-\section{Implementation}\label{implementation}
+\hypertarget{implementation}{%
+\section{Implementation}\label{implementation}}
 
@@
 \item
-  \texttt{mmqreg} in R: Programs Available in Github
+  \texttt{mmqreg} in R: Program Available in mmqreg repository in GitHub
+  (https://github.com/friosavila/mmqreg)
 \item

### 2023-11-01 software/R/v1.2.R
Minor changes in syntax and comments

@@ -1,0 +1,310 @@
+# Version 1.1
+# Output has to be more 'user friendly'
+
+
+mmqreg <- function(formula, data, tau = 0.5, absorb = NULL, weights = NULL,
+                   vcov = "gls"){
+
+  # Input
+  yx <- model.frame(formula, data)
+  y <- as.matrix(yx[, 1])
+  x <- cbind(as.matrix(yx[, 2:ncol(yx)]), 1)
+  n <- nrow(x)
+  k <- ncol(x)
+
+  if (is.null(weights)) {
+    # No weights provided
+
+    if (is.null(absorb)) {
+      # Simple model, no weights
+
+      xx <- crossprod(x)
+      ixx <- solve(xx)
+
+      # Location
+      b <- ixx %*% crossprod(x, y)
+      e <- y - x %*% b
+
+      # Scale
+
+      g <- ixx %*% crossprod(x, abs(e))
+      xg <-  x %*% g
+      se <- e/xg
+
+      # Quantile regression
+
+      se_qr <- quantreg::rq(se ~ 1, tau)
+      qt <- se_qr[["coefficients"]]
+      se_qr <- summary(se_qr, se = "iid", cov = T)
+      f <- c()
+      for (i in 1:length(tau)) {
+        f[i] <- se_qr[[i]][["scale"]]
+      }
+
+    } else {
+      # FE model, no weights
+
+      fe <- model.frame(absorb, data)
+
+      # Centered residualized vars
+      y <- fixest::demean(X = y, f = fe) + colMeans(y)
+      x <- fixest::demean(X = x, f = fe) + matrix(colMeans(x), n, k, T)
+
+      # Location HDFE
+      xx <- crossprod(x)
+      ixx <- solve(xx)
+      b <- ixx %*% crossprod(x, y)
+      e <- y - x %*% b
+
+      # Scale HDFE
+      erc <- fixest::demean(X = abs(e), f = fe) + colMeans(abs(e))
+      g <- ixx %*% crossprod(x, erc)
+      xg <- abs(e) - (erc - x %*% g)
+      se <- e/xg
+
+      # Quantile regression HDFE
+      se_qr <- quantreg::rq(se ~ 1, tau)
+      qt <- se_qr[["coefficients"]]
[…]

### 2023-11-02 software/R/v1.2.R
update

@@ -98,7 +98,7 @@ mmqreg <- function(formula, data, tau = 0.5, absorb = NULL, weights = NULL,
   } else {
     # Weights provided
 
-    weights <- as.vector(weights)
+    weights <- as.matrix(data[, weights])
     nwgt <- weights / mean(weights) # normalized wgts vector
     w <- diag(n); diag(w) <- nwgt   # normalized wgts diagonal matrix
 
@@ -109,11 +109,11 @@ mmqreg <- function(formula, data, tau = 0.5, absorb = NULL, weights = NULL,
       ixx <- solve(xx)
 
       # Location
-      b <- ixx %*% crossprod(t(x) %*% w, y)
+      b <- ixx %*% t(x) %*% w %*% y
       e <- y - x %*% b
 
       # Scale
-      g <- ixx %*% crossprod(t(x) %*% w, abs(e))
+      g <- ixx %*% t(x) %*% w %*% abs(e)
       xg <-  x %*% g
       se <- e/xg
 
@@ -138,12 +138,12 @@ mmqreg <- function(formula, data, tau = 0.5, absorb = NULL, weights = NULL,
       # Location HDFE, weights
       xx <- t(x) %*% w %*% x
       ixx <- solve(xx)
-      b <- ixx %*% crossprod(t(x) %*% w, y)
+      b <- ixx %*% t(x) %*% w %*% y
       e <- y - x %*% b
 
       # Scale HDFE, weights
       erc <- fixest::demean(X = abs(e), f = fe, weights = nwgt) + colMeans(abs(e))
-      g <- ixx %*% crossprod(t(x) %*% w, erc)
+      g <- ixx %*% t(x) %*% w %*% erc
       xg <- abs(e) - (erc - x %*% g)
       se <- e/xg
 
@@ -159,19 +159,21 @@ mmqreg <- function(formula, data, tau = 0.5, absorb = NULL, weights = NULL,
     }
 
     # Influence functions, weights
+    # Helper function 'mult'
     mult <- function(x, e){
       xm <- matrix(NA, nrow = n, ncol = k)
       for (i in 1:k) {
         xm[, i] <- x[, i] * e
       }
       return(xm)
-    } # Helper function
-    if1 <- t(n*ixx%*%t(mult(x, e)))
-    if1 <- if1 * nwgt
+    }
+
[…]

### 2023-11-02 software/R/v1.2.R
update
gls sv definition

@@ -195,8 +195,7 @@ mmqreg <- function(formula, data, tau = 0.5, absorb = NULL, weights = NULL,
   se2.bt <- matrix(NA, k, length(tau), dimnames = dimnames(bt))
 
   # VCOV of estimators -- GLS
-  su <- se
-  sv <- vt/xg
+  sv <- (vt/xg) - 1
   qxx <- apply(if1, 2, function(x) {x/su})
   Pxx <- crossprod(qxx, xg)
   Qxx <- crossprod(qxx)
@@ -310,4 +309,3 @@ mmqreg <- function(formula, data, tau = 0.5, absorb = NULL, weights = NULL,
   }
 
 }
-

### 2023-11-03 software/R/v1.2.R
update

@@ -1,4 +1,4 @@
-# Version 1.1
+# Version 1.2
 # Output has to be more 'user friendly'
 
 
@@ -38,7 +38,11 @@ mmqreg <- function(formula, data, tau = 0.5, absorb = NULL, weights = NULL,
       se_qr <- summary(se_qr, se = "iid", cov = T)
       f <- c()
       for (i in 1:length(tau)) {
-        f[i] <- se_qr[[i]][["scale"]]
+        if (length(tau) == 1) {
+          f[i] <- se_qr[["scale"]]
+        } else {
+          f[i] <- se_qr[[i]][["scale"]]
+        }
       }
 
     } else {
@@ -68,7 +72,11 @@ mmqreg <- function(formula, data, tau = 0.5, absorb = NULL, weights = NULL,
       se_qr <- summary(se_qr, se = "iid", cov = T)
       f <- c()
       for (i in 1:length(tau)) {
-        f[i] <- se_qr[[i]][["scale"]]
+        if (length(tau) == 1) {
+          f[i] <- se_qr[["scale"]]
+        } else {
+          f[i] <- se_qr[[i]][["scale"]]
+        }
       }
     }
 
@@ -123,7 +131,11 @@ mmqreg <- function(formula, data, tau = 0.5, absorb = NULL, weights = NULL,
       se_qr <- summary(se_qr, se = "iid", cov = T)
       f <- c()
       for (i in 1:length(tau)) {
-        f[i] <- se_qr[[i]][["scale"]]
+        if (length(tau) == 1) {
+          f[i] <- se_qr[["scale"]]
+        } else {
+          f[i] <- se_qr[[i]][["scale"]]
+        }
       }
 
     } else {
@@ -153,7 +165,11 @@ mmqreg <- function(formula, data, tau = 0.5, absorb = NULL, weights = NULL,
       se_qr <- summary(se_qr, se = "iid", cov = T)
       f <- c()
       for (i in 1:length(tau)) {
-        f[i] <- se_qr[[i]][["scale"]]
+        if (length(tau) == 1) {
+          f[i] <- se_qr[["scale"]]
+        } else {
+          f[i] <- se_qr[[i]][["scale"]]
+        }
       }
 
     }
[…]

### 2023-11-04 article/article.qmd
Update article.qmd

@@
 \hat\Omega_{ij} &= \frac{1}{N} \sum_i^N \tilde \lambda_{i}(\theta) \tilde \lambda_{j}(\theta)' \\
-\hat\sigma_{ij} &= \frac{1}{N} \sum_i^N \phi_{i} \phi_{j}
+\hat\sigma_{ij} &= \frac{1}{N} \sum_i^N \psi_{i} \psi_{j}
 \end{aligned}
@@
 
-- `mmqreg` in Stata: `net install mmqre, from(https://friosavila.github.io/stpackages)
+- `mmqreg` in Stata: `net install mmqreg, from(https://friosavila.github.io/stpackages)
 - `mmqreg` in R: Program Available in mmqreg repository in GitHub (https://github.com/friosavila/mmqreg)

### 2023-11-04 software/R/v1.2.R
update
output formatted as a 'results' list

@@ -48,7 +48,7 @@ mmqreg <- function(formula, data, tau = 0.5, absorb = NULL, weights = NULL,
     } else {
       # FE model, no weights
 
-      fe <- model.frame(absorb, data)
+      fe <- data[, absorb]
 
       # Centered residualized vars
       y <- fixest::demean(X = y, f = fe) + colMeans(y)
@@ -141,7 +141,9 @@ mmqreg <- function(formula, data, tau = 0.5, absorb = NULL, weights = NULL,
     } else {
       # FE model, weights
 
-      fe <- model.frame(absorb, data)
+      nwgt = as.vector(nwgt)
+
+      fe <- data[, absorb]
 
       # Centered residualized vars, weights
       y <- fixest::demean(X = y, f = fe, weights = nwgt) + colMeans(y)
@@ -200,16 +202,13 @@ mmqreg <- function(formula, data, tau = 0.5, absorb = NULL, weights = NULL,
     ifx <- cbind(if1, if2, ifq)
   }
 
-  # Quantile coefficients b(t)
-  bt <- matrix(b, nrow(b), ncol(qt)) + g %*% qt
-
   # Empty lists and matrices to fill in
   vcov0 <- list()
   vcov1 <- list()
   vcov2 <- list()
-  se0.bt <- matrix(NA, k, length(tau), dimnames = dimnames(bt))
-  se1.bt <- matrix(NA, k, length(tau), dimnames = dimnames(bt))
-  se2.bt <- matrix(NA, k, length(tau), dimnames = dimnames(bt))
+  se0.bt <- matrix(NA, k, length(tau), dimnames = dimnames(b))
+  se1.bt <- matrix(NA, k, length(tau), dimnames = dimnames(b))
+  se2.bt <- matrix(NA, k, length(tau), dimnames = dimnames(b))
 
   # VCOV of estimators -- GLS
   sv <- (vt/xg) - 1
@@ -225,9 +224,9 @@ mmqreg <- function(formula, data, tau = 0.5, absorb = NULL, weights = NULL,
     suvw.i <- cbind(se, sv, sw.i)                  # n x 3
     omgs.i <- (1/n) * crossprod(suvw.i)            # 3 x 3
     # omgs[[i]] <- omgs.i
-    omg.i <- (1/n^2) * cbind(omgs.i[1:2, 1:2] %x% Qxx,
[…]

### 2023-11-07 article/article.qmd
q(\tau)
q(\tau)

@@
       number-depth: 2
-
 ---
 
+```{=html}
 <!--
@@
 -->
-
+```
 # Introduction
 
-Quantile regression (QR), introduced by @koenkerbasset1978, is an estimation strategy used for modeling the relationships between explanatory variables X and the conditional quantiles of the dependent variable $q_\tau (y|x)$.
+Quantile regression (QR), introduced by @koenkerbasset1978, is an estimation strategy used for modeling the relationships between explanatory variables X and the conditional quantiles of the dependent variable $Q_y (\tau|x)$.
 Using QR one can obtain richer characterizations of the relationships between dependent and independent variables, by accounting for otherwise unobserved heterogeneity.
@@
 More recently, @mss2019 (MSS hereafter) proposed a methodology based on a conditional location-scale model similar to the one described in @he1997 and @zhao2000, for the estimation of quantile regressions models for panel data via a method of moments.
-This method allows individual fixed effects allowing to have heterogeneous effects on the entire conditional distribution of the outcome, rather constraining their effect to be a location shift only as in @canay2011, @koenker2004, and @lancaster2000.
+This method allows individual fixed effects allowing to have heterogeneous effects on the entire conditional distribution of the outcome, rather constraining their effect to be a location shift only as in @canay2011, @koenker2004, and @lamarche2010.
 
@@
 It also shows that FWL theorem can be used to control for multiple fixed effects.
-Section 3 presents the results of a small simulation study and Section 4 illustrates the application of the proposed methods with two empirical examples.
+Section 3 presents the results of a small simulation study and Section 4 illustrates the application of the proposed methods with one empirical example.
 Seccion 5 concludes.
@@
 
-Quantile regressions are used to identify relationships between the explanatory variables $x$ and the conditional quantiles of the dependent variable $Q(y|\tau,X)$.
+Quantile regressions are used to identify relationships between the explanatory variables $x$ and the conditional quantiles of the dependent variable $Q_y(\tau|X)$.
 This relationship is commonly assumed to follow a linear functional form:
 
-$$q(Y|X,\tau) =X\beta(\tau)
+$$Q_y(\tau|X) =X\beta(\tau)
 $$ {#eq-eq1}
 
-This allows for nonlinearities in the effect of $X$ on $Y$ across all values of $\tau$.
+This allows for the effect of $X$ on $Y$ to vary across all $\tau$.
 This formulation can also be related to a random coefficient model, where all coefficients are assumed to be some nonlinear function of $\tau$, where $\tau$ follows a random uniform distribution.
@@
 
-$$q(Y|X,\tau) =X\beta+X\gamma(\tau)
-$${#eq-eq2}
+$$Q_y(\tau|X) =X\beta+X\gamma(\tau)
+$$ {#eq-eq2}
 
-Here, the location parameters $\beta$ are typically identified using a linear regression model (as in @mss2019), or a median regression (as in @melly2005), and the scale parameters $\gamma(\tau)$ can be estimated using standard approaches.
+Here, the location parameters $\beta$ are typically identified using a linear regression model (as in @mss2019), or a median regression (as in @zhao2000), and the scale parameters $\gamma(\tau)$ can be estimated using standard approaches.
 
@@
 
-$$q(Y|X,\tau) =X\beta+q(\varepsilon|\tau) \times X\gamma 
+$$Q_y(\tau|X) =X\beta+Q_\varepsilon(\tau) \times X\gamma 
 $$ {#eq-eq5}
@@
 In this setup, the traditional quantile coefficients are identified as the location model coefficients, plus the scale model coefficients moderated by the $\tau_{th}$ unconditional quantile of the standardized error $\varepsilon$.
+For simplicity we will use $q(\tau)$ to denote $Q_\varepsilon(\tau)$ in the rest of the paper.
 
-$$\beta(\tau) = \beta + q(\varepsilon|\tau) \times \gamma 
+$$\beta(\tau) = \beta + q(\tau) \times \gamma 
 $$ {#eq-eq6}
@@
 While this specification imposes a strong assumption on the DGP, it has two advantages over the standard quantile regression model.
-First, because the location and scale model can be identified globally, with only a single paramater ($q(\varepsilon|\tau)$) requiring local estimation, this estimation approach would be more efficient than the standard quantile regression model (@zhao2000).
+First, because the location and scale model can be identified globally, with only a single paramater ($q(\tau)$) requiring local estimation, this estimation approach would be more efficient than the standard quantile regression model [@zhao2000].
 Second, under the assumption that $X\gamma$ is strictly possitive, the model would produce quantile coefficients that do not cross.
@@
 Following MSS, the quantile regression model defined by @eq-eq5 can be estimated using a method of moments approach.
-And while its possible to identify all coefficients ($\beta,\gamma, q(\varepsilon|\tau)$) simultaneously, we describe and use the implementation approach advocated by MSS which identifies each set of coefficients separately.
+And while its possible to identify all coefficients ($\beta,\gamma, q(\tau)$) simultaneously, we describe and use the implementation approach advocated by MSS which identifies each set of coefficients separately.
 
-First, the location model can be estimated using a standard linear regression model, where the dependent variable is the outcome $Y$, and the independent variables are the explanatory variables $X$ (including a constant) with an error $u$, which is by definition heteroskedastic.
+First, the location model can be estimated using a standard linear regression model, where the dependent variable is the outcome $y$, and the independent variables are the explanatory variables $X$ (including a constant) with an error $u$, which is by definition heteroskedastic.
 In this case, the location model coefficients are identified under the following condition:
@@
   |\nu_i| &=x_i'\gamma+\omega_i \\
-  E\big[ x_i \omega_i \big] &=0 \\
    E\big[ x_i (|\nu_i| -x_i'\gamma ) \big] &=0
@@
 $$\begin{aligned}
-  E\left[  \mathbb{1}\left(x_i' (\beta + \gamma q(\varepsilon|\tau)) \geq y_i \right) - \tau \right] &=0  \\
-  E\left[  \mathbb{1}\left(   q(\varepsilon|\tau)\geq \frac{y_i-x_i'\beta}{x_i'\gamma} \right) - \tau \right] &=0  \\
+  E\left[  \mathbb{1}\left(x_i' (\beta +   \gamma q(\tau)) \geq y_i \right) - \tau \right] &=0  \\
+  E\left[  \mathbb{1}\left(   q(\tau) \geq \frac{y_i-x_i'\beta}{x_i'\gamma} \right) - \tau \right] &=0  \\
   \end{aligned}
@@
 
-Where one identifies the quantile of the error $\varepsilon$ using standardized errors $\frac{y_i-x_i'\beta}{x_i'\gamma}$, or by finding the values that identify the overall quantile coefficients $\beta(\tau)=\beta + \gamma q(\varepsilon|\tau)$.
+Where one identifies the quantile of the error $\varepsilon$ using standardized errors $\frac{y_i-x_i'\beta}{x_i'\gamma}$, or by finding the values that identify the overall quantile coefficients $\beta(\tau)=\beta + \gamma q(\tau)$.
 Afterwords, the conditional quantile coefficients is simply defined as the combination of the location and scale coefficients.
@@
   E[x_i  (|\nu_i|-x_i \gamma) ] &=E[h_{2,i}]=0 \\
-  E\left[  \mathbb{1}\left(   q(\varepsilon|\tau)\geq \frac{y_i-x_i'\beta}{x_i'\gamma} \right) - \tau \right] 
+  E\left[  \mathbb{1}\left(   q(\tau)\geq \frac{y_i-x_i'\beta}{x_i'\gamma} \right) - \tau \right] 
   &=E[h_{3,i}]=0 
@@
 
-Call $\theta=[ \beta' \ \ \gamma' \ \ q(\varepsilon|\tau)' ]'$ the set of coefficients that are identified by the modement conditions in @eq-eq10, a just identified model.
+Call $\theta=[ \beta' \ \ \gamma' \ \ q(\tau) ]'$ the set of coefficients that are identified by the modement conditions in @eq-eq10, a just identified model.
 And the function $h_i$ is a vector function that stacks all the moments at the individual level described in @eq-eq10.
@@
 
-In this framework, the quantile regression coefficients, a combination of the location-scale-quantile estimates, will follow a normal distribution with mean $\beta(\tau) = \beta+q(\varepsilon|\tau)\gamma$ and variance-covariance matrix equal to:
+In this framework, the quantile regression coefficients, a combination of the location-scale-quantile estimates, will follow a normal distribution with mean $\beta(\tau) = \beta+\gamma q(\tau)$ and variance-covariance matrix equal to:
 
@@
 
-$$\Xi = [ I(k), \hat q(\varepsilon|\tau) \times I(k), \hat \gamma ]
-$${#eq-eqqtile}
+$$\Xi = [ I(k), \hat q(\tau) \times I(k), \hat \gamma ]
+$$ {#eq-eqqtile}
 
@@
 $$\hat{V}(\theta) = \frac{1}{N^2} \sum_{i=1}^N \lambda_i(\theta) \lambda_i(\theta)'
-$${#eq-eqvcv}
+$$ {#eq-eqvcv}
 
@@
 
-For the specific case of quantile regressions via momoments, the influence functions for the location, scale and quantile coefficients are:[^7]
+For the specific case of quantile regressions via momoments, the influence functions for the location, scale and quantile coefficients are:[^4]
 
-[^7]: The derivation of the influence functions can be found in the appendix.
+[^4]: The derivation of the influence functions can be found in the appendix.
 
@@
   \lambda_{i}(\gamma) \\
-  \lambda_{i}(q(\varepsilon|\tau)) 
+  \lambda_{i}(q(\tau)) 
   \end{bmatrix} \\
@@
 \lambda_{i}(\gamma)&= N(X'X)^{-1} x_i ( x_i' \gamma ) \times (\tilde \varepsilon_i -1\big)\\
-\lambda_{i}(q(\varepsilon|\tau))&=\frac{\tau-\mathbb{1}\big( q(\varepsilon|\tau)  \geq \varepsilon_i  \big) }{f_{\varepsilon}(q(\varepsilon|\tau))}
+\lambda_{i}(q(\tau))&=\frac{\tau-\mathbb{1}\big( q(\tau)  \geq \varepsilon_i  \big) }{f_{\varepsilon}(q(\tau))}
 - \frac{ x_i'\gamma \times \varepsilon_i }{\bar x_i'\gamma} 
--  q(\varepsilon|\tau) \frac{  x_i' \gamma  \times (\tilde \varepsilon_i -1\big)}{\bar x_i'\gamma}
+-  q(\tau) \frac{  x_i' \gamma  \times (\tilde \varepsilon_i -1\big)}{\bar x_i'\gamma}
 \end{aligned}
-$${#eq-ifs}
+$$ {#eq-ifs}
 
@@
   \hat\gamma \\
-  \hat q(\varepsilon|\tau)
+  \hat q(\tau)
   \end{pmatrix}
@@
  \begin{pmatrix}
- \sum \lambda_i(\beta) \lambda_i(\beta)' & \sum \lambda_i(\beta) \lambda_i(\gamma)' & \sum \lambda_i(\beta) \lambda_i(q(\varepsilon|\tau))' \\
- \sum \lambda_i(\gamma) \lambda_i(\beta)' & \sum \lambda_i(\gamma) \lambda_i(\gamma)' & \sum \lambda_i(\gamma) \lambda_i(q(\varepsilon|\tau))' \\
- \sum \lambda_i(q(\varepsilon|\tau) \lambda_i(\beta)' & \sum \lambda_i(q(\varepsilon|\tau))\lambda_i(\gamma)' & \sum \lambda_i(q(\varepsilon|\tau)) \lambda_i(q(\varepsilon|\tau))' 
+ \sum \lambda_i(\beta) \lambda_i(\beta)' & \sum \lambda_i(\beta) \lambda_i(\gamma)' & \sum \lambda_i(\beta) \lambda_i(q(\tau))' \\
+ \sum \lambda_i(\gamma) \lambda_i(\beta)' & \sum \lambda_i(\gamma) \lambda_i(\gamma)' & \sum \lambda_i(\gamma) \lambda_i(q(\tau))' \\
+ \sum \lambda_i(q(\tau)) \lambda_i(\beta)' & \sum \lambda_i(q(\tau))\lambda_i(\gamma)' & \sum \lambda_i(q(\tau)) \lambda_i(q(\tau))' 
   \end{pmatrix}
@@
 
-Call $N_G$ to be the total number of clusteres g, where $g=1\dots N_G$. The clustered variance covariance matrix is given by:[^10]
+Call $N_G$ to be the total number of clusteres g, where $g=1\dots N_G$. The clustered variance covariance matrix is given by:[^5]
 
-[^10]: It should be noted that one could just as well apply the insights of @cameron_robust_2011, allowing for multiway clustering.
+[^5]: It should be noted that one could just as well apply the insights of @cameron_robust_2011, allowing for multiway clustering.
 
@@
 
-The standard errors proposed by MSS can be understood as an application of generalized least squares (GLS), which will be valid as long as the model for heteroskedasticity is correctly specified.[^15] To estimate the GLS-Standard errors, we make use of the following property:
+The standard errors proposed by MSS can be understood as an application of generalized least squares (GLS), which will be valid as long as the model for heteroskedasticity is correctly specified.[^6] To estimate the GLS-Standard errors, we make use of the following property:
 
-[^15]: As discussed in most econometric textbooks, like @cameron2005, one approach to correct for heteroskedasticity, when the heteroskedasticity functional form is known, or can be estimated, is to use weighted least squares.
+[^6]: As discussed in most econometric textbooks, like @cameron2005, one approach to correct for heteroskedasticity, when the heteroskedasticity functional form is known, or can be estimated, is to use weighted least squares.
 While feasible, however, this approach would defeat the purpose of identifying quantile effects exploiting the heteroskedasticity of the model.
@@
 \tilde \lambda_{3,i}&=x_i' \gamma  \\
-\tilde \psi_1 &= \varepsilon_i \\
-\tilde \psi_2 &= \tilde \varepsilon_i -1 \\
-\tilde \psi_3 &= \frac{1}{ x_i' \gamma }\frac{\tau-\mathbb{1}\big( q(\varepsilon|\tau)  \geq \varepsilon_i  \big) }{ f_{\varepsilon}(q(\varepsilon|\tau))} - \frac{\varepsilon_i }{\bar x_i'\gamma} 
--  q(\varepsilon|\tau) \frac{(\tilde \varepsilon_i -1\big)}{\bar x_i'\gamma}
+ \psi_1 &= \varepsilon_i \\
+ \psi_2 &= \tilde \varepsilon_i -1 \\
+ \psi_3 &= \frac{1}{ x_i' \gamma }\frac{\tau-\mathbb{1}\big( q(\tau)  \geq \varepsilon_i  \big) }{ f_{\varepsilon}(q(\tau))} - \frac{\varepsilon_i }{\bar x_i'\gamma} 
+-  q(\tau) \frac{(\tilde \varepsilon_i -1\big)}{\bar x_i'\gamma}
 \end{aligned}
@@
 
-where we assume $x_{i}$ vary across groups $g_1$ and $g_2$, thus are not collinear, and that $\delta's$ and $\zeta's$ are the location and scale effects associated with groups fixed effects.[^4]
+where we assume $x_{i}$ vary across groups $g_1$ and $g_2$, thus are not collinear, and that $\delta's$ and $\zeta's$ are the location and scale effects associated with groups fixed effects.[^7]
 
-[^4]: We could just as well consider multiple sets of fixed effects
+[^7]: We could just as well consider multiple sets of fixed effects
 
@@
 
-Afterwards, we estimate the location model using the centered-residualized variables:[^rc]
+Afterwards, we estimate the location model using the centered-residualized variables:[^8]
+
+[^8]: Using centered-residualized variables allow us to include a constant in the model specification, which simplifies the derivation of the influence functions.
+However, as with other fixed effects models, the constant is not identified, and thus should not be interpreted.
 
@@
 $$
-
-[^rc]: Using centered-residualized variables allow us to include a constant in the model specification, which simplifies the derivation of the influence functions.
-However, as with other fixed effects models, the constant is not identified, and thus should not be interpreted.
 
@@
 @tbl-sim1 reports the bias, simulated standard error and mean squared error.
-We also report the results obtained using an adaptation bias-corrected estimator based on the split-panel jackknife estimator proposed by @dhaene2015.[^jk] These results are labeled JKC.
+We also report the results obtained using an adaptation bias-corrected estimator based on the split-panel jackknife estimator proposed by @dhaene2015.[^9] These results are labeled JKC.
 
-[^jk]: For the implementation, we estimate the model using the full sample, then, randomly assign each observation into one of two groups, and re-estimate the quantile coefficients for each group.
+[^9]: For the implementation, we estimate the model using the full sample, then, randomly assign each observation into one of two groups, and re-estimate the quantile coefficients for each group.
 The bias-corrected estimator is then obtained as $\hat\beta(\tau)_{jkc}=2*\hat\beta(\tau)_{full}-0.5*\big(\hat\beta(\tau)_{s1}+\hat\beta(\tau)_{s1}\big)$.
@@
 
-::: {#tbl-sim1 layout-nrow=2 layout-ncol=2}
+| N = 500      |   Bias   |   Sim SE   |   MSE   | N = 1000     |   Bias   |   Sim SE   |   MSE   |
+|---------|:-------:|:-------:|:-------:|---------|:-------:|:-------:|:-------:|
+| q25          |          |            |         | q25          |          |            |         |
+|  mmqreg      |  0.104   |   0.247    |  0.072  |  mmqreg      |  0.050   |   0.173    |  0.032  |
+|  jkc         |  0.008   |   0.297    |  0.088  |  jkc         |  -0.001  |   0.191    |  0.036  |
+| q75          |          |            |         | q75          |          |            |         |
+|  mmqreg      |  -0.091  |   0.251    |  0.071  |  mmqreg      |  -0.044  |   0.176    |  0.033  |
+|  jkc         |  0.002   |   0.303    |  0.092  |  jkc         |  0.006   |   0.195    |  0.038  |
+| **N = 2000** | **Bias** | **Sim SE** | **MSE** | **N = 4000** | **Bias** | **Sim SE** | **MSE** |
+| q25          |          |            |         | q25          |          |            |         |
+|  mmqreg      |  0.025   |   0.122    |  0.016  |  mmqreg      |  0.012   |   0.087    |  0.008  |
+|  jkc         |  0.003   |   0.129    |  0.017  |  jkc         |  0.000   |   0.089    |  0.008  |
+| q75          |          |            |         | q75          |          |            |         |
+|  mmqreg      |  -0.023  |   0.124    |  0.016  |  mmqreg      |  -0.011  |   0.087    |  0.008  |
+|  jkc         |  0.001   |   0.131    |  0.017  |  jkc         |  0.000   |   0.089    |  0.008  |
 
-| N = 500      |         Bias | Sim SE       |         MSE  |
-| ------------ | :----------: | :----------: | :----------: |
-| q25          |              |              |              |
-| \ mmqreg       |        0.104 |        0.247 |        0.072 |
-| \ jkc          |        0.008 |        0.297 |        0.088 |
-| q75          |              |              |              |
-| \ mmqreg       |       -0.091 |        0.251 |        0.071 |
-| \ jkc          |        0.002 |        0.303 |        0.092 |
-
-| N = 1000     |         Bias | Sim SE       |         MSE  |
-| ------------ | :----------: | :----------: | :----------: |
-| q25          |              |              |              |
-| \ mmqreg       |        0.050 |        0.173 |        0.032 |
-| \ jkc          |       -0.001 |        0.191 |        0.036 |
-| q75          |              |              |              |
-| \ mmqreg       |       -0.044 |        0.176 |        0.033 |
-| \ jkc          |        0.006 |        0.195 |        0.038 |
-
-| N = 1000      |         Bias | Sim SE       |         MSE  |
-| ------------ | :----------: | :----------: | :----------: |
-| q25          |              |              |              |
-| \ mmqreg       |        0.025 |        0.122 |        0.016 |
-| \ jkc          |        0.003 |        0.129 |        0.017 |
-| q75          |              |              |              |
-| \ mmqreg       |       -0.023 |        0.124 |        0.016 |
-| \ jkc          |        0.001 |        0.131 |        0.017 |
-
-| N = 2000      |         Bias | Sim SE       |         MSE  |
-| ------------ | :----------: | :----------: | :----------: |
-| q25          |              |              |              |
-| \ mmqreg       |        0.012 |        0.087 |        0.008 |
-| \ jkc          |        0.000 |        0.089 |        0.008 |
-| q75          |              |              |              |
-| \ mmqreg       |       -0.011 |        0.087 |        0.008 |
-| \ jkc          |        0.000 |        0.089 |        0.008 |
-
-Bias, Simulated Standard error, and Mean Squared Error
-
-:::
+: Bias, Simulated Standard error, and Mean Squared Error {#tbl-sim1}
 
@@
 |             | Het:q25 | Het:q75 | Clust:q25 | Clust:q75 |
-| ------------ | :----------: | :----------: | :----------: | :----------: |
+|-------------|:-------:|:-------:|:---------:|:---------:|
 | Coefficient |  0.550  |  1.442  |   0.775   |   1.229   |
-| SIM\_SE       |        0.154 |        0.155 |        0.109 |        0.107 |
-| GLS\_SE       |        0.476 |        0.451 |        0.288 |        0.221 |
+| SIM_SE      |  0.154  |  0.155  |   0.109   |   0.107   |
+| GLS_SE      |  0.476  |  0.451  |   0.288   |   0.221   |
 | Robust      |  0.140  |  0.139  |   0.087   |   0.088   |
 | Cluster     |         |         |   0.097   |   0.097   |
+
 : Heteroskedasticity misspecification and clustered errors {#tbl-sim2}
@@
 
-|            | polityt |       lyp |     trade |   p1564 |     p65 |      lspl |    oil\_im |    oil\_ex |      ygap |
-| ---------- | :-------: | :-------: | :-------: | :-------: | :-------: | :-------: | :-------: | :-------: | :-------: |
+|          | polityt |  lyp   | trade | p1564 |  p65   |  lspl  | oil_im | oil_ex |  ygap  |
+|----------|:-------:|:------:|:-----:|:-----:|:------:|:------:|:------:|:------:|:------:|
 | Location |         |        |       |       |        |        |        |        |        |
-| \ coeff      |     0.116 |    -0.715 |     0.030 |     0.121 |     0.028 |     0.691 |    -0.047 |    -0.006 |     0.010 |
-| \ se\_gls     |     0.046 |     0.540 |     0.008 |     0.033 |     0.070 |     0.035 |     0.008 |     0.022 |     0.028 |
-| \ se\_r       |     0.047 |     0.597 |     0.008 |     0.031 |     0.070 |     0.037 |     0.007 |     0.017 |     0.021 |
-| \ se\_cl      |     0.046 |     0.465 |     0.007 |     0.032 |     0.071 |     0.035 |     0.010 |     0.020 |     0.023 |
+|  coeff   |  0.116  | -0.715 | 0.030 | 0.121 | 0.028  | 0.691  | -0.047 | -0.006 | 0.010  |
+|  se_gls  |  0.046  | 0.540  | 0.008 | 0.033 | 0.070  | 0.035  | 0.008  | 0.022  | 0.028  |
+|  se_r    |  0.047  | 0.597  | 0.008 | 0.031 | 0.070  | 0.037  | 0.007  | 0.017  | 0.021  |
+|  se_cl   |  0.046  | 0.465  | 0.007 | 0.032 | 0.071  | 0.035  | 0.010  | 0.020  | 0.023  |
 | Scale    |         |        |       |       |        |        |        |        |        |
-| \ coeff      |    -0.097 |    -0.616 |     0.003 |     0.036 |     0.087 |    -0.085 |     0.013 |     0.016 |    -0.004 |
-| \ se\_gls     |     0.032 |     0.371 |     0.005 |     0.023 |     0.048 |     0.024 |     0.006 |     0.015 |     0.019 |
-| \ se\_r       |     0.031 |     0.398 |     0.005 |     0.020 |     0.049 |     0.025 |     0.005 |     0.010 |     0.015 |
-| \ se\_cl      |     0.048 |     0.800 |     0.008 |     0.031 |     0.067 |     0.029 |     0.004 |     0.010 |     0.012 |
+|  coeff   | -0.097  | -0.616 | 0.003 | 0.036 | 0.087  | -0.085 | 0.013  | 0.016  | -0.004 |
+|  se_gls  |  0.032  | 0.371  | 0.005 | 0.023 | 0.048  | 0.024  | 0.006  | 0.015  | 0.019  |
+|  se_r    |  0.031  | 0.398  | 0.005 | 0.020 | 0.049  | 0.025  | 0.005  | 0.010  | 0.015  |
+|  se_cl   |  0.048  | 0.800  | 0.008 | 0.031 | 0.067  | 0.029  | 0.004  | 0.010  | 0.012  |
 | Q25      |         |        |       |       |        |        |        |        |        |
-| \ coeff      |     0.191 |    -0.239 |     0.028 |     0.093 |    -0.039 |     0.756 |    -0.057 |    -0.018 |     0.013 |
-| \ se\_gls     |     0.059 |     0.684 |     0.010 |     0.042 |     0.088 |     0.045 |     0.010 |     0.027 |     0.035 |
-| \ se\_r       |     0.056 |     0.656 |     0.008 |     0.036 |     0.086 |     0.040 |     0.010 |     0.020 |     0.025 |
-| \ se\_cl      |     0.073 |     0.687 |     0.006 |     0.041 |     0.098 |     0.023 |     0.010 |     0.021 |     0.029 |
+|  coeff   |  0.191  | -0.239 | 0.028 | 0.093 | -0.039 | 0.756  | -0.057 | -0.018 | 0.013  |
+|  se_gls  |  0.059  | 0.684  | 0.010 | 0.042 | 0.088  | 0.045  | 0.010  | 0.027  | 0.035  |
+|  se_r    |  0.056  | 0.656  | 0.008 | 0.036 | 0.086  | 0.040  | 0.010  | 0.020  | 0.025  |
+|  se_cl   |  0.073  | 0.687  | 0.006 | 0.041 | 0.098  | 0.023  | 0.010  | 0.021  | 0.029  |
 | Q50      |         |        |       |       |        |        |        |        |        |
-| \ coeff      |     0.108 |    -0.765 |     0.030 |     0.124 |     0.035 |     0.684 |    -0.046 |    -0.005 |     0.009 |
-| \ se\_gls     |     0.046 |     0.535 |     0.007 |     0.033 |     0.069 |     0.035 |     0.008 |     0.022 |     0.027 |
-| \ se\_r       |     0.046 |     0.593 |     0.008 |     0.031 |     0.069 |     0.036 |     0.007 |     0.017 |     0.021 |
-| \ se\_cl      |     0.043 |     0.484 |     0.008 |     0.032 |     0.070 |     0.036 |     0.010 |     0.020 |     0.023 |
+|  coeff   |  0.108  | -0.765 | 0.030 | 0.124 | 0.035  | 0.684  | -0.046 | -0.005 | 0.009  |
+|  se_gls  |  0.046  | 0.535  | 0.007 | 0.033 | 0.069  | 0.035  | 0.008  | 0.022  | 0.027  |
+|  se_r    |  0.046  | 0.593  | 0.008 | 0.031 | 0.069  | 0.036  | 0.007  | 0.017  | 0.021  |
+|  se_cl   |  0.043  | 0.484  | 0.008 | 0.032 | 0.070  | 0.036  | 0.010  | 0.020  | 0.023  |
 | Q75      |         |        |       |       |        |        |        |        |        |
-| \ coeff      |     0.031 |    -1.258 |     0.033 |     0.153 |     0.104 |     0.616 |    -0.036 |     0.008 |     0.006 |
-| \ se\_gls     |     0.048 |     0.551 |     0.008 |     0.034 |     0.071 |     0.036 |     0.008 |     0.022 |     0.028 |
-| \ se\_r       |     0.049 |     0.696 |     0.009 |     0.034 |     0.075 |     0.043 |     0.007 |     0.018 |     0.023 |
-| \ se\_cl      |     0.039 |     0.919 |     0.012 |     0.041 |     0.079 |     0.055 |     0.010 |     0.022 |     0.020 |
+|  coeff   |  0.031  | -1.258 | 0.033 | 0.153 | 0.104  | 0.616  | -0.036 | 0.008  | 0.006  |
+|  se_gls  |  0.048  | 0.551  | 0.008 | 0.034 | 0.071  | 0.036  | 0.008  | 0.022  | 0.028  |
+|  se_r    |  0.049  | 0.696  | 0.009 | 0.034 | 0.075  | 0.043  | 0.007  | 0.018  | 0.023  |
+|  se_cl   |  0.039  | 0.919  | 0.012 | 0.041 | 0.079  | 0.055  | 0.010  | 0.022  | 0.020  |
 
@@
 Considering the estimated effects across quantiles, we observe few differences in the reported GLS standard errors compared to the analytical standard errors reported MSS.
-Our clustered standard errors, however, are closer to the bootstrap based standard errors the authors report.[^20]
+Our clustered standard errors, however, are closer to the bootstrap based standard errors the authors report.[^10]
 
-[^20]: There are two possible reasons that may explain the differences in the GLS standard errors.
+[^10]: There are two possible reasons that may explain the differences in the GLS standard errors.
 On the one hand, in our derivation, the influence function of the standardized $\tau_{th}$ quantile (see #eq-infs) does not have the same leading term as the one reported in MSS (see theorem 3, and the definition of $W$).
@@
 |          | polity |  lyp   | trade | prop1564 | prop65 |  lspl  |  ygap  |
-| ---------- | :-------: | :-------: | :-------: | :-------: | :-------: | :-------: | :-------: |
+|----------|:------:|:------:|:-----:|:--------:|:------:|:------:|:------:|
 | Location |        |        |       |          |        |        |        |
-| \ coeff      |     0.126 |    -0.418 |     0.028 |     0.108 |     0.042 |     0.693 |    -0.014 |
-| \ se\_gls     |     0.087 |     1.157 |     0.015 |     0.072 |     0.136 |     0.066 |     0.053 |
-| \ se\_r       |     0.047 |     0.703 |     0.008 |     0.038 |     0.068 |     0.038 |     0.022 |
-| \ se\_cl      |     0.048 |     0.506 |     0.008 |     0.044 |     0.077 |     0.037 |     0.022 |
+|  coeff   | 0.126  | -0.418 | 0.028 |  0.108   | 0.042  | 0.693  | -0.014 |
+|  se_gls  | 0.087  | 1.157  | 0.015 |  0.072   | 0.136  | 0.066  | 0.053  |
+|  se_r    | 0.047  | 0.703  | 0.008 |  0.038   | 0.068  | 0.038  | 0.022  |
+|  se_cl   | 0.048  | 0.506  | 0.008 |  0.044   | 0.077  | 0.037  | 0.022  |
 | Scale    |        |        |       |          |        |        |        |
-| \ coeff      |    -0.095 |    -1.255 |     0.005 |     0.033 |     0.040 |    -0.081 |     0.008 |
-| \ se\_gls     |     0.081 |     1.073 |     0.014 |     0.067 |     0.126 |     0.061 |     0.049 |
-| \ se\_r       |     0.031 |     0.452 |     0.005 |     0.025 |     0.045 |     0.025 |     0.017 |
-| \ se\_cl      |     0.041 |     0.848 |     0.006 |     0.030 |     0.048 |     0.033 |     0.013 |
+|  coeff   | -0.095 | -1.255 | 0.005 |  0.033   | 0.040  | -0.081 | 0.008  |
+|  se_gls  | 0.081  | 1.073  | 0.014 |  0.067   | 0.126  | 0.061  | 0.049  |
+|  se_r    | 0.031  | 0.452  | 0.005 |  0.025   | 0.045  | 0.025  | 0.017  |
+|  se_cl   | 0.041  | 0.848  | 0.006 |  0.030   | 0.048  | 0.033  | 0.013  |
 | Q25      |        |        |       |          |        |        |        |
-| \ coeff      |     0.201 |     0.576 |     0.025 |     0.082 |     0.010 |     0.757 |    -0.020 |
-| \ se\_gls     |     0.154 |     2.070 |     0.024 |     0.118 |     0.219 |     0.121 |     0.085 |
-| \ se\_r       |     0.058 |     0.751 |     0.008 |     0.049 |     0.080 |     0.040 |     0.026 |
-| \ se\_cl      |     0.073 |     0.761 |     0.006 |     0.052 |     0.087 |     0.023 |     0.027 |
+|  coeff   | 0.201  | 0.576  | 0.025 |  0.082   | 0.010  | 0.757  | -0.020 |
+|  se_gls  | 0.154  | 2.070  | 0.024 |  0.118   | 0.219  | 0.121  | 0.085  |
+|  se_r    | 0.058  | 0.751  | 0.008 |  0.049   | 0.080  | 0.040  | 0.026  |
+|  se_cl   | 0.073  | 0.761  | 0.006 |  0.052   | 0.087  | 0.023  | 0.027  |
 | Q50      |        |        |       |          |        |        |        |
-| \ coeff      |     0.119 |    -0.512 |     0.029 |     0.111 |     0.045 |     0.687 |    -0.013 |
-| \ se\_gls     |     0.091 |     1.230 |     0.014 |     0.070 |     0.130 |     0.072 |     0.051 |
-| \ se\_r       |     0.046 |     0.695 |     0.008 |     0.037 |     0.068 |     0.038 |     0.022 |
-| \ se\_cl      |     0.045 |     0.529 |     0.008 |     0.044 |     0.077 |     0.039 |     0.021 |
+|  coeff   | 0.119  | -0.512 | 0.029 |  0.111   | 0.045  | 0.687  | -0.013 |
+|  se_gls  | 0.091  | 1.230  | 0.014 |  0.070   | 0.130  | 0.072  | 0.051  |
+|  se_r    | 0.046  | 0.695  | 0.008 |  0.037   | 0.068  | 0.038  | 0.022  |
+|  se_cl   | 0.045  | 0.529  | 0.008 |  0.044   | 0.077  | 0.039  | 0.021  |
 | Q75      |        |        |       |          |        |        |        |
-| \ coeff      |     0.041 |    -1.555 |     0.033 |     0.138 |     0.078 |     0.619 |    -0.007 |
-| \ se\_gls     |     0.067 |     0.898 |     0.011 |     0.053 |     0.098 |     0.052 |     0.038 |
-| \ se\_r       |     0.048 |     0.827 |     0.009 |     0.037 |     0.075 |     0.046 |     0.026 |
-| \ se\_cl      |     0.038 |     0.980 |     0.012 |     0.050 |     0.086 |     0.063 |     0.020 |
+|  coeff   | 0.041  | -1.555 | 0.033 |  0.138   | 0.078  | 0.619  | -0.007 |
+|  se_gls  | 0.067  | 0.898  | 0.011 |  0.053   | 0.098  | 0.052  | 0.038  |
+|  se_r    | 0.048  | 0.827  | 0.009 |  0.037   | 0.075  | 0.046  | 0.026  |
+|  se_cl   | 0.038  | 0.980  | 0.012 |  0.050   | 0.086  | 0.063  | 0.020  |
+
 : The determinants of government surpluses: Individual and Time Fixed effects {#tbl-tb2}
@@
 
-$$q(y|\tau,x) = x'(\beta + q(\varepsilon |\tau) \times \gamma)$$
+$$Q_y(\tau|x) = x'(\beta + q(\tau) \times \gamma)$$
 
-This model is identified under the following conditions:
+where $q(\tau)$ is the $\tau_{th}$ quantile of the standardized residual of $\varepsilon$. This model is identified under the following conditions:
 
@@
   E[ (|y_i-x_i'\beta|-x_i' \gamma) x_i ] &=E[h_{2,i}]=0 \\
-  E\left[  \mathbb{1}\left( q(\varepsilon|\tau) x_i'\gamma +x_i'\beta\geq  y_i  \right) - \tau \right] 
+  E\left[  \mathbb{1}\left( q(\tau) x_i'\gamma +x_i'\beta\geq  y_i  \right) - \tau \right] 
    &=E[h_{3,i}]=0 
@@
 $$
-
-For simplicity, for the rest of the appendix, I will use $q^\varepsilon_\tau$ to represent $q(\varepsilon |\tau)$.
 
@@
 $$\bar G(\theta) = \begin{bmatrix}
-\bar G_{11} & G_{12} & G_{13} \\
-\bar G_{21} & \bar G_{22} & G_{23} \\
+\bar G_{11} & \bar G_{12} & \bar G_{13} \\
+\bar G_{21} & \bar G_{22} & \bar G_{23} \\
 \bar G_{31} & \bar G_{32} & \bar G_{13} \\
@@
 \bar G_{2,2} &= -\frac{1}{N} \sum \frac{\partial h_{2,i}}{\partial \gamma'} \\
-             &=  \frac{1}{N} \sum x_i x_i' 
+             &=  \frac{1}{N} \sum x_i x_i' \\
              &= N^{-1} X'X
@@
 $$\begin{aligned}
-h_{3,i} &= \mathbb{1}\left( q^\varepsilon_\tau x_i'\gamma +x_i'\beta - y_i \geq 0 \right) - \tau \text{ or}\\
-h_{3,i} &= \mathbb{1}\left( q^\varepsilon_\tau  \geq \frac{y_i- x_i'\beta}{x_i'\gamma}  \right) - \tau = \mathbb{1}\big( q^\varepsilon_\tau  \geq \varepsilon  \big) - \tau \\
+h_{3,i} &= \mathbb{1}\left(q(\tau) x_i'\gamma +x_i'\beta - y_i \geq 0 \right) - \tau \text{ or}\\
+h_{3,i} &= \mathbb{1}\left( q(\tau)  \geq \frac{y_i- x_i'\beta}{x_i'\gamma}  \right) - \tau = \mathbb{1}\big( q(\tau)  \geq \varepsilon  \big) - \tau \\
 \end{aligned}
@@
 
-$$h_{3,i} \approx I\left( q^\varepsilon_\tau x_i'\gamma +x_i'\beta - y_i  \right) - \tau$$
+$$h_{3,i} \approx I\left( q(\tau) x_i'\gamma +x_i'\beta - y_i  \right) - \tau$$
 
@@
 \bar G_{3,1} &= -\frac{1}{N} \sum \frac{\partial h_{3,i}}{\partial \beta'} \\
-             &= -N^{-1} \sum K_h(q^\varepsilon_\tau x_i'\gamma +x_i'\beta - y_i ) x_i'
+             &= -N^{-1} \sum K_h(q(\tau) x_i'\gamma +x_i'\beta - y_i ) x_i'
 \end{aligned}
@@
 $$\begin{aligned}
-E(K_h(q^\varepsilon_\tau x_i'\gamma +x_i'\beta - y_i )|X) &= f_{y|X}(q^\varepsilon_\tau x_i'\gamma +x_i'\beta) \\
-&=\frac{1}{x_i'\gamma} f_{\varepsilon}(q^\varepsilon_\tau) \\
+E(K_h(q(\tau) x_i'\gamma +x_i'\beta - y_i )|X) &= f_{y|X}(q(\tau) x_i'\gamma +x_i'\beta) \\
+&=\frac{1}{x_i'\gamma} f_{\varepsilon}(q(\tau)) \\
 \end{aligned}
@@
 
-$$\bar G_{3,1} = -N^{-1} f_{\varepsilon}\big(q^\varepsilon_\tau\big) \sum  \frac{x_i'}{x_i'\gamma} 
+$$\bar G_{3,1} = -N^{-1} f_{\varepsilon}\big(q(\tau)\big) \sum  \frac{x_i'}{x_i'\gamma} 
 $$
 
-Asymptotically, however, the expression $\sum\frac{a_i}{b_i}$ can be approximated using taylor expansions by $N\frac{\bar a}{\bar b}$. [^6] Thus, we can rewrite the last term as:
+Asymptotically, however, the expression $\sum\frac{a_i}{b_i}$ can be approximated using taylor expansions by $N\frac{\bar a}{\bar b}$. [^11] Thus, we can rewrite the last term as:
 
-$$\bar G_{3,1} = - f_{\varepsilon}\big(q^\varepsilon_\tau\big) \frac{\bar x_i'}{\bar x_i'\gamma} 
+[^11]: This approximation will be useful when we consider the estimation of the influence functions.
+
+$$\bar G_{3,1} = - f_{\varepsilon}\big(q(\tau)) \frac{\bar x_i'}{\bar x_i'\gamma} 
 $$
-
-[^6]: This approximation will be useful when we consider the estimation of the influence functions.
 
@@
 \bar G_{3,2} &= -\frac{1}{N} \sum \frac{\partial h_{3,i}}{\partial \gamma'} \\
-             &= -N^{-1} \sum K_h(q^\varepsilon_\tau x_i'\gamma +x_i'\beta - y_i ) q^\varepsilon_\tau x_i' \\
-             &=-N^{-1} \sum f_{y|x}(q^\varepsilon_\tau x_i'\gamma +x_i'\beta ) q^\varepsilon_\tau x_i' \\
-             &=-N^{-1} f_{\varepsilon}(q^\varepsilon_\tau) q^\varepsilon_\tau \sum \frac{x_i'}{x_i'\gamma} \\
-             &=- f_{\varepsilon}(q^\varepsilon_\tau) q^\varepsilon_\tau \frac{\bar x_i'}{\bar x_i'\gamma}
+             &= -N^{-1} \sum K_h(q(\tau) x_i'\gamma +x_i'\beta - y_i ) q(\tau) x_i' \\
+             &=-N^{-1} \sum f_{y|x}(q(\tau) x_i'\gamma +x_i'\beta ) q(\tau) x_i' \\
+             &=-N^{-1} f_{\varepsilon}(q(\tau)) q(\tau) \sum \frac{x_i'}{x_i'\gamma} \\
+             &=- f_{\varepsilon}(q(\tau)) q(\tau) \frac{\bar x_i'}{\bar x_i'\gamma}
 \end{aligned}
@@
 $$\begin{aligned}
-\bar G_{3,3} &= -\frac{1}{N} \sum \frac{\partial h_{3,i}}{\partial q^\varepsilon_\tau} \\
- &= -\frac{1}{N} \sum K_h(q^\varepsilon_\tau x_i'\gamma +x_i'\beta - y_i ) x_i'\gamma \\
- &= -\frac{1}{N} \sum f_{y|X}(q^\varepsilon_\tau x_i'\gamma +x_i'\beta) x_i'\gamma \\
- &= -\frac{1}{N} \sum f_{\varepsilon}(q^\varepsilon_\tau) \frac{x_i'\gamma}{ x_i'\gamma} \\
- &= - f_{\varepsilon}(q^\varepsilon_\tau) 
+\bar G_{3,3} &= -\frac{1}{N} \sum \frac{\partial h_{3,i}}{\partial q(\tau)} \\
+ &= -\frac{1}{N} \sum K_h(q(\tau) x_i'\gamma +x_i'\beta - y_i ) x_i'\gamma \\
+ &= -\frac{1}{N} \sum f_{y|X}(q(\tau) x_i'\gamma +x_i'\beta) x_i'\gamma \\
+ &= -\frac{1}{N} \sum f_{\varepsilon}(q(\tau)) \frac{x_i'\gamma}{ x_i'\gamma} \\
+ &= - f_{\varepsilon}(q(\tau)) 
 \end{aligned}
@@
 
-And
-$$\begin{aligned}
+And $$\begin{aligned}
 E[sign(\nu_i)] &= E[\mathbb{1}(\nu_i \geq 0)] - E[\mathbb{1}(\nu_i < 0)] \\
@@
 $$\begin{aligned}
-\lambda_i(q^\varepsilon_\tau)&=\bar G_{3,3}^{-1}
+\lambda_i(q(\tau))&=\bar G_{3,3}^{-1}
 \Big(
@@
 \Big) \\
-&=-\frac{1}{f_{\varepsilon}(q^\varepsilon_\tau)} \times \Bigg( \Big(\mathbb{1} ( q^\varepsilon_\tau  \geq \varepsilon  ) - \tau \Big)  \\
-&+ f_{\varepsilon} (q^\varepsilon_\tau) \frac{\bar x_i'}{\bar x_i'\gamma} 
+&=-\frac{1}{f_{\varepsilon}(q(\tau))} \times \Bigg( \Big(\mathbb{1} ( q(\tau)  \geq \varepsilon  ) - \tau \Big)  \\
+&+ f_{\varepsilon} (q(\tau)) \frac{\bar x_i'}{\bar x_i'\gamma} 
 N (X'X)^{-1} x_i  ( x_i'\gamma \times \varepsilon) \\
-&+ f_{\varepsilon}(q^\varepsilon_\tau) q^\varepsilon_\tau \frac{\bar x_i'}{\bar x_i'\gamma} N(X'X)^{-1} x_i   \big( \tilde \nu_i -x_i' 
+&+ f_{\varepsilon}(q(\tau)) q(\tau) \frac{\bar x_i'}{\bar x_i'\gamma} N(X'X)^{-1} x_i   \big( \tilde \nu_i -x_i' 
   \gamma \big) 
 \Bigg) \\
-&=\frac{\tau-\mathbb{1}\big( q^\varepsilon_\tau  \geq \varepsilon  \big) }{f_{\varepsilon}(q^\varepsilon_\tau)}
+&=\frac{\tau-\mathbb{1}\big( q(\tau)  \geq \varepsilon  \big) }{f_{\varepsilon}(q(\tau))}
 - \frac{ x_i'\gamma \times \varepsilon_i }{\bar x_i'\gamma} 
--  q^\varepsilon_\tau \frac{ \tilde \nu_i -x_i' 
+-  q(\tau) \frac{ \tilde \nu_i -x_i' 
   \gamma }{\bar x_i'\gamma} 
@@
 
-- `mmqreg` in Stata: `net install mmqreg, from(https://friosavila.github.io/stpackages)
+-   `mmqreg` in Stata: \`net install mmqreg, from(https://friosavila.github.io/stpackages)
 -   `mmqreg` in R: Program Available in mmqreg repository in GitHub (https://github.com/friosavila/mmqreg)

### 2023-11-07 article/article.tex
q(\tau)
q(\tau)

--- 2023-11-01 article/article.tex
@@
 explanatory variables X and the conditional quantiles of the dependent
-variable \(q_\tau (y|x)\). Using QR one can obtain richer
+variable \(Q_y (\tau|x)\). Using QR one can obtain richer
 characterizations of the relationships between dependent and independent
@@
 constraining their effect to be a location shift only as in
-\citet{canay2011}, \citet{koenker2004}, and \citet{lancaster2000}.
+\citet{canay2011}, \citet{koenker2004}, and \citet{lamarche2010}.
 
@@
 simulation study and Section 4 illustrates the application of the
-proposed methods with two empirical examples. Seccion 5 concludes.
+proposed methods with one empirical example. Seccion 5 concludes.
 
@@
 explanatory variables \(x\) and the conditional quantiles of the
-dependent variable \(Q(y|\tau,X)\). This relationship is commonly
+dependent variable \(Q_y(\tau|X)\). This relationship is commonly
 assumed to follow a linear functional form:
 
-\begin{equation}\phantomsection\label{eq-eq1}{q(Y|X,\tau) =X\beta(\tau)
+\begin{equation}\phantomsection\label{eq-eq1}{Q_y(\tau|X) =X\beta(\tau)
 }\end{equation}
 
-This allows for nonlinearities in the effect of \(X\) on \(Y\) across
-all values of \(\tau\). This formulation can also be related to a random
-coefficient model, where all coefficients are assumed to be some
-nonlinear function of \(\tau\), where \(\tau\) follows a random uniform
-distribution.
+This allows for the effect of \(X\) on \(Y\) to vary across all
+\(\tau\). This formulation can also be related to a random coefficient
+model, where all coefficients are assumed to be some nonlinear function
+of \(\tau\), where \(\tau\) follows a random uniform distribution.
 
@@
 
-\begin{equation}\phantomsection\label{eq-eq2}{q(Y|X,\tau) =X\beta+X\gamma(\tau)
+\begin{equation}\phantomsection\label{eq-eq2}{Q_y(\tau|X) =X\beta+X\gamma(\tau)
 }\end{equation}
@@
 linear regression model (as in \citet{mss2019}), or a median regression
-(as in \citet{melly2005}), and the scale parameters \(\gamma(\tau)\) can
+(as in \citet{zhao2000}), and the scale parameters \(\gamma(\tau)\) can
 be estimated using standard approaches.
@@
 
-\begin{equation}\phantomsection\label{eq-eq5}{q(Y|X,\tau) =X\beta+q(\varepsilon|\tau) \times X\gamma 
+\begin{equation}\phantomsection\label{eq-eq5}{Q_y(\tau|X) =X\beta+Q_\varepsilon(\tau) \times X\gamma 
 }\end{equation}
@@
 moderated by the \(\tau_{th}\) unconditional quantile of the
-standardized error \(\varepsilon\).
-
-\begin{equation}\phantomsection\label{eq-eq6}{\beta(\tau) = \beta + q(\varepsilon|\tau) \times \gamma 
+standardized error \(\varepsilon\). For simplicity we will use
+\(q(\tau)\) to denote \(Q_\varepsilon(\tau)\) in the rest of the paper.
+
+\begin{equation}\phantomsection\label{eq-eq6}{\beta(\tau) = \beta + q(\tau) \times \gamma 
 }\end{equation}
@@
 because the location and scale model can be identified globally, with
-only a single paramater (\(q(\varepsilon|\tau)\)) requiring local
-estimation, this estimation approach would be more efficient than the
-standard quantile regression model (\citet{zhao2000}). Second, under the
-assumption that \(X\gamma\) is strictly possitive, the model would
-produce quantile coefficients that do not cross.
+only a single paramater (\(q(\tau)\)) requiring local estimation, this
+estimation approach would be more efficient than the standard quantile
+regression model \citep{zhao2000}. Second, under the assumption that
+\(X\gamma\) is strictly possitive, the model would produce quantile
+coefficients that do not cross.
 
@@
 approach. And while its possible to identify all coefficients
-(\(\beta,\gamma, q(\varepsilon|\tau)\)) simultaneously, we describe and
-use the implementation approach advocated by MSS which identifies each
-set of coefficients separately.
+(\(\beta,\gamma, q(\tau)\)) simultaneously, we describe and use the
+implementation approach advocated by MSS which identifies each set of
+coefficients separately.
 
 First, the location model can be estimated using a standard linear
-regression model, where the dependent variable is the outcome \(Y\), and
+regression model, where the dependent variable is the outcome \(y\), and
 the independent variables are the explanatory variables \(X\) (including
@@
 
-Thurd, given the location and scale coefficients, the \(\tau_{th}\)
+Third, given the location and scale coefficients, the \(\tau_{th}\)
 quantile of the error \(\varepsilon\) can be estimated using the
@@
 \begin{equation}\phantomsection\label{eq-eq9}{\begin{aligned}
-  E\left[  \mathbb{1}\left(x_i' (\beta + \gamma q(\varepsilon|\tau)) \geq y_i \right) - \tau \right] &=0  \\
-  E\left[  \mathbb{1}\left(   q(\varepsilon|\tau)\geq \frac{y_i-x_i'\beta}{x_i'\gamma} \right) - \tau \right] &=0  \\
+  E\left[  \mathbb{1}\left(x_i' (\beta +   \gamma q(\tau)) \geq y_i \right) - \tau \right] &=0  \\
+  E\left[  \mathbb{1}\left(   q(\tau) \geq \frac{y_i-x_i'\beta}{x_i'\gamma} \right) - \tau \right] &=0  \\
   \end{aligned}
@@
 the values that identify the overall quantile coefficients
-\(\beta(\tau)=\beta + \gamma q(\varepsilon|\tau)\). Afterwords, the
-conditional quantile coefficients is simply defined as the combination
-of the location and scale coefficients.
+\(\beta(\tau)=\beta + \gamma q(\tau)\). Afterwords, the conditional
+quantile coefficients is simply defined as the combination of the
+location and scale coefficients.
 
@@
 
-Call \(\theta=[ \beta' \ \ \gamma' \ \ q(\varepsilon|\tau)' ]'\) the set
-of coefficients that are identified by the modement conditions in
+Call \(\theta=[ \beta' \ \ \gamma' \ \ q(\tau) ]'\) the set of
+coefficients that are identified by the modement conditions in
 Equation~\ref{eq-eq10}, a just identified model. And the function
@@
 of the location-scale-quantile estimates, will follow a normal
-distribution with mean \(\beta(\tau) = \beta+q(\varepsilon|\tau)\gamma\)
-and variance-covariance matrix equal to:
+distribution with mean \(\beta(\tau) = \beta+\gamma q(\tau)\) and
+variance-covariance matrix equal to:
 
@@
 
-\begin{equation}\phantomsection\label{eq-eqqtile}{\Xi = [ I(k), \hat q(\varepsilon|\tau) \times I(k), \hat \gamma ]
+\begin{equation}\phantomsection\label{eq-eqqtile}{\Xi = [ I(k), \hat q(\tau) \times I(k), \hat \gamma ]
 }\end{equation}
@@
 \lambda_{i}(\gamma)&= N(X'X)^{-1} x_i ( x_i' \gamma ) \times (\tilde \varepsilon_i -1\big)\\
-\lambda_{i}(q(\varepsilon|\tau))&=\frac{\tau-\mathbb{1}\big( q(\varepsilon|\tau)  \geq \varepsilon_i  \big) }{f_{\varepsilon}(q(\varepsilon|\tau))}
+\lambda_{i}(q(\tau))&=\frac{\tau-\mathbb{1}\big( q(\tau)  \geq \varepsilon_i  \big) }{f_{\varepsilon}(q(\tau))}
 - \frac{ x_i'\gamma \times \varepsilon_i }{\bar x_i'\gamma} 
--  q(\varepsilon|\tau) \frac{  x_i' \gamma  \times (\tilde \varepsilon_i -1\big)}{\bar x_i'\gamma}
+-  q(\tau) \frac{  x_i' \gamma  \times (\tilde \varepsilon_i -1\big)}{\bar x_i'\gamma}
 \end{aligned}
@@
 
-\begin{table}
-
-\caption{\label{tbl-sim1}Bias, Simulated Standard error, and Mean
-Squared Error}
-
-\begin{minipage}[t]{0.50\linewidth}
-
-\begin{longtable}[]{@{}lccc@{}}
+\begin{longtable}[]{@{}
+  >{\raggedright\arraybackslash}p{(\columnwidth - 14\tabcolsep) * \real{0.1250}}
+  >{\centering\arraybackslash}p{(\columnwidth - 14\tabcolsep) * \real{0.1250}}
+  >{\centering\arraybackslash}p{(\columnwidth - 14\tabcolsep) * \real{0.1250}}
+  >{\centering\arraybackslash}p{(\columnwidth - 14\tabcolsep) * \real{0.1250}}
+  >{\raggedright\arraybackslash}p{(\columnwidth - 14\tabcolsep) * \real{0.1250}}
+  >{\centering\arraybackslash}p{(\columnwidth - 14\tabcolsep) * \real{0.1250}}
+  >{\centering\arraybackslash}p{(\columnwidth - 14\tabcolsep) * \real{0.1250}}
+  >{\centering\arraybackslash}p{(\columnwidth - 14\tabcolsep) * \real{0.1250}}@{}}
+\caption{Bias, Simulated Standard error, and Mean Squared
+Error}\label{tbl-sim1}\tabularnewline
 \toprule\noalign{}
-N = 500 & Bias & Sim SE & MSE \\
+\begin{minipage}[b]{\linewidth}\raggedright
+N = 500
+\end{minipage} & \begin{minipage}[b]{\linewidth}\centering
+Bias
+\end{minipage} & \begin{minipage}[b]{\linewidth}\centering
+Sim SE
+\end{minipage} & \begin{minipage}[b]{\linewidth}\centering
+MSE
+\end{minipage} & \begin{minipage}[b]{\linewidth}\raggedright
+N = 1000
+\end{minipage} & \begin{minipage}[b]{\linewidth}\centering
+Bias
+\end{minipage} & \begin{minipage}[b]{\linewidth}\centering
+Sim SE
+\end{minipage} & \begin{minipage}[b]{\linewidth}\centering
+MSE
+\end{minipage} \\
+\midrule\noalign{}
+\endfirsthead
+\toprule\noalign{}
+\begin{minipage}[b]{\linewidth}\raggedright
+N = 500
+\end{minipage} & \begin{minipage}[b]{\linewidth}\centering
+Bias
+\end{minipage} & \begin{minipage}[b]{\linewidth}\centering
+Sim SE
+\end{minipage} & \begin{minipage}[b]{\linewidth}\centering
+MSE
+\end{minipage} & \begin{minipage}[b]{\linewidth}\raggedright
+N = 1000
+\end{minipage} & \begin{minipage}[b]{\linewidth}\centering
+Bias
+\end{minipage} & \begin{minipage}[b]{\linewidth}\centering
+Sim SE
+\end{minipage} & \begin{minipage}[b]{\linewidth}\centering
+MSE
+\end{minipage} \\
 \midrule\noalign{}
@@
 \endlastfoot
-q25 & & & \\
-~mmqreg & 0.104 & 0.247 & 0.072 \\
-~jkc & 0.008 & 0.297 & 0.088 \\
-q75 & & & \\
-~mmqreg & -0.091 & 0.251 & 0.071 \\
-~jkc & 0.002 & 0.303 & 0.092 \\
+q25 & & & & q25 & & & \\
+~mmqreg & 0.104 & 0.247 & 0.072 & ~mmqreg & 0.050 & 0.173 & 0.032 \\
+~jkc & 0.008 & 0.297 & 0.088 & ~jkc & -0.001 & 0.191 & 0.036 \\
+q75 & & & & q75 & & & \\
+~mmqreg & -0.091 & 0.251 & 0.071 & ~mmqreg & -0.044 & 0.176 & 0.033 \\
+~jkc & 0.002 & 0.303 & 0.092 & ~jkc & 0.006 & 0.195 & 0.038 \\
+\textbf{N = 2000} & \textbf{Bias} & \textbf{Sim SE} & \textbf{MSE} &
+\textbf{N = 4000} & \textbf{Bias} & \textbf{Sim SE} & \textbf{MSE} \\
+q25 & & & & q25 & & & \\
+~mmqreg & 0.025 & 0.122 & 0.016 & ~mmqreg & 0.012 & 0.087 & 0.008 \\
+~jkc & 0.003 & 0.129 & 0.017 & ~jkc & 0.000 & 0.089 & 0.008 \\
+q75 & & & & q75 & & & \\
+~mmqreg & -0.023 & 0.124 & 0.016 & ~mmqreg & -0.011 & 0.087 & 0.008 \\
+~jkc & 0.001 & 0.131 & 0.017 & ~jkc & 0.000 & 0.089 & 0.008 \\
 \end{longtable}
-
-\end{minipage}%
-%
-\begin{minipage}[t]{0.50\linewidth}
-
-\begin{longtable}[]{@{}lccc@{}}
-\toprule\noalign{}
-N = 1000 & Bias & Sim SE & MSE \\
-\midrule\noalign{}
-\endhead
-\bottomrule\noalign{}
-\endlastfoot
-q25 & & & \\
-~mmqreg & 0.050 & 0.173 & 0.032 \\
-~jkc & -0.001 & 0.191 & 0.036 \\
-q75 & & & \\
-~mmqreg & -0.044 & 0.176 & 0.033 \\
-~jkc & 0.006 & 0.195 & 0.038 \\
-\end{longtable}
-
-\end{minipage}%
-\newline
-\begin{minipage}[t]{0.50\linewidth}
-
-\begin{longtable}[]{@{}lccc@{}}
-\toprule\noalign{}
-N = 1000 & Bias & Sim SE & MSE \\
-\midrule\noalign{}
-\endhead
-\bottomrule\noalign{}
-\endlastfoot
-q25 & & & \\
-~mmqreg & 0.025 & 0.122 & 0.016 \\
-~jkc & 0.003 & 0.129 & 0.017 \\
-q75 & & & \\
-~mmqreg & -0.023 & 0.124 & 0.016 \\
-~jkc & 0.001 & 0.131 & 0.017 \\
-\end{longtable}
-
-\end{minipage}%
-%
-\begin{minipage}[t]{0.50\linewidth}
-
-\begin{longtable}[]{@{}lccc@{}}
-\toprule\noalign{}
-N = 2000 & Bias & Sim SE & MSE \\
-\midrule\noalign{}
-\endhead
-\bottomrule\noalign{}
-\endlastfoot
-q25 & & & \\
-~mmqreg & 0.012 & 0.087 & 0.008 \\
-~jkc & 0.000 & 0.089 & 0.008 \\
-q75 & & & \\
-~mmqreg & -0.011 & 0.087 & 0.008 \\
-~jkc & 0.000 & 0.089 & 0.008 \\
-\end{longtable}
-
-\end{minipage}%
-
-\end{table}%
 
@@
 
-\begin{longtable}[]{@{}
-  >{\raggedright\arraybackslash}p{(\columnwidth - 8\tabcolsep) * \real{0.2000}}
-  >{\centering\arraybackslash}p{(\columnwidth - 8\tabcolsep) * \real{0.2000}}
-  >{\centering\arraybackslash}p{(\columnwidth - 8\tabcolsep) * \real{0.2000}}
-  >{\centering\arraybackslash}p{(\columnwidth - 8\tabcolsep) * \real{0.2000}}
-  >{\centering\arraybackslash}p{(\columnwidth - 8\tabcolsep) * \real{0.2000}}@{}}
+\begin{longtable}[]{@{}lcccc@{}}
 \caption{Heteroskedasticity misspecification and clustered
@@
 \toprule\noalign{}
-\begin{minipage}[b]{\linewidth}\raggedright
-\end{minipage} & \begin{minipage}[b]{\linewidth}\centering
-Het:q25
-\end{minipage} & \begin{minipage}[b]{\linewidth}\centering
-Het:q75
-\end{minipage} & \begin{minipage}[b]{\linewidth}\centering
-Clust:q25
-\end{minipage} & \begin{minipage}[b]{\linewidth}\centering
-Clust:q75
-\end{minipage} \\
+& Het:q25 & Het:q75 & Clust:q25 & Clust:q75 \\
 \midrule\noalign{}
@@
 \begin{longtable}[]{@{}
-  >{\raggedright\arraybackslash}p{(\columnwidth - 18\tabcolsep) * \real{0.1099}}
-  >{\centering\arraybackslash}p{(\columnwidth - 18\tabcolsep) * \real{0.0989}}
-  >{\centering\arraybackslash}p{(\columnwidth - 18\tabcolsep) * \real{0.0989}}
-  >{\centering\arraybackslash}p{(\columnwidth - 18\tabcolsep) * \real{0.0989}}
-  >{\centering\arraybackslash}p{(\columnwidth - 18\tabcolsep) * \real{0.0989}}
-  >{\centering\arraybackslash}p{(\columnwidth - 18\tabcolsep) * \real{0.0989}}
-  >{\centering\arraybackslash}p{(\columnwidth - 18\tabcolsep) * \real{0.0989}}
-  >{\centering\arraybackslash}p{(\columnwidth - 18\tabcolsep) * \real{0.0989}}
-  >{\centering\arraybackslash}p{(\columnwidth - 18\tabcolsep) * \real{0.0989}}
-  >{\centering\arraybackslash}p{(\columnwidth - 18\tabcolsep) * \real{0.0989}}@{}}
+  >{\raggedright\arraybackslash}p{(\columnwidth - 18\tabcolsep) * \real{0.1235}}
+  >{\centering\arraybackslash}p{(\columnwidth - 18\tabcolsep) * \real{0.1111}}
+  >{\centering\arraybackslash}p{(\columnwidth - 18\tabcolsep) * \real{0.0988}}
+  >{\centering\arraybackslash}p{(\columnwidth - 18\tabcolsep) * \real{0.0864}}
+  >{\centering\arraybackslash}p{(\columnwidth - 18\tabcolsep) * \real{0.0864}}
+  >{\centering\arraybackslash}p{(\columnwidth - 18\tabcolsep) * \real{0.0988}}
+  >{\centering\arraybackslash}p{(\columnwidth - 18\tabcolsep) * \real{0.0988}}
+  >{\centering\arraybackslash}p{(\columnwidth - 18\tabcolsep) * \real{0.0988}}
+  >{\centering\arraybackslash}p{(\columnwidth - 18\tabcolsep) * \real{0.0988}}
+  >{\centering\arraybackslash}p{(\columnwidth - 18\tabcolsep) * \real{0.0988}}@{}}
 \caption{The determinants of government surpluses: Individual Fixed
@@
 \begin{longtable}[]{@{}
-  >{\raggedright\arraybackslash}p{(\columnwidth - 14\tabcolsep) * \real{0.1370}}
-  >{\centering\arraybackslash}p{(\columnwidth - 14\tabcolsep) * \real{0.1233}}
-  >{\centering\arraybackslash}p{(\columnwidth - 14\tabcolsep) * \real{0.1233}}
-  >{\centering\arraybackslash}p{(\columnwidth - 14\tabcolsep) * \real{0.1233}}
-  >{\centering\arraybackslash}p{(\columnwidth - 14\tabcolsep) * \real{0.1233}}
-  >{\centering\arraybackslash}p{(\columnwidth - 14\tabcolsep) * \real{0.1233}}
-  >{\centering\arraybackslash}p{(\columnwidth - 14\tabcolsep) * \real{0.1233}}
-  >{\centering\arraybackslash}p{(\columnwidth - 14\tabcolsep) * \real{0.1233}}@{}}
+  >{\raggedright\arraybackslash}p{(\columnwidth - 14\tabcolsep) * \real{0.1493}}
+  >{\centering\arraybackslash}p{(\columnwidth - 14\tabcolsep) * \real{0.1194}}
+  >{\centering\arraybackslash}p{(\columnwidth - 14\tabcolsep) * \real{0.1194}}
+  >{\centering\arraybackslash}p{(\columnwidth - 14\tabcolsep) * \real{0.1045}}
+  >{\centering\arraybackslash}p{(\columnwidth - 14\tabcolsep) * \real{0.1493}}
+  >{\centering\arraybackslash}p{(\columnwidth - 14\tabcolsep) * \real{0.1194}}
+  >{\centering\arraybackslash}p{(\columnwidth - 14\tabcolsep) * \real{0.1194}}
+  >{\centering\arraybackslash}p{(\columnwidth - 14\tabcolsep) * \real{0.1194}}@{}}
 \caption{The determinants of government surpluses: Individual and Time
@@
 
-\[q(y|\tau,x) = x'(\beta + q(\varepsilon |\tau) \times \gamma)\]
-
-This model is identified under the following conditions:
+\[q(y|\tau,x) = x'(\beta + q(\tau) \times \gamma)\]
+
+where \(q(\tau)\) is the \(\tau_{th}\) quantile of the standardized
+residual of \(\varepsilon\). This model is identified under the
+following conditions:
 
@@
 \]
-
-For simplicity, for the rest of the appendix, I will use
-\(q^\varepsilon_\tau\) to represent \(q(\varepsilon |\tau)\).
 
@@
 \[\begin{aligned}
-h_{3,i} &= \mathbb{1}\left( q^\varepsilon_\tau x_i'\gamma +x_i'\beta - y_i \geq 0 \right) - \tau \text{ or}\\
-h_{3,i} &= \mathbb{1}\left( q^\varepsilon_\tau  \geq \frac{y_i- x_i'\beta}{x_i'\gamma}  \right) - \tau = \mathbb{1}\big( q^\varepsilon_\tau  \geq \varepsilon  \big) - \tau \\
+h_{3,i} &= \mathbb{1}\left(q(\tau) x_i'\gamma +x_i'\beta - y_i \geq 0 \right) - \tau \text{ or}\\
+h_{3,i} &= \mathbb{1}\left( q(\tau)  \geq \frac{y_i- x_i'\beta}{x_i'\gamma}  \right) - \tau = \mathbb{1}\big( q(\tau)  \geq \varepsilon  \big) - \tau \\
 \end{aligned}
@@
 
-\[h_{3,i} \approx I\left( q^\varepsilon_\tau x_i'\gamma +x_i'\beta - y_i  \right) - \tau\]
+\[h_{3,i} \approx I\left( q(\tau) x_i'\gamma +x_i'\beta - y_i  \right) - \tau\]
 
@@
 
-\[\bar G_{3,1} = -N^{-1} f_{\varepsilon}\big(q^\varepsilon_\tau\big) \sum  \frac{x_i'}{x_i'\gamma} 
+\[\bar G_{3,1} = -N^{-1} f_{\varepsilon}\big(q(\tau)\big) \sum  \frac{x_i'}{x_i'\gamma} 
 \]
@@
 
-\[\bar G_{3,1} = - f_{\varepsilon}\big(q^\varepsilon_\tau\big) \frac{\bar x_i'}{\bar x_i'\gamma} 
+\[\bar G_{3,1} = - f_{\varepsilon}\big(q(\tau)) \frac{\bar x_i'}{\bar x_i'\gamma} 
 \]
@@
 \[\begin{aligned}
-\bar G_{3,3} &= -\frac{1}{N} \sum \frac{\partial h_{3,i}}{\partial q^\varepsilon_\tau} \\
- &= -\frac{1}{N} \sum K_h(q^\varepsilon_\tau x_i'\gamma +x_i'\beta - y_i ) x_i'\gamma \\
- &= -\frac{1}{N} \sum f_{y|X}(q^\varepsilon_\tau x_i'\gamma +x_i'\beta) x_i'\gamma \\
- &= -\frac{1}{N} \sum f_{\varepsilon}(q^\varepsilon_\tau) \frac{x_i'\gamma}{ x_i'\gamma} \\
- &= - f_{\varepsilon}(q^\varepsilon_\tau) 
+\bar G_{3,3} &= -\frac{1}{N} \sum \frac{\partial h_{3,i}}{\partial q(\tau)} \\
+ &= -\frac{1}{N} \sum K_h(q(\tau) x_i'\gamma +x_i'\beta - y_i ) x_i'\gamma \\
+ &= -\frac{1}{N} \sum f_{y|X}(q(\tau) x_i'\gamma +x_i'\beta) x_i'\gamma \\
+ &= -\frac{1}{N} \sum f_{\varepsilon}(q(\tau)) \frac{x_i'\gamma}{ x_i'\gamma} \\
+ &= - f_{\varepsilon}(q(\tau)) 
 \end{aligned}
@@
 \[\begin{aligned}
-\lambda_i(q^\varepsilon_\tau)&=\bar G_{3,3}^{-1}
+\lambda_i(q(\tau))&=\bar G_{3,3}^{-1}
 \Big(
@@
 \item
-  \texttt{mmqreg} in Stata: `net install mmqre,
+  \texttt{mmqreg} in Stata: `net install mmqreg,
   from(https://friosavila.github.io/stpackages)
 \item
-  \texttt{mmqreg} in R: Programs Available in Github
+  \texttt{mmqreg} in R: Program Available in mmqreg repository in GitHub
+  (https://github.com/friosavila/mmqreg)
 \item

### 2023-11-08 article/article.qmd
s
s

@@
 ---
-title: Quantile Regressions via Method of Moments with multiple fixed effects
+title: Quantile Regressions via Method of Moments with multiple fixed effects \tnoteref{t1}
 author:
@@
           name: World Bank                 
-    note: |
-      The opinions expressed in this paper are those of the authors and do not necessarily reflect the views of the World Bank, its Board of Directors, or the countries it represents         
 abstract: |
@@
       number-depth: 2
+include-in-header: 
+      text: |
+        \tnotetext[t1]{The opinions expressed in this paper are those of the authors and do not necessarily reflect the views of the World Bank, its Board of Directors, or the countries it represents.}
 ---

### 2023-11-08 extra/extra.qmd
s
s

---
title: Short Paper \tnoteref{t1,t2}
subtitle: A Short Subtitle
author:
  - name: Alice Anonymous
    email: alice@example.com
    affiliations: 
        - id: some-tech
          name: Some Institute of Technology
          department: Department Name
    attributes:
        corresponding: true
    note: This is the first author footnote.
  - name: Bob Security
    email: bob@example.com
    affiliations:
        - id: another-u
          name: Another University
          department: Department Name
          address: Street Address
          city: City
          state: State
          postal-code: Postal Code
    note: |
      Another author footnote, this is a very long footnote and it should be a really long footnote. But this footnote is not yet sufficiently long enough to make two lines of footnote text.
  - name: Cat Memes
    email: cat@example.com
    affiliations:
        - ref: another-u
    note: Yet another author footnote.
  - name: Derek Zoolander
    email: derek@example.com
    affilations:
        - ref: some-tech
abstract: |
  This is the abstract. Lorem ipsum dolor sit amet, consectetur adipiscing elit. Vestibulum augue turpis, dictum non malesuada a, volutpat eget velit. Nam placerat turpis purus, eu tristique ex tincidunt et. Mauris sed augue eget turpis ultrices tincidunt. Sed et mi in leo porta egestas. Aliquam non laoreet velit. Nunc quis ex vitae eros aliquet auctor nec ac libero. Duis laoreet sapien eu mi luctus, in bibendum leo molestie. Sed hendrerit diam diam, ac dapibus nisl volutpat vitae. Aliquam bibendum varius libero, eu efficitur justo rutrum at. Sed at tempus elit.
keywords: 
  - keyword1
  - keyword2
thanks: To my firends and family.
date: last-modified
bibliography: bibliography.bib
format:
  elsevier-pdf:
    keep-tex: true
    journal:
      name: Journal Name
      formatting: preprint
      model: 3p
      cite-style: super
include-in-header: 
      text: |
        \tnotetext[t1]{This document is a collaborative effort.}
        \tnotetext[t2]{The second title footnote which is a longer longer than the first one and with an intention to fill in up more than one line while formatting.}
---

Please make sure that your manuscript follows the guidelines in the 
Guide for Authors of the relevant journal. It is not necessary to 
typeset your manuscript in exactly the same way as an article, 
unless you are submitting to a camera-ready copy (CRC) journal.

For detailed instructions regarding the elsevier article class, see   <https://www.elsevier.com/authors/policies-and-guidelines/latex-instructions>

# Bibliography styles

Here are two sample references:  @Feynman1963118 @Dirac1953888.

By default, natbib will be used with the `authoryear` style, set in `classoption` variable in YAML. 
You can sets extra options with `natbiboptions` variable in YAML header. Example

```
natbiboptions: longnamesfirst,angle,semicolon
```

There are various more specific bibliography styles available at
<https://support.stmdocs.in/wiki/index.php?title=Model-wise_bibliographic_style_files>. 
To use one of these, add it in the header using, for example, `biblio-style: model1-num-names`.

## Using CSL

If `cite-method` is set to `citeproc` in `elsevier_article()`, then pandoc is used for citations instead of `natbib`. In this case, the `csl` option is used to format the references. By default, this template will provide an appropriate style, but alternative `csl` files are available from <https://www.zotero.org/styles?q=elsevier>. These can be downloaded
and stored locally, or the url can be used as in the example header.

# Equations

Here is an equation:
$$ 
  f_{X}(x) = \left(\frac{\alpha}{\beta}\right)
  \left(\frac{x}{\beta}\right)^{\alpha-1}
  e^{-\left(\frac{x}{\beta}\right)^{\alpha}}; 
  \alpha,\beta,x > 0 .
$$

Inline equations work as well: $\sum_{i = 2}^\infty\{\alpha_i^\beta\}$

# Figures and tables

@fig-meaningless is generated using an R chunk.

```{r}
#| label: fig-meaningless
#| fig-cap: A meaningless scatterplot
#| fig-width: 5
#| fig-height: 5
#| fig-align: center
#| out-width: 50%
#| echo: false
plot(runif(25), runif(25))
```

# Tables coming from R

Tables can also be generated using R chunks, as shown in @tbl-simple example.

```{r}
#| label: tbl-simple
#| tbl-cap: Caption centered above table
#| echo: true
knitr::kable(head(mtcars)[,1:4])
```

# References {-}

### 2023-11-08 extra/extra.tex
s
s

% Options for packages loaded elsewhere
\PassOptionsToPackage{unicode}{hyperref}
\PassOptionsToPackage{hyphens}{url}
\PassOptionsToPackage{dvipsnames,svgnames,x11names}{xcolor}
%
\documentclass[
  super,
  preprint,
  3p]{elsarticle}

\usepackage{amsmath,amssymb}
\usepackage{iftex}
\ifPDFTeX
  \usepackage[T1]{fontenc}
  \usepackage[utf8]{inputenc}
  \usepackage{textcomp} % provide euro and other symbols
\else % if luatex or xetex
  \usepackage{unicode-math}
  \defaultfontfeatures{Scale=MatchLowercase}
  \defaultfontfeatures[\rmfamily]{Ligatures=TeX,Scale=1}
\fi
\usepackage{lmodern}
\ifPDFTeX\else  
    % xetex/luatex font selection
\fi
% Use upquote if available, for straight quotes in verbatim environments
\IfFileExists{upquote.sty}{\usepackage{upquote}}{}
\IfFileExists{microtype.sty}{% use microtype if available
  \usepackage[]{microtype}
  \UseMicrotypeSet[protrusion]{basicmath} % disable protrusion for tt fonts
}{}
\makeatletter
\@ifundefined{KOMAClassName}{% if non-KOMA class
  \IfFileExists{parskip.sty}{%
    \usepackage{parskip}
  }{% else
    \setlength{\parindent}{0pt}
    \setlength{\parskip}{6pt plus 2pt minus 1pt}}
}{% if KOMA class
  \KOMAoptions{parskip=half}}
\makeatother
\usepackage{xcolor}
\setlength{\emergencystretch}{3em} % prevent overfull lines
\setcounter{secnumdepth}{5}
% Make \paragraph and \subparagraph free-standing
\ifx\paragraph\undefined\else
  \let\oldparagraph\paragraph
  \renewcommand{\paragraph}[1]{\oldparagraph{#1}\mbox{}}
\fi
\ifx\subparagraph\undefined\else
  \let\oldsubparagraph\subparagraph
  \renewcommand{\subparagraph}[1]{\oldsubparagraph{#1}\mbox{}}
\fi

\usepackage{color}
\usepackage{fancyvrb}
\newcommand{\VerbBar}{|}
\newcommand{\VERB}{\Verb[commandchars=\\\{\}]}
\DefineVerbatimEnvironment{Highlighting}{Verbatim}{commandchars=\\\{\}}
% Add ',fontsize=\small' for more characters per line
\usepackage{framed}
\definecolor{shadecolor}{RGB}{241,243,245}
\newenvironment{Shaded}{\begin{snugshade}}{\end{snugshade}}
\newcommand{\AlertTok}[1]{\textcolor[rgb]{0.68,0.00,0.00}{#1}}
\newcommand{\AnnotationTok}[1]{\textcolor[rgb]{0.37,0.37,0.37}{#1}}
\newcommand{\AttributeTok}[1]{\textcolor[rgb]{0.40,0.45,0.13}{#1}}
\newcommand{\BaseNTok}[1]{\textcolor[rgb]{0.68,0.00,0.00}{#1}}
\newcommand{\BuiltInTok}[1]{\textcolor[rgb]{0.00,0.23,0.31}{#1}}
\newcommand{\CharTok}[1]{\textcolor[rgb]{0.13,0.47,0.30}{#1}}
\newcommand{\CommentTok}[1]{\textcolor[rgb]{0.37,0.37,0.37}{#1}}
\newcommand{\CommentVarTok}[1]{\textcolor[rgb]{0.37,0.37,0.37}{\textit{#1}}}
\newcommand{\ConstantTok}[1]{\textcolor[rgb]{0.56,0.35,0.01}{#1}}
\newcommand{\ControlFlowTok}[1]{\textcolor[rgb]{0.00,0.23,0.31}{#1}}
\newcommand{\DataTypeTok}[1]{\textcolor[rgb]{0.68,0.00,0.00}{#1}}
\newcommand{\DecValTok}[1]{\textcolor[rgb]{0.68,0.00,0.00}{#1}}
\newcommand{\DocumentationTok}[1]{\textcolor[rgb]{0.37,0.37,0.37}{\textit{#1}}}
\newcommand{\ErrorTok}[1]{\textcolor[rgb]{0.68,0.00,0.00}{#1}}
\newcommand{\ExtensionTok}[1]{\textcolor[rgb]{0.00,0.23,0.31}{#1}}
\newcommand{\FloatTok}[1]{\textcolor[rgb]{0.68,0.00,0.00}{#1}}
\newcommand{\FunctionTok}[1]{\textcolor[rgb]{0.28,0.35,0.67}{#1}}
\newcommand{\ImportTok}[1]{\textcolor[rgb]{0.00,0.46,0.62}{#1}}
\newcommand{\InformationTok}[1]{\textcolor[rgb]{0.37,0.37,0.37}{#1}}
\newcommand{\KeywordTok}[1]{\textcolor[rgb]{0.00,0.23,0.31}{#1}}
\newcommand{\NormalTok}[1]{\textcolor[rgb]{0.00,0.23,0.31}{#1}}
\newcommand{\OperatorTok}[1]{\textcolor[rgb]{0.37,0.37,0.37}{#1}}
\newcommand{\OtherTok}[1]{\textcolor[rgb]{0.00,0.23,0.31}{#1}}
\newcommand{\PreprocessorTok}[1]{\textcolor[rgb]{0.68,0.00,0.00}{#1}}
\newcommand{\RegionMarkerTok}[1]{\textcolor[rgb]{0.00,0.23,0.31}{#1}}
\newcommand{\SpecialCharTok}[1]{\textcolor[rgb]{0.37,0.37,0.37}{#1}}
\newcommand{\SpecialStringTok}[1]{\textcolor[rgb]{0.13,0.47,0.30}{#1}}
\newcommand{\StringTok}[1]{\textcolor[rgb]{0.13,0.47,0.30}{#1}}
\newcommand{\VariableTok}[1]{\textcolor[rgb]{0.07,0.07,0.07}{#1}}
\newcommand{\VerbatimStringTok}[1]{\textcolor[rgb]{0.13,0.47,0.30}{#1}}
\newcommand{\WarningTok}[1]{\textcolor[rgb]{0.37,0.37,0.37}{\textit{#1}}}

\providecommand{\tightlist}{%
  \setlength{\itemsep}{0pt}\setlength{\parskip}{0pt}}\usepackage{longtable,booktabs,array}
\usepackage{calc} % for calculating minipage widths
% Correct order of tables after \paragraph or \subparagraph
\usepackage{etoolbox}
\makeatletter
\patchcmd\longtable{\par}{\if@noskipsec\mbox{}\fi\par}{}{}
\makeatother
% Allow footnotes in longtable head/foot
\IfFileExists{footnotehyper.sty}{\usepackage{footnotehyper}}{\usepackage{footnote}}
\makesavenoteenv{longtable}
\usepackage{graphicx}
\makeatletter
\def\maxwidth{\ifdim\Gin@nat@width>\linewidth\linewidth\else\Gin@nat@width\fi}
\def\maxheight{\ifdim\Gin@nat@height>\textheight\textheight\else\Gin@nat@height\fi}
\makeatother
% Scale images if necessary, so that they will not overflow the page
% margins by default, and it is still possible to overwrite the defaults
% using explicit options in \includegraphics[width, height, ...]{}
\setkeys{Gin}{width=\maxwidth,height=\maxheight,keepaspectratio}
% Set default figure placement to htbp
\makeatletter
\def\fps@figure{htbp}
\makeatother

\tnotetext[t1]{This document is a collaborative effort.}
\tnotetext[t2]{The second title footnote which is a longer longer than the first one and with an intention to fill in up more than one line while formatting.}
\makeatletter
\@ifpackageloaded{caption}{}{\usepackage{caption}}
\AtBeginDocument{%
\ifdefined\contentsname
  \renewcommand*\contentsname{Table of contents}
\else
  \newcommand\contentsname{Table of contents}
\fi
\ifdefined\listfigurename
  \renewcommand*\listfigurename{List of Figures}
\else
  \newcommand\listfigurename{List of Figures}
\fi
\ifdefined\listtablename
  \renewcommand*\listtablename{List of Tables}
\else
  \newcommand\listtablename{List of Tables}
\fi
\ifdefined\figurename
  \renewcommand*\figurename{Figure}
\else
  \newcommand\figurename{Figure}
\fi
\ifdefined\tablename
  \renewcommand*\tablename{Table}
\else
  \newcommand\tablename{Table}
\fi
}
\@ifpackageloaded{float}{}{\usepackage{float}}
\floatstyle{ruled}
\@ifundefined{c@chapter}{\newfloat{codelisting}{h}{lop}}{\newfloat{codelisting}{h}{lop}[chapter]}
\floatname{codelisting}{Listing}
\newcommand*\listoflistings{\listof{codelisting}{List of Listings}}
\makeatother
\makeatletter
\makeatother
\makeatletter
\@ifpackageloaded{caption}{}{\usepackage{caption}}
\@ifpackageloaded{subcaption}{}{\usepackage{subcaption}}
\makeatother
\journal{Journal Name}
\ifLuaTeX
  \usepackage{selnolig}  % disable illegal ligatures
\fi
\usepackage[]{natbib}
\bibliographystyle{elsarticle-num}
\IfFileExists{bookmark.sty}{\usepackage{bookmark}}{\usepackage{hyperref}}
\IfFileExists{xurl.sty}{\usepackage{xurl}}{} % add URL line breaks if available
\urlstyle{same} % disable monospaced font for URLs
\hypersetup{
  pdftitle={Short Paper },
  pdfauthor={Alice Anonymous; Bob Security; Cat Memes; Derek Zoolander},
  pdfkeywords={keyword1, keyword2},
  colorlinks=true,
  linkcolor={blue},
  filecolor={Maroon},
  citecolor={Blue},
  urlcolor={Blue},
  pdfcreator={LaTeX via pandoc}}

\setlength{\parindent}{6pt}
\begin{document}

\begin{frontmatter}
\title{Short Paper \tnoteref{t1,t2} \\\large{A Short Subtitle} }
\author[1]{Alice Anonymous%
\corref{cor1}%
\fnref{fn1}}
 \ead{alice@example.com} 
\author[2]{Bob Security%
%
\fnref{fn2}}
 \ead{bob@example.com} 
\author[2]{Cat Memes%
%
\fnref{fn3}}
 \ead{cat@example.com} 
\author[]{Derek Zoolander%
%
}
 \ead{derek@example.com}

\affiliation[1]{organization={Some Institute of Technology, Department
Name},,postcodesep={}}
\affiliation[2]{organization={Another University, Department
Name},addressline={Street Address},city={City},postcode={Postal
Code},postcodesep={}}

\cortext[cor1]{Corresponding author}
\fntext[fn1]{This is the first author footnote.}
\fntext[fn2]{Another author footnote, this is a very long footnote and
it should be a really long footnote. But this footnote is not yet
sufficiently long enough to make two lines of footnote text.}
\fntext[fn3]{Yet another author footnote.}

\begin{abstract}
This is the abstract. Lorem ipsum dolor sit amet, consectetur adipiscing
elit. Vestibulum augue turpis, dictum non malesuada a, volutpat eget
velit. Nam placerat turpis purus, eu tristique ex tincidunt et. Mauris
sed augue eget turpis ultrices tincidunt. Sed et mi in leo porta
egestas. Aliquam non laoreet velit. Nunc quis ex vitae eros aliquet
auctor nec ac libero. Duis laoreet sapien eu mi luctus, in bibendum leo
molestie. Sed hendrerit diam diam, ac dapibus nisl volutpat vitae.
Aliquam bibendum varius libero, eu efficitur justo rutrum at. Sed at
tempus elit.
\end{abstract}

\begin{keyword}
    keyword1 \sep 
    keyword2
\end{keyword}
\end{frontmatter}
    Please make sure that your manuscript follows the guidelines in the
Guide for Authors of the relevant journal. It is not necessary to
typeset your manuscript in exactly the same way as an article, unless
you are submitting to a camera-ready copy (CRC) journal.

For detailed instructions regarding the elsevier article class, see
\url{https://www.elsevier.com/authors/policies-and-guidelines/latex-instructions}

\section{Bibliography styles}\label{bibliography-styles}

Here are two sample references: \citet{Feynman1963118}
\citet{Dirac1953888}.

By default, natbib will be used with the \texttt{authoryear} style, set
in \texttt{classoption} variable in YAML. You can sets extra options
with \texttt{natbiboptions} variable in YAML header. Example

\begin{verbatim}
natbiboptions: longnamesfirst,angle,semicolon
\end{verbatim}

There are various more specific bibliography styles available at
\url{https://support.stmdocs.in/wiki/index.php?title=Model-wise_bibliographic_style_files}.
To use one of these, add it in the header using, for example,
\texttt{biblio-style:\ model1-num-names}.

\subsection{Using CSL}\label{using-csl}

If \texttt{cite-method} is set to \texttt{citeproc} in
\texttt{elsevier\_article()}, then pandoc is used for citations instead
of \texttt{natbib}. In this case, the \texttt{csl} option is used to
format the references. By default, this template will provide an
appropriate style, but alternative \texttt{csl} files are available from
\url{https://www.zotero.org/styles?q=elsevier}. These can be downloaded
and stored locally, or the url can be used as in the example header.

\section{Equations}\label{equations}

Here is an equation: \[ 
  f_{X}(x) = \left(\frac{\alpha}{\beta}\right)
  \left(\frac{x}{\beta}\right)^{\alpha-1}
  e^{-\left(\frac{x}{\beta}\right)^{\alpha}}; 
  \alpha,\beta,x > 0 .
\]

Inline equations work as well: \(\sum_{i = 2}^\infty\{\alpha_i^\beta\}\)

\section{Figures and tables}\label{figures-and-tables}

Figure~\ref{fig-meaningless} is generated using an R chunk.

\begin{figure}

\centering{

\includegraphics[width=0.5\textwidth,height=\textheight]{extra_files/figure-pdf/fig-meaningless-1.pdf}

}

\caption{\label{fig-meaningless}A meaningless scatterplot}

\end{figure}%

\section{Tables coming from R}\label{tables-coming-from-r}

Tables can also be generated using R chunks, as shown in
Table~\ref{tbl-simple} example.

\begin{Shaded}
\begin{Highlighting}[]
\NormalTok{knitr}\SpecialCharTok{::}\FunctionTok{kable}\NormalTok{(}\FunctionTok{head}\NormalTok{(mtcars)[,}\DecValTok{1}\SpecialCharTok{:}\DecValTok{4}\NormalTok{])}
\end{Highlighting}
\end{Shaded}

\begin{table}

\caption{\label{tbl-simple}Caption centered above table}

\centering{

\begin{longtable}[]{@{}lrrrr@{}}
\toprule\noalign{}
& mpg & cyl & disp & hp \\
\midrule\noalign{}
\endhead
\bottomrule\noalign{}
\endlastfoot
Mazda RX4 & 21.0 & 6 & 160 & 110 \\
Mazda RX4 Wag & 21.0 & 6 & 160 & 110 \\
Datsun 710 & 22.8 & 4 & 108 & 93 \\
Hornet 4 Drive & 21.4 & 6 & 258 & 110 \\
Hornet Sportabout & 18.7 & 8 & 360 & 175 \\
Valiant & 18.1 & 6 & 225 & 105 \\
\end{longtable}

\addtocounter{table}{-1}

}

\end{table}%

\renewcommand\refname{References}
  \bibliography{bibliography.bib}

\end{document}

### 2023-11-10 article/article.tex

--- 2023-11-01 article/article.tex
@@
 \begin{frontmatter}
-\title{Quantile Regressions via Method of Moments with multiple fixed
-effects}
+\title{Estimating Quantile Regressions with Multiple Fixed Effects through Method of Moments}
+\fnref{fn1}
+
 \author[1]{Fernando Rios-Avila%
@@
  \ead{friosavi@levy.org}
+
 \author[2]{Leonardo Siles%
@@
 %
-\fnref{fn1}}
+}
  \ead{gcanavire@worldbank.org}
@@
 authors and do not necessarily reflect the views of the World Bank, its
-Board of Directors, or the countries it represents}
+Board of Directors, or the countries it represents.}
 
@@
 This paper proposes a new method to estimate quantile regressions with
-multiple fixed effects. The method expands on the strategy proposed by
-\citet{mss2019}, allowing for multiple fixed effects, and providing
-various alternatives for the estimation of Standard errors. We provide
+multiple fixed effects. The method, which expands on the strategy proposed by
+\citet{mss2019}, allows for the inclusion of multiple fixed effects and provides
+various alternatives for the estimation of standard errors. We provide
 Monte Carlo simulations to show the finite sample properties of the
@@
 we apply the proposed method to estimate the determinants of the surplus
-of government as a share of GDP allowing for both time and country fixed
+of government as a share of GDP, allowing for both time and country fixed
 effects.
@@
 \begin{keyword}
-    Fixed effects \sep Linear heteroskedasticity \sep Location-scale
-model \sep 
-    Quantile regression
+    Fixed Effects \sep Linear Heteroskedasticity \sep Location-Scale Model \sep Quantile Regression
 \end{keyword}
+
 \end{frontmatter}
@@
 estimation strategy used for modeling the relationships between
-explanatory variables X and the conditional quantiles of the dependent
+explanatory variables \(X\) and the conditional quantiles of the dependent
 variable \(q_\tau (y|x)\). Using QR one can obtain richer
 characterizations of the relationships between dependent and independent
-variables, by accounting for otherwise unobserved heterogeneity.
+variables by accounting for otherwise unobserved heterogeneity.
 
@@
 effects in the framework of panel data. However, as described in
-\citet{neymanscott1948}, and \citet{lancaster2000}, when individual
-fixed effects are included in quantile regression analysis it generates
-an incidental parameter problem. While many strategies have been
+\citet{neymanscott1948} and \citet{lancaster2000}, when individual
+fixed effects are included in quantile regression analysis an incidental parameter problem is generated. While many strategies have been
 proposed for estimating this type of model (see
 \citet{galvao2017quantile} for a brief review), neither has become
-standard because of their restrictive assumptions in regards to the
-individual effects, the computational complexity, and implementation.
+standard because of their restrictive assumptions in regard to the inclusion of 
+individual and multiple fixed effects, the computational complexity, and implementation.
 
 More recently, \citet{mss2019} (MSS hereafter) proposed a methodology
-based on a conditional location-scale model similar to the one described
+based on a conditional location-scale model, similar to the one described
 in \citet{he1997} and \citet{zhao2000}, for the estimation of quantile
 regressions models for panel data via a method of moments. This method
-allows individual fixed effects allowing to have heterogeneous effects
-on the entire conditional distribution of the outcome, rather
-constraining their effect to be a location shift only as in
+allows individual fixed effects to have heterogeneous effects
+on the entire conditional distribution of the outcome, rather than
+constraining their effect to be a location shift only, as in
 \citet{canay2011}, \citet{koenker2004}, and \citet{lancaster2000}.
 
-In principle, under the assumption that data generating process behind
+In principle, under the assumption that the data-generating process behind
 the data is based on a multiplicative heteroskedastic process that is
 linear in parameters \citep[\citet{mss2019}, \citet{he1997},
-\citet{zhao2000}]{cameron2005}, the effect of a variable \(X\) on the
+\citet{zhao2000}, \citet{cameron2005}], the effect of a variable \(X\) on the
 \(q_{th}\) quantile can be derived as the combination of a location
-effect, and scale effect moderated by the quantile of an underlying
-i.i.d. error. For statistical inference, MSS derives the asymptotic
-distribution of the estimator, suggesting the use of bootstrap standard
-errors, as well.
-
-While this methodology is not meant to substitute the use of standard
-quantile regression analysis, given the assumptions required for the
+effect and a scale effect moderated by the quantile of an underlying
+independent and identically distributed (i.i.d.) error. For statistical inference, MSS derives the asymptotic distribution of the estimator, suggesting the use of bootstrap standard errors as well.
+
+This methodology is not meant to substitute for the use of standard
+quantile regression analysis. That said, given the assumptions required for the
 identification of the model, it provides a simple and fast alternative
@@
 In this framework, our paper expands on \citet{mss2019}, following some
-of the suggestions by the authors regarding further research. First,
-making use of the properties of GMM estimators, we derive various
+of the suggestions by these authors regarding further research. First,
+making use of the properties of generalized method of moments (GMM) estimators, we derive various
 alternatives for the estimation of standard errors based on the
-empirical Influence functions of the estimators. Second, we reconsider
-the application of Frisch--Waugh--Lovell (FWL) theorem
+empirical influence functions of the estimators. Second, we reconsider
+the application of Frisch-Waugh-Lovell (FWL) theorem
 (\citet{frishwaugh1933} and \citet{lovell1963}) to extend the MSS
-estimator to allow for the inclusion of multiple fixed effects, for
-example, individual and year fixed effects.
-
-The rest of the paper is restructured as follows. Section 2 presents the
-basic setup of the location-Scale model described in \citet{he1997} and
+estimator to allow for the inclusion of multiple fixed effects, such as individual and year fixed effects.
+
+The rest of the paper is structured as follows: section 2 presents the
+basic setup of the location-scale model described in \citet{he1997} and
 \citet{zhao2000}, tying the relationship between the standard quantile
-regression model, and the location and scale model. It also revisits MSS
-methodology, proposing alternative estimators for the standard errors
+regression model and the location-scale model. It also revisits the
+methodology of MSS, proposing alternative estimators for the standard errors
 based on the properties of GMM estimators and the empirical influence
-functions. It also shows that FWL theorem can be used to control for
+functions. It also shows that the FWL theorem can be used to control for
 multiple fixed effects. Section 3 presents the results of a small
-simulation study and Section 4 illustrates the application of the
-proposed methods with two empirical examples. Seccion 5 concludes.
+simulation study and section 4 illustrates the application of the
+proposed methods with two empirical examples. Section 5 concludes.
 
@@
 \hypertarget{sec-betas}{%
-\subsection{Quantile Regression: Location-Scale model}\label{sec-betas}}
+\subsection{Quantile Regression: Location-Scale Model}\label{sec-betas}}
 
 Quantile regressions are used to identify relationships between the
-explanatory variables \(x\) and the conditional quantiles of the
-dependent variable \(Q(y|\tau,X)\). This relationship is commonly
+explanatory variables \(X\) and the conditional quantiles of the
+dependent variable \(Q(Y|\tau,X)\). This relationship is commonly
 assumed to follow a linear functional form:
@@
 \begin{equation}\protect\hypertarget{eq-eq1}{}{q(Y|X,\tau) =X\beta(\tau)
-}\label{eq-eq1}\end{equation}
+}\label{eq-eq1}\end{equation}.
 
@@
 all values of \(\tau\). This formulation can also be related to a random
-coefficient model, where all coefficients are assumed to be some
-nonlinear function of \(\tau\), where \(\tau\) follows a random uniform
+coefficient model, in which all coefficients are assumed to be some
+nonlinear function of \(\tau\) where \(\tau\) follows a random uniform
 distribution.
@@
 models: the location model, which describes the central tendency of the
-conditional distribution, and the scale model, which describes
+conditional distribution; and the scale model, which describes
 deviations from the central tendency:
@@
 \begin{equation}\protect\hypertarget{eq-eq2}{}{q(Y|X,\tau) =X\beta+X\gamma(\tau)
-}\label{eq-eq2}\end{equation}
+}\label{eq-eq2}\end{equation}.
 
 Here, the location parameters \(\beta\) are typically identified using a
-linear regression model (as in \citet{mss2019}), or a median regression
-(as in \citet{melly2005}), and the scale parameters \(\gamma(\tau)\) can
+linear regression model (as in \citet{mss2019}) or a median regression
+(as in \citet{melly2005}) and the scale parameters \(\gamma(\tau)\) can
 be estimated using standard approaches.
@@
 \left( \sum_{i\in y_i\geq x_i'\beta} \tau (y_i - x_i'\beta) - \sum_{i\in y_i<x_i'\beta} (1-\tau)(y_i - x_i'\beta) \right)
-}\label{eq-eq3}\end{equation}
+}\label{eq-eq3}\end{equation}.
 
 One characteristic of this estimator is that the \(\beta(\tau)\)
-coefficients are identified locally, and thus the estimated quantile
+coefficients are identified locally and thus the estimated quantile
 coefficients will exhibit considerable variation when analyzed across
@@
   local weighted approach \citep{kaplan2017}, as well as identifying the
-  full set of quantile coefficients simultaneously assuming some
+  full set of quantile coefficients while simultaneously assuming some
   parametric functional forms \citep{frumentobotai2016}.}
@@
 \end{aligned}
-}\label{eq-eq4}\end{equation}
-
-Under the assumption that \(\varepsilon\) is an independent and
-identically distributed (iid) unobserved random variable that is
+}\label{eq-eq4}\end{equation}.
+
+Under the assumption that \(\varepsilon\) is an i.i.d. unobserved random variable that is
 independent of \(X\), the conditional quantile of \(Y\) given \(X\) and
-\(\tau\) can be written as:
+\(\tau\) can be written as
 
 \begin{equation}\protect\hypertarget{eq-eq5}{}{q(Y|X,\tau) =X\beta+q(\varepsilon|\tau) \times X\gamma 
-}\label{eq-eq5}\end{equation}
+}\label{eq-eq5}\end{equation}.
 
 In this setup, the traditional quantile coefficients are identified as
-the location model coefficients, plus the scale model coefficients
+the location model coefficients plus the scale model coefficients
 moderated by the \(\tau_{th}\) unconditional quantile of the
@@
 \begin{equation}\protect\hypertarget{eq-eq6}{}{\beta(\tau) = \beta + q(\varepsilon|\tau) \times \gamma 
-}\label{eq-eq6}\end{equation}
+}\label{eq-eq6}\end{equation}.
 
@@
 two advantages over the standard quantile regression model. First,
-because the location and scale model can be identified globally, with
-only a single paramater (\(q(\varepsilon|\tau)\)) requiring local
-estimation, this estimation approach would be more efficient than the
+because the location -scale model can be identified globally, with
+only a single parameter (\(q(\varepsilon|\tau)\)) requiring local
+estimation, this estimation approach will be more efficient than the
 standard quantile regression model (\citet{zhao2000}). Second, under the
-assumption that \(X\gamma\) is strictly possitive, the model would
+assumption that \(X\gamma\) is strictly positive, the model will
 produce quantile coefficients that do not cross.
@@
 Following MSS, the quantile regression model defined by
-Equation~\ref{eq-eq5} can be estimated using a method of moments
-approach. And while its possible to identify all coefficients
+Equation~\ref{eq-eq5} can be estimated using a generalized method of moments
+approach. And while it is possible to identify all coefficients
 (\(\beta,\gamma, q(\varepsilon|\tau)\)) simultaneously, we describe and
-use the implementation approach advocated by MSS which identifies each
+use the implementation approach advocated by MSS, which identifies each
 set of coefficients separately.
@@
 First, the location model can be estimated using a standard linear
-regression model, where the dependent variable is the outcome \(Y\), and
+regression model where the dependent variable is the outcome \(Y\) and
 the independent variables are the explanatory variables \(X\) (including
 a constant) with an error \(u\), which is by definition heteroskedastic.
-In this case, the location model coefficients are identified under the
+In this case, the location-model coefficients are identified under the
 following condition:
@@
       \end{aligned}
-}\label{eq-eq7}\end{equation}
+}\label{eq-eq7}\end{equation}.
 
@@
 characteristics \(X\). For this we use the absolute value of the errors
-from the location model \(u\) as dependent variable, which would allow
+from the location model \(u\) as dependent variable, which allows
 us to estimate the conditional standard deviation (rather than
@@
   \end{aligned}
-}\label{eq-eq8}\end{equation}
+}\label{eq-eq8}\end{equation}.
 
@@
   \end{aligned}
-}\label{eq-eq9}\end{equation}
-
-Where one identifies the quantile of the error \(\varepsilon\) using
-standardized errors \(\frac{y_i-x_i'\beta}{x_i'\gamma}\), or by finding
+}\label{eq-eq9}\end{equation},
+
+where one identifies the quantile of the error \(\varepsilon\) using
+standardized errors \(\frac{y_i-x_i'\beta}{x_i'\gamma}\) or by finding
 the values that identify the overall quantile coefficients
-\(\beta(\tau)=\beta + \gamma q(\varepsilon|\tau)\). Afterwords, the
-conditional quantile coefficients is simply defined as the combination
+\(\beta(\tau)=\beta + \gamma q(\varepsilon|\tau)\). Afterwards, the
+conditional quantile coefficients are simply defined as the combination
 of the location and scale coefficients.
@@
 \hypertarget{sec-se}{%
-\subsection{Standard Errors: GLS, Robust, Clustered}\label{sec-se}}
+\subsection{Standard Errors: GLS, Robust, and Clustered}\label{sec-se}}
 
@@
 regression coefficients using the location-scale model with
-heteroskedstic linear errors can be estimated using a the following set
-of moments, which fits in the Generalized Method of Moments framework:
+heteroskedastic linear errors can be estimated using the following set
+of moments, which fits within the GMM framework:
 
@@
 Under the conditions described in \citet{newey_chapter_1994} (see
-section 7), \citet{cameron2005} (see chapter 6.3.9) or as shown in
-\citet{mss2019}, the location, scale and residual quantile coefficients
+section 7), \citet{cameron2005} (see chapter 6.3.9), or as shown in
+\citet{mss2019}, the location, scale, and residual quantile coefficients
 are asymptotically normal.\footnote{\citet{zhao2000} also shows that the
-  quantile coefficients for the location-scale model also follows a
+  quantile coefficients for the location-scale model follow a
   normal distribution, but uses the assumption that the location model
@@
 Call \(\theta=[ \beta' \ \ \gamma' \ \ q(\varepsilon|\tau)' ]'\) the set
-of coefficients that are identified by the modement conditions in
-Equation~\ref{eq-eq10}, a just identified model. And the function
-\(h_i\) is a vector function that stacks all the moments at the
-individual level described in Equation~\ref{eq-eq10}. Then
+of coefficients that are identified by the moment conditions in
+Equation~\ref{eq-eq10}, a just identified model, and the function
+\(h_i\) is a vector function that stacks all the moments described in Equation~\ref{eq-eq10} at the individual level. Then
 \(\hat\theta\) follows a normal distribution with mean \(\theta\) and
-variance-covariance matrix \(V(\theta)\) that is estimated as:
+variance-covariance matrix \(V(\theta)\) that is estimated as
 
@@
 \bar G(\hat\theta)^{-1} 
-\]
-
-Which is equivalent to the Eicker-White Heteroskedastic-Consistent
+\],
+
+which is equivalent to the Eicker-White heteroskedasticity-consistent
 estimator for least-squares estimators.
 
-Here, the inner product is the moment covariance matrix, and
+Here, the inner product is the moment covariance matrix and
 \(\bar{G}(\theta)\) is the Jacobian matrix of the moment equations
@@
 distribution with mean \(\beta(\tau) = \beta+q(\varepsilon|\tau)\gamma\)
-and variance-covariance matrix equal to:
+and variance-covariance matrix equal to
 
 \[\hat{V}(\beta(\tau)) = \Xi \hat{V}(\hat\theta) \Xi'
-\]
-
-where \(\Xi\) is a \(k \times (2k+1)\) matrix defined as:
+\],
+
+where \(\Xi\) is a \(k \times (2k+1)\) matrix defined as
 
 \begin{equation}\protect\hypertarget{eq-eqqtile}{}{\Xi = [ I(k), \hat q(\varepsilon|\tau) \times I(k), \hat \gamma ]
-}\label{eq-eqqtile}\end{equation}
+}\label{eq-eqqtile}\end{equation},
 
@@
 While it is possible to estimate the variance-covariance matrix using
-simultaneous model estimation, for a just identified model, it is more
-efficient to estimate each set of coefficients separately. Afterwards,
+simultaneous model estimation for a just identified model, it is more
+efficient to estimate each set of coefficients separately. Afterward,
 the variance-covariance matrix can be estimated using the empirical
 influence functions of the estimators (see \citet{jann_2020} for an
-overview of the application, and \citet{hampel2005} for an in-depth
+overview of the application and \citet{hampel2005} for an in-depth
 review).
@@
 \(\lambda_i(\theta)\), the variance-covariance matrix can be estimated
-as:
+as
 
 \begin{equation}\protect\hypertarget{eq-eqvcv}{}{\hat{V}(\theta) = \frac{1}{N^2} \sum_{i=1}^N \lambda_i(\theta) \lambda_i(\theta)'
-}\label{eq-eqvcv}\end{equation}
-
-where the influence functions are defined as:
-
-\[\lambda_i(\theta) = \bar G(\theta)^{-1} h_i(\theta)\]
-
-For the specific case of quantile regressions via momoments, the
-influence functions for the location, scale and quantile coefficients
-are:\footnote{The derivation of the influence functions can be found in
+}\label{eq-eqvcv}\end{equation},
+
+where the influence functions are defined as
+
+\[\lambda_i(\theta) = \bar G(\theta)^{-1} h_i(\theta)\].
+
+For the specific case of quantile regressions through moments, the
+influence functions for the location, scale, and quantile coefficients
+are\footnote{The derivation of the influence functions can be found in
   the appendix.}
@@
 \end{aligned}
-}\label{eq-ifs}\end{equation}
-
-The different types of Standard errors estimation, thus, depend on the
+}\label{eq-ifs}\end{equation}.
+
+The different types of standard errors estimation thus depend on the
 assumptions imposed for the estimation of \(V(\theta)\).
@@
 
-The first, and most natural standard error estimator is given by
+The first and most natural standard error estimator is given by
 equation Equation~\ref{eq-eqvcv}. This is equivalent to the Eicker-White
-Heteroskedastic-Consistent estimator for least-squares estimators.
+heteroskedasticity-consistent estimator for least-squares estimators.
 Considering the location-scale model, the variance-covariance matrix for
-the quantile coefficients can be estimated as:
+the quantile coefficients can be estimated as
 
@@
   \end{pmatrix}
-\]
-
-This estimator of Standard errors should be robust to arbitrary
+\].
+
+This estimator of standard errors should be robust to arbitrary
 heteroskedasticity. However, because the location-scale specification
 relies on the correct specification of the model heteroskedasticity,
-large differences in Standard errors compared to GLS-standard errors may
+large differences in standard errors compared to GLS-standard errors may
 be an indication of misspecification of the model.
@@
 individual level is important. If the unobserved error \(\varepsilon\)
-is correlated within clusters, GLS-Standard errors could be severily
+is correlated within clusters, generalized least squares (GLS) standard errors could be severely
 biased. The standard recommendation has been to report block-bootstrap
-standard errors, clustering at the individual level.
-
-Since we have access to the influence functions, it is straight forward
+standard errors, clustered at the individual level.
+
+Because we have access to the influence functions, it is straightforward
 to estimate one-way clustered standard errors.
 
-Call \(N_G\) to be the total number of clusteres g, where
+Let \(N_G\) be the total number of clusters $g$, where
 \(g=1\dots N_G\). The clustered variance covariance matrix is given
-by:\footnote{It should be noted that one could just as well apply the
+by\footnote{It should be noted that one could just as well apply the
   insights of \citet{cameron_robust_2011}, allowing for multiway
@@
   \end{pmatrix}
-\]
-
-Where \(S\lambda_i(\theta)\) is the sum of the influence functions over
+\],
+
+where \(S\lambda_i(\theta)\) is the sum of the influence functions over
 all observations within a given cluster \(g\).
@@
 The standard errors proposed by MSS can be understood as an application
-of generalized least squares (GLS), which will be valid as long as the
+of GLS, which will be valid as long as the
 model for heteroskedasticity is correctly specified.\footnote{As
-  discussed in most econometric textbooks, like \citet{cameron2005}, one
+  discussed in most econometric textbooks, for example \citet{cameron2005}, one
   approach to correct for heteroskedasticity, when the
-  heteroskedasticity functional form is known, or can be estimated, is
-  to use weighted least squares. While feasible, however, this approach
+  heteroskedasticity functional form is known or can be estimated, is
+  to use weighted least squares. While feasible, this approach
   would defeat the purpose of identifying quantile effects exploiting
-  the heteroskedasticity of the model.} To estimate the GLS-Standard
+  the heteroskedasticity of the model.} To estimate the GLS standard
 errors, we make use of the following property:
@@
 \end{aligned}
-\]
+\].
 
@@
 specified, we can apply the law of iterated expectations and rewrite the
-variance-covariance matrix as:
+variance-covariance matrix as
 
@@
 the heteroskedasticity the model uses to identify the quantile
-coefficients. We can apply the same principle to find the GLS-Standard
+coefficients. We can apply the same principle to find the GLS standard
 errors for the system of location-scale and quantile coefficients. To do
-this, define the following modified influence functions:
+this, we define the following modified influence functions:
 
@@
 \end{aligned}
-\]
-
-Then, the GLS-Standard errors for the location-scale and quantile
-coefficients can be estimated as:
+\].
+
+Then, the GLS standard errors for the location-scale and quantile
+coefficients can be estimated as
 
@@
   \end{pmatrix}
-\]
+\],
 
@@
 \end{aligned}
-\]
-
-This estimator of Standard errors is equivalent to the one derived by
-MSS by Theorem 3.
+\].
+
+This estimator of standard errors is equivalent to the one derived by
+MSS using Theorem 3.
 
@@
 Using the setup described in the previous section, \citet{mss2019}
-proposes an extension to the model proposed by \citet{he1997} that would
-allow for the estimation of quantile regression models with panel data,
-allowing for the inclusion of individual fixed effects. However, as the
+proposes an extension to the model proposed by \citet{he1997} that enables the estimation of quantile regression models with panel data while
+allowing for the inclusion of individual fixed effects. Moreover, as the
 authors suggest, the methodology can be generalized to allow for the
-inclusion of multiple fixed effects. This type of analysis may be useful
+inclusion of multiple fixed effects. This type of analysis can be useful
 when considering data such as employer-employee linked data
-\citep{abowed2006}, or teacher-student linked data
+\citep{abowed2006} or teacher-student linked data
 \citep{harrissass2011}. Or, in the most common case, allowing to control
@@
 
-Reconsider the original model, and assume there are sets of unobserved
+We return to the original model and now assume there are sets of unobserved
 heterogeneity that are assumed to be constant across observations, if
@@
 individual fixed effects and the time fixed effects. Without loss of
-generality, we can assume that the data generating process is as
+generality, we can assume that the data-generating process is as
 follows:
@@
   \end{aligned}
-\]
-
-where we assume \(x_{i}\) vary across groups \(g_1\) and \(g_2\), thus
-are not collinear, and that \(\delta's\) and \(\zeta's\) are the
+\],
+
+where we assume \(x_{i}\) vary across groups \(g_1\) and \(g_2\) (and thus
+are not collinear) and that \(\delta's\) and \(\zeta's\) are the
 location and scale effects associated with groups fixed
 effects.\footnote{We could just as well consider multiple sets of fixed
-  effects}
+  effects.}
 
 If the dimension of groups \(g_k\) is low, this model could be estimated
-using a dummy inclussion approach following Section~\ref{sec-betas}, and
-standard errors obtained as discussed in Section~\ref{sec-se}. However,
+using a dummy inclusion approach following section~\ref{sec-betas} and
+the standard errors obtained as discussed in section~\ref{sec-se}. However,
 if the dimensionality of \(g_k\) is high, the dummy inclusion approach
-may not be feasible. Instead, a more feasible approach is to apply the
-Frisch-Waugh-Lovell (FWL) theorem, and partial out the impact of the
-group fixed effects on the control variables \(x_{i}\), the outcome of
-interest \(y_{i}\), with a similar approach for the identification of
-\(\sigma(x)\). In the case of unbalanced setups, with multiple groups,
+may not be feasible. A more feasible approach is to apply the
+FWL theorem and partial out the impact of the
+group fixed effects on the control variables \(x_{i}\), and the outcome of
+interest \(y_{i}\), using a similar approach for the identification of
+\(\sigma(x)\). In the case of unbalanced setups with multiple groups,
 the estimation involves iterative processes for which various approaches
-have been suggested and implemented (see
-\citet{correia_feasible_nodate}, \citet{gaure2013}, \citet{rios2015},
-among others).
-
-When applying the partialing out approach, some modifications to the
-approach described in Section~\ref{sec-betas} are needed.
+have been suggested and implemented (see for example
+\citet{correia_feasible_nodate}, \citet{gaure2013}, \citet{rios2015}
+).
+
+When applying the partialing-out approach, some modifications to the
+approach described in section~\ref{sec-betas} are needed.
 
 First, for all dependent and independent variables in the model
-(\(w=y,x\)), we partial out the group fixed effects, and obtain the
+(\(w=y,x\)), we partial out the group fixed effects and obtain the
 centered-residualized variables:
@@
 \end{aligned}
-\]
-
-Afterwards, we estimate the location model using the
+\].
+
+Afterward, we estimate the location model using the
 centered-residualized variables:\footnote{Using centered-residualized
-  variables allow us to include a constant in the model specification,
+  variables allows us to include a constant in the model specification,
   which simplifies the derivation of the influence functions. However,
-  as with other fixed effects models, the constant is not identified,
+  as with other fixed effects models, the constant is not identified
   and thus should not be interpreted.}
@@
 \[y_{i}^{rc} = x_{i}^{rc'} \beta + \nu_{i}
-\]
-
-Since \(|\hat \nu_i|\) is the dependent variable for the scale model, we
-apply the partialling out and recentering to this expression
-(\(|\hat \nu_i|^{rc}\)), and use that to estimate the model:
-
-\[|\hat\nu_{i}|^{rc} = x_{i}^{rc'} \gamma + \omega_{i}\]
-
-Finally the standardized residuals \(\varepsilon_i\) can be obtained as
-follows
-
-\[\hat{\varepsilon}_{i} = \frac{\nu_{i}}{|\hat\nu_{i}|- \hat \omega_{i}}\]
+\].
+
+Because \(|\hat \nu_i|\) is the dependent variable for the scale model, we
+apply the partialing out and recentering to this expression
+(\(|\hat \nu_i|^{rc}\)), and use that to estimate the following model:
+
+\[|\hat\nu_{i}|^{rc} = x_{i}^{rc'} \gamma + \omega_{i}\].
+
+Finally, the standardized residuals \(\varepsilon_i\) can be obtained as
+follows:
+
+\[\hat{\varepsilon}_{i} = \frac{\nu_{i}}{|\hat\nu_{i}|- \hat \omega_{i}}\],
 
@@
 conditional standard deviation
-\(\sigma(x_i)=x_{i}' \gamma + \zeta_{g1} + \zeta_{g2}\)
+\(\sigma(x_i)=x_{i}' \gamma + \zeta_{g1} + \zeta_{g2}\).
 
 The \(\tau_{th}\) quantile of the error \(\varepsilon\) can be estimated
-as usual, and the variance-covariance matrices obtained in the same way
-as before (see Section~\ref{sec-se}), but using \(x_{i}^{rc}\) instead
+as usual and the variance-covariance matrices obtained in the same way
+as before (see section~\ref{sec-se}) by using \(x_{i}^{rc}\) instead
 of \(x_{i}\) when estimating the influence functions for all estimated
@@
 structure that is more general than the panel structure. For this
-excercise, we consider the following data generating process:
+exercise, we consider the following data-generating process:
 
 \[y_i = \alpha_{1i} + \alpha_{2i} + x_i + (1+x_i + \alpha_{1i} + \alpha_{2i} ) \varepsilon_i
-\]
-
-where \(\alpha_{1i}\sim \chi^2(1)\), \(\alpha_{2i} \sim \chi^2(1)\) and
-\(x_i = 0.5 * (\chi_i +0.5(\alpha_{1i}+\alpha_{2i}))\) with
+\],
+
+where \(\alpha_{1i}\sim \chi^2(1)\), \(\alpha_{2i} \sim \chi^2(1)\), and
+\(x_i = 0.5 * (\chi_i +0.5(\alpha_{1i}+\alpha_{2i}))\), with
 \(\chi_i \sim \chi^2(1)\). We only consider the case when the error term
-\(\varepsilon_i\) is assumed to be normally distributed with mean zero
+\(\varepsilon_i\) is assumed to be normally distributed with mean 0
 and standard deviation of 0.5. We assume that there are 50 mutually
 exclusive fixed effect groups for each set of fixed effects.
-Observations are assigned to each subgroup randomly, using a uniform
-distribution between 1 and 50. We consider a sample sizes of 500, 1000,
-2000 and 4000 observations, which implies an average of 10, 20, 40 and
+Observations are assigned to each subgroup randomly using a uniform
+distribution between 1 and 50. We consider sample sizes of 500, 1000,
+2000, and 4000 observations, which implies an average of 10, 20, 40, and
 80 observations per group. The model is estimated using the
-location-scale model with heteroskedastic linear errors, and we report
+location-scale model with heteroskedastic linear errors and we report
 the coefficients for the 25th and 75th quantiles. We run this excercise
-5000 times. \textbf{?@tbl-sim1} reports the bias, simulated standard
-error and mean squared error. We also report the results obtained using
+5000 times. ?@tbl-sim1 reports the bias, simulated standard
+error, and mean squared error. We also report the results obtained using
 an adaptation bias-corrected estimator based on the split-panel
 jackknife estimator proposed by \citet{dhaene2015}.\footnote{For the
-  implementation, we estimate the model using the full sample, then,
-  randomly assign each observation into one of two groups, and
-  re-estimate the quantile coefficients for each group. The
+  implementation, we first estimate the model using the full sample, then
+  randomly assign each observation into one of two groups, and finally
+  reestimate the quantile coefficients for each group. The
   bias-corrected estimator is then obtained as
@@
 
-Similar to the findings in MSS, we find that the estimator presents a
-bias when the sample is small (\(N=500\)), but this bias shrinks as the
-sample sizes increases. As MSS describes, the bias seems to be
+Similar to the findings in MSS, we find that while the estimator presents a
+bias when the sample is small (\(N=500\)), this bias shrinks as the
+sample size increases. As MSS describes, the bias seems to be
 proportional to the sample size, or more precisely to \(N/N_{g1}\) and
@@
 observations per group. Interestingly, the bias-corrected estimator
-presents an almost zero bias, even when the samples are small (about 10
-observations per sub-group). Also replicating the results of MSS,
-despite bias reduction obtained using the JKC estimator, the standard
-errors and mean squared error (MSE) are larger than without correction.
+presents an almost 0 bias, even when the samples are small (about 10
+observations per subgroup).
+Moreover, we find that despite the bias reduction obtained using the JKC estimator, the standard errors and mean squared error (MSE) are larger than without correction, which also replicates the results of MSS,
 
@@
 
-\caption{Bias, Simulated Standard error, and Mean Squared
-Error}\begin{minipage}[t]{0.50\linewidth}
+\caption{Bias, Simulated Standard Error, and MSE}\begin{minipage}[t]{0.50\linewidth}
 
@@
 
-As described in section Section~\ref{sec-se}, GLS-Standard errors may
+As described in section Section~\ref{sec-se}, GLS standard errors may
 not be appropriate if heteroskedasticity in the model is misspecified.
-This could happen if the heteroskedasticity is not linear in parameters,
-or if there is correlations within groups. To show the performance of
-the GLS-Standard errors, we consider two additional simulations. To see
+This could happen if the heteroskedasticity is not linear in parameters
+or if there are correlations within groups. To show the performance of
+the GLS standard errors, we consider two additional simulations. To see
 the impact of heteroskedasticity misspecification, we assume the DGP is
-given by:
+given by
 
 \[y_i = \alpha_{1i} + \alpha_{2i} + x_i + (1+x_i + \sqrt{x_i} +\alpha_{1i} + \alpha_{2i} ) \varepsilon_i
-\]
+\].
 
@@
 the case where the error \(\varepsilon\) is correlated within groups
-defined by the first fixed effect. Specifically:
-
-\[\varepsilon_i =0.5*(\sqrt{0.5} z_i + \sqrt{0.5} w_g)\]
+defined by the first fixed effect, specifically
+
+\[\varepsilon_i =0.5*(\sqrt{0.5} z_i + \sqrt{0.5} w_g)\],
 
@@
 
-For the simulation, we run the excercise 5000 times, using a sample of
-size \(N=2000\). The results from both simulations are reported in the
-Table~\ref{tbl-sim2}. We report the average coefficient, simulation
-based Standard errors, and the standard errors using GLS, robust and
+For the simulation, we run the exercise 5000 times, using a sample of
+size \(N=2000\). The results from both simulations are reported in 
+Table~\ref{tbl-sim2}. We report the average coefficient, simulation-based standard errors, and the standard errors using GLS, robust, and
 clustered estimations.
@@
 
-As expected, the GLS-standard errors are biased, and the bias is larger
+As expected, the GLS standard errors are biased and the bias is larger
 in the case of misspecified heteroskedasticity. In fact, with
-heteroskedastic misspecification, the average GLS-SE (.476) is almost
+heteroskedasticity misspecification, the average GLS-SE (0.476) is almost
 three times as large as the simulation-based standard error (0.154). In
@@
 \hypertarget{illustrative-application}{%
-\section{Illustrative application}\label{illustrative-application}}
-
-In this section we replicate one of the excercises from MSS, allowing
-for time and individual fixed effects, as well as for different standard
+\section{Illustrative Application}\label{illustrative-application}}
+
+In this section we replicate one of the exercises from MSS, allowing
+for time and individual fixed effects as well as for different standard
 errors estimations. We use data from \citet{persson_economic_2005}, to
-estimate the relationship between surplus of goverment as share of GDP,
+estimate the relationship between surplus of government as share of GDP
 and a measure of quality of democracy (POLITY); log of real income per
-capita (LYP); trade volume as share of GDP (TRADE), Share of population
-between 15-65 uears of age (P1564), the share of the population 65 years
-or older (P65); one-year lag of the dependent variable (LSP); oil prices
-in US dollars differntiating importer and exported countries (OILIM and
+capita (LYP); trade volume as share of GDP (TRADE); share of population
+between 15 and 65 years of age (P1564); the share of the population 65 years
+and older (P65); one-year lag of the dependent variable (LSP); oil prices
+in US dollars, differentiating between importer and exporter countries (OILIM and
 OILEX); and the output gap (YGAP). In addition to country fixed effects
-(as illustrated in MSS), we also show results allowing for time fixed
+(as illustrated in MSS), we show results allowing for time fixed
 effects. Table~\ref{tbl-tb1} and Table~\ref{tbl-tb2} provide the results
-for the model with and without time fixed effects, respectively. It show
-cases the location and scale coefficients, as well as the quantile
-coefficients for the 25th, 50th and 75th quantiles. We also report
-GLS-Standard errors, Robust standard errors (brackets) and clustered
+for the model with and without time fixed effects, respectively. The tables showcase the location and scale coefficients, as well as the quantile
+coefficients for the 25th, 50th, and 75th quantiles. We also report
+GLS standard errors, robust standard errors (brackets), and clustered
 standard errors at the country level.
@@
   >{\centering\arraybackslash}p{(\columnwidth - 18\tabcolsep) * \real{0.0989}}@{}}
-\caption{\label{tbl-tb1}The determinants of government surpluses:
-Individual Fixed effects}\tabularnewline
+\caption{\label{tbl-tb1}Determinants of Government Surpluses:
+Individual Fixed Effects}\tabularnewline
 \toprule\noalign{}
@@
 
-As expected, Table~\ref{tbl-tb1} shows that point estimates are
-identical to the ones reported in \citet{mss2019} (Table 6), including
+As expected, Table~\ref{tbl-tb1} shows that the point estimates are
+identical to those reported in \citet{mss2019} (Table 6), including
 analytical standard errors (GLS). With our estimator, however, we are
-able to also produce both robust and clustered standard errors for
-location and scale coefficients. Except for a few cases, robust and
-clustered standard errors are larger than GLS standard errors, which may
+also able to produce both robust and clustered standard errors for
+location and scale coefficients. Except for a few cases, the robust and
+clustered standard errors are larger than the GLS standard errors, which may
 be an indication of misspecification of the model. The GLS standard
-errors we report differ from the ones in MSS because they use panel
+errors we report differ from those in MSS, because they use panel
 standard errors, which are equivalent to our clustered standard errors,
@@
 differences in the reported GLS standard errors compared to the
-analytical standard errors reported MSS. Our clustered standard errors,
-however, are closer to the bootstrap based standard errors the authors
-report.\footnote{There are two possible reasons that may explain the
-  differences in the GLS standard errors. On the one hand, in our
-  derivation, the influence function of the standardized \(\tau_{th}\)
+analytical standard errors reported in MSS. Our clustered standard errors,
+however, are closer to the bootstrap-based standard errors the authors
+report.\footnote{The differences in the GLS standard errors may be due that in our
+  derivation the influence function of the standardized \(\tau_{th}\)
   quantile (see \#eq-infs) does not have the same leading term as the
-  one reported in MSS (see theorem 3, and the definition of \(W\)).}
+  one reported in MSS (see Theorem 3 and the definition of \(W\)).}
 
@@
 variable is excluded from the model specification. Accounting for time
-fixed effects does not change the general conclusions one could make
+fixed effects does not change the general conclusions that can be drawn,
 based on the results from Table~\ref{tbl-tb1}. The two largest
 differences are that the log of income per capita has a positive effect
-on Government Surpluses, but only for the 25th quantile, because of the
-largest impact on the Scale component. Similarly, we observe that the
-income gap now has an impact on Government surplus that is always
-negative, but increasing across quantiles. In both instances, the
+on Government surpluses, but only for the 25th quantile, because at this point the largest impact on the Scale component is felt. Similarly, we observe that the
+income gap has an impact on Government surpluses that is always
+negative and increasing across quantiles. In both instances, the
 effects are not statistically significant.
@@
   >{\centering\arraybackslash}p{(\columnwidth - 14\tabcolsep) * \real{0.1233}}@{}}
-\caption{\label{tbl-tb2}The determinants of government surpluses:
-Individual and Time Fixed effects}\tabularnewline
+\caption{\label{tbl-tb2}Determinants of Government Surpluses:
+Individual and Time Fixed Effects}\tabularnewline
 \toprule\noalign{}
@@
 In this paper, we have extended the methodology proposed by
-\citet{mss2019}, allowing for the estimation of quantile regression
-models with multiple sets of fixed effects, as well as alternative
-Standard Errors estimations. This methodology would allow researchers to
-implement more comprehensive analysis of datasets characterized by
+\citet{mss2019} in order to estimate quantile regression
+models with multiple sets of fixed effects as well as with alternative
+standard errors. This methodology will allow researchers to
+implement more-comprehensive analyses of data sets characterized by
 complex hierarchies and unobserved heterogeneity. This extension is
@@
 Using a small simulation study, we show that our extended approach is as
-effective in identifying the parameters of interest as \citet{mss2019}
-indicated, even in contexts with two sets of fixed effects. Notably, the
+effective in identifying the parameters of interest as that of \citet{mss2019}, even in contexts with two sets of fixed effects. Notably, the
 bias-corrected estimator based on the split-panel jackknife estimator
-exhibits promising results, mitigating biases when samples are small,
+exhibits promising results, mitigating biases when samples are small
 but increasing standard errors.
@@
 Furthermore, we have assessed the impact of misspecified
-heteroskedasticity and intra-cluster correlation on the performance of
+heteroskedasticity and intracluster correlation on the performance of
 standard error estimations. Our findings emphasize the importance of
@@
 inference. In particular, we find that GLS standard errors are biased
-when the model heteroskedasticity is misspecified, and that robust and
+when the model heteroskedasticity is misspecified and that robust and
 clustered standard errors perform better in these cases. This may also
-suggest a venue for future research, testing the validity of the
-location-scale model assumption.
+suggest a venue for future research, in which the validity of the location-scale model assumption is tested.
 
@@
 \hypertarget{derivation-of-the-influence-functions}{%
-\section{Derivation of the influence
-functions}\label{derivation-of-the-influence-functions}}
+\section{Derivation of the Influence
+Functions}\label{derivation-of-the-influence-functions}}
 
@@
 is linear in parameters, with an heteroskedastic error term that is also
-linear function of parameters:
+a linear function of parameters:
 
@@
 \end{aligned}
-\]
+\],
 
 where \(\varepsilon\) is an unobserved i.i.d. random variable that is
-independent of \(x\), and such that \(x\gamma\) is larger than zero for
+independent of \(x\) and such that \(x\gamma\) is larger than 0 for
 any \(x\).
@@
 In this case, the \(\tau_{th}\) conditional quantile model can be
-written as:
-
-\[q(y|\tau,x) = x'(\beta + q(\varepsilon |\tau) \times \gamma)\]
+written as
+
+\[q(y|\tau,x) = x'(\beta + q(\varepsilon |\tau) \times \gamma)\].
 
@@
 \end{aligned}
-\]
-
-For simplicity, for the rest of the appendix, I will use
+\].
+
+For simplicity, for the rest of the appendix we use
 \(q^\varepsilon_\tau\) to represent \(q(\varepsilon |\tau)\).
@@
 \hypertarget{estimation-of-the-variance-covariance-matrix}{%
-\subsection{Estimation of the variance-covariance
-matrix}\label{estimation-of-the-variance-covariance-matrix}}
-
-In this model, to estimate the variance-covariance matrix the set of
+\subsection{Estimation of the Variance-Covariance
+Matrix}\label{estimation-of-the-variance-covariance-matrix}}
+
+In this model, to estimate the variance-covariance matrix of the set of
 coefficients \(\theta'=[\beta' \ \gamma' \ q^\varepsilon_\tau]\), we
 need to obtain the influence functions of all coefficients, which are
-defined as:
+defined as
 
@@
 \end{bmatrix}
-\]
-
-where the Jacobian matrix \(\bar G(\theta)\) is defined as:
+\],
+
+where the Jacobian matrix \(\bar G(\theta)\) is defined as
 
@@
 \end{bmatrix}
-\]
+\],
 
@@
 \[\bar G_{j,k} = - \frac 1 N \sum_{i=1}^N \frac{\partial h_{j,i}}{\partial \theta_k'} \ \forall j,k \in 1,2,3
-\]
-
-\textbf{First Moment Condition: Location Model}
+\].
+
+First Moment Condition: Location Model
 
@@
 \bar G_{1,2} = \bar G_{1,3} = 0
-\]
-
-\textbf{Second Moment Condition: Scale model}
+\].
+
+Second Moment Condition: Scale Model
 
@@
 \(y_i-x_i'\beta\), is uncorrelated with \(x\), we can simplify the
-expression as:
+expression as
 
@@
 
-\textbf{Third Moment Condition: Quantile of Standardized Residual}
+Third Moment Condition: Quantile of Standardized Residual
 
@@
 \end{aligned}
-\]
+\].
 
 Because the indicator function \(\mathbb{1}()\) is not differentiable,
-we borrow from the non-parametric literature, and approximate the
+we borrow from the nonparametric literature and approximate the
 indicator function with the integral of a kernel density function
-\(I()\). This function \(I()\), is monotonic and symetrical function
-around zero, with a domain over the real numbers, and a range between 0
+\(I()\). This function, \(I()\), is a monotonic and symmetrical function
+around 0, with a domain over the real numbers, and a range between 0
 and 1.
@@
 \lim_{h\rightarrow 0} I\left(\frac{z}{h}\right) \approx \mathbb{1}(z\geq 0)
-\]
-
-Thus the function \(h_{3,i}\) can be approximated as:
-
-\[h_{3,i} \approx I\left( q^\varepsilon_\tau x_i'\gamma +x_i'\beta - y_i  \right) - \tau\]
-
-Now, we can obtain the Jacobian matrix \(\bar G_{3,1}\) as:
+\].
+
+Thus the function \(h_{3,i}\) can be approximated as
+
+\[h_{3,i} \approx I\left( q^\varepsilon_\tau x_i'\gamma +x_i'\beta - y_i  \right) - \tau\].
+
+Now, we can obtain the Jacobian matrix \(\bar G_{3,1}\) as
 
@@
 \end{aligned}
-\]
+\].
 
 Under the assumption that we have enough observations within each
-combination of \(x\), and of multiplicative heteroskedasticity, we have:
+combination of \(x\) that are of multiplicative heteroskedasticity, we have
 
@@
 \end{aligned}
-\]
+\],
 
 where \(f_{y|X}\) is the conditional probability density function of
-\(y\) given \(X\), and \(f_\varepsilon\) is the unconditional
+\(y\) given \(X\) and \(f_\varepsilon\) is the unconditional
 distribution of the standardized error. With this, we can rewrite the
-Jacobian matrix as:
+Jacobian matrix as
 
 \[\bar G_{3,1} = -N^{-1} f_{\varepsilon}\big(q^\varepsilon_\tau\big) \sum  \frac{x_i'}{x_i'\gamma} 
-\]
+\].
 
 Asymptotically, however, the expression \(\sum\frac{a_i}{b_i}\) can be
-approximated using taylor expansions by \(N\frac{\bar a}{\bar b}\).
-\footnote{This approximation will be useful when we consider the
-  estimation of the influence functions.} Thus, we can rewrite the last
-term as:
+approximated using Taylor expansions by \(N\frac{\bar a}{\bar b}\).
+\footnote{This approximation will be useful when we consider the estimation of the influence functions.} Thus, we can rewrite the last
+term as
 
 \[\bar G_{3,1} = - f_{\varepsilon}\big(q^\varepsilon_\tau\big) \frac{\bar x_i'}{\bar x_i'\gamma} 
-\]
+\].
 
@@
 
-and the Jacobian for the third matrix \(\bar G_{3,3}\) is:
+and the Jacobian for the third matrix \(\bar G_{3,3}\) is
 
@@
 \hypertarget{influence-functions}{%
-\subsection{Influence functions}\label{influence-functions}}
-
-\textbf{Location coefficients}
+\subsection{Influence Functions}\label{influence-functions}}
+
+Location Coefficients
 
 \[\lambda_i(\beta) = \bar G^{-1}_{1,1} h_{1,i} = N (X'X)^{-1}(x_i (y_i-x_i'\beta)) = N (X'X)^{-1}(x_i \nu_i)
-\]
-
-Which can also be written as a function of the standardized residuals:
+\],
+
+which can also be written as a function of the standardized residuals:
 
@@
 
-\textbf{Scale Coefficients}
+Scale Coefficients
 
@@
 
-And \[\begin{aligned}
+and \[\begin{aligned}
 E[sign(\nu_i)] &= E[\mathbb{1}(\nu_i \geq 0)] - E[\mathbb{1}(\nu_i < 0)] \\
@@
 \citet{mss2019} and \citet{im2000}. If the scale function is strictly
-possitive, it also follows that
+positive, it also follows that
 \(\mathbb{1}(\nu_i \geq 0)= \mathbb{1}(\varepsilon_i \geq 0)\). Thus, it
-can be simplified as:
+can be simplified as
 
@@
 \end{aligned}
-\]
-
-\textbf{Quantile of standardized residual}
+\].
+
+Quantile of Standardized Residual
 
@@
 The method described here can be implemented using any of the following
-packages
+packages:
 
@@
 \item
-  \texttt{mmqreg} in Stata: `net install mmqre,
-  from(https://friosavila.github.io/stpackages)
+  \texttt{mmqreg} in Stata: net install mmqre,
+  (https://friosavila.github.io/stpackages)
 \item
-  \texttt{mmqreg} in R: Program Available in mmqreg repository in GitHub
+  \texttt{mmqreg} in R: Program available in mmqreg repository on GitHub
   (https://github.com/friosavila/mmqreg)
@@
 \item
-  \texttt{mmqreg} in julia:
+  \texttt{mmqreg} in Julia:
 \end{itemize}

### 2023-11-13 article/article.tex
Revert "update CG"
This reverts commit 77ae13d0bd502eb1f2836fcd140a6af5ce0c6cce.

--- 2023-11-07 article/article.tex
@@
 
+\tnotetext[t1]{The opinions expressed in this paper are those of the authors and do not necessarily reflect the views of the World Bank, its Board of Directors, or the countries it represents.}
 \makeatletter
@@
 \hypersetup{
-  pdftitle={Quantile Regressions via Method of Moments with multiple fixed effects},
+  pdftitle={Quantile Regressions via Method of Moments with multiple fixed effects },
   pdfauthor={Fernando Rios-Avila; Leonardo Siles; Gustavo Canavire-Bacarreza},
@@
 \title{Quantile Regressions via Method of Moments with multiple fixed
-effects}
+effects \tnoteref{t1}}
 \author[1]{Fernando Rios-Avila%
@@
 \cortext[cor1]{Corresponding author}
-
-\fntext[fn1]{The opinions expressed in this paper are those of the
-authors and do not necessarily reflect the views of the World Bank, its
-Board of Directors, or the countries it represents}
 
@@
 
-\[q(y|\tau,x) = x'(\beta + q(\tau) \times \gamma)\]
+\[Q_y(\tau|x) = x'(\beta + q(\tau) \times \gamma)\]
 
@@
 \[\bar G(\theta) = \begin{bmatrix}
-\bar G_{11} & G_{12} & G_{13} \\
-\bar G_{21} & \bar G_{22} & G_{23} \\
+\bar G_{11} & \bar G_{12} & \bar G_{13} \\
+\bar G_{21} & \bar G_{22} & \bar G_{23} \\
 \bar G_{31} & \bar G_{32} & \bar G_{13} \\
@@
 \[\begin{aligned}
-E(K_h(q^\varepsilon_\tau x_i'\gamma +x_i'\beta - y_i )|X) &= f_{y|X}(q^\varepsilon_\tau x_i'\gamma +x_i'\beta) \\
-&=\frac{1}{x_i'\gamma} f_{\varepsilon}(q^\varepsilon_\tau) \\
+E(K_h(q(\tau) x_i'\gamma +x_i'\beta - y_i )|X) &= f_{y|X}(q(\tau) x_i'\gamma +x_i'\beta) \\
+&=\frac{1}{x_i'\gamma} f_{\varepsilon}(q(\tau)) \\
 \end{aligned}

### 2023-11-13 article/article.qmd
s
s

@@
   This paper proposes a new method to estimate quantile regressions with multiple fixed effects.
-The method expands on the strategy proposed by @mss2019, allowing for multiple fixed effects, and providing various alternatives for the estimation of Standard errors.
+The method, which expands on the strategy proposed by @mss2019, allows for the inclusion of multiple fixed effects and provides various alternatives for the estimation of standard errors.
 We provide Monte Carlo simulations to show the finite sample properties of the proposed method in the presence of two sets of fixed effects.
-Finally, we apply the proposed method to estimate the determinants of the surplus of government as a share of GDP allowing for both time and country fixed effects.
+Finally, we apply the proposed method to estimate the determinants of the surplus of government as a share of GDP, allowing for both time and country fixed effects.
+
 keywords: 
@@
     journal:
-      name: Journal Name
       formatting: review
@@
 
-```{=html}
 <!--
@@
 -->
-```
+
 # Introduction
@@
 A relatively recent development in the literature has focused on extending quantile regressions analysis to include individual fixed effects in the framework of panel data.
-However, as described in @neymanscott1948, and @lancaster2000, when individual fixed effects are included in quantile regression analysis it generates an incidental parameter problem.
-While many strategies have been proposed for estimating this type of model (see @galvao2017quantile for a brief review), neither has become standard because of their restrictive assumptions in regards to the individual effects, the computational complexity, and implementation.
+However, as described in @neymanscott1948, and @lancaster2000,  when individual fixed effects are included in quantile regression analysis an incidental parameter problem is generated.
+While many strategies have been proposed for estimating this type of model (see @galvao2017quantile for a brief review), neither has become standard because of their restrictive assumptions in regard to the inclusion of individual and multiple fixed effects, the computational complexity, and implementation.
 
-More recently, @mss2019 (MSS hereafter) proposed a methodology based on a conditional location-scale model similar to the one described in @he1997 and @zhao2000, for the estimation of quantile regressions models for panel data via a method of moments.
-This method allows individual fixed effects allowing to have heterogeneous effects on the entire conditional distribution of the outcome, rather constraining their effect to be a location shift only as in @canay2011, @koenker2004, and @lamarche2010.
+More recently, @mss2019 (MSS hereafter) proposed a methodology based on a conditional location-scale model, similar to the one described in @he1997 and @zhao2000, for the estimation of quantile regressions models for panel data via a method of moments.
+This method allows individual fixed effects to have heterogeneous effects on the entire conditional distribution of the outcome, rather than constraining their effect to be a location shift only, as in @canay2011, @koenker2004, and @lamarche2010.
 
-In principle, under the assumption that data generating process behind the data is based on a multiplicative heteroskedastic process that is linear in parameters [@cameron2005, @mss2019, @he1997, @zhao2000], the effect of a variable $X$ on the $q_{th}$ quantile can be derived as the combination of a location effect, and scale effect moderated by the quantile of an underlying i.i.d.
+In principle, under the assumption that data-generating process behind the data is based on a multiplicative heteroskedastic process that is linear in parameters [@mss2019, @he1997, @zhao2000, @cameron2005], the effect of a variable $X$ on the $q_{th}$ quantile can be derived as the combination of a location effect, and scale effect moderated by the quantile of an underlying i.i.d.
 error.
@@
 
-While this methodology is not meant to substitute the use of standard quantile regression analysis, given the assumptions required for the identification of the model, it provides a simple and fast alternative for the estimation of quantile regression models with individual fixed effects.
+This methodology is not meant to substitute for the use of standard quantile regression analysis.
+That said, given the assumptions required for the identification of the model, it provides a simple and fast alternative for the estimation of quantile regression models with individual fixed effects.
 
-In this framework, our paper expands on @mss2019, following some of the suggestions by the authors regarding further research.
-First, making use of the properties of GMM estimators, we derive various alternatives for the estimation of standard errors based on the empirical Influence functions of the estimators.
-Second, we reconsider the application of Frisch--Waugh--Lovell (FWL) theorem (@frishwaugh1933 and @lovell1963) to extend the MSS estimator to allow for the inclusion of multiple fixed effects, for example, individual and year fixed effects.
+In this framework, our paper expands on @mss2019, following some of the suggestions by these authors regarding further research.
+First, making use of the properties of generalized method of moments (GMM) estimators, we derive various alternatives for the estimation of standard errors based on the empirical influence functions of the estimators.
+Second, we reconsider the application of Frisch-Waugh-Lovell (FWL) theorem [@frishwaugh1933 and @lovell1963] to extend the MSS estimator to allow for the inclusion of multiple fixed effects, for example, individual and year fixed effects.
 
-The rest of the paper is restructured as follows.
-Section 2 presents the basic setup of the location-Scale model described in @he1997 and @zhao2000, tying the relationship between the standard quantile regression model, and the location and scale model.
-It also revisits MSS methodology, proposing alternative estimators for the standard errors based on the properties of GMM estimators and the empirical influence functions.
-It also shows that FWL theorem can be used to control for multiple fixed effects.
-Section 3 presents the results of a small simulation study and Section 4 illustrates the application of the proposed methods with one empirical example.
-Seccion 5 concludes.
+The rest of the paper is structured as follows: section 2 presents the basic setup of the location-scale model described in @he1997 and @zhao2000, tying the relationship between the standard quantile regression model and the location-scale model.
+It also revisits the methodology of MSS, proposing alternative estimators for the standard errors based on the properties of GMM estimators and the empirical influence functions.
+It also shows that the FWL theorem can be used to control for multiple fixed effects.
+Section 3 presents the results of a small simulation study and section 4 illustrates the application of the proposed methods with two empirical examples.
+Section 5 concludes.
 
@@
 
-Quantile regressions are used to identify relationships between the explanatory variables $x$ and the conditional quantiles of the dependent variable $Q_y(\tau|X)$.
+Quantile regressions are used to identify relationships between the explanatory variables $X$ and the conditional quantiles of the dependent variable $Q_y(\tau|X)$.
 This relationship is commonly assumed to follow a linear functional form:
@@
 
-This allows for the effect of $X$ on $Y$ to vary across all $\tau$.
-This formulation can also be related to a random coefficient model, where all coefficients are assumed to be some nonlinear function of $\tau$, where $\tau$ follows a random uniform distribution.
+This allows for nonlinearities in the effect of $X$ on $Y$ across all values of $\tau$.
+This formulation can also be related to a random coefficient model, in which all coefficients are assumed to be some nonlinear function of $\tau$ where $\tau$ follows a random uniform distribution.
 
 An alternative formulation of quantile regressions is the location-scale model.
-This approach assumes that the conditional quantile of $Y$ given $X$ and $\tau$ can be expressed as a combination of two models: the location model, which describes the central tendency of the conditional distribution, and the scale model, which describes deviations from the central tendency:
+This approach assumes that the conditional quantile of $Y$ given $X$ and $\tau$ can be expressed as a combination of two models: the location model, which describes the central tendency of the conditional distribution; and the scale model, which describes deviations from the central tendency:
 
@@
 
-Here, the location parameters $\beta$ are typically identified using a linear regression model (as in @mss2019), or a median regression (as in @zhao2000), and the scale parameters $\gamma(\tau)$ can be estimated using standard approaches.
+Here, the location parameters $\beta$ are typically identified using a linear regression model (as in @mss2019) or a median regression (as in @zhao2000) and the scale parameters $\gamma(\tau)$ can be estimated using standard approaches.
 
@@
 
-One characteristic of this estimator is that the $\beta(\tau)$ coefficients are identified locally, and thus the estimated quantile coefficients will exhibit considerable variation when analyzed across $\tau$.
+One characteristic of this estimator is that the $\beta(\tau)$ coefficients are identified locally and thus the estimated quantile coefficients will exhibit considerable variation when analyzed across $\tau$.
 It is also implicit that if one requires an analysis of the entire distribution, it would be necessary to estimate the model for each quantile.[^1]
 
-[^1]: There are other estimators that provide smoother estimates for the quantile regression coefficients using a kernel local weighted approach [@kaplan2017], as well as identifying the full set of quantile coefficients simultaneously assuming some parametric functional forms [@frumentobotai2016].
+[^1]: There are other estimators that provide smoother estimates for the quantile regression coefficients using a kernel local weighted approach [@kaplan2017], as well as identifying the full set of quantile coefficients while simultaneously assuming some parametric functional forms [@frumentobotai2016].
 
@@
 
-Under the assumption that $\varepsilon$ is an independent and identically distributed (iid) unobserved random variable that is independent of $X$, the conditional quantile of $Y$ given $X$ and $\tau$ can be written as:
+Under the assumption that $\varepsilon$ is an i.i.d. unobserved random variable that is independent of $X$, the conditional quantile of $Y$ given $X$ and $\tau$ can be written as
 
@@
 
-In this setup, the traditional quantile coefficients are identified as the location model coefficients, plus the scale model coefficients moderated by the $\tau_{th}$ unconditional quantile of the standardized error $\varepsilon$.
+In this setup, the traditional quantile coefficients are identified as the location model coefficients plus the scale model coefficients moderated by the $\tau_{th}$ unconditional quantile of the standardized error $\varepsilon$.
 For simplicity we will use $q(\tau)$ to denote $Q_\varepsilon(\tau)$ in the rest of the paper.
@@
 While this specification imposes a strong assumption on the DGP, it has two advantages over the standard quantile regression model.
-First, because the location and scale model can be identified globally, with only a single paramater ($q(\tau)$) requiring local estimation, this estimation approach would be more efficient than the standard quantile regression model [@zhao2000].
-Second, under the assumption that $X\gamma$ is strictly possitive, the model would produce quantile coefficients that do not cross.
+First, because the location-scale model can be identified globally, with only a single parameter ($q(\tau)$) requiring local estimation, this estimation approach will be more efficient than the standard quantile regression model (@zhao2000).
+Second, under the assumption that $X\gamma$ is strictly positive, the model will produce quantile coefficients that do not cross.
 
-Following MSS, the quantile regression model defined by @eq-eq5 can be estimated using a method of moments approach.
-And while its possible to identify all coefficients ($\beta,\gamma, q(\tau)$) simultaneously, we describe and use the implementation approach advocated by MSS which identifies each set of coefficients separately.
+Following MSS, the quantile regression model defined by @eq-eq5 can be estimated using a generalized method of moments approach.
+And while it is possible to identify all coefficients ($\beta,\gamma, q(\tau)$) simultaneously, we describe and use the implementation approach advocated by MSS, which identifies each set of coefficients separately.
 
-First, the location model can be estimated using a standard linear regression model, where the dependent variable is the outcome $y$, and the independent variables are the explanatory variables $X$ (including a constant) with an error $u$, which is by definition heteroskedastic.
-In this case, the location model coefficients are identified under the following condition:
+First, the location model can be estimated using a standard linear regression model, where the dependent variable is the outcome $Y$ and the independent variables are the explanatory variables $X$ (including a constant) with an error $u$, which is by definition heteroskedastic.
+In this case, the location-model coefficients are identified under the following condition:
 
@@
 Second, after the location model is estimated, the scale coefficients can be identified by modeling heteroskedasticity as a linear function of characteristics $X$.
-For this we use the absolute value of the errors from the location model $u$ as dependent variable, which would allow us to estimate the conditional standard deviation (rather than conditional variance) of the errors.
+For this we use the absolute value of the errors from the location model $u$ as dependent variable, which allows us to estimate the conditional standard deviation (rather than conditional variance) of the errors.
 In this case, the coefficients are identified under the following condition:
@@
 
-Where one identifies the quantile of the error $\varepsilon$ using standardized errors $\frac{y_i-x_i'\beta}{x_i'\gamma}$, or by finding the values that identify the overall quantile coefficients $\beta(\tau)=\beta + \gamma q(\tau)$.
-Afterwords, the conditional quantile coefficients is simply defined as the combination of the location and scale coefficients.
+where one identifies the quantile of the error $\varepsilon$ using standardized errors $\frac{y_i-x_i'\beta}{x_i'\gamma}$ or by finding the values that identify the overall quantile coefficients $\beta(\tau)=\beta + \gamma q(\tau)$.
+Afterwards, the conditional quantile coefficients are simply defined as the combination of the location and scale coefficients.
 
@@
 
-As discussed in the previous section, the estimation of quantile regression coefficients using the location-scale model with heteroskedstic linear errors can be estimated using a the following set of moments, which fits in the Generalized Method of Moments framework:
+As discussed in the previous section, the estimation of quantile regression coefficients using the location-scale model with heteroskedastic linear errors can be estimated using a the following set of moments, which fits within the GMM framework:
 
@@
 
-Under the conditions described in @newey_chapter_1994 (see section 7), @cameron2005 (see chapter 6.3.9) or as shown in @mss2019, the location, scale and residual quantile coefficients are asymptotically normal.[^3]
+Under the conditions described in @newey_chapter_1994 (see section 7), @cameron2005 (see chapter 6.3.9), or as shown in @mss2019, the location, scale, and residual quantile coefficients are asymptotically normal.[^3]
 
-[^3]: @zhao2000 also shows that the quantile coefficients for the location-scale model also follows a normal distribution, but uses the assumption that the location model is derived using a least absolute deviation approach (median regression).
+[^3]: @zhao2000 also shows that the quantile coefficients for the location-scale model follow a normal distribution, but uses the assumption that the location model is derived using a least absolute deviation approach (median regression).
 
-Call $\theta=[ \beta' \ \ \gamma' \ \ q(\tau) ]'$ the set of coefficients that are identified by the modement conditions in @eq-eq10, a just identified model.
-And the function $h_i$ is a vector function that stacks all the moments at the individual level described in @eq-eq10.
-Then $\hat\theta$ follows a normal distribution with mean $\theta$ and variance-covariance matrix $V(\theta)$ that is estimated as:
+Call $\theta=[ \beta' \ \ \gamma' \ \ q(\tau) ]'$ the set of coefficients that are identified by the moment conditions in @eq-eq10, a just identified model, and the function $h_i$ is a vector function that stacks all the moments described in @eq-eq10 at the individual level.
+Then $\hat\theta$ follows a normal distribution with mean $\theta$ and variance-covariance matrix $V(\theta)$ that is estimated as
 
@@
 
-Which is equivalent to the Eicker-White Heteroskedastic-Consistent estimator for least-squares estimators.
+which is equivalent to the Eicker-White heteroskedasticity-consistent estimator for least-squares estimators.
 
-Here, the inner product is the moment covariance matrix, and $\bar{G}(\theta)$ is the Jacobian matrix of the moment equations evaluated at $\hat\theta$.
+Here, the inner product is the moment covariance matrix and $\bar{G}(\theta)$ is the Jacobian matrix of the moment equations evaluated at $\hat\theta$.
 
@@
 
-In this framework, the quantile regression coefficients, a combination of the location-scale-quantile estimates, will follow a normal distribution with mean $\beta(\tau) = \beta+\gamma q(\tau)$ and variance-covariance matrix equal to:
+In this framework, the quantile regression coefficients, a combination of the location-scale-quantile estimates, will follow a normal distribution with mean $\beta(\tau) = \beta+\gamma q(\varepsilon | \tau)$ and variance-covariance matrix equal to
 
@@
 
-where $\Xi$ is a $k \times (2k+1)$ matrix defined as:
+where $\Xi$ is a $k \times (2k+1)$ matrix defined as
 
@@
 
-While it is possible to estimate the variance-covariance matrix using simultaneous model estimation, for a just identified model, it is more efficient to estimate each set of coefficients separately.
-Afterwards, the variance-covariance matrix can be estimated using the empirical influence functions of the estimators (see @jann_2020 for an overview of the application, and @hampel2005 for an in-depth review).
+While it is possible to estimate the variance-covariance matrix using simultaneous model estimation for a just identified model, it is more efficient to estimate each set of coefficients separately.
+Afterward, the variance-covariance matrix can be estimated using the empirical influence functions of the estimators (see @jann_2020 for an overview of the application and @hampel2005 for an in-depth review).
 
-Specifically, given an arbitrary vector of empirical influence functions $\lambda_i(\theta)$, the variance-covariance matrix can be estimated as:
+Specifically, given an arbitrary vector of empirical influence functions $\lambda_i(\theta)$, the variance-covariance matrix can be estimated as
 
@@
 
-For the specific case of quantile regressions via momoments, the influence functions for the location, scale and quantile coefficients are:[^4]
+For the specific case of quantile regressions through moments, the influence functions for the location, scale, and quantile coefficients are[^4]
 
@@
 
-The different types of Standard errors estimation, thus, depend on the assumptions imposed for the estimation of $V(\theta)$.
+The different types of standard errors estimation thus depend on the assumptions imposed for the estimation of $V(\theta)$.
 
@@
 
-The first, and most natural standard error estimator is given by equation @eq-eqvcv.
-This is equivalent to the Eicker-White Heteroskedastic-Consistent estimator for least-squares estimators.
-Considering the location-scale model, the variance-covariance matrix for the quantile coefficients can be estimated as:
+The first and most natural standard error estimator is given by equation @eq-eqvcv.
+This is equivalent to the Eicker-White heteroskedasticity-consistent estimator for least-squares estimators.
+Considering the location-scale model, the variance-covariance matrix for the quantile coefficients can be estimated as
 
@@
 
-This estimator of Standard errors should be robust to arbitrary heteroskedasticity.
-However, because the location-scale specification relies on the correct specification of the model heteroskedasticity, large differences in Standard errors compared to GLS-standard errors may be an indication of misspecification of the model.
+This estimator of standard errors should be robust to arbitrary heteroskedasticity.
+However, because the location-scale specification relies on the correct specification of the model heteroskedasticity, large differences in standard errors compared to GLS-standard errors may be an indication of misspecification of the model.
 
@@
 Because one of the typical applications of quantile regressions is the analysis of panel data, allowing for clustered standard errors at the individual level is important.
-If the unobserved error $\varepsilon$ is correlated within clusters, GLS-Standard errors could be severily biased.
-The standard recommendation has been to report block-bootstrap standard errors, clustering at the individual level.
+If the unobserved error $\varepsilon$ is correlated within clusters, generalized least squares (GLS) standard errors could be severely biased.
+The standard recommendation has been to report block-bootstrap standard errors, clustered at the individual level.
 
-Since we have access to the influence functions, it is straight forward to estimate one-way clustered standard errors.
+Because we have access to the influence functions, it is straightforward to estimate one-way clustered standard errors.
 
-Call $N_G$ to be the total number of clusteres g, where $g=1\dots N_G$. The clustered variance covariance matrix is given by:[^5]
+Let $N_G$ be the total number of clusters $g$, where $g=1\dots N_G$. The clustered variance covariance matrix is given by[^5]
 
@@
 
-Where $S\lambda_i(\theta)$ is the sum of the influence functions over all observations within a given cluster $g$.
+where $S\lambda_i(\theta)$ is the sum of the influence functions over all observations within a given cluster $g$.
 
@@
 
-The standard errors proposed by MSS can be understood as an application of generalized least squares (GLS), which will be valid as long as the model for heteroskedasticity is correctly specified.[^6] To estimate the GLS-Standard errors, we make use of the following property:
+The standard errors proposed by MSS can be understood as an application of GLS, which will be valid as long as the model for heteroskedasticity is correctly specified.[^6] To estimate the GLS standard errors, we make use of the following property:
 
-[^6]: As discussed in most econometric textbooks, like @cameron2005, one approach to correct for heteroskedasticity, when the heteroskedasticity functional form is known, or can be estimated, is to use weighted least squares.
-While feasible, however, this approach would defeat the purpose of identifying quantile effects exploiting the heteroskedasticity of the model.
+[^6]: As discussed in most econometric textbooks, for example @cameron2005, one approach to correct for heteroskedasticity, when the heteroskedasticity functional form is known or can be estimated, is to use weighted least squares.
+While feasible this approach would defeat the purpose of identifying quantile effects exploiting the heteroskedasticity of the model.
 
@@
 
-Under the assumption that the model for heteroskedasticity is correctly specified, we can apply the law of iterated expectations and rewrite the variance-covariance matrix as:
+Under the assumption that the model for heteroskedasticity is correctly specified, we can apply the law of iterated expectations and rewrite the variance-covariance matrix as
 
@@
 This standard error estimator is an application of GLS that accounts for the heteroskedasticity the model uses to identify the quantile coefficients.
-We can apply the same principle to find the GLS-Standard errors for the system of location-scale and quantile coefficients.
-To do this, define the following modified influence functions:
+We can apply the same principle to find the GLS standard errors for the system of location-scale and quantile coefficients.
+To do this, we define the following modified influence functions:
 
@@
 \tilde \lambda_{3,i}&=x_i' \gamma  \\
- \psi_1 &= \varepsilon_i \\
- \psi_2 &= \tilde \varepsilon_i -1 \\
- \psi_3 &= \frac{1}{ x_i' \gamma }\frac{\tau-\mathbb{1}\big( q(\tau)  \geq \varepsilon_i  \big) }{ f_{\varepsilon}(q(\tau))} - \frac{\varepsilon_i }{\bar x_i'\gamma} 
+ \psi_{i,1} &= \varepsilon_i \\
+ \psi_{i,2} &= \tilde \varepsilon_i -1 \\
+ \psi_{i,3} &= \frac{1}{ x_i' \gamma }\frac{\tau-\mathbb{1}\big( q(\tau)  \geq \varepsilon_i  \big) }{ f_{\varepsilon}(q(\tau))} - \frac{\varepsilon_i }{\bar x_i'\gamma} 
 -  q(\tau) \frac{(\tilde \varepsilon_i -1\big)}{\bar x_i'\gamma}
@@
 
-Then, the GLS-Standard errors for the location-scale and quantile coefficients can be estimated as:
+Then, the GLS standard errors for the location-scale and quantile coefficients can be estimated as
 
@@
 $$\begin{aligned}
-\hat\Omega_{ij} &= \frac{1}{N} \sum_i^N \tilde \lambda_{i}(\theta) \tilde \lambda_{j}(\theta)' \\
-\hat\sigma_{ij} &= \frac{1}{N} \sum_i^N \psi_{i} \psi_{j}
+\hat\Omega_{jk} &= \frac{1}{N} \sum_{i=1}^N \tilde \lambda_{i,j}(\theta) \tilde \lambda_{i,k}(\theta)' \\
+\hat\sigma_{jk} &= \frac{1}{N} \sum_{i=1}^N \psi_{i,j} \psi_{i,k}
 \end{aligned}
@@
 
-This estimator of Standard errors is equivalent to the one derived by MSS by Theorem 3.
+This estimator of stand ard errors is equivalent to the one derived by MSS using Theorem 3.
 
@@
 
-Using the setup described in the previous section, @mss2019 proposes an extension to the model proposed by @he1997 that would allow for the estimation of quantile regression models with panel data, allowing for the inclusion of individual fixed effects.
+Using the setup described in the previous section, @mss2019 proposes an extension to the model proposed by @he1997 that enables the estimation of quantile regression models with panel data, allowing for the inclusion of individual fixed effects.
 However, as the authors suggest, the methodology can be generalized to allow for the inclusion of multiple fixed effects.
-This type of analysis may be useful when considering data such as employer-employee linked data [@abowed2006], or teacher-student linked data [@harrissass2011].
+This type of analysis can be useful when considering data such as employer-employee linked data [@abowed2006] or teacher-student linked data [@harrissass2011].
 Or, in the most common case, allowing to control for both individual and time fixed effects.
 
-Reconsider the original model, and assume there are sets of unobserved heterogeneity that are assumed to be constant across observations, if they belong to common groups.
+We return to the original model and now assume there are sets of unobserved heterogeneity that are assumed to be constant across observations, if they belong to common groups.
 In panel data, the groups would be the individual fixed effects and the time fixed effects.
-Without loss of generality, we can assume that the data generating process is as follows:
+Without loss of generality, we can assume that the data-generating process is as follows:
 
@@
 
-where we assume $x_{i}$ vary across groups $g_1$ and $g_2$, thus are not collinear, and that $\delta's$ and $\zeta's$ are the location and scale effects associated with groups fixed effects.[^7]
+where we assume $x_{i}$ vary across groups $g_1$ and $g_2$ (and thus are not collinear) and that $\delta's$ and $\zeta's$ are the location and scale effects associated with groups fixed effects.[^7]
 
-[^7]: We could just as well consider multiple sets of fixed effects
+[^7]: We could just as well consider multiple sets of fixed effects.
 
-If the dimension of groups $g_k$ is low, this model could be estimated using a dummy inclussion approach following @sec-betas, and standard errors obtained as discussed in @sec-se.
+If the dimension of groups $g_k$ is low, this model could be estimated using a dummy inclusion approach following @sec-betas, and the standard errors obtained as discussed in @sec-se.
 However, if the dimensionality of $g_k$ is high, the dummy inclusion approach may not be feasible.
-Instead, a more feasible approach is to apply the Frisch-Waugh-Lovell (FWL) theorem, and partial out the impact of the group fixed effects on the control variables $x_{i}$, the outcome of interest $y_{i}$, with a similar approach for the identification of $\sigma(x)$.
-In the case of unbalanced setups, with multiple groups, the estimation involves iterative processes for which various approaches have been suggested and implemented (see @correia_feasible_nodate, @gaure2013, @rios2015, among others).
+A more feasible approach is to apply the FWL theorem and partial out the impact of the group fixed effects on the control variables $x_{i}$, and the outcome of interest $y_{i}$, using a similar approach for the identification of $\sigma(x)$.
+In the case of unbalanced setups with multiple groups, the estimation involves iterative processes for which various approaches have been suggested and implemented (see for example, @correia_feasible_nodate, @gaure2013, @rios2015, among others).
 
-When applying the partialing out approach, some modifications to the approach described in @sec-betas are needed.
+When applying the partialing-out approach, some modifications to the approach described in @sec-betas are needed.
 
-First, for all dependent and independent variables in the model ($w=y,x$), we partial out the group fixed effects, and obtain the centered-residualized variables:
+First, for all dependent and independent variables in the model ($w=y,x$), we partial out the group fixed effects and obtain the centered-residualized variables:
 
@@
 
-Afterwards, we estimate the location model using the centered-residualized variables:[^8]
+Afterward, we estimate the location model using the centered-residualized variables:[^8]
 
-[^8]: Using centered-residualized variables allow us to include a constant in the model specification, which simplifies the derivation of the influence functions.
-However, as with other fixed effects models, the constant is not identified, and thus should not be interpreted.
+[^8]: Using centered-residualized variables allows us to include a constant in the model specification, which simplifies the derivation of the influence functions.
+However, as with other fixed effects models, the constant is not identified and thus should not be interpreted.
 
@@
 
-Since $|\hat \nu_i|$ is the dependent variable for the scale model, we apply the partialling out and recentering to this expression ($|\hat \nu_i|^{rc}$), and use that to estimate the model:
+Because $|\hat \nu_i|$ is the dependent variable for the scale model, we apply the partialing out and recentering to this expression ($|\hat \nu_i|^{rc}$), and use that to estimate the following model:
 
@@
 
-Finally the standardized residuals $\varepsilon_i$ can be obtained as follows
+Finally, the standardized residuals $\varepsilon_i$ can be obtained as follows:
 
@@
 
-The $\tau_{th}$ quantile of the error $\varepsilon$ can be estimated as usual, and the variance-covariance matrices obtained in the same way as before (see @sec-se), but using $x_{i}^{rc}$ instead of $x_{i}$ when estimating the influence functions for all estimated coefficients.
+The $\tau_{th}$ quantile of the error $\varepsilon$ can be estimated as usual and the variance-covariance matrices obtained in the same way as before (see @sec-se) by using $x_{i}^{rc}$ instead of $x_{i}$ when estimating the influence functions for all estimated coefficients.
 
@@
 In contrast with MSS, we consider a two-way fixed effect structure that is more general than the panel structure.
-For this excercise, we consider the following data generating process:
+For this exercise, we consider the following data-generating process:
 
@@
 
-where $\alpha_{1i}\sim \chi^2(1)$, $\alpha_{2i} \sim \chi^2(1)$ and $x_i = 0.5 * (\chi_i +0.5(\alpha_{1i}+\alpha_{2i}))$ with $\chi_i \sim \chi^2(1)$.
-We only consider the case when the error term $\varepsilon_i$ is assumed to be normally distributed with mean zero and standard deviation of 0.5.
+where $\alpha_{1i}\sim \chi^2(1)$, $\alpha_{2i} \sim \chi^2(1)$, and $x_i = 0.5 * (\chi_i +0.5(\alpha_{1i}+\alpha_{2i}))$, with $\chi_i \sim \chi^2(1)$.
+We only consider the case when the error term $\varepsilon_i$ is assumed to be normally distributed with mean 0 and standard deviation of 0.5.
 We assume that there are 50 mutually exclusive fixed effect groups for each set of fixed effects.
-Observations are assigned to each subgroup randomly, using a uniform distribution between 1 and 50.
-We consider a sample sizes of 500, 1000, 2000 and 4000 observations, which implies an average of 10, 20, 40 and 80 observations per group.
-The model is estimated using the location-scale model with heteroskedastic linear errors, and we report the coefficients for the 25th and 75th quantiles.
+Observations are assigned to each subgroup randomly using a uniform distribution between 1 and 50.
+We consider sample sizes of 500, 1000, 2000, and 4000 observations, which implies an average of 10, 20, 40, and 80 observations per group.
+The model is estimated using the location-scale model with heteroskedastic linear errors and we report the coefficients for the 25th and 75th quantiles.
 We run this excercise 5000 times.
-@tbl-sim1 reports the bias, simulated standard error and mean squared error.
+@tbl-sim1 reports the bias, simulated standard error, and mean squared error.
 We also report the results obtained using an adaptation bias-corrected estimator based on the split-panel jackknife estimator proposed by @dhaene2015.[^9] These results are labeled JKC.
 
-[^9]: For the implementation, we estimate the model using the full sample, then, randomly assign each observation into one of two groups, and re-estimate the quantile coefficients for each group.
+[^9]: For the implementation, we first estimate the model using the full sample, then randomly assign each observation into one of two groups, and finally reestimate the quantile coefficients for each group.
 The bias-corrected estimator is then obtained as $\hat\beta(\tau)_{jkc}=2*\hat\beta(\tau)_{full}-0.5*\big(\hat\beta(\tau)_{s1}+\hat\beta(\tau)_{s1}\big)$.
 
-Similar to the findings in MSS, we find that the estimator presents a bias when the sample is small ($N=500$), but this bias shrinks as the sample sizes increases.
+Similar to the findings in MSS, we find that while the estimator presents a bias when the sample is small ($N=500$), this bias shrinks as the sample size increases.
 As MSS describes, the bias seems to be proportional to the sample size, or more precisely to $N/N_{g1}$ and $N/N_{g2}$, where $N_{g1}$ and $N_{g2}$ are the average number of observations per group.
-Interestingly, the bias-corrected estimator presents an almost zero bias, even when the samples are small (about 10 observations per sub-group).
-Also replicating the results of MSS, despite bias reduction obtained using the JKC estimator, the standard errors and mean squared error (MSE) are larger than without correction.
+Interestingly, the bias-corrected estimator presents an almost 0 bias, even when the samples are small (about 10 observations per subgroup).
+Moreover, we find that despite the bias reduction obtained using the JKC estimator, the standard errors and mean squared error (MSE) are larger than without correction, which also replicates the results of MSS,
 
@@
 
-As described in section @sec-se, GLS-Standard errors may not be appropriate if heteroskedasticity in the model is misspecified.
-This could happen if the heteroskedasticity is not linear in parameters, or if there is correlations within groups.
-To show the performance of the GLS-Standard errors, we consider two additional simulations.
-To see the impact of heteroskedasticity misspecification, we assume the DGP is given by:
+As described in section @sec-se, GLS standard errors may not be appropriate if heteroskedasticity in the model is misspecified.
+This could happen if the heteroskedasticity is not linear in parameters or if there are correlations within groups.
+To show the performance of the GLS standard errors, we consider two additional simulations.
+To see the impact of heteroskedasticity misspecification, we assume the DGP is given by
 
@@
 The results from both simulations are reported in the @tbl-sim2.
-We report the average coefficient, simulation based Standard errors, and the standard errors using GLS, robust and clustered estimations.
+We report the average coefficient, simulation-based standard errors, and the standard errors using GLS, robust and clustered estimations.
 
@@
 
-As expected, the GLS-standard errors are biased, and the bias is larger in the case of misspecified heteroskedasticity.
-In fact, with heteroskedastic misspecification, the average GLS-SE (.476) is almost three times as large as the simulation-based standard error (0.154).
+As expected, the GLS standard errors are biased and the bias is larger in the case of misspecified heteroskedasticity.
+In fact, with heteroskedasticity misspecification, the average GLS-SE (0.476) is almost three times as large as the simulation-based standard error (0.154).
 In this first case, robust standard errors perform better, but with a small difference (0.14 to 0.154).
@@
 
-In this section we replicate one of the excercises from MSS, allowing for time and individual fixed effects, as well as for different standard errors estimations.
-We use data from @persson_economic_2005, to estimate the relationship between surplus of goverment as share of GDP, and a measure of quality of democracy (POLITY); log of real income per capita (LYP); trade volume as share of GDP (TRADE), Share of population between 15-65 uears of age (P1564), the share of the population 65 years or older (P65); one-year lag of the dependent variable (LSP); oil prices in US dollars differntiating importer and exported countries (OILIM and OILEX); and the output gap (YGAP).
-In addition to country fixed effects (as illustrated in MSS), we also show results allowing for time fixed effects.
+In this section we replicate one of the exercises from MSS, allowing for time and individual fixed effects as well as for different standard errors estimations.
+We use data from @persson_economic_2005, to estimate the relationship between surplus of government as share of GDP, and a measure of quality of democracy (POLITY); log of real income per capita (LYP); trade volume as share of GDP (TRADE); share of population between 15 and 65 years of age (P1564); the share of the population 65 years and older (P65); one-year lag of the dependent variable (LSP); oil prices in US dollars, differntiating between importer and exporter countries (OILIM and OILEX); and the output gap (YGAP).
+In addition to country fixed effects (as illustrated in MSS), we show results allowing for time fixed effects.
 @tbl-tb1 and @tbl-tb2 provide the results for the model with and without time fixed effects, respectively.
-It show cases the location and scale coefficients, as well as the quantile coefficients for the 25th, 50th and 75th quantiles.
-We also report GLS-Standard errors, Robust standard errors (brackets) and clustered standard errors at the country level.
+The tables showcase the location and scale coefficients, as well as the quantile coefficients for the 25th, 50th and 75th quantiles.
+We also report GLS standard errors, robust standard errors (brackets) and clustered standard errors at the country level.
 
@@
 
-: The determinants of government surpluses: Individual Fixed effects {#tbl-tb1}
+: Determinants of Government Surpluses: Individual Fixed Effects {#tbl-tb1}
 
-As expected, @tbl-tb1 shows that point estimates are identical to the ones reported in @mss2019 (Table 6), including analytical standard errors (GLS).
-With our estimator, however, we are able to also produce both robust and clustered standard errors for location and scale coefficients.
-Except for a few cases, robust and clustered standard errors are larger than GLS standard errors, which may be an indication of misspecification of the model.
-The GLS standard errors we report differ from the ones in MSS because they use panel standard errors, which are equivalent to our clustered standard errors, instead of the analytical standard errors we derive.
+As expected, @tbl-tb1 shows that the point estimates are identical to those reported in @mss2019 (Table 6), including analytical standard errors (GLS).
+With our estimator, however, we are also able to produce both robust and clustered standard errors for location and scale coefficients.
+Except for a few cases, the robust and clustered standard errors are larger than the GLS standard errors, which may be an indication of misspecification of the model.
+The GLS standard errors we report differ from those in MSS, because they use panel standard errors, which are equivalent to our clustered standard errors, instead of the analytical standard errors we derive.
 
-Considering the estimated effects across quantiles, we observe few differences in the reported GLS standard errors compared to the analytical standard errors reported MSS.
-Our clustered standard errors, however, are closer to the bootstrap based standard errors the authors report.[^10]
+Considering the estimated effects across quantiles, we observe few differences in the reported GLS standard errors compared to the analytical standard errors reported in MSS.
+Our clustered standard errors, however, are closer to the bootstrap-based standard errors the authors report.[^10]
 
-[^10]: There are two possible reasons that may explain the differences in the GLS standard errors.
-On the one hand, in our derivation, the influence function of the standardized $\tau_{th}$ quantile (see #eq-infs) does not have the same leading term as the one reported in MSS (see theorem 3, and the definition of $W$).
+[^10]: The differences in the GLS standard errors may be due that in our derivation the influence function of the standardized $\tau_{th}$ quantile (see #eq-infs) does not have the same leading term as the one reported in MSS (see Theorem 3, and the definition of $W$).
 
@@
 Because oil prices only vary across years, the variable is excluded from the model specification.
-Accounting for time fixed effects does not change the general conclusions one could make based on the results from @tbl-tb1.
-The two largest differences are that the log of income per capita has a positive effect on Government Surpluses, but only for the 25th quantile, because of the largest impact on the Scale component.
-Similarly, we observe that the income gap now has an impact on Government surplus that is always negative, but increasing across quantiles.
+Accounting for time fixed effects does not change the general conclusions that can be drawn, based on the results from @tbl-tb1.
+The two largest differences are that the log of income per capita has a positive effect on government surpluses, but only for the 25th quantile, because at this point the largest impact on the Scale component is felt.
+Similarly, we observe that the income gap has an impact on government surplus that is always negative and increasing across quantiles.
 In both instances, the effects are not statistically significant.
@@
 
-: The determinants of government surpluses: Individual and Time Fixed effects {#tbl-tb2}
+: The Determinants of Government Surpluses: Individual and Time Fixed Effects {#tbl-tb2}
 
@@
 
-In this paper, we have extended the methodology proposed by @mss2019, allowing for the estimation of quantile regression models with multiple sets of fixed effects, as well as alternative Standard Errors estimations.
-This methodology would allow researchers to implement more comprehensive analysis of datasets characterized by complex hierarchies and unobserved heterogeneity.
+In this paper, we have extended the methodology proposed by @mss2019 in order to estimate quantile regression models with multiple sets of fixed effects as well as with alternative standard errrors.
+This methodology will allow researchers to implement more-comprehensive analyses of data sets characterized by complex hierarchies and unobserved heterogeneity.
 This extension is particularly valuable in contexts where group specific effects vary across the conditional distribution of the outcome of interest.
 
-Using a small simulation study, we show that our extended approach is as effective in identifying the parameters of interest as @mss2019 indicated, even in contexts with two sets of fixed effects.
-Notably, the bias-corrected estimator based on the split-panel jackknife estimator exhibits promising results, mitigating biases when samples are small, but increasing standard errors.
+Using a small simulation study, we show that our extended approach is as effective in identifying the parameters of interest as that of @mss2019, even in contexts with two sets of fixed effects.
+Notably, the bias-corrected estimator based on the split-panel jackknife estimator exhibits promising results, mitigating biases when samples are small but increasing standard errors.
 
-Furthermore, we have assessed the impact of misspecified heteroskedasticity and intra-cluster correlation on the performance of standard error estimations.
+Furthermore, we have assessed the impact of misspecified heteroskedasticity and intracluster correlation on the performance of standard error estimations.
 Our findings emphasize the importance of using appropriate standard error estimators to ensure accurate inference.
-In particular, we find that GLS standard errors are biased when the model heteroskedasticity is misspecified, and that robust and clustered standard errors perform better in these cases.
-This may also suggest a venue for future research, testing the validity of the location-scale model assumption.
+In particular, we find that GLS standard errors are biased when the model heteroskedasticity is misspecified and that robust and clustered standard errors perform better in these cases.
+This may also suggest a venue for future research, in which the validity of the location-scale model assumption is tested.
 
@@
 
-The estimation of quantile regression via moments assumes that the DGP is linear in parameters, with an heteroskedastic error term that is also linear function of parameters:
+The estimation of quantile regression via moments assumes that the DGP is linear in parameters, with an heteroskedastic error term that is also a linear function of parameters:
 
@@
 
-where $\varepsilon$ is an unobserved i.i.d. random variable that is independent of $x$, and such that $x\gamma$ is larger than zero for any $x$.
+where $\varepsilon$ is an unobserved i.i.d. random variable that is independent of $x$ and such that $x\gamma$ is larger than 0 for any $x$.
 
-In this case, the $\tau_{th}$ conditional quantile model can be written as:
+In this case, the $\tau_{th}$ conditional quantile model can be written as
 
-$$Q_y(\tau|x) = x'(\beta + q(\tau) \times \gamma)$$
+$$q(y | \tau, x) = x'(\beta + q(\varepsilon | \tau) \times \gamma)$$
 
-where $q(\tau)$ is the $\tau_{th}$ quantile of the standardized residual of $\varepsilon$. This model is identified under the following conditions:
+This model is identified under the following conditions:
 
@@
 
-## Estimation of the variance-covariance matrix
+For simplicity, the rest of the appendix uses $q^\varepsilon_\tau$ to represent $q(\varepsilon | \tau)$.
 
-In this model, to estimate the variance-covariance matrix the set of coefficients $\theta'=[\beta' \ \gamma' \ q^\varepsilon_\tau]$, we need to obtain the influence functions of all coefficients, which are defined as:
+## Estimation of the Variance-Covariance Matrix
+
+In this model, to estimate the variance-covariance matrix the set of coefficients $\theta'=[\beta' \ \gamma' \ q^\varepsilon_\tau]$, we need to obtain the influence functions of all coefficients, which are defined as
 
@@
 
-where the Jacobian matrix $\bar G(\theta)$ is defined as:
+where the Jacobian matrix $\bar G(\theta)$ is defined as
 
@@
 
-**First Moment Condition: Location Model**
+First Moment Condition: Location Model
 
@@
 
-**Second Moment Condition: Scale model**
+Second Moment Condition: Scale model
 
@@
 
-Under the assumption $\varepsilon_i \times x\gamma$, or in this case $y_i-x_i'\beta$, is uncorrelated with $x$, we can simplify the expression as:
+Under the assumption $\varepsilon_i \times x\gamma$, or in this case $y_i-x_i'\beta$, is uncorrelated with $x$, we can simplify the expression as
 
@@
 
-**Third Moment Condition: Quantile of Standardized Residual**
+Third Moment Condition: Quantile of Standardized Residual
 
@@
 
-Because the indicator function $\mathbb{1}()$ is not differentiable, we borrow from the non-parametric literature, and approximate the indicator function with the integral of a kernel density function $I()$.
-This function $I()$, is monotonic and symetrical function around zero, with a domain over the real numbers, and a range between 0 and 1.
+Because the indicator function $\mathbb{1}()$ is not differentiable, we borrow from the nonparametric literature and approximate the indicator function with the integral of a kernel density function $I()$.
+This function, $I()$, is a monotonic and symmetrical function around 0, with a domain over the real numbers, and a range between 0 and 1.
 
@@
 
-Thus the function $h_{3,i}$ can be approximated as:
+Thus the function $h_{3,i}$ can be approximated as
 
@@
 
-Under the assumption that we have enough observations within each combination of $x$, and of multiplicative heteroskedasticity, we have:
+Under the assumption that we have enough observations within each combination of $x$ that are of multiplicative heteroskedasticity, we have
 
@@
 
-where $f_{y|X}$ is the conditional probability density function of $y$ given $X$, and $f_\varepsilon$ is the unconditional distribution of the standardized error.
-With this, we can rewrite the Jacobian matrix as:
+where $f_{y|X}$ is the conditional probability density function of $y$ given $X$ and $f_\varepsilon$ is the unconditional distribution of the standardized error.
+With this, we can rewrite the Jacobian matrix as
 
@@
 
-Asymptotically, however, the expression $\sum\frac{a_i}{b_i}$ can be approximated using taylor expansions by $N\frac{\bar a}{\bar b}$. [^11] Thus, we can rewrite the last term as:
+Asymptotically, however, the expression $\sum\frac{a_i}{b_i}$ can be approximated using Taylor expansions by $N\frac{\bar a}{\bar b}$. [^11] Thus, we can rewrite the last term as
 
@@
 
-and the Jacobian for the third matrix $\bar G_{3,3}$ is:
+and the Jacobian for the third matrix $\bar G_{3,3}$ is
 
@@
 
-## Influence functions
+## Influence Functions
 
-**Location coefficients**
+Location Coefficients
 
@@
 
-Which can also be written as a function of the standardized residuals:
+which can also be written as a function of the standardized residuals:
 
@@
 
-**Scale Coefficients**
+Scale Coefficients
 
@@
 
-And $$\begin{aligned}
+and
+
+$$\begin{aligned}
 E[sign(\nu_i)] &= E[\mathbb{1}(\nu_i \geq 0)] - E[\mathbb{1}(\nu_i < 0)] \\
@@
 This last expression is the equivalent simplification used in @mss2019 and @im2000.
-If the scale function is strictly possitive, it also follows that $\mathbb{1}(\nu_i \geq 0)= \mathbb{1}(\varepsilon_i \geq 0)$.
-Thus, it can be simplified as:
+If the scale function is strictly positive, it also follows that $\mathbb{1}(\nu_i \geq 0)= \mathbb{1}(\varepsilon_i \geq 0)$.
+Thus, it can be simplified as
 
@@
 
-**Quantile of standardized residual**
+Quantile of Standardized Residual
 
@@
 
-The method described here can be implemented using any of the following packages
+The method described here can be implemented using any of the following packages:
 
 -   `mmqreg` in Stata: \`net install mmqreg, from(https://friosavila.github.io/stpackages)
--   `mmqreg` in R: Program Available in mmqreg repository in GitHub (https://github.com/friosavila/mmqreg)
+-   `mmqreg` in R: Program available in mmqreg repository on GitHub (https://github.com/friosavila/mmqreg)
 -   `mmqreg` in Python:
--   `mmqreg` in julia:
+-   `mmqreg` in Julia:

### 2023-11-13 article/article.tex
s
s

--- 2023-11-10 article/article.tex
@@
 \begin{frontmatter}
-\title{Estimating Quantile Regressions with Multiple Fixed Effects through Method of Moments}
-\fnref{fn1}
-
+\title{Quantile Regressions via Method of Moments with multiple fixed
+effects \tnoteref{t1}}
 \author[1]{Fernando Rios-Avila%
@@
  \ead{friosavi@levy.org} 
-
 \author[2]{Leonardo Siles%
@@
 
-\fntext[fn1]{The opinions expressed in this paper are those of the
-authors and do not necessarily reflect the views of the World Bank, its
-Board of Directors, or the countries it represents.}
-
 \begin{abstract}
 This paper proposes a new method to estimate quantile regressions with
-multiple fixed effects. The method, which expands on the strategy proposed by
-\citet{mss2019}, allows for the inclusion of multiple fixed effects and provides
-various alternatives for the estimation of standard errors. We provide
-Monte Carlo simulations to show the finite sample properties of the
-proposed method in the presence of two sets of fixed effects. Finally,
-we apply the proposed method to estimate the determinants of the surplus
-of government as a share of GDP, allowing for both time and country fixed
-effects.
+multiple fixed effects. The method, which expands on the strategy
+proposed by \citet{mss2019}, allows for the inclusion of multiple fixed
+effects and provides various alternatives for the estimation of standard
+errors. We provide Monte Carlo simulations to show the finite sample
+properties of the proposed method in the presence of two sets of fixed
+effects. Finally, we apply the proposed method to estimate the
+determinants of the surplus of government as a share of GDP, allowing
+for both time and country fixed effects.
 \end{abstract}
@@
 \begin{keyword}
-    Fixed Effects \sep Linear Heteroskedasticity \sep Location-Scale Model \sep Quantile Regression
+    Fixed effects \sep Linear heteroskedasticity \sep Location-scale
+model \sep 
+    Quantile regression
 \end{keyword}
-
 \end{frontmatter}
-    \ifdefined\Shaded\renewenvironment{Shaded}{\begin{tcolorbox}[interior hidden, borderline west={3pt}{0pt}{shadecolor}, boxrule=0pt, sharp corners, enhanced, breakable, frame hidden]}{\end{tcolorbox}}\fi
+    \ifdefined\Shaded\renewenvironment{Shaded}{\begin{tcolorbox}[borderline west={3pt}{0pt}{shadecolor}, breakable, frame hidden, interior hidden, enhanced, boxrule=0pt, sharp corners]}{\end{tcolorbox}}\fi
 
@@
 estimation strategy used for modeling the relationships between
-explanatory variables \(X\) and the conditional quantiles of the dependent
-variable \(q_\tau (y|x)\). Using QR one can obtain richer
+explanatory variables X and the conditional quantiles of the dependent
+variable \(Q_y (\tau|x)\). Using QR one can obtain richer
 characterizations of the relationships between dependent and independent
-variables by accounting for otherwise unobserved heterogeneity.
+variables, by accounting for otherwise unobserved heterogeneity.
 
@@
 effects in the framework of panel data. However, as described in
-\citet{neymanscott1948} and \citet{lancaster2000}, when individual
-fixed effects are included in quantile regression analysis an incidental parameter problem is generated. While many strategies have been
-proposed for estimating this type of model (see
-\citet{galvao2017quantile} for a brief review), neither has become
-standard because of their restrictive assumptions in regard to the inclusion of 
-individual and multiple fixed effects, the computational complexity, and implementation.
+\citet{neymanscott1948}, and \citet{lancaster2000}, when individual
+fixed effects are included in quantile regression analysis an incidental
+parameter problem is generated. While many strategies have been proposed
+for estimating this type of model (see \citet{galvao2017quantile} for a
+brief review), neither has become standard because of their restrictive
+assumptions in regard to the inclusion of individual and multiple fixed
+effects, the computational complexity, and implementation.
 
 More recently, \citet{mss2019} (MSS hereafter) proposed a methodology
-based on a conditional location-scale model, similar to the one described
-in \citet{he1997} and \citet{zhao2000}, for the estimation of quantile
-regressions models for panel data via a method of moments. This method
-allows individual fixed effects to have heterogeneous effects
-on the entire conditional distribution of the outcome, rather than
+based on a conditional location-scale model, similar to the one
+described in \citet{he1997} and \citet{zhao2000}, for the estimation of
+quantile regressions models for panel data via a method of moments. This
+method allows individual fixed effects to have heterogeneous effects on
+the entire conditional distribution of the outcome, rather than
 constraining their effect to be a location shift only, as in
-\citet{canay2011}, \citet{koenker2004}, and \citet{lancaster2000}.
-
-In principle, under the assumption that the data-generating process behind
+\citet{canay2011}, \citet{koenker2004}, and \citet{lamarche2010}.
+
+In principle, under the assumption that data-generating process behind
 the data is based on a multiplicative heteroskedastic process that is
-linear in parameters \citep[\citet{mss2019}, \citet{he1997},
-\citet{zhao2000}, \citet{cameron2005}], the effect of a variable \(X\) on the
+linear in parameters \citep[\citet{he1997}, \citet{zhao2000},
+\citet{cameron2005}]{mss2019}, the effect of a variable \(X\) on the
 \(q_{th}\) quantile can be derived as the combination of a location
-effect and a scale effect moderated by the quantile of an underlying
-independent and identically distributed (i.i.d.) error. For statistical inference, MSS derives the asymptotic distribution of the estimator, suggesting the use of bootstrap standard errors as well.
+effect, and scale effect moderated by the quantile of an underlying
+i.i.d. error. For statistical inference, MSS derives the asymptotic
+distribution of the estimator, suggesting the use of bootstrap standard
+errors, as well.
 
 This methodology is not meant to substitute for the use of standard
-quantile regression analysis. That said, given the assumptions required for the
-identification of the model, it provides a simple and fast alternative
-for the estimation of quantile regression models with individual fixed
-effects.
+quantile regression analysis. That said, given the assumptions required
+for the identification of the model, it provides a simple and fast
+alternative for the estimation of quantile regression models with
+individual fixed effects.
 
@@
 of the suggestions by these authors regarding further research. First,
-making use of the properties of generalized method of moments (GMM) estimators, we derive various
-alternatives for the estimation of standard errors based on the
-empirical influence functions of the estimators. Second, we reconsider
-the application of Frisch-Waugh-Lovell (FWL) theorem
-(\citet{frishwaugh1933} and \citet{lovell1963}) to extend the MSS
-estimator to allow for the inclusion of multiple fixed effects, such as individual and year fixed effects.
+making use of the properties of generalized method of moments (GMM)
+estimators, we derive various alternatives for the estimation of
+standard errors based on the empirical influence functions of the
+estimators. Second, we reconsider the application of Frisch-Waugh-Lovell
+(FWL) theorem \citep[ and \citet{lovell1963}]{frishwaugh1933} to extend
+the MSS estimator to allow for the inclusion of multiple fixed effects,
+for example, individual and year fixed effects.
 
@@
 regression model and the location-scale model. It also revisits the
-methodology of MSS, proposing alternative estimators for the standard errors
-based on the properties of GMM estimators and the empirical influence
-functions. It also shows that the FWL theorem can be used to control for
-multiple fixed effects. Section 3 presents the results of a small
-simulation study and section 4 illustrates the application of the
+methodology of MSS, proposing alternative estimators for the standard
+errors based on the properties of GMM estimators and the empirical
+influence functions. It also shows that the FWL theorem can be used to
+control for multiple fixed effects. Section 3 presents the results of a
+small simulation study and section 4 illustrates the application of the
 proposed methods with two empirical examples. Section 5 concludes.
@@
 \hypertarget{sec-betas}{%
-\subsection{Quantile Regression: Location-Scale Model}\label{sec-betas}}
+\subsection{Quantile Regression: Location-Scale model}\label{sec-betas}}
 
@@
 explanatory variables \(X\) and the conditional quantiles of the
-dependent variable \(Q(Y|\tau,X)\). This relationship is commonly
+dependent variable \(Q_y(\tau|X)\). This relationship is commonly
 assumed to follow a linear functional form:
 
-\begin{equation}\protect\hypertarget{eq-eq1}{}{q(Y|X,\tau) =X\beta(\tau)
-}\label{eq-eq1}\end{equation}.
+\begin{equation}\protect\hypertarget{eq-eq1}{}{Q_y(\tau|X) =X\beta(\tau)
+}\label{eq-eq1}\end{equation}
 
@@
 
-\begin{equation}\protect\hypertarget{eq-eq2}{}{q(Y|X,\tau) =X\beta+X\gamma(\tau)
-}\label{eq-eq2}\end{equation}.
+\begin{equation}\protect\hypertarget{eq-eq2}{}{Q_y(\tau|X) =X\beta+X\gamma(\tau)
+}\label{eq-eq2}\end{equation}
 
@@
 linear regression model (as in \citet{mss2019}) or a median regression
-(as in \citet{melly2005}) and the scale parameters \(\gamma(\tau)\) can
+(as in \citet{zhao2000}) and the scale parameters \(\gamma(\tau)\) can
 be estimated using standard approaches.
@@
 \left( \sum_{i\in y_i\geq x_i'\beta} \tau (y_i - x_i'\beta) - \sum_{i\in y_i<x_i'\beta} (1-\tau)(y_i - x_i'\beta) \right)
-}\label{eq-eq3}\end{equation}.
+}\label{eq-eq3}\end{equation}
 
@@
 \end{aligned}
-}\label{eq-eq4}\end{equation}.
-
-Under the assumption that \(\varepsilon\) is an i.i.d. unobserved random variable that is
-independent of \(X\), the conditional quantile of \(Y\) given \(X\) and
-\(\tau\) can be written as
-
-\begin{equation}\protect\hypertarget{eq-eq5}{}{q(Y|X,\tau) =X\beta+q(\varepsilon|\tau) \times X\gamma 
-}\label{eq-eq5}\end{equation}.
+}\label{eq-eq4}\end{equation}
+
+Under the assumption that \(\varepsilon\) is an i.i.d. unobserved random
+variable that is independent of \(X\), the conditional quantile of \(Y\)
+given \(X\) and \(\tau\) can be written as
+
+\begin{equation}\protect\hypertarget{eq-eq5}{}{Q_y(\tau|X) =X\beta+Q_\varepsilon(\tau) \times X\gamma 
+}\label{eq-eq5}\end{equation}
 
@@
 moderated by the \(\tau_{th}\) unconditional quantile of the
-standardized error \(\varepsilon\).
-
-\begin{equation}\protect\hypertarget{eq-eq6}{}{\beta(\tau) = \beta + q(\varepsilon|\tau) \times \gamma 
-}\label{eq-eq6}\end{equation}.
+standardized error \(\varepsilon\). For simplicity we will use
+\(q(\tau)\) to denote \(Q_\varepsilon(\tau)\) in the rest of the paper.
+
+\begin{equation}\protect\hypertarget{eq-eq6}{}{\beta(\tau) = \beta + q(\tau) \times \gamma 
+}\label{eq-eq6}\end{equation}
 
@@
 two advantages over the standard quantile regression model. First,
-because the location -scale model can be identified globally, with
-only a single parameter (\(q(\varepsilon|\tau)\)) requiring local
-estimation, this estimation approach will be more efficient than the
-standard quantile regression model (\citet{zhao2000}). Second, under the
-assumption that \(X\gamma\) is strictly positive, the model will
-produce quantile coefficients that do not cross.
+because the location-scale model can be identified globally, with only a
+single parameter (\(q(\tau)\)) requiring local estimation, this
+estimation approach will be more efficient than the standard quantile
+regression model (\citet{zhao2000}). Second, under the assumption that
+\(X\gamma\) is strictly positive, the model will produce quantile
+coefficients that do not cross.
 
 Following MSS, the quantile regression model defined by
-Equation~\ref{eq-eq5} can be estimated using a generalized method of moments
-approach. And while it is possible to identify all coefficients
-(\(\beta,\gamma, q(\varepsilon|\tau)\)) simultaneously, we describe and
-use the implementation approach advocated by MSS, which identifies each
-set of coefficients separately.
+Equation~\ref{eq-eq5} can be estimated using a generalized method of
+moments approach. And while it is possible to identify all coefficients
+(\(\beta,\gamma, q(\tau)\)) simultaneously, we describe and use the
+implementation approach advocated by MSS, which identifies each set of
+coefficients separately.
 
 First, the location model can be estimated using a standard linear
-regression model where the dependent variable is the outcome \(Y\) and
+regression model, where the dependent variable is the outcome \(Y\) and
 the independent variables are the explanatory variables \(X\) (including
@@
       \end{aligned}
-}\label{eq-eq7}\end{equation}.
+}\label{eq-eq7}\end{equation}
 
@@
 characteristics \(X\). For this we use the absolute value of the errors
-from the location model \(u\) as dependent variable, which allows
-us to estimate the conditional standard deviation (rather than
-conditional variance) of the errors. In this case, the coefficients are
-identified under the following condition:
+from the location model \(u\) as dependent variable, which allows us to
+estimate the conditional standard deviation (rather than conditional
+variance) of the errors. In this case, the coefficients are identified
+under the following condition:
 
@@
   |\nu_i| &=x_i'\gamma+\omega_i \\
-  E\big[ x_i \omega_i \big] &=0 \\
    E\big[ x_i (|\nu_i| -x_i'\gamma ) \big] &=0
   \end{aligned}
-}\label{eq-eq8}\end{equation}.
+}\label{eq-eq8}\end{equation}
 
@@
 \begin{equation}\protect\hypertarget{eq-eq9}{}{\begin{aligned}
-  E\left[  \mathbb{1}\left(x_i' (\beta + \gamma q(\varepsilon|\tau)) \geq y_i \right) - \tau \right] &=0  \\
-  E\left[  \mathbb{1}\left(   q(\varepsilon|\tau)\geq \frac{y_i-x_i'\beta}{x_i'\gamma} \right) - \tau \right] &=0  \\
-  \end{aligned}
-}\label{eq-eq9}\end{equation},
+  E\left[  \mathbb{1}\left(x_i' (\beta +   \gamma q(\tau)) \geq y_i \right) - \tau \right] &=0  \\
+  E\left[  \mathbb{1}\left(   q(\tau) \geq \frac{y_i-x_i'\beta}{x_i'\gamma} \right) - \tau \right] &=0  \\
+  \end{aligned}
+}\label{eq-eq9}\end{equation}
 
@@
 the values that identify the overall quantile coefficients
-\(\beta(\tau)=\beta + \gamma q(\varepsilon|\tau)\). Afterwards, the
-conditional quantile coefficients are simply defined as the combination
-of the location and scale coefficients.
+\(\beta(\tau)=\beta + \gamma q(\tau)\). Afterwards, the conditional
+quantile coefficients are simply defined as the combination of the
+location and scale coefficients.
 
 \hypertarget{sec-se}{%
-\subsection{Standard Errors: GLS, Robust, and Clustered}\label{sec-se}}
+\subsection{Standard Errors: GLS, Robust, Clustered}\label{sec-se}}
 
@@
 regression coefficients using the location-scale model with
-heteroskedastic linear errors can be estimated using the following set
+heteroskedastic linear errors can be estimated using a the following set
 of moments, which fits within the GMM framework:
@@
 are asymptotically normal.\footnote{\citet{zhao2000} also shows that the
-  quantile coefficients for the location-scale model follow a
-  normal distribution, but uses the assumption that the location model
-  is derived using a least absolute deviation approach (median
-  regression).}
-
-Call \(\theta=[ \beta' \ \ \gamma' \ \ q(\varepsilon|\tau)' ]'\) the set
-of coefficients that are identified by the moment conditions in
+  quantile coefficients for the location-scale model follow a normal
+  distribution, but uses the assumption that the location model is
+  derived using a least absolute deviation approach (median regression).}
+
+Call \(\theta=[ \beta' \ \ \gamma' \ \ q(\tau) ]'\) the set of
+coefficients that are identified by the moment conditions in
 Equation~\ref{eq-eq10}, a just identified model, and the function
-\(h_i\) is a vector function that stacks all the moments described in Equation~\ref{eq-eq10} at the individual level. Then
-\(\hat\theta\) follows a normal distribution with mean \(\theta\) and
+\(h_i\) is a vector function that stacks all the moments described in
+Equation~\ref{eq-eq10} at the individual level. Then \(\hat\theta\)
+follows a normal distribution with mean \(\theta\) and
 variance-covariance matrix \(V(\theta)\) that is estimated as
@@
 \bar G(\hat\theta)^{-1} 
-\],
+\]
 
@@
 of the location-scale-quantile estimates, will follow a normal
-distribution with mean \(\beta(\tau) = \beta+q(\varepsilon|\tau)\gamma\)
-and variance-covariance matrix equal to
+distribution with mean
+\(\beta(\tau) = \beta+\gamma q(\varepsilon | \tau)\) and
+variance-covariance matrix equal to
 
 \[\hat{V}(\beta(\tau)) = \Xi \hat{V}(\hat\theta) \Xi'
-\],
+\]
 
@@
 
-\begin{equation}\protect\hypertarget{eq-eqqtile}{}{\Xi = [ I(k), \hat q(\varepsilon|\tau) \times I(k), \hat \gamma ]
-}\label{eq-eqqtile}\end{equation},
+\begin{equation}\protect\hypertarget{eq-eqqtile}{}{\Xi = [ I(k), \hat q(\tau) \times I(k), \hat \gamma ]
+}\label{eq-eqqtile}\end{equation}
 
@@
 \begin{equation}\protect\hypertarget{eq-eqvcv}{}{\hat{V}(\theta) = \frac{1}{N^2} \sum_{i=1}^N \lambda_i(\theta) \lambda_i(\theta)'
-}\label{eq-eqvcv}\end{equation},
-
-where the influence functions are defined as
-
-\[\lambda_i(\theta) = \bar G(\theta)^{-1} h_i(\theta)\].
+}\label{eq-eqvcv}\end{equation}
+
+where the influence functions are defined as:
+
+\[\lambda_i(\theta) = \bar G(\theta)^{-1} h_i(\theta)\]
 
@@
 \lambda_{i}(\gamma)&= N(X'X)^{-1} x_i ( x_i' \gamma ) \times (\tilde \varepsilon_i -1\big)\\
-\lambda_{i}(q(\varepsilon|\tau))&=\frac{\tau-\mathbb{1}\big( q(\varepsilon|\tau)  \geq \varepsilon_i  \big) }{f_{\varepsilon}(q(\varepsilon|\tau))}
+\lambda_{i}(q(\tau))&=\frac{\tau-\mathbb{1}\big( q(\tau)  \geq \varepsilon_i  \big) }{f_{\varepsilon}(q(\tau))}
 - \frac{ x_i'\gamma \times \varepsilon_i }{\bar x_i'\gamma} 
--  q(\varepsilon|\tau) \frac{  x_i' \gamma  \times (\tilde \varepsilon_i -1\big)}{\bar x_i'\gamma}
-\end{aligned}
-}\label{eq-ifs}\end{equation}.
+-  q(\tau) \frac{  x_i' \gamma  \times (\tilde \varepsilon_i -1\big)}{\bar x_i'\gamma}
+\end{aligned}
+}\label{eq-ifs}\end{equation}
 
@@
 
-The first and most natural standard error estimator is given by
-equation Equation~\ref{eq-eqvcv}. This is equivalent to the Eicker-White
+The first and most natural standard error estimator is given by equation
+Equation~\ref{eq-eqvcv}. This is equivalent to the Eicker-White
 heteroskedasticity-consistent estimator for least-squares estimators.
@@
  \begin{pmatrix}
- \sum \lambda_i(\beta) \lambda_i(\beta)' & \sum \lambda_i(\beta) \lambda_i(\gamma)' & \sum \lambda_i(\beta) \lambda_i(q(\varepsilon|\tau))' \\
- \sum \lambda_i(\gamma) \lambda_i(\beta)' & \sum \lambda_i(\gamma) \lambda_i(\gamma)' & \sum \lambda_i(\gamma) \lambda_i(q(\varepsilon|\tau))' \\
- \sum \lambda_i(q(\varepsilon|\tau) \lambda_i(\beta)' & \sum \lambda_i(q(\varepsilon|\tau))\lambda_i(\gamma)' & \sum \lambda_i(q(\varepsilon|\tau)) \lambda_i(q(\varepsilon|\tau))' 
+ \sum \lambda_i(\beta) \lambda_i(\beta)' & \sum \lambda_i(\beta) \lambda_i(\gamma)' & \sum \lambda_i(\beta) \lambda_i(q(\tau))' \\
+ \sum \lambda_i(\gamma) \lambda_i(\beta)' & \sum \lambda_i(\gamma) \lambda_i(\gamma)' & \sum \lambda_i(\gamma) \lambda_i(q(\tau))' \\
+ \sum \lambda_i(q(\tau)) \lambda_i(\beta)' & \sum \lambda_i(q(\tau))\lambda_i(\gamma)' & \sum \lambda_i(q(\tau)) \lambda_i(q(\tau))' 
   \end{pmatrix}
-\].
+\]
 
@@
 individual level is important. If the unobserved error \(\varepsilon\)
-is correlated within clusters, generalized least squares (GLS) standard errors could be severely
-biased. The standard recommendation has been to report block-bootstrap
-standard errors, clustered at the individual level.
+is correlated within clusters, generalized least squares (GLS) standard
+errors could be severely biased. The standard recommendation has been to
+report block-bootstrap standard errors, clustered at the individual
+level.
 
@@
 
-Let \(N_G\) be the total number of clusters $g$, where
+Let \(N_G\) be the total number of clusters \(g\), where
 \(g=1\dots N_G\). The clustered variance covariance matrix is given
@@
   \end{pmatrix}
-\],
+\]
 
@@
 The standard errors proposed by MSS can be understood as an application
-of GLS, which will be valid as long as the
-model for heteroskedasticity is correctly specified.\footnote{As
-  discussed in most econometric textbooks, for example \citet{cameron2005}, one
-  approach to correct for heteroskedasticity, when the
-  heteroskedasticity functional form is known or can be estimated, is
-  to use weighted least squares. While feasible, this approach
-  would defeat the purpose of identifying quantile effects exploiting
-  the heteroskedasticity of the model.} To estimate the GLS standard
-errors, we make use of the following property:
+of GLS, which will be valid as long as the model for heteroskedasticity
+is correctly specified.\footnote{As discussed in most econometric
+  textbooks, for example \citet{cameron2005}, one approach to correct
+  for heteroskedasticity, when the heteroskedasticity functional form is
+  known or can be estimated, is to use weighted least squares. While
+  feasible this approach would defeat the purpose of identifying
+  quantile effects exploiting the heteroskedasticity of the model.} To
+estimate the GLS standard errors, we make use of the following property:
 
@@
 \end{aligned}
-\].
+\]
 
@@
 \tilde \lambda_{3,i}&=x_i' \gamma  \\
-\tilde \psi_1 &= \varepsilon_i \\
-\tilde \psi_2 &= \tilde \varepsilon_i -1 \\
-\tilde \psi_3 &= \frac{1}{ x_i' \gamma }\frac{\tau-\mathbb{1}\big( q(\varepsilon|\tau)  \geq \varepsilon_i  \big) }{ f_{\varepsilon}(q(\varepsilon|\tau))} - \frac{\varepsilon_i }{\bar x_i'\gamma} 
--  q(\varepsilon|\tau) \frac{(\tilde \varepsilon_i -1\big)}{\bar x_i'\gamma}
-\end{aligned}
-\].
+ \psi_{i,1} &= \varepsilon_i \\
+ \psi_{i,2} &= \tilde \varepsilon_i -1 \\
+ \psi_{i,3} &= \frac{1}{ x_i' \gamma }\frac{\tau-\mathbb{1}\big( q(\tau)  \geq \varepsilon_i  \big) }{ f_{\varepsilon}(q(\tau))} - \frac{\varepsilon_i }{\bar x_i'\gamma} 
+-  q(\tau) \frac{(\tilde \varepsilon_i -1\big)}{\bar x_i'\gamma}
+\end{aligned}
+\]
 
@@
 \[\begin{aligned}
-\hat\Omega_{ij} &= \frac{1}{N} \sum_i^N \tilde \lambda_{i}(\theta) \tilde \lambda_{j}(\theta)' \\
-\hat\sigma_{ij} &= \frac{1}{N} \sum_i^N \phi_{i} \phi_{j}
-\end{aligned}
-\].
-
-This estimator of standard errors is equivalent to the one derived by
+\hat\Omega_{jk} &= \frac{1}{N} \sum_{i=1}^N \tilde \lambda_{i,j}(\theta) \tilde \lambda_{i,k}(\theta)' \\
+\hat\sigma_{jk} &= \frac{1}{N} \sum_{i=1}^N \psi_{i,j} \psi_{i,k}
+\end{aligned}
+\]
+
+This estimator of stand ard errors is equivalent to the one derived by
 MSS using Theorem 3.
@@
 Using the setup described in the previous section, \citet{mss2019}
-proposes an extension to the model proposed by \citet{he1997} that enables the estimation of quantile regression models with panel data while
-allowing for the inclusion of individual fixed effects. Moreover, as the
+proposes an extension to the model proposed by \citet{he1997} that
+enables the estimation of quantile regression models with panel data,
+allowing for the inclusion of individual fixed effects. However, as the
 authors suggest, the methodology can be generalized to allow for the
@@
 
-We return to the original model and now assume there are sets of unobserved
-heterogeneity that are assumed to be constant across observations, if
-they belong to common groups. In panel data, the groups would be the
-individual fixed effects and the time fixed effects. Without loss of
-generality, we can assume that the data-generating process is as
-follows:
+We return to the original model and now assume there are sets of
+unobserved heterogeneity that are assumed to be constant across
+observations, if they belong to common groups. In panel data, the groups
+would be the individual fixed effects and the time fixed effects.
+Without loss of generality, we can assume that the data-generating
+process is as follows:
 
@@
   \end{aligned}
-\],
-
-where we assume \(x_{i}\) vary across groups \(g_1\) and \(g_2\) (and thus
-are not collinear) and that \(\delta's\) and \(\zeta's\) are the
+\]
+
+where we assume \(x_{i}\) vary across groups \(g_1\) and \(g_2\) (and
+thus are not collinear) and that \(\delta's\) and \(\zeta's\) are the
 location and scale effects associated with groups fixed
@@
 If the dimension of groups \(g_k\) is low, this model could be estimated
-using a dummy inclusion approach following section~\ref{sec-betas} and
-the standard errors obtained as discussed in section~\ref{sec-se}. However,
-if the dimensionality of \(g_k\) is high, the dummy inclusion approach
-may not be feasible. A more feasible approach is to apply the
-FWL theorem and partial out the impact of the
-group fixed effects on the control variables \(x_{i}\), and the outcome of
-interest \(y_{i}\), using a similar approach for the identification of
-\(\sigma(x)\). In the case of unbalanced setups with multiple groups,
-the estimation involves iterative processes for which various approaches
-have been suggested and implemented (see for example
-\citet{correia_feasible_nodate}, \citet{gaure2013}, \citet{rios2015}
-).
+using a dummy inclusion approach following Section~\ref{sec-betas}, and
+the standard errors obtained as discussed in Section~\ref{sec-se}.
+However, if the dimensionality of \(g_k\) is high, the dummy inclusion
+approach may not be feasible. A more feasible approach is to apply the
+FWL theorem and partial out the impact of the group fixed effects on the
+control variables \(x_{i}\), and the outcome of interest \(y_{i}\),
+using a similar approach for the identification of \(\sigma(x)\). In the
+case of unbalanced setups with multiple groups, the estimation involves
+iterative processes for which various approaches have been suggested and
+implemented (see for example, \citet{correia_feasible_nodate},
+\citet{gaure2013}, \citet{rios2015}, among others).
 
 When applying the partialing-out approach, some modifications to the
-approach described in section~\ref{sec-betas} are needed.
+approach described in Section~\ref{sec-betas} are needed.
 
@@
   which simplifies the derivation of the influence functions. However,
-  as with other fixed effects models, the constant is not identified
-  and thus should not be interpreted.}
+  as with other fixed effects models, the constant is not identified and
+  thus should not be interpreted.}
 
 \[y_{i}^{rc} = x_{i}^{rc'} \beta + \nu_{i}
-\].
-
-Because \(|\hat \nu_i|\) is the dependent variable for the scale model, we
-apply the partialing out and recentering to this expression
+\]
+
+Because \(|\hat \nu_i|\) is the dependent variable for the scale model,
+we apply the partialing out and recentering to this expression
 (\(|\hat \nu_i|^{rc}\)), and use that to estimate the following model:
 
-\[|\hat\nu_{i}|^{rc} = x_{i}^{rc'} \gamma + \omega_{i}\].
+\[|\hat\nu_{i}|^{rc} = x_{i}^{rc'} \gamma + \omega_{i}\]
 
@@
 
-\[\hat{\varepsilon}_{i} = \frac{\nu_{i}}{|\hat\nu_{i}|- \hat \omega_{i}}\],
+\[\hat{\varepsilon}_{i} = \frac{\nu_{i}}{|\hat\nu_{i}|- \hat \omega_{i}}\]
 
@@
 conditional standard deviation
-\(\sigma(x_i)=x_{i}' \gamma + \zeta_{g1} + \zeta_{g2}\).
+\(\sigma(x_i)=x_{i}' \gamma + \zeta_{g1} + \zeta_{g2}\)
 
@@
 as usual and the variance-covariance matrices obtained in the same way
-as before (see section~\ref{sec-se}) by using \(x_{i}^{rc}\) instead
-of \(x_{i}\) when estimating the influence functions for all estimated
+as before (see Section~\ref{sec-se}) by using \(x_{i}^{rc}\) instead of
+\(x_{i}\) when estimating the influence functions for all estimated
 coefficients.
@@
 \[y_i = \alpha_{1i} + \alpha_{2i} + x_i + (1+x_i + \alpha_{1i} + \alpha_{2i} ) \varepsilon_i
-\],
+\]
 
@@
 \(\chi_i \sim \chi^2(1)\). We only consider the case when the error term
-\(\varepsilon_i\) is assumed to be normally distributed with mean 0
-and standard deviation of 0.5. We assume that there are 50 mutually
+\(\varepsilon_i\) is assumed to be normally distributed with mean 0 and
+standard deviation of 0.5. We assume that there are 50 mutually
 exclusive fixed effect groups for each set of fixed effects.
@@
 the coefficients for the 25th and 75th quantiles. We run this excercise
-5000 times. ?@tbl-sim1 reports the bias, simulated standard
+5000 times. Table~\ref{tbl-sim1} reports the bias, simulated standard
 error, and mean squared error. We also report the results obtained using
@@
 jackknife estimator proposed by \citet{dhaene2015}.\footnote{For the
-  implementation, we first estimate the model using the full sample, then
-  randomly assign each observation into one of two groups, and finally
-  reestimate the quantile coefficients for each group. The
+  implementation, we first estimate the model using the full sample,
+  then randomly assign each observation into one of two groups, and
+  finally reestimate the quantile coefficients for each group. The
   bias-corrected estimator is then obtained as
@@
 
-Similar to the findings in MSS, we find that while the estimator presents a
-bias when the sample is small (\(N=500\)), this bias shrinks as the
-sample size increases. As MSS describes, the bias seems to be
+Similar to the findings in MSS, we find that while the estimator
+presents a bias when the sample is small (\(N=500\)), this bias shrinks
+as the sample size increases. As MSS describes, the bias seems to be
 proportional to the sample size, or more precisely to \(N/N_{g1}\) and
@@
 presents an almost 0 bias, even when the samples are small (about 10
-observations per subgroup).
-Moreover, we find that despite the bias reduction obtained using the JKC estimator, the standard errors and mean squared error (MSE) are larger than without correction, which also replicates the results of MSS,
-
-\begin{table}
-
-\caption{Bias, Simulated Standard Error, and MSE}\begin{minipage}[t]{0.50\linewidth}
-
-{\centering
-
-\begin{longtable}[]{@{}lccc@{}}
+observations per subgroup). Moreover, we find that despite the bias
+reduction obtained using the JKC estimator, the standard errors and mean
+squared error (MSE) are larger than without correction, which also
+replicates the results of MSS,
+
+\hypertarget{tbl-sim1}{}
+\begin{longtable}[]{@{}
+  >{\raggedright\arraybackslash}p{(\columnwidth - 14\tabcolsep) * \real{0.1250}}
+  >{\centering\arraybackslash}p{(\columnwidth - 14\tabcolsep) * \real{0.1250}}
+  >{\centering\arraybackslash}p{(\columnwidth - 14\tabcolsep) * \real{0.1250}}
+  >{\centering\arraybackslash}p{(\columnwidth - 14\tabcolsep) * \real{0.1250}}
+  >{\raggedright\arraybackslash}p{(\columnwidth - 14\tabcolsep) * \real{0.1250}}
+  >{\centering\arraybackslash}p{(\columnwidth - 14\tabcolsep) * \real{0.1250}}
+  >{\centering\arraybackslash}p{(\columnwidth - 14\tabcolsep) * \real{0.1250}}
+  >{\centering\arraybackslash}p{(\columnwidth - 14\tabcolsep) * \real{0.1250}}@{}}
+\caption{\label{tbl-sim1}Bias, Simulated Standard error, and Mean
+Squared Error}\tabularnewline
 \toprule\noalign{}
-N = 500 & Bias & Sim SE & MSE \\
+\begin{minipage}[b]{\linewidth}\raggedright
+N = 500
+\end{minipage} & \begin{minipage}[b]{\linewidth}\centering
+Bias
+\end{minipage} & \begin{minipage}[b]{\linewidth}\centering
+Sim SE
+\end{minipage} & \begin{minipage}[b]{\linewidth}\centering
+MSE
+\end{minipage} & \begin{minipage}[b]{\linewidth}\raggedright
+N = 1000
+\end{minipage} & \begin{minipage}[b]{\linewidth}\centering
+Bias
+\end{minipage} & \begin{minipage}[b]{\linewidth}\centering
+Sim SE
+\end{minipage} & \begin{minipage}[b]{\linewidth}\centering
+MSE
+\end{minipage} \\
+\midrule\noalign{}
+\endfirsthead
+\toprule\noalign{}
+\begin{minipage}[b]{\linewidth}\raggedright
+N = 500
+\end{minipage} & \begin{minipage}[b]{\linewidth}\centering
+Bias
+\end{minipage} & \begin{minipage}[b]{\linewidth}\centering
+Sim SE
+\end{minipage} & \begin{minipage}[b]{\linewidth}\centering
+MSE
+\end{minipage} & \begin{minipage}[b]{\linewidth}\raggedright
+N = 1000
+\end{minipage} & \begin{minipage}[b]{\linewidth}\centering
+Bias
+\end{minipage} & \begin{minipage}[b]{\linewidth}\centering
+Sim SE
+\end{minipage} & \begin{minipage}[b]{\linewidth}\centering
+MSE
+\end{minipage} \\
 \midrule\noalign{}
@@
 \endlastfoot
-q25 & & & \\
-~mmqreg & 0.104 & 0.247 & 0.072 \\
-~jkc & 0.008 & 0.297 & 0.088 \\
-q75 & & & \\
-~mmqreg & -0.091 & 0.251 & 0.071 \\
-~jkc & 0.002 & 0.303 & 0.092 \\
+q25 & & & & q25 & & & \\
+~mmqreg & 0.104 & 0.247 & 0.072 & ~mmqreg & 0.050 & 0.173 & 0.032 \\
+~jkc & 0.008 & 0.297 & 0.088 & ~jkc & -0.001 & 0.191 & 0.036 \\
+q75 & & & & q75 & & & \\
+~mmqreg & -0.091 & 0.251 & 0.071 & ~mmqreg & -0.044 & 0.176 & 0.033 \\
+~jkc & 0.002 & 0.303 & 0.092 & ~jkc & 0.006 & 0.195 & 0.038 \\
+\textbf{N = 2000} & \textbf{Bias} & \textbf{Sim SE} & \textbf{MSE} &
+\textbf{N = 4000} & \textbf{Bias} & \textbf{Sim SE} & \textbf{MSE} \\
+q25 & & & & q25 & & & \\
+~mmqreg & 0.025 & 0.122 & 0.016 & ~mmqreg & 0.012 & 0.087 & 0.008 \\
+~jkc & 0.003 & 0.129 & 0.017 & ~jkc & 0.000 & 0.089 & 0.008 \\
+q75 & & & & q75 & & & \\
+~mmqreg & -0.023 & 0.124 & 0.016 & ~mmqreg & -0.011 & 0.087 & 0.008 \\
+~jkc & 0.001 & 0.131 & 0.017 & ~jkc & 0.000 & 0.089 & 0.008 \\
 \end{longtable}
-
-}
-
-\end{minipage}%
-%
-\begin{minipage}[t]{0.50\linewidth}
-
-{\centering
-
-\begin{longtable}[]{@{}lccc@{}}
-\toprule\noalign{}
-N = 1000 & Bias & Sim SE & MSE \\
-\midrule\noalign{}
-\endhead
-\bottomrule\noalign{}
-\endlastfoot
-q25 & & & \\
-~mmqreg & 0.050 & 0.173 & 0.032 \\
-~jkc & -0.001 & 0.191 & 0.036 \\
-q75 & & & \\
-~mmqreg & -0.044 & 0.176 & 0.033 \\
-~jkc & 0.006 & 0.195 & 0.038 \\
-\end{longtable}
-
-}
-
-\end{minipage}%
-\newline
-\begin{minipage}[t]{0.50\linewidth}
-
-{\centering
-
-\begin{longtable}[]{@{}lccc@{}}
-\toprule\noalign{}
-N = 1000 & Bias & Sim SE & MSE \\
-\midrule\noalign{}
-\endhead
-\bottomrule\noalign{}
-\endlastfoot
-q25 & & & \\
-~mmqreg & 0.025 & 0.122 & 0.016 \\
-~jkc & 0.003 & 0.129 & 0.017 \\
-q75 & & & \\
-~mmqreg & -0.023 & 0.124 & 0.016 \\
-~jkc & 0.001 & 0.131 & 0.017 \\
-\end{longtable}
-
-}
-
-\end{minipage}%
-%
-\begin{minipage}[t]{0.50\linewidth}
-
-{\centering
-
-\begin{longtable}[]{@{}lccc@{}}
-\toprule\noalign{}
-N = 2000 & Bias & Sim SE & MSE \\
-\midrule\noalign{}
-\endhead
-\bottomrule\noalign{}
-\endlastfoot
-q25 & & & \\
-~mmqreg & 0.012 & 0.087 & 0.008 \\
-~jkc & 0.000 & 0.089 & 0.008 \\
-q75 & & & \\
-~mmqreg & -0.011 & 0.087 & 0.008 \\
-~jkc & 0.000 & 0.089 & 0.008 \\
-\end{longtable}
-
-}
-
-\end{minipage}%
-
-\end{table}
 
@@
 \[y_i = \alpha_{1i} + \alpha_{2i} + x_i + (1+x_i + \sqrt{x_i} +\alpha_{1i} + \alpha_{2i} ) \varepsilon_i
-\].
+\]
 
@@
 the case where the error \(\varepsilon\) is correlated within groups
-defined by the first fixed effect, specifically
-
-\[\varepsilon_i =0.5*(\sqrt{0.5} z_i + \sqrt{0.5} w_g)\],
+defined by the first fixed effect. Specifically:
+
+\[\varepsilon_i =0.5*(\sqrt{0.5} z_i + \sqrt{0.5} w_g)\]
 
@@
 
-For the simulation, we run the exercise 5000 times, using a sample of
-size \(N=2000\). The results from both simulations are reported in 
-Table~\ref{tbl-sim2}. We report the average coefficient, simulation-based standard errors, and the standard errors using GLS, robust, and
-clustered estimations.
+For the simulation, we run the excercise 5000 times, using a sample of
+size \(N=2000\). The results from both simulations are reported in the
+Table~\ref{tbl-sim2}. We report the average coefficient,
+simulation-based standard errors, and the standard errors using GLS,
+robust and clustered estimations.
 
 \hypertarget{tbl-sim2}{}
-\begin{longtable}[]{@{}
-  >{\raggedright\arraybackslash}p{(\columnwidth - 8\tabcolsep) * \real{0.2000}}
-  >{\centering\arraybackslash}p{(\columnwidth - 8\tabcolsep) * \real{0.2000}}
-  >{\centering\arraybackslash}p{(\columnwidth - 8\tabcolsep) * \real{0.2000}}
-  >{\centering\arraybackslash}p{(\columnwidth - 8\tabcolsep) * \real{0.2000}}
-  >{\centering\arraybackslash}p{(\columnwidth - 8\tabcolsep) * \real{0.2000}}@{}}
+\begin{longtable}[]{@{}lcccc@{}}
 \caption{\label{tbl-sim2}Heteroskedasticity misspecification and
@@
 in the case of misspecified heteroskedasticity. In fact, with
-heteroskedasticity misspecification, the average GLS-SE (0.476) is almost
-three times as large as the simulation-based standard error (0.154). In
-this first case, robust standard errors perform better, but with a small
-difference (0.14 to 0.154). In the case of clustered correlation, GLS-SE
-also performs poorly. Robust standard errors perform better, but seem to
-underestimate the magnitude of the true standard errors. Finally,
-cluster standard errors perform the best, with a small difference
-between the simulation-based standard errors (0.097 to 0.109).
+heteroskedasticity misspecification, the average GLS-SE (0.476) is
+almost three times as large as the simulation-based standard error
+(0.154). In this first case, robust standard errors perform better, but
+with a small difference (0.14 to 0.154). In the case of clustered
+correlation, GLS-SE also performs poorly. Robust standard errors perform
+better, but seem to underestimate the magnitude of the true standard
+errors. Finally, cluster standard errors perform the best, with a small
+difference between the simulation-based standard errors (0.097 to
+0.109).
 
 \hypertarget{illustrative-application}{%
-\section{Illustrative Application}\label{illustrative-application}}
-
-In this section we replicate one of the exercises from MSS, allowing
-for time and individual fixed effects as well as for different standard
+\section{Illustrative application}\label{illustrative-application}}
+
+In this section we replicate one of the exercises from MSS, allowing for
+time and individual fixed effects as well as for different standard
 errors estimations. We use data from \citet{persson_economic_2005}, to
-estimate the relationship between surplus of government as share of GDP
+estimate the relationship between surplus of government as share of GDP,
 and a measure of quality of democracy (POLITY); log of real income per
 capita (LYP); trade volume as share of GDP (TRADE); share of population
-between 15 and 65 years of age (P1564); the share of the population 65 years
-and older (P65); one-year lag of the dependent variable (LSP); oil prices
-in US dollars, differentiating between importer and exporter countries (OILIM and
-OILEX); and the output gap (YGAP). In addition to country fixed effects
-(as illustrated in MSS), we show results allowing for time fixed
-effects. Table~\ref{tbl-tb1} and Table~\ref{tbl-tb2} provide the results
-for the model with and without time fixed effects, respectively. The tables showcase the location and scale coefficients, as well as the quantile
-coefficients for the 25th, 50th, and 75th quantiles. We also report
-GLS standard errors, robust standard errors (brackets), and clustered
-standard errors at the country level.
+between 15 and 65 years of age (P1564); the share of the population 65
+years and older (P65); one-year lag of the dependent variable (LSP); oil
+prices in US dollars, differntiating between importer and exporter
+countries (OILIM and OILEX); and the output gap (YGAP). In addition to
+country fixed effects (as illustrated in MSS), we show results allowing
+for time fixed effects. Table~\ref{tbl-tb1} and Table~\ref{tbl-tb2}
+provide the results for the model with and without time fixed effects,
+respectively. The tables showcase the location and scale coefficients,
+as well as the quantile coefficients for the 25th, 50th and 75th
+quantiles. We also report GLS standard errors, robust standard errors
+(brackets) and clustered standard errors at the country level.
 
@@
 \begin{longtable}[]{@{}
-  >{\raggedright\arraybackslash}p{(\columnwidth - 18\tabcolsep) * \real{0.1099}}
-  >{\centering\arraybackslash}p{(\columnwidth - 18\tabcolsep) * \real{0.0989}}
-  >{\centering\arraybackslash}p{(\columnwidth - 18\tabcolsep) * \real{0.0989}}
-  >{\centering\arraybackslash}p{(\columnwidth - 18\tabcolsep) * \real{0.0989}}
-  >{\centering\arraybackslash}p{(\columnwidth - 18\tabcolsep) * \real{0.0989}}
-  >{\centering\arraybackslash}p{(\columnwidth - 18\tabcolsep) * \real{0.0989}}
-  >{\centering\arraybackslash}p{(\columnwidth - 18\tabcolsep) * \real{0.0989}}
-  >{\centering\arraybackslash}p{(\columnwidth - 18\tabcolsep) * \real{0.0989}}
-  >{\centering\arraybackslash}p{(\columnwidth - 18\tabcolsep) * \real{0.0989}}
-  >{\centering\arraybackslash}p{(\columnwidth - 18\tabcolsep) * \real{0.0989}}@{}}
-\caption{\label{tbl-tb1}Determinants of Government Surpluses:
-Individual Fixed Effects}\tabularnewline
+  >{\raggedright\arraybackslash}p{(\columnwidth - 18\tabcolsep) * \real{0.1235}}
+  >{\centering\arraybackslash}p{(\columnwidth - 18\tabcolsep) * \real{0.1111}}
+  >{\centering\arraybackslash}p{(\columnwidth - 18\tabcolsep) * \real{0.0988}}
+  >{\centering\arraybackslash}p{(\columnwidth - 18\tabcolsep) * \real{0.0864}}
+  >{\centering\arraybackslash}p{(\columnwidth - 18\tabcolsep) * \real{0.0864}}
+  >{\centering\arraybackslash}p{(\columnwidth - 18\tabcolsep) * \real{0.0988}}
+  >{\centering\arraybackslash}p{(\columnwidth - 18\tabcolsep) * \real{0.0988}}
+  >{\centering\arraybackslash}p{(\columnwidth - 18\tabcolsep) * \real{0.0988}}
+  >{\centering\arraybackslash}p{(\columnwidth - 18\tabcolsep) * \real{0.0988}}
+  >{\centering\arraybackslash}p{(\columnwidth - 18\tabcolsep) * \real{0.0988}}@{}}
+\caption{\label{tbl-tb1}Determinants of Government Surpluses: Individual
+Fixed Effects}\tabularnewline
 \toprule\noalign{}
@@
 location and scale coefficients. Except for a few cases, the robust and
-clustered standard errors are larger than the GLS standard errors, which may
-be an indication of misspecification of the model. The GLS standard
+clustered standard errors are larger than the GLS standard errors, which
+may be an indication of misspecification of the model. The GLS standard
 errors we report differ from those in MSS, because they use panel
@@
 differences in the reported GLS standard errors compared to the
-analytical standard errors reported in MSS. Our clustered standard errors,
-however, are closer to the bootstrap-based standard errors the authors
-report.\footnote{The differences in the GLS standard errors may be due that in our
-  derivation the influence function of the standardized \(\tau_{th}\)
-  quantile (see \#eq-infs) does not have the same leading term as the
-  one reported in MSS (see Theorem 3 and the definition of \(W\)).}
+analytical standard errors reported in MSS. Our clustered standard
+errors, however, are closer to the bootstrap-based standard errors the
+authors report.\footnote{The differences in the GLS standard errors may
+  be due that in our derivation the influence function of the
+  standardized \(\tau_{th}\) quantile (see \#eq-infs) does not have the
+  same leading term as the one reported in MSS (see Theorem 3, and the
+  definition of \(W\)).}
 
@@
 differences are that the log of income per capita has a positive effect
-on Government surpluses, but only for the 25th quantile, because at this point the largest impact on the Scale component is felt. Similarly, we observe that the
-income gap has an impact on Government surpluses that is always
-negative and increasing across quantiles. In both instances, the
+on government surpluses, but only for the 25th quantile, because at this
+point the largest impact on the Scale component is felt. Similarly, we
+observe that the income gap has an impact on government surplus that is
+always negative and increasing across quantiles. In both instances, the
 effects are not statistically significant.
@@
 \begin{longtable}[]{@{}
-  >{\raggedright\arraybackslash}p{(\columnwidth - 14\tabcolsep) * \real{0.1370}}
-  >{\centering\arraybackslash}p{(\columnwidth - 14\tabcolsep) * \real{0.1233}}
-  >{\centering\arraybackslash}p{(\columnwidth - 14\tabcolsep) * \real{0.1233}}
-  >{\centering\arraybackslash}p{(\columnwidth - 14\tabcolsep) * \real{0.1233}}
-  >{\centering\arraybackslash}p{(\columnwidth - 14\tabcolsep) * \real{0.1233}}
-  >{\centering\arraybackslash}p{(\columnwidth - 14\tabcolsep) * \real{0.1233}}
-  >{\centering\arraybackslash}p{(\columnwidth - 14\tabcolsep) * \real{0.1233}}
-  >{\centering\arraybackslash}p{(\columnwidth - 14\tabcolsep) * \real{0.1233}}@{}}
-\caption{\label{tbl-tb2}Determinants of Government Surpluses:
+  >{\raggedright\arraybackslash}p{(\columnwidth - 14\tabcolsep) * \real{0.1493}}
+  >{\centering\arraybackslash}p{(\columnwidth - 14\tabcolsep) * \real{0.1194}}
+  >{\centering\arraybackslash}p{(\columnwidth - 14\tabcolsep) * \real{0.1194}}
+  >{\centering\arraybackslash}p{(\columnwidth - 14\tabcolsep) * \real{0.1045}}
+  >{\centering\arraybackslash}p{(\columnwidth - 14\tabcolsep) * \real{0.1493}}
+  >{\centering\arraybackslash}p{(\columnwidth - 14\tabcolsep) * \real{0.1194}}
+  >{\centering\arraybackslash}p{(\columnwidth - 14\tabcolsep) * \real{0.1194}}
+  >{\centering\arraybackslash}p{(\columnwidth - 14\tabcolsep) * \real{0.1194}}@{}}
+\caption{\label{tbl-tb2}The Determinants of Government Surpluses:
 Individual and Time Fixed Effects}\tabularnewline
@@
 In this paper, we have extended the methodology proposed by
-\citet{mss2019} in order to estimate quantile regression
-models with multiple sets of fixed effects as well as with alternative
-standard errors. This methodology will allow researchers to
-implement more-comprehensive analyses of data sets characterized by
-complex hierarchies and unobserved heterogeneity. This extension is
-particularly valuable in contexts where group specific effects vary
-across the conditional distribution of the outcome of interest.
+\citet{mss2019} in order to estimate quantile regression models with
+multiple sets of fixed effects as well as with alternative standard
+errrors. This methodology will allow researchers to implement
+more-comprehensive analyses of data sets characterized by complex
+hierarchies and unobserved heterogeneity. This extension is particularly
+valuable in contexts where group specific effects vary across the
+conditional distribution of the outcome of interest.
 
 Using a small simulation study, we show that our extended approach is as
-effective in identifying the parameters of interest as that of \citet{mss2019}, even in contexts with two sets of fixed effects. Notably, the
-bias-corrected estimator based on the split-panel jackknife estimator
-exhibits promising results, mitigating biases when samples are small
-but increasing standard errors.
+effective in identifying the parameters of interest as that of
+\citet{mss2019}, even in contexts with two sets of fixed effects.
+Notably, the bias-corrected estimator based on the split-panel jackknife
+estimator exhibits promising results, mitigating biases when samples are
+small but increasing standard errors.
 
@@
 clustered standard errors perform better in these cases. This may also
-suggest a venue for future research, in which the validity of the location-scale model assumption is tested.
+suggest a venue for future research, in which the validity of the
+location-scale model assumption is tested.
 
@@
 \hypertarget{derivation-of-the-influence-functions}{%
-\section{Derivation of the Influence
-Functions}\label{derivation-of-the-influence-functions}}
+\section{Derivation of the influence
+functions}\label{derivation-of-the-influence-functions}}
 
@@
 \end{aligned}
-\],
+\]
 
 where \(\varepsilon\) is an unobserved i.i.d. random variable that is
-independent of \(x\) and such that \(x\gamma\) is larger than 0 for
-any \(x\).
+independent of \(x\) and such that \(x\gamma\) is larger than 0 for any
+\(x\).
 
@@
 
-\[q(y|\tau,x) = x'(\beta + q(\varepsilon |\tau) \times \gamma)\].
+\[q(y | \tau, x) = x'(\beta + q(\varepsilon | \tau) \times \gamma)\]
 
@@
   E[ (|y_i-x_i'\beta|-x_i' \gamma) x_i ] &=E[h_{2,i}]=0 \\
-  E\left[  \mathbb{1}\left( q(\varepsilon|\tau) x_i'\gamma +x_i'\beta\geq  y_i  \right) - \tau \right] 
+  E\left[  \mathbb{1}\left( q(\tau) x_i'\gamma +x_i'\beta\geq  y_i  \right) - \tau \right] 
    &=E[h_{3,i}]=0 
 \end{aligned}
-\].
-
-For simplicity, for the rest of the appendix we use
-\(q^\varepsilon_\tau\) to represent \(q(\varepsilon |\tau)\).
+\]
+
+For simplicity, the rest of the appendix uses \(q^\varepsilon_\tau\) to
+represent \(q(\varepsilon | \tau)\).
 
@@
 
-In this model, to estimate the variance-covariance matrix of the set of
+In this model, to estimate the variance-covariance matrix the set of
 coefficients \(\theta'=[\beta' \ \gamma' \ q^\varepsilon_\tau]\), we
@@
 \end{bmatrix}
-\],
+\]
 
@@
 \[\bar G(\theta) = \begin{bmatrix}
-\bar G_{11} & G_{12} & G_{13} \\
-\bar G_{21} & \bar G_{22} & G_{23} \\
+\bar G_{11} & \bar G_{12} & \bar G_{13} \\
+\bar G_{21} & \bar G_{22} & \bar G_{23} \\
 \bar G_{31} & \bar G_{32} & \bar G_{13} \\
 \end{bmatrix}
-\],
+\]
 
@@
 \[\bar G_{j,k} = - \frac 1 N \sum_{i=1}^N \frac{\partial h_{j,i}}{\partial \theta_k'} \ \forall j,k \in 1,2,3
-\].
+\]
 
@@
 \bar G_{1,2} = \bar G_{1,3} = 0
-\].
-
-Second Moment Condition: Scale Model
+\]
+
+Second Moment Condition: Scale model
 
@@
 \bar G_{2,2} &= -\frac{1}{N} \sum \frac{\partial h_{2,i}}{\partial \gamma'} \\
-             &=  \frac{1}{N} \sum x_i x_i' 
+             &=  \frac{1}{N} \sum x_i x_i' \\
              &= N^{-1} X'X
 \end{aligned}
-\].
+\]
 
@@
 \[\begin{aligned}
-h_{3,i} &= \mathbb{1}\left( q^\varepsilon_\tau x_i'\gamma +x_i'\beta - y_i \geq 0 \right) - \tau \text{ or}\\
-h_{3,i} &= \mathbb{1}\left( q^\varepsilon_\tau  \geq \frac{y_i- x_i'\beta}{x_i'\gamma}  \right) - \tau = \mathbb{1}\big( q^\varepsilon_\tau  \geq \varepsilon  \big) - \tau \\
-\end{aligned}
-\].
+h_{3,i} &= \mathbb{1}\left(q(\tau) x_i'\gamma +x_i'\beta - y_i \geq 0 \right) - \tau \text{ or}\\
+h_{3,i} &= \mathbb{1}\left( q(\tau)  \geq \frac{y_i- x_i'\beta}{x_i'\gamma}  \right) - \tau = \mathbb{1}\big( q(\tau)  \geq \varepsilon  \big) - \tau \\
+\end{aligned}
+\]
 
@@
 \(I()\). This function, \(I()\), is a monotonic and symmetrical function
-around 0, with a domain over the real numbers, and a range between 0
-and 1.
+around 0, with a domain over the real numbers, and a range between 0 and
+1.
 
@@
 \lim_{h\rightarrow 0} I\left(\frac{z}{h}\right) \approx \mathbb{1}(z\geq 0)
-\].
+\]
 
@@
 
-\[h_{3,i} \approx I\left( q^\varepsilon_\tau x_i'\gamma +x_i'\beta - y_i  \right) - \tau\].
-
-Now, we can obtain the Jacobian matrix \(\bar G_{3,1}\) as
+\[h_{3,i} \approx I\left( q(\tau) x_i'\gamma +x_i'\beta - y_i  \right) - \tau\]
+
+Now, we can obtain the Jacobian matrix \(\bar G_{3,1}\) as:
 
@@
 \bar G_{3,1} &= -\frac{1}{N} \sum \frac{\partial h_{3,i}}{\partial \beta'} \\
-             &= -N^{-1} \sum K_h(q^\varepsilon_\tau x_i'\gamma +x_i'\beta - y_i ) x_i'
-\end{aligned}
-\].
+             &= -N^{-1} \sum K_h(q(\tau) x_i'\gamma +x_i'\beta - y_i ) x_i'
+\end{aligned}
+\]
 
 Under the assumption that we have enough observations within each
-combination of \(x\) that are of multiplicative heteroskedasticity, we have
-
-\[\begin{aligned}
-E(K_h(q^\varepsilon_\tau x_i'\gamma +x_i'\beta - y_i )|X) &= f_{y|X}(q^\varepsilon_\tau x_i'\gamma +x_i'\beta) \\
-&=\frac{1}{x_i'\gamma} f_{\varepsilon}(q^\varepsilon_\tau) \\
-\end{aligned}
-\],
+combination of \(x\) that are of multiplicative heteroskedasticity, we
+have
+
+\[\begin{aligned}
+E(K_h(q(\tau) x_i'\gamma +x_i'\beta - y_i )|X) &= f_{y|X}(q(\tau) x_i'\gamma +x_i'\beta) \\
+&=\frac{1}{x_i'\gamma} f_{\varepsilon}(q(\tau)) \\
+\end{aligned}
+\]
 
@@
 
-\[\bar G_{3,1} = -N^{-1} f_{\varepsilon}\big(q^\varepsilon_\tau\big) \sum  \frac{x_i'}{x_i'\gamma} 
-\].
+\[\bar G_{3,1} = -N^{-1} f_{\varepsilon}\big(q(\tau)\big) \sum  \frac{x_i'}{x_i'\gamma} 
+\]
 
@@
 approximated using Taylor expansions by \(N\frac{\bar a}{\bar b}\).
-\footnote{This approximation will be useful when we consider the estimation of the influence functions.} Thus, we can rewrite the last
+\footnote{This approximation will be useful when we consider the
+  estimation of the influence functions.} Thus, we can rewrite the last
 term as
 
-\[\bar G_{3,1} = - f_{\varepsilon}\big(q^\varepsilon_\tau\big) \frac{\bar x_i'}{\bar x_i'\gamma} 
-\].
+\[\bar G_{3,1} = - f_{\varepsilon}\big(q(\tau)) \frac{\bar x_i'}{\bar x_i'\gamma} 
+\]
 
@@
 \[\lambda_i(\beta) = \bar G^{-1}_{1,1} h_{1,i} = N (X'X)^{-1}(x_i (y_i-x_i'\beta)) = N (X'X)^{-1}(x_i \nu_i)
-\],
+\]
 
@@
 
-and \[\begin{aligned}
+and
+
+\[\begin{aligned}
 E[sign(\nu_i)] &= E[\mathbb{1}(\nu_i \geq 0)] - E[\mathbb{1}(\nu_i < 0)] \\
@@
 \item
-  \texttt{mmqreg} in Stata: net install mmqre,
-  (https://friosavila.github.io/stpackages)
+  \texttt{mmqreg} in Stata: `net install mmqreg,
+  from(https://friosavila.github.io/stpackages)
 \item

### 2023-11-17 article/article.qmd

@@
 ---
-title: Quantile Regressions via Method of Moments with multiple fixed effects \tnoteref{t1}
+title: Estimating Quantile Regressions with Multiple Fixed Effects through Method of Moments \tnoteref{t1}
 author:
@@
   - name: Leonardo Siles
-    email: leonardosiles@hotmail.com
+    email: leonardo.siles@ucb.edu.bo
     affiliations:

### 2024-02-06 article/article.qmd
c
update and Sims

@@
 Quantile regression (QR), introduced by @koenkerbasset1978, is an estimation strategy used for modeling the relationships between explanatory variables X and the conditional quantiles of the dependent variable $Q_y (\tau|x)$.
-Using QR one can obtain richer characterizations of the relationships between dependent and independent variables, by accounting for otherwise unobserved heterogeneity.
+Using QR one can obtain richer characterizations of the relationships between dependent and independent variables, by exploring how the variables relate along the entire conditional distribution.
 
@@
 
-In this framework, our paper expands on @mss2019, following some of the suggestions by these authors regarding further research.
+In this framework, our paper expands on @mss2019 in two ways.
 First, making use of the properties of generalized method of moments (GMM) estimators, we derive various alternatives for the estimation of standard errors based on the empirical influence functions of the estimators.
-Second, we reconsider the application of Frisch-Waugh-Lovell (FWL) theorem [@frishwaugh1933 and @lovell1963] to extend the MSS estimator to allow for the inclusion of multiple fixed effects, for example, individual and year fixed effects.
+Even if the model is correctly specified, robust standard errors perform better than GLS standard errors due small violations of the model assumptions due to sampling variability.
+Furthermore, clustered standard errors may help to further account for typically unobserved correlations across observations.
+Second, we reconsider the application of Frisch-Waugh-Lovell (FWL) theorem [@frishwaugh1933 and @lovell1963] to extend the MSS estimator and allow for the inclusion of multiple fixed effects.
+This extension may be useful for empirical analysis, as it is common to control for multiple fixed effects such as individual and time fixed effects.
 
@@
 It also shows that the FWL theorem can be used to control for multiple fixed effects.
-Section 3 presents the results of a small simulation study and section 4 illustrates the application of the proposed methods with two empirical examples.
+Section 3 presents the results of a small simulation study and section 4 illustrates the application of the proposed methods with one empirical example.
 Section 5 concludes.
@@
 
-This allows for nonlinearities in the effect of $X$ on $Y$ across all values of $\tau$.
-This formulation can also be related to a random coefficient model, in which all coefficients are assumed to be some nonlinear function of $\tau$ where $\tau$ follows a random uniform distribution.
+This allows for a linear effect of $X$ on $Y$, but that could vary across values of $\tau$.
 
@@
 
-Here, the location parameters $\beta$ are typically identified using a linear regression model (as in @mss2019) or a median regression (as in @zhao2000) and the scale parameters $\gamma(\tau)$ can be estimated using standard approaches.
+Here, the location parameters $\beta$ are typically identified using a linear regression model (as in @mss2019) or a median regression (as in @he1997 and @zhao2000) and the scale parameters $\gamma(\tau)$ can be estimated using standard approaches.
 
@@
 
-One insightful extension to the location-scale parameterizations suggested by @he1997, @cameron2005, and @mss2019 is to assume that the data-generating process (DGP) can be written as a linear model with a multiplicative heteroskedastic process that is linear in parameters.[^2]
+One insightful extension to the location-scale parameterizations suggested by @he1997, @zhao2000, @cameron2005, and @mss2019 is to assume that the data-generating process (DGP) can be written as a linear model with a multiplicative heteroskedastic process that is linear in parameters.[^2]
 
@@
 In this setup, the traditional quantile coefficients are identified as the location model coefficients plus the scale model coefficients moderated by the $\tau_{th}$ unconditional quantile of the standardized error $\varepsilon$.
-For simplicity we will use $q(\tau)$ to denote $Q_\varepsilon(\tau)$ in the rest of the paper.
+For simplicity we will use $q_\tau$ to denote $Q_\varepsilon(\tau)$ in the rest of the paper.
 
-$$\beta(\tau) = \beta + q(\tau) \times \gamma 
+$$\beta(\tau) = \beta + q_\tau \times \gamma 
 $$ {#eq-eq6}
@@
 While this specification imposes a strong assumption on the DGP, it has two advantages over the standard quantile regression model.
-First, because the location-scale model can be identified globally, with only a single parameter ($q(\tau)$) requiring local estimation, this estimation approach will be more efficient than the standard quantile regression model (@zhao2000).
-Second, under the assumption that $X\gamma$ is strictly positive, the model will produce quantile coefficients that do not cross.
+First, because the location-scale model can be identified globally, with only a single parameter ($q_\tau$) requiring local estimation, this estimation approach will be more efficient than the standard quantile regression model (@zhao2000).
+Second, under the assumption that $X\gamma$ is strictly positive, the model will produce quantile coefficients that do not cross (@he1997).
 
 Following MSS, the quantile regression model defined by @eq-eq5 can be estimated using a generalized method of moments approach.
-And while it is possible to identify all coefficients ($\beta,\gamma, q(\tau)$) simultaneously, we describe and use the implementation approach advocated by MSS, which identifies each set of coefficients separately.
+And while it is possible to identify all coefficients ($\beta,\gamma, q_\tau$) simultaneously, we describe and use the implementation approach advocated by MSS, which identifies each set of coefficients separately.
 
@@
 
+It should be noticed that the estimation of the standard errors (next section) requires that the Scale component prediction $x_i'\gamma$ is strictly positive, because it represents the conditional standard deviation of the error $\nu_i$.
+Because this component is identified using a linear model, some values for $x_i'\gamma$ may be negative, which will affect the estimation of the standard errors, as shown in the simulation study.
+
 Third, given the location and scale coefficients, the $\tau_{th}$ quantile of the error $\varepsilon$ can be estimated using the following condition:
@@
 $$\begin{aligned}
-  E\left[  \mathbb{1}\left(x_i' (\beta +   \gamma q(\tau)) \geq y_i \right) - \tau \right] &=0  \\
-  E\left[  \mathbb{1}\left(   q(\tau) \geq \frac{y_i-x_i'\beta}{x_i'\gamma} \right) - \tau \right] &=0  \\
+  E\left[  \mathbb{1}\left(x_i' (\beta +   \gamma q_\tau) \geq y_i \right) - \tau \right] &=0  \\
+  E\left[  \mathbb{1}\left(   q_\tau \geq \frac{y_i-x_i'\beta}{x_i'\gamma} \right) - \tau \right] &=0  \\
   \end{aligned}
@@
 
-where one identifies the quantile of the error $\varepsilon$ using standardized errors $\frac{y_i-x_i'\beta}{x_i'\gamma}$ or by finding the values that identify the overall quantile coefficients $\beta(\tau)=\beta + \gamma q(\tau)$.
+where one identifies the quantile of the error $\varepsilon$ using standardized errors $\frac{y_i-x_i'\beta}{x_i'\gamma}$ or by finding the values that identify the overall quantile coefficients $\beta(\tau)=\beta + \gamma q_\tau$.
 Afterwards, the conditional quantile coefficients are simply defined as the combination of the location and scale coefficients.
@@
   E[x_i  (|\nu_i|-x_i \gamma) ] &=E[h_{2,i}]=0 \\
-  E\left[  \mathbb{1}\left(   q(\tau)\geq \frac{y_i-x_i'\beta}{x_i'\gamma} \right) - \tau \right] 
-  &=E[h_{3,i}]=0 
+  E\left[  \mathbb{1}\left(   q_\tau\geq \frac{y_i-x_i'\beta}{x_i'\gamma} \right) - \tau \right]  &=E[h_{3,i}]=0 
   \end{aligned}
-$$ {#eq-eq10}
+$${#eq-eq10}
 
@@
 
-Call $\theta=[ \beta' \ \ \gamma' \ \ q(\tau) ]'$ the set of coefficients that are identified by the moment conditions in @eq-eq10, a just identified model, and the function $h_i$ is a vector function that stacks all the moments described in @eq-eq10 at the individual level.
+Call $\theta=[ \beta' \ \ \gamma' \ \ q_\tau ]'$ the set of coefficients that are identified by the moment conditions in @eq-eq10, a just identified model, and the function $h_i$ is a vector function that stacks all the moments described in @eq-eq10 at the individual level.
 Then $\hat\theta$ follows a normal distribution with mean $\theta$ and variance-covariance matrix $V(\theta)$ that is estimated as
@@
 
-In this framework, the quantile regression coefficients, a combination of the location-scale-quantile estimates, will follow a normal distribution with mean $\beta(\tau) = \beta+\gamma q(\varepsilon | \tau)$ and variance-covariance matrix equal to
+In this framework, the quantile regression coefficients, a combination of the location-scale-quantile estimates, will follow a normal distribution with mean $\beta(\tau) = \beta+\gamma q_\tau$ and variance-covariance matrix equal to
 
@@
 
-$$\Xi = [ I(k), \hat q(\tau) \times I(k), \hat \gamma ]
-$$ {#eq-eqqtile}
+$$\Xi = [ I(k), \hat q_\tau \times I(k), \hat \gamma ]
+$${#eq-eqqtile}
 
@@
 
-For the specific case of quantile regressions through moments, the influence functions for the location, scale, and quantile coefficients are[^4]
+For the specific case of quantile regressions via moments, the influence functions for the location, scale, and quantile coefficients are[^4]
 
@@
   \lambda_{i}(\gamma) \\
-  \lambda_{i}(q(\tau)) 
+  \lambda_{i}(q_\tau) 
   \end{bmatrix} \\
@@
 \lambda_{i}(\gamma)&= N(X'X)^{-1} x_i ( x_i' \gamma ) \times (\tilde \varepsilon_i -1\big)\\
-\lambda_{i}(q(\tau))&=\frac{\tau-\mathbb{1}\big( q(\tau)  \geq \varepsilon_i  \big) }{f_{\varepsilon}(q(\tau))}
+\lambda_{i}(q_\tau)&=\frac{\tau-\mathbb{1}\big( q_\tau  \geq \varepsilon_i  \big) }{f_{\varepsilon}(q_\tau)}
 - \frac{ x_i'\gamma \times \varepsilon_i }{\bar x_i'\gamma} 
--  q(\tau) \frac{  x_i' \gamma  \times (\tilde \varepsilon_i -1\big)}{\bar x_i'\gamma}
+-  q_\tau \frac{  x_i' \gamma  \times (\tilde \varepsilon_i -1\big)}{\bar x_i'\gamma}
 \end{aligned}
@@
   \hat\gamma \\
-  \hat q(\tau)
+  \hat q_\tau
   \end{pmatrix}
@@
  \begin{pmatrix}
- \sum \lambda_i(\beta) \lambda_i(\beta)' & \sum \lambda_i(\beta) \lambda_i(\gamma)' & \sum \lambda_i(\beta) \lambda_i(q(\tau))' \\
- \sum \lambda_i(\gamma) \lambda_i(\beta)' & \sum \lambda_i(\gamma) \lambda_i(\gamma)' & \sum \lambda_i(\gamma) \lambda_i(q(\tau))' \\
- \sum \lambda_i(q(\tau)) \lambda_i(\beta)' & \sum \lambda_i(q(\tau))\lambda_i(\gamma)' & \sum \lambda_i(q(\tau)) \lambda_i(q(\tau))' 
+ \sum \lambda_i(\beta) \lambda_i(\beta)' & \sum \lambda_i(\beta) \lambda_i(\gamma)' & \sum \lambda_i(\beta) \lambda_i(q_\tau)' \\
+ \sum \lambda_i(\gamma) \lambda_i(\beta)' & \sum \lambda_i(\gamma) \lambda_i(\gamma)' & \sum \lambda_i(\gamma) \lambda_i(q_\tau)' \\
+ \sum \lambda_i(q_\tau) \lambda_i(\beta)' & \sum \lambda_i(q_\tau)\lambda_i(\gamma)' & \sum \lambda_i(q_\tau) \lambda_i(q_\tau)' 
   \end{pmatrix}
@@
 
-This estimator of standard errors should be robust to arbitrary heteroskedasticity.
-However, because the location-scale specification relies on the correct specification of the model heteroskedasticity, large differences in standard errors compared to GLS-standard errors may be an indication of misspecification of the model.
+This estimator of standard errors may prove useful for two reasons.
+First, this estimator would be robust to misspecification of the scale model assumptions, and thus it could be used as an informal test for the validity of the model assumptions when compared to the GLS-standard error (@sec-gls).
+Second, as shown in the simulation study, this estimator performs better than GLS-standard errors even if the model is correctly specified, because of problemes caused when $x\hat\gamma$ is not strictly positive.
 
@@
 
-### GLS Standard Errors
+### GLS Standard Errors {#sec-gls}
 
@@
  \psi_{i,2} &= \tilde \varepsilon_i -1 \\
- \psi_{i,3} &= \frac{1}{ x_i' \gamma }\frac{\tau-\mathbb{1}\big( q(\tau)  \geq \varepsilon_i  \big) }{ f_{\varepsilon}(q(\tau))} - \frac{\varepsilon_i }{\bar x_i'\gamma} 
--  q(\tau) \frac{(\tilde \varepsilon_i -1\big)}{\bar x_i'\gamma}
+ \psi_{i,3} &= \frac{1}{ x_i' \gamma }\frac{\tau-\mathbb{1}\big( q_\tau  \geq \varepsilon_i  \big) }{ f_{\varepsilon}(q_\tau)} - \frac{\varepsilon_i }{\bar x_i'\gamma} 
+-  q_\tau \frac{(\tilde \varepsilon_i -1\big)}{\bar x_i'\gamma}
 \end{aligned}
@@
  \begin{pmatrix}
- \hat\sigma_{11} \hat\Omega_{11} & \hat\sigma_{12} \hat\Omega_{12} & \hat\sigma_{11} \hat\Omega_{13} \\
- \hat\sigma_{21} \hat\Omega_{21} & \hat\sigma_{22} \hat\Omega_{22} & \hat\sigma_{21} \hat\Omega_{23} \\
- \hat\sigma_{31} \hat\Omega_{31} & \hat\sigma_{32} \hat\Omega_{32} & \hat\sigma_{33} \hat\Omega_{33}
+ \hat\sigma_{11} \hat\Omega_{11} & \hat\sigma_{12} \hat\Omega_{12} & \hat\sigma_{13} \hat\Omega_{13} \\
+ \hat\sigma_{12} \hat\Omega_{12} & \hat\sigma_{22} \hat\Omega_{22} & \hat\sigma_{23} \hat\Omega_{23} \\
+ \hat\sigma_{13} \hat\Omega_{13} & \hat\sigma_{23} \hat\Omega_{23} & \hat\sigma_{33} \hat\Omega_{33}
   \end{pmatrix}
@@
 
-This estimator of stand ard errors is equivalent to the one derived by MSS using Theorem 3.
+This estimator of standard errors is equivalent to the one derived by MSS using Theorem 3.
+Empirically, the simulation study shows that this estimator may severily over estimate the standard errors, even if the model is correctly specified.
+This happens because the sample estimates of the scale model coefficients may be negative or close to zero.
 
@@
 
-Using the setup described in the previous section, @mss2019 proposes an extension to the model proposed by @he1997 that enables the estimation of quantile regression models with panel data, allowing for the inclusion of individual fixed effects.
-However, as the authors suggest, the methodology can be generalized to allow for the inclusion of multiple fixed effects.
+Using the setup described in the previous section, MSS proposes an extension to the model proposed by @he1997 that enables the estimation of quantile regression models with panel data, allowing for the inclusion of individual fixed effects.
+However, the methodology can also be generalized to allow for the inclusion of multiple fixed effects.
 This type of analysis can be useful when considering data such as employer-employee linked data [@abowed2006] or teacher-student linked data [@harrissass2011].
@@
 
-We return to the original model and now assume there are sets of unobserved heterogeneity that are assumed to be constant across observations, if they belong to common groups.
-In panel data, the groups would be the individual fixed effects and the time fixed effects.
+We return to the original model and now assume there are sets of unobserved heterogeneity that are constant across observations, if they belong to common groups.
 Without loss of generality, we can assume that the data-generating process is as follows:
@@
 
-where we assume $x_{i}$ vary across groups $g_1$ and $g_2$ (and thus are not collinear) and that $\delta's$ and $\zeta's$ are the location and scale effects associated with groups fixed effects.[^7]
+where we assume $x_{i}$ vary across groups $g_1$ and $g_2$ (and thus are not collinear) and that $\delta's$ and $\zeta's$ are the location and scale effects associated with the groups fixed effects.[^7]
 
@@
 If the dimension of groups $g_k$ is low, this model could be estimated using a dummy inclusion approach following @sec-betas, and the standard errors obtained as discussed in @sec-se.
-However, if the dimensionality of $g_k$ is high, the dummy inclusion approach may not be feasible.
-A more feasible approach is to apply the FWL theorem and partial out the impact of the group fixed effects on the control variables $x_{i}$, and the outcome of interest $y_{i}$, using a similar approach for the identification of $\sigma(x)$.
+However, if the dimensionality of $g_k$ is high, the dummy inclusion approach may not be computationally feasible.
+A more feasible approach is to apply the FWL theorem and partial out the impact of the group fixed effects on the control variables $x_{i}$, and the outcome of interest $y_{i}$, and using a similar approach for the identification of $\sigma(x)$.
 In the case of unbalanced setups with multiple groups, the estimation involves iterative processes for which various approaches have been suggested and implemented (see for example, @correia_feasible_nodate, @gaure2013, @rios2015, among others).
@@
 where $\alpha_{1i}\sim \chi^2(1)$, $\alpha_{2i} \sim \chi^2(1)$, and $x_i = 0.5 * (\chi_i +0.5(\alpha_{1i}+\alpha_{2i}))$, with $\chi_i \sim \chi^2(1)$.
-We only consider the case when the error term $\varepsilon_i$ is assumed to be normally distributed with mean 0 and standard deviation of 0.5.
-We assume that there are 50 mutually exclusive fixed effect groups for each set of fixed effects.
+We only consider the case when the error term $\varepsilon_i$ is assumed to follow a centered $\chi^2$ distribution.[^99] We assume that there are 50 mutually exclusive groups for each set of fixed effects.
 Observations are assigned to each subgroup randomly using a uniform distribution between 1 and 50.
@@
 
+[^99]: Specifically we assume $\varepsilon=\frac{r_i}{5}-1$, where $r_i$ follows a chi-squared distribution such that $r_i \sim \chi^2(5)$.
+Simulations under the assumption of normal errors are available upon request.
+
 [^9]: For the implementation, we first estimate the model using the full sample, then randomly assign each observation into one of two groups, and finally reestimate the quantile coefficients for each group.
-The bias-corrected estimator is then obtained as $\hat\beta(\tau)_{jkc}=2*\hat\beta(\tau)_{full}-0.5*\big(\hat\beta(\tau)_{s1}+\hat\beta(\tau)_{s1}\big)$.
+The bias-corrected estimator is then obtained as $\hat\beta(\tau)_{jkc}=2*\hat\beta(\tau)_{full}-0.5*\big(\hat\beta(\tau)_{s1}+\hat\beta(\tau)_{s2}\big)$.
 
-Similar to the findings in MSS, we find that while the estimator presents a bias when the sample is small ($N=500$), this bias shrinks as the sample size increases.
+Similar to the findings in MSS, we find that while the estimator presents a substantial bias when the sample is small ($N=500$), this bias shrinks as the sample size increases.
 As MSS describes, the bias seems to be proportional to the sample size, or more precisely to $N/N_{g1}$ and $N/N_{g2}$, where $N_{g1}$ and $N_{g2}$ are the average number of observations per group.
-Interestingly, the bias-corrected estimator presents an almost 0 bias, even when the samples are small (about 10 observations per subgroup).
-Moreover, we find that despite the bias reduction obtained using the JKC estimator, the standard errors and mean squared error (MSE) are larger than without correction, which also replicates the results of MSS,
+Interestingly, the bias-corrected estimator presents an almost 0 bias for the 25th percentile, even when the samples are small (about 10 observations per subgroup).
+In contrast, when considering the 75th percentile, the simple estimator shows smaller bias than the Jacknife estimator.[^88: This is also consistent with simulations with a single fixed effect] In either case, despite the bias reduction obtained using the JKC estimator, the standard errors  are larger than without correction.
+For the 25th quantile, the reduction in bias is large enough to produce a smaller Mean Squared Error (MSE) than the simple estimator.
+This is similar to the results of MSS.
 
-| N = 500      |   Bias   |   Sim SE   |   MSE   | N = 1000     |   Bias   |   Sim SE   |   MSE   |
-|---------|:-------:|:-------:|:-------:|---------|:-------:|:-------:|:-------:|
-| q25          |          |            |         | q25          |          |            |         |
-|  mmqreg      |  0.104   |   0.247    |  0.072  |  mmqreg      |  0.050   |   0.173    |  0.032  |
-|  jkc         |  0.008   |   0.297    |  0.088  |  jkc         |  -0.001  |   0.191    |  0.036  |
-| q75          |          |            |         | q75          |          |            |         |
-|  mmqreg      |  -0.091  |   0.251    |  0.071  |  mmqreg      |  -0.044  |   0.176    |  0.033  |
-|  jkc         |  0.002   |   0.303    |  0.092  |  jkc         |  0.006   |   0.195    |  0.038  |
-| **N = 2000** | **Bias** | **Sim SE** | **MSE** | **N = 4000** | **Bias** | **Sim SE** | **MSE** |
-| q25          |          |            |         | q25          |          |            |         |
-|  mmqreg      |  0.025   |   0.122    |  0.016  |  mmqreg      |  0.012   |   0.087    |  0.008  |
-|  jkc         |  0.003   |   0.129    |  0.017  |  jkc         |  0.000   |   0.089    |  0.008  |
-| q75          |          |            |         | q75          |          |            |         |
-|  mmqreg      |  -0.023  |   0.124    |  0.016  |  mmqreg      |  -0.011  |   0.087    |  0.008  |
-|  jkc         |  0.001   |   0.131    |  0.017  |  jkc         |  0.000   |   0.089    |  0.008  |
+::: {#tbl-sim1}
 
-: Bias, Simulated Standard error, and Mean Squared Error {#tbl-sim1}
+{{< include tb1.tex >}}
+
+Bias, Simulated Standard error, and Mean Squared Error 
+:::
 
@@
 
-$$q(y | \tau, x) = x'(\beta + q(\varepsilon | \tau) \times \gamma)$$
+$$Q_y(\tau|X) = x'(\beta +Q_\varepsilon(\tau)  \times \gamma)$$
 
@@
   E[ (|y_i-x_i'\beta|-x_i' \gamma) x_i ] &=E[h_{2,i}]=0 \\
-  E\left[  \mathbb{1}\left( q(\tau) x_i'\gamma +x_i'\beta\geq  y_i  \right) - \tau \right] 
+  E\left[  \mathbb{1}\left( Q_\varepsilon(\tau) x_i'\gamma +x_i'\beta\geq  y_i  \right) - \tau \right] 
    &=E[h_{3,i}]=0 
@@
 
-For simplicity, the rest of the appendix uses $q^\varepsilon_\tau$ to represent $q(\varepsilon | \tau)$.
+For simplicity, the rest of the appendix uses $q_\tau$ to represent  $Q_\varepsilon(\tau)$.
 
@@
 
-In this model, to estimate the variance-covariance matrix the set of coefficients $\theta'=[\beta' \ \gamma' \ q^\varepsilon_\tau]$, we need to obtain the influence functions of all coefficients, which are defined as
+In this model, to estimate the variance-covariance matrix the set of coefficients $\theta'=[\beta' \ \gamma' \ q_\tau]$, we need to obtain the influence functions of all coefficients, which are defined as
 
@@
 $$\begin{aligned}
-h_{3,i} &= \mathbb{1}\left(q(\tau) x_i'\gamma +x_i'\beta - y_i \geq 0 \right) - \tau \text{ or}\\
-h_{3,i} &= \mathbb{1}\left( q(\tau)  \geq \frac{y_i- x_i'\beta}{x_i'\gamma}  \right) - \tau = \mathbb{1}\big( q(\tau)  \geq \varepsilon  \big) - \tau \\
+h_{3,i} &= \mathbb{1}\left( q_\tau  x_i'\gamma +x_i'\beta - y_i \geq 0 \right) - \tau \text{ or}\\
+h_{3,i} &= \mathbb{1}\left( q_\tau  \geq \frac{y_i- x_i'\beta}{x_i'\gamma}  \right) - \tau = \mathbb{1}\big( q_\tau \geq \varepsilon  \big) - \tau \\
 \end{aligned}
@@
 
-Because the indicator function $\mathbb{1}()$ is not differentiable, we borrow from the nonparametric literature and approximate the indicator function with the integral of a kernel density function $I()$.
-This function, $I()$, is a monotonic and symmetrical function around 0, with a domain over the real numbers, and a range between 0 and 1.
-
-With an arbirarily small bandwidth $h$, this function will approximate the indicator function:
+Because the indicator function $\mathbb{1}()$ is not differentiable, we borrow from the nonparametric literature to approximate this function with a kernel function.
+Call $k()$ a well behaved kernel function that is symetric around 0, and $K()$ its integral, with range between 0 and 1.
+With an arbirarily small bandwidth $h$, we can use the function $K()$ to approximate the indicator function:
 
 $$
-\lim_{h\rightarrow 0} I\left(\frac{z}{h}\right) \approx \mathbb{1}(z\geq 0)
+\lim_{h\rightarrow 0} K\left(\frac{z}{h}\right) \approx \mathbb{1}(z\geq 0)
 $$
@@
 
-$$h_{3,i} \approx I\left( q(\tau) x_i'\gamma +x_i'\beta - y_i  \right) - \tau$$
+$$h_{3,i} \approx K\left( \frac{1}{h} \Big( q_\tau x_i'\gamma +x_i'\beta - y_i  \Big) \right) - \tau
+$$
 
@@
 \bar G_{3,1} &= -\frac{1}{N} \sum \frac{\partial h_{3,i}}{\partial \beta'} \\
-             &= -N^{-1} \sum K_h(q(\tau) x_i'\gamma +x_i'\beta - y_i ) x_i'
+             &= -N^{-1} \sum \frac{1}{h} k\left( \frac{1}{h} \Big( q_\tau x_i'\gamma +x_i'\beta - y_i  \Big) \right) x_i' \\ 
+             &= -N^{-1} \sum \frac{1}{h} k\left( \frac{1}{h} \big( q_\tau x_i'\gamma - \nu_i \big)   \right) x_i'  \\
+             &= -N^{-1} \sum \frac{1}{h} k\left( \frac{1}{h} ( q_\tau - \varepsilon_i ) x_i'\gamma  \right) x_i'  
 \end{aligned}
@@
 
-Under the assumption that we have enough observations within each combination of $x$ that are of multiplicative heteroskedasticity, we have
+If we condition on $X$, use the law of iterated expectations, and assume that $\varepsilon_i$ is homoskedastic, we can obtain:
 
 $$\begin{aligned}
-E(K_h(q(\tau) x_i'\gamma +x_i'\beta - y_i )|X) &= f_{y|X}(q(\tau) x_i'\gamma +x_i'\beta) \\
-&=\frac{1}{x_i'\gamma} f_{\varepsilon}(q(\tau)) \\
+\bar G_{3,1} &= -N^{-1} \sum \frac{1}{h} k\left( \frac{1}{h} ( q_\tau - \varepsilon_i ) x_i'\gamma  \right) x_i'  \\
+             &= -N^{-1} \sum \frac{1}{h} k\left( \frac{q_\tau - \varepsilon_i}{h}  \right)  \frac{x_i'}{x_i'\gamma}  \\
+             &= -N^{-1} f_\varepsilon (q_\tau) \sum  \frac{x_i'}{x_i'\gamma}  
 \end{aligned}
@@
 
-where $f_{y|X}$ is the conditional probability density function of $y$ given $X$ and $f_\varepsilon$ is the unconditional distribution of the standardized error.
-With this, we can rewrite the Jacobian matrix as
-
-$$\bar G_{3,1} = -N^{-1} f_{\varepsilon}\big(q(\tau)\big) \sum  \frac{x_i'}{x_i'\gamma} 
+Finally, this simplifies to:
+$$\begin{aligned}
+\bar G_{3,1} &\simeq -  f_\varepsilon (q_\tau) \frac{\bar x_i'}{ \bar x_i' \gamma} 
+\end{aligned}
 $$
 
-Asymptotically, however, the expression $\sum\frac{a_i}{b_i}$ can be approximated using Taylor expansions by $N\frac{\bar a}{\bar b}$. [^11] Thus, we can rewrite the last term as
+where we use the fact that asymptotically, the expression $\frac{1}{N}\sum \frac{a_i}{b_i}$ can be approximated using Taylor expansions by $\frac{\bar a}{\bar b}$.
+[^11] Thus, we can rewrite the last term as
 
 [^11]: This approximation will be useful when we consider the estimation of the influence functions.
-
-$$\bar G_{3,1} = - f_{\varepsilon}\big(q(\tau)) \frac{\bar x_i'}{\bar x_i'\gamma} 
-$$
 
@@
 \bar G_{3,2} &= -\frac{1}{N} \sum \frac{\partial h_{3,i}}{\partial \gamma'} \\
-             &= -N^{-1} \sum K_h(q(\tau) x_i'\gamma +x_i'\beta - y_i ) q(\tau) x_i' \\
-             &=-N^{-1} \sum f_{y|x}(q(\tau) x_i'\gamma +x_i'\beta ) q(\tau) x_i' \\
-             &=-N^{-1} f_{\varepsilon}(q(\tau)) q(\tau) \sum \frac{x_i'}{x_i'\gamma} \\
-             &=- f_{\varepsilon}(q(\tau)) q(\tau) \frac{\bar x_i'}{\bar x_i'\gamma}
+             &= -N^{-1} \sum \frac{1}{h} k\left( \frac{1}{h} ( q_\tau - \varepsilon_i ) x_i'\gamma  \right) q_\tau x_i'  \\
+             &= -N^{-1} \sum \frac{1}{h} k\left( \frac{q_\tau - \varepsilon_i}{h}    \right) q_\tau \frac{x_i'}{x_i'\gamma}  \\
+             &\simeq  -  f(q_\tau)  q_\tau \frac{\bar x'}{\bar x'\gamma}
 \end{aligned}
@@
 $$\begin{aligned}
-\bar G_{3,3} &= -\frac{1}{N} \sum \frac{\partial h_{3,i}}{\partial q(\tau)} \\
- &= -\frac{1}{N} \sum K_h(q(\tau) x_i'\gamma +x_i'\beta - y_i ) x_i'\gamma \\
- &= -\frac{1}{N} \sum f_{y|X}(q(\tau) x_i'\gamma +x_i'\beta) x_i'\gamma \\
- &= -\frac{1}{N} \sum f_{\varepsilon}(q(\tau)) \frac{x_i'\gamma}{ x_i'\gamma} \\
- &= - f_{\varepsilon}(q(\tau)) 
+\bar G_{3,3} &= -\frac{1}{N} \sum \frac{\partial h_{3,i}}{\partial q_\tau} \\
+             &= -N^{-1} \sum \frac{1}{h} k\left( \frac{1}{h} ( q_\tau - \varepsilon_i ) x_i'\gamma  \right) x_i'\gamma  \\
+             &= -N^{-1} \sum \frac{1}{h} k\left( \frac{q_\tau - \varepsilon_i}{h}   \right) \frac{x_i'\gamma}{x_i'\gamma}  \\
+             &\simeq  -  f(q_\tau)  
 \end{aligned}
@@
 $$\begin{aligned}
-\lambda_i(q(\tau))&=\bar G_{3,3}^{-1}
+\lambda_i(q_\tau)&=\bar G_{3,3}^{-1}
 \Big(
@@
 \Big) \\
-&=-\frac{1}{f_{\varepsilon}(q(\tau))} \times \Bigg( \Big(\mathbb{1} ( q(\tau)  \geq \varepsilon  ) - \tau \Big)  \\
-&+ f_{\varepsilon} (q(\tau)) \frac{\bar x_i'}{\bar x_i'\gamma} 
+&=-\frac{1}{f_{\varepsilon}(q_\tau)} \times \Bigg( \Big(\mathbb{1} ( q_\tau  \geq \varepsilon  ) - \tau \Big)  \\
+&+ f_{\varepsilon} (q_\tau) \frac{\bar x_i'}{\bar x_i'\gamma} 
 N (X'X)^{-1} x_i  ( x_i'\gamma \times \varepsilon) \\
-&+ f_{\varepsilon}(q(\tau)) q(\tau) \frac{\bar x_i'}{\bar x_i'\gamma} N(X'X)^{-1} x_i   \big( \tilde \nu_i -x_i' 
+&+ f_{\varepsilon}(q_\tau) q_\tau \frac{\bar x_i'}{\bar x_i'\gamma} N(X'X)^{-1} x_i   \big( \tilde \nu_i -x_i' 
   \gamma \big) 
 \Bigg) \\
-&=\frac{\tau-\mathbb{1}\big( q(\tau)  \geq \varepsilon  \big) }{f_{\varepsilon}(q(\tau))}
+&=\frac{\tau-\mathbb{1}\big( q_\tau  \geq \varepsilon  \big) }{f_{\varepsilon}(q_\tau)}
 - \frac{ x_i'\gamma \times \varepsilon_i }{\bar x_i'\gamma} 
--  q(\tau) \frac{ \tilde \nu_i -x_i' 
+-  q_\tau \frac{ \tilde \nu_i -x_i' 
   \gamma }{\bar x_i'\gamma} 

### 2024-02-06 article/article.tex
c
update and Sims

@@
 \bibliographystyle{elsarticle-harv}
-\IfFileExists{bookmark.sty}{\usepackage{bookmark}}{\usepackage{hyperref}}
+\usepackage{bookmark}
+
 \IfFileExists{xurl.sty}{\usepackage{xurl}}{} % add URL line breaks if available
@@
 \hypersetup{
-  pdftitle={Quantile Regressions via Method of Moments with multiple fixed effects },
+  pdftitle={Estimating Quantile Regressions with Multiple Fixed Effects through Method of Moments },
   pdfauthor={Fernando Rios-Avila; Leonardo Siles; Gustavo Canavire-Bacarreza},
@@
 \begin{frontmatter}
-\title{Quantile Regressions via Method of Moments with multiple fixed
-effects \tnoteref{t1}}
+\title{Estimating Quantile Regressions with Multiple Fixed Effects
+through Method of Moments \tnoteref{t1}}
 \author[1]{Fernando Rios-Avila%
@@
 }
- \ead{leonardosiles@hotmail.com} 
+ \ead{leonardo.siles@ucb.edu.bo} 
 \author[3]{Gustavo Canavire-Bacarreza%
@@
 \end{frontmatter}
-    \ifdefined\Shaded\renewenvironment{Shaded}{\begin{tcolorbox}[borderline west={3pt}{0pt}{shadecolor}, breakable, frame hidden, interior hidden, enhanced, boxrule=0pt, sharp corners]}{\end{tcolorbox}}\fi
-
-\hypertarget{introduction}{%
-\section{Introduction}\label{introduction}}
+
+\section{Introduction}\label{introduction}
 
@@
 characterizations of the relationships between dependent and independent
-variables, by accounting for otherwise unobserved heterogeneity.
+variables, by exploring how the variables relate along the entire
+conditional distribution.
 
@@
 
-In this framework, our paper expands on \citet{mss2019}, following some
-of the suggestions by these authors regarding further research. First,
-making use of the properties of generalized method of moments (GMM)
-estimators, we derive various alternatives for the estimation of
+In this framework, our paper expands on \citet{mss2019} in two ways.
+First, making use of the properties of generalized method of moments
+(GMM) estimators, we derive various alternatives for the estimation of
 standard errors based on the empirical influence functions of the
-estimators. Second, we reconsider the application of Frisch-Waugh-Lovell
-(FWL) theorem \citep[ and \citet{lovell1963}]{frishwaugh1933} to extend
-the MSS estimator to allow for the inclusion of multiple fixed effects,
-for example, individual and year fixed effects.
+estimators. Even if the model is correctly specified, robust standard
+errors perform better than GLS standard errors due small violations of
+the model assumptions due to sampling variability. Furthermore,
+clustered standard errors may help to further account for typically
+unobserved correlations across observations. Second, we reconsider the
+application of Frisch-Waugh-Lovell (FWL) theorem \citep[ and
+\citet{lovell1963}]{frishwaugh1933} to extend the MSS estimator and
+allow for the inclusion of multiple fixed effects. This extension may be
+useful for empirical analysis, as it is common to control for multiple
+fixed effects such as individual and time fixed effects.
 
@@
 small simulation study and section 4 illustrates the application of the
-proposed methods with two empirical examples. Section 5 concludes.
-
-\hypertarget{sec-method}{%
-\section{Methodology}\label{sec-method}}
-
-\hypertarget{sec-betas}{%
-\subsection{Quantile Regression: Location-Scale model}\label{sec-betas}}
+proposed methods with one empirical example. Section 5 concludes.
+
+\section{Methodology}\label{sec-method}
+
+\subsection{Quantile Regression: Location-Scale model}\label{sec-betas}
 
@@
 
-\begin{equation}\protect\hypertarget{eq-eq1}{}{Q_y(\tau|X) =X\beta(\tau)
-}\label{eq-eq1}\end{equation}
-
-This allows for nonlinearities in the effect of \(X\) on \(Y\) across
-all values of \(\tau\). This formulation can also be related to a random
-coefficient model, in which all coefficients are assumed to be some
-nonlinear function of \(\tau\) where \(\tau\) follows a random uniform
-distribution.
+\begin{equation}\phantomsection\label{eq-eq1}{Q_y(\tau|X) =X\beta(\tau)
+}\end{equation}
+
+This allows for a linear effect of \(X\) on \(Y\), but that could vary
+across values of \(\tau\).
 
@@
 
-\begin{equation}\protect\hypertarget{eq-eq2}{}{Q_y(\tau|X) =X\beta+X\gamma(\tau)
-}\label{eq-eq2}\end{equation}
+\begin{equation}\phantomsection\label{eq-eq2}{Q_y(\tau|X) =X\beta+X\gamma(\tau)
+}\end{equation}
 
@@
 linear regression model (as in \citet{mss2019}) or a median regression
-(as in \citet{zhao2000}) and the scale parameters \(\gamma(\tau)\) can
-be estimated using standard approaches.
+(as in \citet{he1997} and \citet{zhao2000}) and the scale parameters
+\(\gamma(\tau)\) can be estimated using standard approaches.
 
@@
 One insightful extension to the location-scale parameterizations
-suggested by \citet{he1997}, \citet{cameron2005}, and \citet{mss2019} is
-to assume that the data-generating process (DGP) can be written as a
-linear model with a multiplicative heteroskedastic process that is
-linear in parameters.\footnote{\citet{mss2019} also discuss a model
-  where heteroskedasticity can be an arbitrary nonlinear function
-  \(\sigma(x_i'\gamma)\), but develop the estimator for the linear case,
-  i.e., when \(\sigma()\) is the identity function.}
-
-\begin{equation}\protect\hypertarget{eq-eq4}{}{\begin{aligned}
+suggested by \citet{he1997}, \citet{zhao2000}, \citet{cameron2005}, and
+\citet{mss2019} is to assume that the data-generating process (DGP) can
+be written as a linear model with a multiplicative heteroskedastic
+process that is linear in parameters.\footnote{\citet{mss2019} also
+  discuss a model where heteroskedasticity can be an arbitrary nonlinear
+  function \(\sigma(x_i'\gamma)\), but develop the estimator for the
+  linear case, i.e., when \(\sigma()\) is the identity function.}
+
+\begin{equation}\phantomsection\label{eq-eq4}{\begin{aligned}
 y_i &=x_i'\beta+\nu_i \\
@@
 
-\begin{equation}\protect\hypertarget{eq-eq5}{}{Q_y(\tau|X) =X\beta+Q_\varepsilon(\tau) \times X\gamma 
-}\label{eq-eq5}\end{equation}
+\begin{equation}\phantomsection\label{eq-eq5}{Q_y(\tau|X) =X\beta+Q_\varepsilon(\tau) \times X\gamma 
+}\end{equation}
 
@@
 standardized error \(\varepsilon\). For simplicity we will use
-\(q(\tau)\) to denote \(Q_\varepsilon(\tau)\) in the rest of the paper.
-
-\begin{equation}\protect\hypertarget{eq-eq6}{}{\beta(\tau) = \beta + q(\tau) \times \gamma 
-}\label{eq-eq6}\end{equation}
+\(q_\tau\) to denote \(Q_\varepsilon(\tau)\) in the rest of the paper.
+
+\begin{equation}\phantomsection\label{eq-eq6}{\beta(\tau) = \beta + q_\tau \times \gamma 
+}\end{equation}
 
@@
 because the location-scale model can be identified globally, with only a
-single parameter (\(q(\tau)\)) requiring local estimation, this
+single parameter (\(q_\tau\)) requiring local estimation, this
 estimation approach will be more efficient than the standard quantile
@@
 \(X\gamma\) is strictly positive, the model will produce quantile
-coefficients that do not cross.
+coefficients that do not cross (\citet{he1997}).
 
@@
 moments approach. And while it is possible to identify all coefficients
-(\(\beta,\gamma, q(\tau)\)) simultaneously, we describe and use the
+(\(\beta,\gamma, q_\tau\)) simultaneously, we describe and use the
 implementation approach advocated by MSS, which identifies each set of
@@
   \end{aligned}
-}\label{eq-eq8}\end{equation}
+}\end{equation}
+
+It should be noticed that the estimation of the standard errors (next
+section) requires that the Scale component prediction \(x_i'\gamma\) is
+strictly positive, because it represents the conditional standard
+deviation of the error \(\nu_i\). Because this component is identified
+using a linear model, some values for \(x_i'\gamma\) may be negative,
+which will affect the estimation of the standard errors, as shown in the
+simulation study.
 
@@
 
-\begin{equation}\protect\hypertarget{eq-eq9}{}{\begin{aligned}
-  E\left[  \mathbb{1}\left(x_i' (\beta +   \gamma q(\tau)) \geq y_i \right) - \tau \right] &=0  \\
-  E\left[  \mathbb{1}\left(   q(\tau) \geq \frac{y_i-x_i'\beta}{x_i'\gamma} \right) - \tau \right] &=0  \\
-  \end{aligned}
-}\label{eq-eq9}\end{equation}
+\begin{equation}\phantomsection\label{eq-eq9}{\begin{aligned}
+  E\left[  \mathbb{1}\left(x_i' (\beta +   \gamma q_\tau) \geq y_i \right) - \tau \right] &=0  \\
+  E\left[  \mathbb{1}\left(   q_\tau \geq \frac{y_i-x_i'\beta}{x_i'\gamma} \right) - \tau \right] &=0  \\
+  \end{aligned}
+}\end{equation}
 
@@
 the values that identify the overall quantile coefficients
-\(\beta(\tau)=\beta + \gamma q(\tau)\). Afterwards, the conditional
+\(\beta(\tau)=\beta + \gamma q_\tau\). Afterwards, the conditional
 quantile coefficients are simply defined as the combination of the
@@
 
-\begin{equation}\protect\hypertarget{eq-eq10}{}{\begin{aligned}
+\begin{equation}\phantomsection\label{eq-eq10}{\begin{aligned}
   E[x_i \nu_i  ] &= E[h_{1,i}]=0 \\
   E[x_i  (|\nu_i|-x_i \gamma) ] &=E[h_{2,i}]=0 \\
-  E\left[  \mathbb{1}\left(   q(\tau)\geq \frac{y_i-x_i'\beta}{x_i'\gamma} \right) - \tau \right] 
-  &=E[h_{3,i}]=0 
-  \end{aligned}
-}\label{eq-eq10}\end{equation}
+  E\left[  \mathbb{1}\left(   q_\tau\geq \frac{y_i-x_i'\beta}{x_i'\gamma} \right) - \tau \right]  &=E[h_{3,i}]=0 
+  \end{aligned}
+}\end{equation}
 
@@
 
-Call \(\theta=[ \beta' \ \ \gamma' \ \ q(\tau) ]'\) the set of
+Call \(\theta=[ \beta' \ \ \gamma' \ \ q_\tau ]'\) the set of
 coefficients that are identified by the moment conditions in
@@
 of the location-scale-quantile estimates, will follow a normal
-distribution with mean
-\(\beta(\tau) = \beta+\gamma q(\varepsilon | \tau)\) and
+distribution with mean \(\beta(\tau) = \beta+\gamma q_\tau\) and
 variance-covariance matrix equal to
@@
 
-\begin{equation}\protect\hypertarget{eq-eqqtile}{}{\Xi = [ I(k), \hat q(\tau) \times I(k), \hat \gamma ]
-}\label{eq-eqqtile}\end{equation}
+\begin{equation}\phantomsection\label{eq-eqqtile}{\Xi = [ I(k), \hat q_\tau \times I(k), \hat \gamma ]
+}\end{equation}
 
@@
 
-\begin{equation}\protect\hypertarget{eq-eqvcv}{}{\hat{V}(\theta) = \frac{1}{N^2} \sum_{i=1}^N \lambda_i(\theta) \lambda_i(\theta)'
-}\label{eq-eqvcv}\end{equation}
+\begin{equation}\phantomsection\label{eq-eqvcv}{\hat{V}(\theta) = \frac{1}{N^2} \sum_{i=1}^N \lambda_i(\theta) \lambda_i(\theta)'
+}\end{equation}
 
@@
 
-For the specific case of quantile regressions through moments, the
-influence functions for the location, scale, and quantile coefficients
+For the specific case of quantile regressions via moments, the influence
+functions for the location, scale, and quantile coefficients
 are\footnote{The derivation of the influence functions can be found in
@@
 \lambda_{i}(\gamma)&= N(X'X)^{-1} x_i ( x_i' \gamma ) \times (\tilde \varepsilon_i -1\big)\\
-\lambda_{i}(q(\tau))&=\frac{\tau-\mathbb{1}\big( q(\tau)  \geq \varepsilon_i  \big) }{f_{\varepsilon}(q(\tau))}
+\lambda_{i}(q_\tau)&=\frac{\tau-\mathbb{1}\big( q_\tau  \geq \varepsilon_i  \big) }{f_{\varepsilon}(q_\tau)}
 - \frac{ x_i'\gamma \times \varepsilon_i }{\bar x_i'\gamma} 
--  q(\tau) \frac{  x_i' \gamma  \times (\tilde \varepsilon_i -1\big)}{\bar x_i'\gamma}
-\end{aligned}
-}\label{eq-ifs}\end{equation}
+-  q_\tau \frac{  x_i' \gamma  \times (\tilde \varepsilon_i -1\big)}{\bar x_i'\gamma}
+\end{aligned}
+}\end{equation}
 
@@
 
-This estimator of standard errors should be robust to arbitrary
-heteroskedasticity. However, because the location-scale specification
-relies on the correct specification of the model heteroskedasticity,
-large differences in standard errors compared to GLS-standard errors may
-be an indication of misspecification of the model.
-
-\hypertarget{clustered-standard-errors}{%
+This estimator of standard errors may prove useful for two reasons.
+First, this estimator would be robust to misspecification of the scale
+model assumptions, and thus it could be used as an informal test for the
+validity of the model assumptions when compared to the GLS-standard
+error (Section~\ref{sec-gls}). Second, as shown in the simulation study,
+this estimator performs better than GLS-standard errors even if the
+model is correctly specified, because of problemes caused when
+\(x\hat\gamma\) is not strictly positive.
+
 \subsubsection{Clustered Standard
-Errors}\label{clustered-standard-errors}}
+Errors}\label{clustered-standard-errors}
 
@@
 
-\hypertarget{gls-standard-errors}{%
-\subsubsection{GLS Standard Errors}\label{gls-standard-errors}}
+\subsubsection{GLS Standard Errors}\label{sec-gls}
 
@@
 
-This estimator of stand ard errors is equivalent to the one derived by
-MSS using Theorem 3.
-
-\hypertarget{multiple-fixed-effects-expanding-on-mss2019}{%
+This estimator of standard errors is equivalent to the one derived by
+MSS using Theorem 3. Empirically, the simulation study shows that this
+estimator may severily over estimate the standard errors, even if the
+model is correctly specified. This happens because the sample estimates
+of the scale model coefficients may be negative or close to zero.
+
 \subsection{\texorpdfstring{Multiple Fixed Effects: Expanding on
-\citet{mss2019}}{Multiple Fixed Effects: Expanding on @mss2019}}\label{multiple-fixed-effects-expanding-on-mss2019}}
-
-Using the setup described in the previous section, \citet{mss2019}
-proposes an extension to the model proposed by \citet{he1997} that
-enables the estimation of quantile regression models with panel data,
-allowing for the inclusion of individual fixed effects. However, as the
-authors suggest, the methodology can be generalized to allow for the
-inclusion of multiple fixed effects. This type of analysis can be useful
-when considering data such as employer-employee linked data
-\citep{abowed2006} or teacher-student linked data
-\citep{harrissass2011}. Or, in the most common case, allowing to control
-for both individual and time fixed effects.
+\citet{mss2019}}{Multiple Fixed Effects: Expanding on @mss2019}}\label{multiple-fixed-effects-expanding-on-mss2019}
+
+Using the setup described in the previous section, MSS proposes an
+extension to the model proposed by \citet{he1997} that enables the
+estimation of quantile regression models with panel data, allowing for
+the inclusion of individual fixed effects. However, the methodology can
+also be generalized to allow for the inclusion of multiple fixed
+effects. This type of analysis can be useful when considering data such
+as employer-employee linked data \citep{abowed2006} or teacher-student
+linked data \citep{harrissass2011}. Or, in the most common case,
+allowing to control for both individual and time fixed effects.
 
 We return to the original model and now assume there are sets of
-unobserved heterogeneity that are assumed to be constant across
-observations, if they belong to common groups. In panel data, the groups
-would be the individual fixed effects and the time fixed effects.
-Without loss of generality, we can assume that the data-generating
-process is as follows:
+unobserved heterogeneity that are constant across observations, if they
+belong to common groups. Without loss of generality, we can assume that
+the data-generating process is as follows:
 
@@
 thus are not collinear) and that \(\delta's\) and \(\zeta's\) are the
-location and scale effects associated with groups fixed
+location and scale effects associated with the groups fixed
 effects.\footnote{We could just as well consider multiple sets of fixed
@@
 However, if the dimensionality of \(g_k\) is high, the dummy inclusion
-approach may not be feasible. A more feasible approach is to apply the
-FWL theorem and partial out the impact of the group fixed effects on the
-control variables \(x_{i}\), and the outcome of interest \(y_{i}\),
-using a similar approach for the identification of \(\sigma(x)\). In the
-case of unbalanced setups with multiple groups, the estimation involves
-iterative processes for which various approaches have been suggested and
-implemented (see for example, \citet{correia_feasible_nodate},
-\citet{gaure2013}, \citet{rios2015}, among others).
+approach may not be computationally feasible. A more feasible approach
+is to apply the FWL theorem and partial out the impact of the group
+fixed effects on the control variables \(x_{i}\), and the outcome of
+interest \(y_{i}\), and using a similar approach for the identification
+of \(\sigma(x)\). In the case of unbalanced setups with multiple groups,
+the estimation involves iterative processes for which various approaches
+have been suggested and implemented (see for example,
+\citet{correia_feasible_nodate}, \citet{gaure2013}, \citet{rios2015},
+among others).
 
@@
 
-\hypertarget{simulation-evidence}{%
-\section{Simulation Evidence}\label{simulation-evidence}}
+\section{Simulation Evidence}\label{simulation-evidence}
 
@@
 \(\chi_i \sim \chi^2(1)\). We only consider the case when the error term
-\(\varepsilon_i\) is assumed to be normally distributed with mean 0 and
-standard deviation of 0.5. We assume that there are 50 mutually
-exclusive fixed effect groups for each set of fixed effects.
-Observations are assigned to each subgroup randomly using a uniform
-distribution between 1 and 50. We consider sample sizes of 500, 1000,
-2000, and 4000 observations, which implies an average of 10, 20, 40, and
-80 observations per group. The model is estimated using the
+\(\varepsilon_i\) is assumed to follow a centered \(\chi^2\)
+distribution.\footnote{Specifically we assume
+  \(\varepsilon=\frac{r_i}{5}-1\), where \(r_i\) follows a chi-squared
+  distribution such that \(r_i \sim \chi^2(5)\). Simulations under the
+  assumption of normal errors are available upon request.} We assume
+that there are 50 mutually exclusive groups for each set of fixed
+effects. Observations are assigned to each subgroup randomly using a
+uniform distribution between 1 and 50. We consider sample sizes of 500,
+1000, 2000, and 4000 observations, which implies an average of 10, 20,
+40, and 80 observations per group. The model is estimated using the
 location-scale model with heteroskedastic linear errors and we report
@@
   bias-corrected estimator is then obtained as
-  \(\hat\beta(\tau)_{jkc}=2*\hat\beta(\tau)_{full}-0.5*\big(\hat\beta(\tau)_{s1}+\hat\beta(\tau)_{s1}\big)\).}
+  \(\hat\beta(\tau)_{jkc}=2*\hat\beta(\tau)_{full}-0.5*\big(\hat\beta(\tau)_{s1}+\hat\beta(\tau)_{s2}\big)\).}
 These results are labeled JKC.
@@
 Similar to the findings in MSS, we find that while the estimator
-presents a bias when the sample is small (\(N=500\)), this bias shrinks
-as the sample size increases. As MSS describes, the bias seems to be
-proportional to the sample size, or more precisely to \(N/N_{g1}\) and
-\(N/N_{g2}\), where \(N_{g1}\) and \(N_{g2}\) are the average number of
-observations per group. Interestingly, the bias-corrected estimator
-presents an almost 0 bias, even when the samples are small (about 10
-observations per subgroup). Moreover, we find that despite the bias
-reduction obtained using the JKC estimator, the standard errors and mean
-squared error (MSE) are larger than without correction, which also
-replicates the results of MSS,
-
-\hypertarget{tbl-sim1}{}
-\begin{longtable}[]{@{}
-  >{\raggedright\arraybackslash}p{(\columnwidth - 14\tabcolsep) * \real{0.1250}}
-  >{\centering\arraybackslash}p{(\columnwidth - 14\tabcolsep) * \real{0.1250}}
-  >{\centering\arraybackslash}p{(\columnwidth - 14\tabcolsep) * \real{0.1250}}
-  >{\centering\arraybackslash}p{(\columnwidth - 14\tabcolsep) * \real{0.1250}}
-  >{\raggedright\arraybackslash}p{(\columnwidth - 14\tabcolsep) * \real{0.1250}}
-  >{\centering\arraybackslash}p{(\columnwidth - 14\tabcolsep) * \real{0.1250}}
-  >{\centering\arraybackslash}p{(\columnwidth - 14\tabcolsep) * \real{0.1250}}
-  >{\centering\arraybackslash}p{(\columnwidth - 14\tabcolsep) * \real{0.1250}}@{}}
+presents a substantial bias when the sample is small (\(N=500\)), this
+bias shrinks as the sample size increases. As MSS describes, the bias
+seems to be proportional to the sample size, or more precisely to
+\(N/N_{g1}\) and \(N/N_{g2}\), where \(N_{g1}\) and \(N_{g2}\) are the
+average number of observations per group. Interestingly, the
+bias-corrected estimator presents an almost 0 bias for the 25th
+percentile, even when the samples are small (about 10 observations per
+subgroup). In contrast, when considering the 75th percentile, the simple
+estimator shows smaller bias than the Jacknife estimator.{[}\^{}88: This
+is also consistent with simulations with a single fixed effect{]} In
+either case, despite the bias reduction obtained using the JKC
+estimator, the standard errors are larger than without correction. For
+the 25th quantile, the reduction in bias is large enough to produce a
+smaller Mean Squared Error (MSE) than the simple estimator. This is
+similar to the results of MSS.
+
+\begin{table}
+
 \caption{\label{tbl-sim1}Bias, Simulated Standard error, and Mean
-Squared Error}\tabularnewline
-\toprule\noalign{}
-\begin{minipage}[b]{\linewidth}\raggedright
-N = 500
-\end{minipage} & \begin{minipage}[b]{\linewidth}\centering
-Bias
-\end{minipage} & \begin{minipage}[b]{\linewidth}\centering
-Sim SE
-\end{minipage} & \begin{minipage}[b]{\linewidth}\centering
-MSE
-\end{minipage} & \begin{minipage}[b]{\linewidth}\raggedright
-N = 1000
-\end{minipage} & \begin{minipage}[b]{\linewidth}\centering
-Bias
-\end{minipage} & \begin{minipage}[b]{\linewidth}\centering
-Sim SE
-\end{minipage} & \begin{minipage}[b]{\linewidth}\centering
-MSE
-\end{minipage} \\
-\midrule\noalign{}
-\endfirsthead
-\toprule\noalign{}
-\begin{minipage}[b]{\linewidth}\raggedright
-N = 500
-\end{minipage} & \begin{minipage}[b]{\linewidth}\centering
-Bias
-\end{minipage} & \begin{minipage}[b]{\linewidth}\centering
-Sim SE
-\end{minipage} & \begin{minipage}[b]{\linewidth}\centering
-MSE
-\end{minipage} & \begin{minipage}[b]{\linewidth}\raggedright
-N = 1000
-\end{minipage} & \begin{minipage}[b]{\linewidth}\centering
-Bias
-\end{minipage} & \begin{minipage}[b]{\linewidth}\centering
-Sim SE
-\end{minipage} & \begin{minipage}[b]{\linewidth}\centering
-MSE
-\end{minipage} \\
-\midrule\noalign{}
-\endhead
-\bottomrule\noalign{}
-\endlastfoot
-q25 & & & & q25 & & & \\
-~mmqreg & 0.104 & 0.247 & 0.072 & ~mmqreg & 0.050 & 0.173 & 0.032 \\
-~jkc & 0.008 & 0.297 & 0.088 & ~jkc & -0.001 & 0.191 & 0.036 \\
-q75 & & & & q75 & & & \\
-~mmqreg & -0.091 & 0.251 & 0.071 & ~mmqreg & -0.044 & 0.176 & 0.033 \\
-~jkc & 0.002 & 0.303 & 0.092 & ~jkc & 0.006 & 0.195 & 0.038 \\
-\textbf{N = 2000} & \textbf{Bias} & \textbf{Sim SE} & \textbf{MSE} &
-\textbf{N = 4000} & \textbf{Bias} & \textbf{Sim SE} & \textbf{MSE} \\
-q25 & & & & q25 & & & \\
-~mmqreg & 0.025 & 0.122 & 0.016 & ~mmqreg & 0.012 & 0.087 & 0.008 \\
-~jkc & 0.003 & 0.129 & 0.017 & ~jkc & 0.000 & 0.089 & 0.008 \\
-q75 & & & & q75 & & & \\
-~mmqreg & -0.023 & 0.124 & 0.016 & ~mmqreg & -0.011 & 0.087 & 0.008 \\
-~jkc & 0.001 & 0.131 & 0.017 & ~jkc & 0.000 & 0.089 & 0.008 \\
-\end{longtable}
+Squared Error}
+
+\centering{
+
+\begin{tabular}{l*{6}{c}cccccccccccc}
+\hline
+            &     \multicolumn{3}{c}{N = 500}   &     \multicolumn{3}{c}{N = 1000}            \\
+            &  Mean Bias &          SE&        MSE&   Mean Bias&          SE&        MSE \\
+\hline
+q25         &            &            &            &            &            &            \\
+\ mmqreg      &       0.173&       0.233&       0.084&       0.100&       0.155&       0.034\\
+\ jkc         &       0.051&       0.278&       0.080&       0.022&       0.170&       0.029\\
+\hline
+q75         &            &            &            &            &            &            \\
+\ mmqreg      &      -0.039&       0.384&       0.149&      -0.003&       0.279&       0.078\\
+\ jkc         &       0.067&       0.469&       0.224&       0.033&       0.305&       0.094\\
+\hline
+            &     \multicolumn{3}{c}{N = 2000}   &     \multicolumn{3}{c}{N = 4000}            \\
+            &  Mean Bias &          SE&        MSE&   Mean Bias&          SE&        MSE \\
+\hline
+q25         &            &            &            &            &            &            \\
+\ mmqreg      &       0.052&       0.107&       0.014&       0.027&       0.074&       0.006\\
+\ jkc         &       0.007&       0.113&       0.013&       0.002&       0.077&       0.006\\
+\hline
+q75         &            &            &            &            &            &            \\
+\ mmqreg      &       0.004&       0.195&       0.038&       0.007&       0.138&       0.019\\
+\ jkc         &       0.009&       0.204&       0.042&       0.004&       0.141&       0.020\\
+\hline
+\multicolumn{7}{p{.7\textwidth}}{ \footnotesize Note: mmqreg - The proposed estimator. 
+JKC-Jacknife Bias Corrected Estimator. SE- Simulated Standard Error.
+MSE - Mean Squared Error. Mean bias is the difference 
+between the estimated coefficient and the analytical true value. }\\
+\end{tabular}
+
+}
+
+\end{table}%
 
@@
 
-\hypertarget{tbl-sim2}{}
 \begin{longtable}[]{@{}lcccc@{}}
-\caption{\label{tbl-sim2}Heteroskedasticity misspecification and
-clustered errors}\tabularnewline
+\caption{Heteroskedasticity misspecification and clustered
+errors}\label{tbl-sim2}\tabularnewline
 \toprule\noalign{}
@@
 
-\hypertarget{illustrative-application}{%
-\section{Illustrative application}\label{illustrative-application}}
+\section{Illustrative application}\label{illustrative-application}
 
@@
   >{\centering\arraybackslash}p{(\columnwidth - 18\tabcolsep) * \real{0.0988}}@{}}
-\caption{\label{tbl-tb1}Determinants of Government Surpluses: Individual
-Fixed Effects}\tabularnewline
+\caption{Determinants of Government Surpluses: Individual Fixed
+Effects}\label{tbl-tb1}\tabularnewline
 \toprule\noalign{}
@@
   >{\centering\arraybackslash}p{(\columnwidth - 14\tabcolsep) * \real{0.1194}}@{}}
-\caption{\label{tbl-tb2}The Determinants of Government Surpluses:
-Individual and Time Fixed Effects}\tabularnewline
+\caption{The Determinants of Government Surpluses: Individual and Time
+Fixed Effects}\label{tbl-tb2}\tabularnewline
 \toprule\noalign{}
@@
 
-\hypertarget{conclusions}{%
-\section{Conclusions}\label{conclusions}}
+\section{Conclusions}\label{conclusions}
 
@@
 
-\hypertarget{references}{%
-\section*{References}\label{references}}
+\section*{References}\label{references}
 \addcontentsline{toc}{section}{References}
@@
 
-\hypertarget{derivation-of-the-influence-functions}{%
 \section{Derivation of the influence
-functions}\label{derivation-of-the-influence-functions}}
-
-\hypertarget{model-identification}{%
-\subsection{Model Identification}\label{model-identification}}
+functions}\label{derivation-of-the-influence-functions}
+
+\subsection{Model Identification}\label{model-identification}
 
@@
 
-\[q(y | \tau, x) = x'(\beta + q(\varepsilon | \tau) \times \gamma)\]
+\[Q_y(\tau|X) = x'(\beta +Q_\varepsilon(\tau)  \times \gamma)\]
 
@@
 
-For simplicity, the rest of the appendix uses \(q^\varepsilon_\tau\) to
-represent \(q(\varepsilon | \tau)\).
-
-\hypertarget{estimation-of-the-variance-covariance-matrix}{%
+For simplicity, the rest of the appendix uses \(q_\tau\) to represent
+\(Q_\varepsilon(\tau)\).
+
 \subsection{Estimation of the Variance-Covariance
-Matrix}\label{estimation-of-the-variance-covariance-matrix}}
+Matrix}\label{estimation-of-the-variance-covariance-matrix}
 
 In this model, to estimate the variance-covariance matrix the set of
-coefficients \(\theta'=[\beta' \ \gamma' \ q^\varepsilon_\tau]\), we
-need to obtain the influence functions of all coefficients, which are
-defined as
+coefficients \(\theta'=[\beta' \ \gamma' \ q_\tau]\), we need to obtain
+the influence functions of all coefficients, which are defined as
 
@@
 \[\begin{aligned}
-h_{3,i} &= \mathbb{1}\left(q(\tau) x_i'\gamma +x_i'\beta - y_i \geq 0 \right) - \tau \text{ or}\\
-h_{3,i} &= \mathbb{1}\left( q(\tau)  \geq \frac{y_i- x_i'\beta}{x_i'\gamma}  \right) - \tau = \mathbb{1}\big( q(\tau)  \geq \varepsilon  \big) - \tau \\
+h_{3,i} &= \mathbb{1}\left( q_\tau  x_i'\gamma +x_i'\beta - y_i \geq 0 \right) - \tau \text{ or}\\
+h_{3,i} &= \mathbb{1}\left( q_\tau  \geq \frac{y_i- x_i'\beta}{x_i'\gamma}  \right) - \tau = \mathbb{1}\big( q_\tau \geq \varepsilon  \big) - \tau \\
 \end{aligned}
@@
 Because the indicator function \(\mathbb{1}()\) is not differentiable,
-we borrow from the nonparametric literature and approximate the
-indicator function with the integral of a kernel density function
-\(I()\). This function, \(I()\), is a monotonic and symmetrical function
-around 0, with a domain over the real numbers, and a range between 0 and
-1.
-
-With an arbirarily small bandwidth \(h\), this function will approximate
-the indicator function:
+we borrow from the nonparametric literature to approximate this function
+with a kernel function. Call \(k()\) a well behaved kernel function that
+is symetric around 0, and \(K()\) its integral, with range between 0 and
+1. With an arbirarily small bandwidth \(h\), we can use the function
+\(K()\) to approximate the indicator function:
 
 \[
-\lim_{h\rightarrow 0} I\left(\frac{z}{h}\right) \approx \mathbb{1}(z\geq 0)
+\lim_{h\rightarrow 0} K\left(\frac{z}{h}\right) \approx \mathbb{1}(z\geq 0)
 \]
@@
 
-\[h_{3,i} \approx I\left( q(\tau) x_i'\gamma +x_i'\beta - y_i  \right) - \tau\]
+\[h_{3,i} \approx K\left( \frac{1}{h} \Big( q_\tau x_i'\gamma +x_i'\beta - y_i  \Big) \right) - \tau
+\]
 
@@
 \bar G_{3,1} &= -\frac{1}{N} \sum \frac{\partial h_{3,i}}{\partial \beta'} \\
-             &= -N^{-1} \sum K_h(q(\tau) x_i'\gamma +x_i'\beta - y_i ) x_i'
-\end{aligned}
-\]
-
-Under the assumption that we have enough observations within each
-combination of \(x\) that are of multiplicative heteroskedasticity, we
-have
-
-\[\begin{aligned}
-E(K_h(q(\tau) x_i'\gamma +x_i'\beta - y_i )|X) &= f_{y|X}(q(\tau) x_i'\gamma +x_i'\beta) \\
-&=\frac{1}{x_i'\gamma} f_{\varepsilon}(q(\tau)) \\
-\end{aligned}
-\]
-
-where \(f_{y|X}\) is the conditional probability density function of
-\(y\) given \(X\) and \(f_\varepsilon\) is the unconditional
-distribution of the standardized error. With this, we can rewrite the
-Jacobian matrix as
-
-\[\bar G_{3,1} = -N^{-1} f_{\varepsilon}\big(q(\tau)\big) \sum  \frac{x_i'}{x_i'\gamma} 
-\]
-
-Asymptotically, however, the expression \(\sum\frac{a_i}{b_i}\) can be
-approximated using Taylor expansions by \(N\frac{\bar a}{\bar b}\).
-\footnote{This approximation will be useful when we consider the
-  estimation of the influence functions.} Thus, we can rewrite the last
-term as
-
-\[\bar G_{3,1} = - f_{\varepsilon}\big(q(\tau)) \frac{\bar x_i'}{\bar x_i'\gamma} 
-\]
+             &= -N^{-1} \sum \frac{1}{h} k\left( \frac{1}{h} \Big( q_\tau x_i'\gamma +x_i'\beta - y_i  \Big) \right) x_i' \\ 
+             &= -N^{-1} \sum \frac{1}{h} k\left( \frac{1}{h} \big( q_\tau x_i'\gamma - \nu_i \big)   \right) x_i'  \\
+             &= -N^{-1} \sum \frac{1}{h} k\left( \frac{1}{h} ( q_\tau - \varepsilon_i ) x_i'\gamma  \right) x_i'  
+\end{aligned}
+\]
+
+If we condition on \(X\), use the law of iterated expectations, and
+assume that \(\varepsilon_i\) is homoskedastic, we can obtain:
+
+\[\begin{aligned}
+\bar G_{3,1} &= -N^{-1} \sum \frac{1}{h} k\left( \frac{1}{h} ( q_\tau - \varepsilon_i ) x_i'\gamma  \right) x_i'  \\
+             &= -N^{-1} \sum \frac{1}{h} k\left( \frac{q_\tau - \varepsilon_i}{h}  \right)  \frac{x_i'}{x_i'\gamma}  \\
+             &= -N^{-1} f_\varepsilon (q_\tau) \sum  \frac{x_i'}{x_i'\gamma}  
+\end{aligned}
+\]
+
+Finally, this simplifies to: \[\begin{aligned}
+\bar G_{3,1} &\simeq -  f_\varepsilon (q_\tau) \frac{\bar x_i'}{ \bar x_i' \gamma} 
+\end{aligned}
+\]
+
+where we use the fact that asymptotically, the expression
+\(\frac{1}{N}\sum \frac{a_i}{b_i}\) can be approximated using Taylor
+expansions by \(\frac{\bar a}{\bar b}\). \footnote{This approximation
+  will be useful when we consider the estimation of the influence
+  functions.} Thus, we can rewrite the last term as
 
@@
 \[\begin{aligned}
-\bar G_{3,3} &= -\frac{1}{N} \sum \frac{\partial h_{3,i}}{\partial q(\tau)} \\
- &= -\frac{1}{N} \sum K_h(q(\tau) x_i'\gamma +x_i'\beta - y_i ) x_i'\gamma \\
- &= -\frac{1}{N} \sum f_{y|X}(q(\tau) x_i'\gamma +x_i'\beta) x_i'\gamma \\
- &= -\frac{1}{N} \sum f_{\varepsilon}(q(\tau)) \frac{x_i'\gamma}{ x_i'\gamma} \\
- &= - f_{\varepsilon}(q(\tau)) 
-\end{aligned}
-\]
-
-\hypertarget{influence-functions}{%
-\subsection{Influence Functions}\label{influence-functions}}
+\bar G_{3,3} &= -\frac{1}{N} \sum \frac{\partial h_{3,i}}{\partial q_\tau} \\
+             &= -N^{-1} \sum \frac{1}{h} k\left( \frac{1}{h} ( q_\tau - \varepsilon_i ) x_i'\gamma  \right) x_i'\gamma  \\
+             &= -N^{-1} \sum \frac{1}{h} k\left( \frac{q_\tau - \varepsilon_i}{h}   \right) \frac{x_i'\gamma}{x_i'\gamma}  \\
+             &\simeq  -  f(q_\tau)  
+\end{aligned}
+\]
+
+\subsection{Influence Functions}\label{influence-functions}
 
@@
 \[\begin{aligned}
-\lambda_i(q(\tau))&=\bar G_{3,3}^{-1}
+\lambda_i(q_\tau)&=\bar G_{3,3}^{-1}
 \Big(
@@
 
-\hypertarget{implementation}{%
-\section{Implementation}\label{implementation}}
+\section{Implementation}\label{implementation}
 

### 2024-02-07 article/article.qmd
s
update Paper

@@
 ---
-title: Estimating Quantile Regressions with Multiple Fixed Effects through Method of Moments \tnoteref{t1}
+title: Estimating Quantile Regressions with Multiple Fixed Effects through Method of Moments \tnoteref{t1,t2}
 author:
@@
           name: Levy Economics Institute of Bard College
+          city: Annandale-on-Hudson, NY
+          country: USA          
     attributes:
@@
     affiliations:
-        - name: Universidad Católica Boliviana
-          id: ucb
+        - id: ucb
+          name: Universidad Católica Boliviana
+          city: La Paz
+          country: Bolivia
   - name: Gustavo Canavire-Bacarreza
@@
         - id: wb
-          name: World Bank                 
+          name: The World Bank                 
+          city: Washington, D.C.
+          country: USA
 abstract: |
@@
         \tnotetext[t1]{The opinions expressed in this paper are those of the authors and do not necessarily reflect the views of the World Bank, its Board of Directors, or the countries it represents.}
+        \tnotetext[t2]{The authors would like to thank Enrique Pinzon an Joao Santos-Silva for their helpful comments and suggestions.}
+
 ---
@@
 While this specification imposes a strong assumption on the DGP, it has two advantages over the standard quantile regression model.
-First, because the location-scale model can be identified globally, with only a single parameter ($q_\tau$) requiring local estimation, this estimation approach will be more efficient than the standard quantile regression model (@zhao2000).
-Second, under the assumption that $X\gamma$ is strictly positive, the model will produce quantile coefficients that do not cross (@he1997).
+First, because the location-scale model can be identified globally, with only a single parameter ($q_\tau$) requiring local estimation, this estimation approach will be more efficient than the standard quantile regression model [@zhao2000].
+Second, under the assumption that $X\gamma$ is strictly positive, the model will produce quantile coefficients that do not cross [@he1997].
 
@@
 
-This estimator of standard errors may prove useful for two reasons.
-First, this estimator would be robust to misspecification of the scale model assumptions, and thus it could be used as an informal test for the validity of the model assumptions when compared to the GLS-standard error (@sec-gls).
-Second, as shown in the simulation study, this estimator performs better than GLS-standard errors even if the model is correctly specified, because of problemes caused when $x\hat\gamma$ is not strictly positive.
-
 ### Clustered Standard Errors
@@
 This estimator of standard errors is equivalent to the one derived by MSS using Theorem 3.
-Empirically, the simulation study shows that this estimator may severily over estimate the standard errors, even if the model is correctly specified.
-This happens because the sample estimates of the scale model coefficients may be negative or close to zero.
+Empirically, the simulation study shows that this estimator may be very sensitive to predictions of the scale model.
+In the simulation study, we show that when the sample small, and the likelihood of predicting zero or negative values for the scale model is high, the GLS standard errors may be unreasonably large.
 
@@
 We consider a simple model with a single explanatory variable $x$.
-In contrast with MSS, we consider a two-way fixed effect structure that is more general than the panel structure.
+In contrast with MSS, we consider a two-way fixed effect structure.
 For this exercise, we consider the following data-generating process:
 
-$$y_i = \alpha_{1i} + \alpha_{2i} + x_i + (1+x_i + \alpha_{1i} + \alpha_{2i} ) \varepsilon_i
+$$y_i = \alpha_{1i} + \alpha_{2i} + x_i + (2+x_i + \alpha_{1i} + \alpha_{2i} ) \varepsilon_i
 $$
@@
 Observations are assigned to each subgroup randomly using a uniform distribution between 1 and 50.
+
+To assess the alternative Standard error estimators, we consider a second data-generating process where the error term is correlated within clusters.
+For this, we assume observations are assigned ramdomly to 100 mutually exclusive groups, which are independent from the fixed effect groups.
+In this setup the data-generating process is:
+
+$$\begin{aligned}
+y_i &= \alpha_{1i} + \alpha_{2i} + x_i + (2+x_i + \alpha_{1i} + \alpha_{2i} )*\kappa_i \\
+\kappa_i &= inv-\chi^2_5(r_{i})/5-1 \\
+r_i &= \Phi((\sqrt{.25}*s_{i}+\sqrt{.75}*s_{g}))
+\end{aligned}
+$$
+
+where $s_{i}\sim N(0,1)$ and $s_{g}\sim N(0,1)$, are errors that vary across individuals $i$ or across clusters $g$.
+$\Phi()$ is the cumulative distribution function of a normal distribution, and $inv-\chi^2_5()$ is the inverse function for a Chi-2 distribution with 5 degrees of freedom.
+With this setup, we generate an error structure with a strong intra-cluster correlation, but without affecting the model specification assumption.^[We do not consider the case of misspecification of the scale model because that change would not only have an impact on the standard errors, but also affect the bias of the estimated coefficients]
+
 We consider sample sizes of 500, 1000, 2000, and 4000 observations, which implies an average of 10, 20, 40, and 80 observations per group.
@@
 We run this excercise 5000 times.
-@tbl-sim1 reports the bias, simulated standard error, and mean squared error.
+@tbl-sim1 reports the bias, simulated standard error, and mean squared error, using the first data generation structure only.
 We also report the results obtained using an adaptation bias-corrected estimator based on the split-panel jackknife estimator proposed by @dhaene2015.[^9] These results are labeled JKC.
@@
 Similar to the findings in MSS, we find that while the estimator presents a substantial bias when the sample is small ($N=500$), this bias shrinks as the sample size increases.
-As MSS describes, the bias seems to be proportional to the sample size, or more precisely to $N/N_{g1}$ and $N/N_{g2}$, where $N_{g1}$ and $N_{g2}$ are the average number of observations per group.
-Interestingly, the bias-corrected estimator presents an almost 0 bias for the 25th percentile, even when the samples are small (about 10 observations per subgroup).
+As MSS describes, the bias seems to be proportional to the sample size, or more precisely to the average number of observations per sub-group.
+Interestingly, the bias-corrected estimator presents an almost 0 bias for the 25th percentile, even when the samples are small.
 In contrast, when considering the 75th percentile, the simple estimator shows smaller bias than the Jacknife estimator.[^88: This is also consistent with simulations with a single fixed effect] In either case, despite the bias reduction obtained using the JKC estimator, the standard errors are larger than without correction.
@@
 
-As described in section @sec-se, GLS standard errors may not be appropriate if heteroskedasticity in the model is misspecified.
-This could happen if the heteroskedasticity is not linear in parameters or if there are correlations within groups.
-To show the performance of the GLS standard errors, we consider two additional simulations.
-To see the impact of heteroskedasticity misspecification, we assume the DGP is given by
+To evaluate the performance of the different standard errors, we present bias, 95% coverage of the biased corrected estimates, as well as the simulated standard errors, average and median of the standard errors obtained using the GLS, robust SE, and clustered standard SE.
+@tbl-sim2 considers the d.g.p.
+without intra-cluster correlation, while @tbl-sim3 considers the d.g.p.
+that induces intra-cluster correlations.
+All simulations consider 5000 repetitions.
 
-$$y_i = \alpha_{1i} + \alpha_{2i} + x_i + (1+x_i + \sqrt{x_i} +\alpha_{1i} + \alpha_{2i} ) \varepsilon_i
-$$
+The bias magnitude in @tbl-sim2 and @tbl-sim3 is comparable to those observed in @tbl-sim1, with simulated standard errors that show to be slighly larger when we allow for intra-cluster correlations, just as expected.
+When assuming there is no need to clustered standard errors (@tbl-sim2), the coverage associated to GLS standard errors is above 95% when the samples are small, but it approximates to 95% as the sample size increases.
+On the other and, the coverage rates associated to Robust Standard errors are closer to 90%, albeit increasing slighly for larger samples.
 
-To show the impact of ignoring correlation within groups, we consider the case where the error $\varepsilon$ is correlated within groups defined by the first fixed effect. Specifically:
+One of the main reason that the GLS-Standard errors achieve higher than expected rates of coverage may be related to the fact that the Standard error estimator is very sensitive to near zero predictions from the scale model.
+As shown in @tbl-sim2, average and median GLS-SE are considerably larger than the simulated standard errors when the sample are small.
+While robust standard errors are less sensitive to this problem, producing more stable results, they tend to underestimate the magnitude of the true standard errors in small samples.
+This translates into the lower coverage rates.
 
-$$\varepsilon_i =0.5*(\sqrt{0.5} z_i + \sqrt{0.5} w_g)$$
+::: {#tbl-sim2}
 
-where $z_i~N(0,1)$ and $w_g~N(0,1)$, with $g$ being the $g_{th}$ group defined by the first fixed effect.
+{{< include tb2.tex >}}
 
-For the simulation, we run the excercise 5000 times, using a sample of size $N=2000$.
-The results from both simulations are reported in the @tbl-sim2.
-We report the average coefficient, simulation-based standard errors, and the standard errors using GLS, robust and clustered estimations.
+95% Coverage Ratio, and Standard Error Estimation: No Intra-cluster Correlation
+:::
 
-|             | Het:q25 | Het:q75 | Clust:q25 | Clust:q75 |
-|-------------|:-------:|:-------:|:---------:|:---------:|
-| Coefficient |  0.550  |  1.442  |   0.775   |   1.229   |
-| SIM_SE      |  0.154  |  0.155  |   0.109   |   0.107   |
-| GLS_SE      |  0.476  |  0.451  |   0.288   |   0.221   |
-| Robust      |  0.140  |  0.139  |   0.087   |   0.088   |
-| Cluster     |         |         |   0.097   |   0.097   |
+When we consider the presence of Intra-Cluster correlation, @tbl-sim3, we still observe similar problems with the GLS-SE, albeit with high coverage rates.
+While Robust and Clustered Standard errors are in average smaller than the Simulated Standard errors, coverage rates are above 90%.
+Clustered standard errors perform the best only when the sample size is large, with Robust standard error producing low Standard errors estimates.
 
-: Heteroskedasticity misspecification and clustered errors {#tbl-sim2}
+::: {#tbl-sim3}
 
-One of the conclusions from the results in @tbl-sim2 is that the results for the 25th and 75th quantiles are mostly identical, because of the symmetric error we used in the simulation.
-On the one hand, because the error structure is misspecified, we should expect to see a large bias in the estimated coefficients, especially in cases of misspecified heteroskedasticity.
-However, the purpose of this exercise is not to demonstrate the unbiasedness of the coefficients, but rather to assess the performance of the standard error estimation.
+{{< include tb3.tex >}}
 
-As expected, the GLS standard errors are biased and the bias is larger in the case of misspecified heteroskedasticity.
-In fact, with heteroskedasticity misspecification, the average GLS-SE (0.476) is almost three times as large as the simulation-based standard error (0.154).
-In this first case, robust standard errors perform better, but with a small difference (0.14 to 0.154).
-In the case of clustered correlation, GLS-SE also performs poorly.
-Robust standard errors perform better, but seem to underestimate the magnitude of the true standard errors.
-Finally, cluster standard errors perform the best, with a small difference between the simulation-based standard errors (0.097 to 0.109).
+95% Coverage Ratio, and Standard Error Estimation: With Intra-cluster Correlation
+:::
+
+Overall, the simulation study shows that using GLS-SE estimator may be appropriate when the sample is relatively large.
+When there is suspected presence of intra-cluster correlation, the use of clustered standard errors is recommended in larger samples.
+However, when the sample is small, the use of robust standard errors may be appropriate if GLS standard errors when there is the risk of near-zero predictions from the scale model.
 
@@
 
+May be worth noting that the GLS SE are almost twice as large as the robust and clustered standard errors.
+This is consistent with the results from the simulation study.
+Examining the predictions of the scale model, we find that there are 9 observations with a negative predicted scale, and 9 observations that could be considered outliers.
+This may be the reason for the large GLS standard errors.
+
 |          | polity |  lyp   | trade | prop1564 | prop65 |  lspl  |  ygap  |
@@
 
-Furthermore, we have assessed the impact of misspecified heteroskedasticity and intracluster correlation on the performance of standard error estimations.
+Furthermore, we have assessed the impact of intracluster correlation on the performance of standard error estimations.
 Our findings emphasize the importance of using appropriate standard error estimators to ensure accurate inference.
-In particular, we find that GLS standard errors are biased when the model heteroskedasticity is misspecified and that robust and clustered standard errors perform better in these cases.
-This may also suggest a venue for future research, in which the validity of the location-scale model assumption is tested.
+In particular, we find that GLS standard errors are biased when when the scale model predictions are close to zero or negative, and that Robust and clustered standard errors are more stable in those scenarios.
+Clustered Standard errors perform the best in the presence of intra-cluster correlation, but the advantage is only evident when the sample size is large.
+
+Finally, we have illustrated the application of our extended methodology using data from @persson_economic_2005.
+Our results are consistent with those reported in @mss2019, and we are able to provide robust and clustered standard errors for the location and scale coefficients.
+We find that the GLS standard errors are almost twice as large as the robust and clustered standard errors, which is consistent with the results from our simulation study.
+Nevertheless, there is no drastic change in the original conclusions.
 
@@
 
--   `mmqreg` in Stata: \`net install mmqreg, from(https://friosavila.github.io/stpackages)
--   `mmqreg` in R: Program available in mmqreg repository on GitHub (https://github.com/friosavila/mmqreg)
--   `mmqreg` in Python:
--   `mmqreg` in Julia:
+-   `mmqreg` in Stata: `net install mmqreg, from(https://friosavila.github.io/stpackages)`
+-   `mmqreg` in R: Available on GitHub (https://github.com/friosavila/mmqreg)

### 2024-02-07 article/article.tex
s
update Paper

@@
 \tnotetext[t1]{The opinions expressed in this paper are those of the authors and do not necessarily reflect the views of the World Bank, its Board of Directors, or the countries it represents.}
+\tnotetext[t2]{The authors would like to thank Enrique Pinzon an Joao Santos-Silva for their helpful comments and suggestions.}
 \makeatletter
@@
 \title{Estimating Quantile Regressions with Multiple Fixed Effects
-through Method of Moments \tnoteref{t1}}
+through Method of Moments \tnoteref{t1,t2}}
 \author[1]{Fernando Rios-Avila%
@@
 \affiliation[1]{organization={Levy Economics Institute of Bard
-College},,postcodesep={}}
-\affiliation[2]{organization={Universidad Católica
-Boliviana},,postcodesep={}}
-\affiliation[3]{organization={World Bank},,postcodesep={}}
+College},city={Annandale-on-Hudson,
+NY},country={USA},countrysep={,},postcodesep={}}
+\affiliation[2]{organization={Universidad Católica Boliviana},city={La
+Paz},country={Bolivia},countrysep={,},postcodesep={}}
+\affiliation[3]{organization={The World Bank},city={Washington,
+D.C.},country={USA},countrysep={,},postcodesep={}}
 
@@
 estimation approach will be more efficient than the standard quantile
-regression model (\citet{zhao2000}). Second, under the assumption that
+regression model \citep{zhao2000}. Second, under the assumption that
 \(X\gamma\) is strictly positive, the model will produce quantile
-coefficients that do not cross (\citet{he1997}).
+coefficients that do not cross \citep{he1997}.
 
@@
 
-This estimator of standard errors may prove useful for two reasons.
-First, this estimator would be robust to misspecification of the scale
-model assumptions, and thus it could be used as an informal test for the
-validity of the model assumptions when compared to the GLS-standard
-error (Section~\ref{sec-gls}). Second, as shown in the simulation study,
-this estimator performs better than GLS-standard errors even if the
-model is correctly specified, because of problemes caused when
-\(x\hat\gamma\) is not strictly positive.
-
 \subsubsection{Clustered Standard
@@
 MSS using Theorem 3. Empirically, the simulation study shows that this
-estimator may severily over estimate the standard errors, even if the
-model is correctly specified. This happens because the sample estimates
-of the scale model coefficients may be negative or close to zero.
+estimator may be very sensitive to predictions of the scale model. In
+the simulation study, we show that when the sample small, and the
+likelihood of predicting zero or negative values for the scale model is
+high, the GLS standard errors may be unreasonably large.
 
@@
 variable \(x\). In contrast with MSS, we consider a two-way fixed effect
-structure that is more general than the panel structure. For this
-exercise, we consider the following data-generating process:
-
-\[y_i = \alpha_{1i} + \alpha_{2i} + x_i + (1+x_i + \alpha_{1i} + \alpha_{2i} ) \varepsilon_i
+structure. For this exercise, we consider the following data-generating
+process:
+
+\[y_i = \alpha_{1i} + \alpha_{2i} + x_i + (2+x_i + \alpha_{1i} + \alpha_{2i} ) \varepsilon_i
 \]
@@
 effects. Observations are assigned to each subgroup randomly using a
-uniform distribution between 1 and 50. We consider sample sizes of 500,
-1000, 2000, and 4000 observations, which implies an average of 10, 20,
-40, and 80 observations per group. The model is estimated using the
-location-scale model with heteroskedastic linear errors and we report
-the coefficients for the 25th and 75th quantiles. We run this excercise
-5000 times. Table~\ref{tbl-sim1} reports the bias, simulated standard
-error, and mean squared error. We also report the results obtained using
-an adaptation bias-corrected estimator based on the split-panel
-jackknife estimator proposed by \citet{dhaene2015}.\footnote{For the
-  implementation, we first estimate the model using the full sample,
-  then randomly assign each observation into one of two groups, and
-  finally reestimate the quantile coefficients for each group. The
-  bias-corrected estimator is then obtained as
+uniform distribution between 1 and 50.
+
+To assess the alternative Standard error estimators, we consider a
+second data-generating process where the error term is correlated within
+clusters. For this, we assume observations are assigned ramdomly to 100
+mutually exclusive groups, which are independent from the fixed effect
+groups. In this setup the data-generating process is:
+
+\[\begin{aligned}
+y_i &= \alpha_{1i} + \alpha_{2i} + x_i + (2+x_i + \alpha_{1i} + \alpha_{2i} )*\kappa_i \\
+\kappa_i &= inv-\chi^2_5(r_{i})/5-1 \\
+r_i &= \Phi((\sqrt{.25}*s_{i}+\sqrt{.75}*s_{g}))
+\end{aligned}
+\]
+
+where \(s_{i}\sim N(0,1)\) and \(s_{g}\sim N(0,1)\), are errors that
+vary across individuals \(i\) or across clusters \(g\). \(\Phi()\) is
+the cumulative distribution function of a normal distribution, and
+\(inv-\chi^2_5()\) is the inverse function for a Chi-2 distribution with
+5 degrees of freedom. With this setup, we generate an error structure
+with a strong intra-cluster correlation, but without affecting the model
+specification assumption.\footnote{We do not consider the case of
+  misspecification of the scale model because that change would not only
+  have an impact on the standard errors, but also affect the bias of the
+  estimated coefficients}
+
+We consider sample sizes of 500, 1000, 2000, and 4000 observations,
+which implies an average of 10, 20, 40, and 80 observations per group.
+The model is estimated using the location-scale model with
+heteroskedastic linear errors and we report the coefficients for the
+25th and 75th quantiles. We run this excercise 5000 times.
+Table~\ref{tbl-sim1} reports the bias, simulated standard error, and
+mean squared error, using the first data generation structure only. We
+also report the results obtained using an adaptation bias-corrected
+estimator based on the split-panel jackknife estimator proposed by
+\citet{dhaene2015}.\footnote{For the implementation, we first estimate
+  the model using the full sample, then randomly assign each observation
+  into one of two groups, and finally reestimate the quantile
+  coefficients for each group. The bias-corrected estimator is then
+  obtained as
   \(\hat\beta(\tau)_{jkc}=2*\hat\beta(\tau)_{full}-0.5*\big(\hat\beta(\tau)_{s1}+\hat\beta(\tau)_{s2}\big)\).}
@@
 bias shrinks as the sample size increases. As MSS describes, the bias
-seems to be proportional to the sample size, or more precisely to
-\(N/N_{g1}\) and \(N/N_{g2}\), where \(N_{g1}\) and \(N_{g2}\) are the
-average number of observations per group. Interestingly, the
+seems to be proportional to the sample size, or more precisely to the
+average number of observations per sub-group. Interestingly, the
 bias-corrected estimator presents an almost 0 bias for the 25th
-percentile, even when the samples are small (about 10 observations per
-subgroup). In contrast, when considering the 75th percentile, the simple
-estimator shows smaller bias than the Jacknife estimator.{[}\^{}88: This
-is also consistent with simulations with a single fixed effect{]} In
-either case, despite the bias reduction obtained using the JKC
-estimator, the standard errors are larger than without correction. For
-the 25th quantile, the reduction in bias is large enough to produce a
-smaller Mean Squared Error (MSE) than the simple estimator. This is
-similar to the results of MSS.
+percentile, even when the samples are small. In contrast, when
+considering the 75th percentile, the simple estimator shows smaller bias
+than the Jacknife estimator.{[}\^{}88: This is also consistent with
+simulations with a single fixed effect{]} In either case, despite the
+bias reduction obtained using the JKC estimator, the standard errors are
+larger than without correction. For the 25th quantile, the reduction in
+bias is large enough to produce a smaller Mean Squared Error (MSE) than
+the simple estimator. This is similar to the results of MSS.
 
@@
 q25         &            &            &            &            &            &            \\
-\ mmqreg      &       0.173&       0.233&       0.084&       0.100&       0.155&       0.034\\
-\ jkc         &       0.051&       0.278&       0.080&       0.022&       0.170&       0.029\\
+mmqreg      &       0.169&       0.267&       0.099&       0.092&       0.172&       0.038\\
+jkc         &       0.048&       0.318&       0.104&       0.014&       0.189&       0.036\\
 \hline
 q75         &            &            &            &            &            &            \\
-\ mmqreg      &      -0.039&       0.384&       0.149&      -0.003&       0.279&       0.078\\
-\ jkc         &       0.067&       0.469&       0.224&       0.033&       0.305&       0.094\\
+mmqreg      &      -0.050&       0.446&       0.202&      -0.010&       0.310&       0.096\\
+jkc         &       0.048&       0.546&       0.301&       0.018&       0.339&       0.115\\
 \hline
@@
 q25         &            &            &            &            &            &            \\
-\ mmqreg      &       0.052&       0.107&       0.014&       0.027&       0.074&       0.006\\
-\ jkc         &       0.007&       0.113&       0.013&       0.002&       0.077&       0.006\\
+mmqreg      &       0.050&       0.119&       0.017&       0.026&       0.084&       0.008\\
+jkc         &       0.006&       0.126&       0.016&       0.003&       0.087&       0.008\\
 \hline
 q75         &            &            &            &            &            &            \\
-\ mmqreg      &       0.004&       0.195&       0.038&       0.007&       0.138&       0.019\\
-\ jkc         &       0.009&       0.204&       0.042&       0.004&       0.141&       0.020\\
+mmqreg      &       0.001&       0.215&       0.046&       0.003&       0.151&       0.023\\
+jkc         &       0.006&       0.222&       0.049&       0.002&       0.154&       0.024\\
 \hline
@@
 
-As described in section Section~\ref{sec-se}, GLS standard errors may
-not be appropriate if heteroskedasticity in the model is misspecified.
-This could happen if the heteroskedasticity is not linear in parameters
-or if there are correlations within groups. To show the performance of
-the GLS standard errors, we consider two additional simulations. To see
-the impact of heteroskedasticity misspecification, we assume the DGP is
-given by
-
-\[y_i = \alpha_{1i} + \alpha_{2i} + x_i + (1+x_i + \sqrt{x_i} +\alpha_{1i} + \alpha_{2i} ) \varepsilon_i
-\]
-
-To show the impact of ignoring correlation within groups, we consider
-the case where the error \(\varepsilon\) is correlated within groups
-defined by the first fixed effect. Specifically:
-
-\[\varepsilon_i =0.5*(\sqrt{0.5} z_i + \sqrt{0.5} w_g)\]
-
-where \(z_i~N(0,1)\) and \(w_g~N(0,1)\), with \(g\) being the \(g_{th}\)
-group defined by the first fixed effect.
-
-For the simulation, we run the excercise 5000 times, using a sample of
-size \(N=2000\). The results from both simulations are reported in the
-Table~\ref{tbl-sim2}. We report the average coefficient,
-simulation-based standard errors, and the standard errors using GLS,
-robust and clustered estimations.
-
-\begin{longtable}[]{@{}lcccc@{}}
-\caption{Heteroskedasticity misspecification and clustered
-errors}\label{tbl-sim2}\tabularnewline
-\toprule\noalign{}
-& Het:q25 & Het:q75 & Clust:q25 & Clust:q75 \\
-\midrule\noalign{}
-\endfirsthead
-\toprule\noalign{}
-& Het:q25 & Het:q75 & Clust:q25 & Clust:q75 \\
-\midrule\noalign{}
-\endhead
-\bottomrule\noalign{}
-\endlastfoot
-Coefficient & 0.550 & 1.442 & 0.775 & 1.229 \\
-SIM\_SE & 0.154 & 0.155 & 0.109 & 0.107 \\
-GLS\_SE & 0.476 & 0.451 & 0.288 & 0.221 \\
-Robust & 0.140 & 0.139 & 0.087 & 0.088 \\
-Cluster & & & 0.097 & 0.097 \\
-\end{longtable}
-
-One of the conclusions from the results in Table~\ref{tbl-sim2} is that
-the results for the 25th and 75th quantiles are mostly identical,
-because of the symmetric error we used in the simulation. On the one
-hand, because the error structure is misspecified, we should expect to
-see a large bias in the estimated coefficients, especially in cases of
-misspecified heteroskedasticity. However, the purpose of this exercise
-is not to demonstrate the unbiasedness of the coefficients, but rather
-to assess the performance of the standard error estimation.
-
-As expected, the GLS standard errors are biased and the bias is larger
-in the case of misspecified heteroskedasticity. In fact, with
-heteroskedasticity misspecification, the average GLS-SE (0.476) is
-almost three times as large as the simulation-based standard error
-(0.154). In this first case, robust standard errors perform better, but
-with a small difference (0.14 to 0.154). In the case of clustered
-correlation, GLS-SE also performs poorly. Robust standard errors perform
-better, but seem to underestimate the magnitude of the true standard
-errors. Finally, cluster standard errors perform the best, with a small
-difference between the simulation-based standard errors (0.097 to
-0.109).
+To evaluate the performance of the different standard errors, we present
+bias, 95\% coverage of the biased corrected estimates, as well as the
+simulated standard errors, average and median of the standard errors
+obtained using the GLS, robust SE, and clustered standard SE.
+Table~\ref{tbl-sim2} considers the d.g.p. without intra-cluster
+correlation, while Table~\ref{tbl-sim3} considers the d.g.p. that
+induces intra-cluster correlations. All simulations consider 5000
+repetitions.
+
+The bias magnitude in Table~\ref{tbl-sim2} and Table~\ref{tbl-sim3} is
+comparable to those observed in Table~\ref{tbl-sim1}, with simulated
+standard errors that show to be slighly larger when we allow for
+intra-cluster correlations, just as expected. When assuming there is no
+need to clustered standard errors (Table~\ref{tbl-sim2}), the coverage
+associated to GLS standard errors is above 95\% when the samples are
+small, but it approximates to 95\% as the sample size increases. On the
+other and, the coverage rates associated to Robust Standard errors are
+closer to 90\%, albeit increasing slighly for larger samples.
+
+One of the main reason that the GLS-Standard errors achieve higher than
+expected rates of coverage may be related to the fact that the Standard
+error estimator is very sensitive to near zero predictions from the
+scale model. As shown in Table~\ref{tbl-sim2}, average and median GLS-SE
+are considerably larger than the simulated standard errors when the
+sample are small. While robust standard errors are less sensitive to
+this problem, producing more stable results, they tend to underestimate
+the magnitude of the true standard errors in small samples. This
+translates into the lower coverage rates.
+
+\begin{table}
+
+\caption{\label{tbl-sim2}95\% Coverage Ratio, and Standard Error
+Estimation: No Intra-cluster Correlation}
+
+\centering{
+
+\begin{tabular}[hbt!]{l*{10}{c}cccccccccccccccccccc}
+\hline 
+            &      \multicolumn{4}{c}{Q25}   &      \multicolumn{4}{c}{Q75}   &\\
+    N        &  =500& =1000 & =2000     &    =4000 &  =500& =1000 & =2000     &   =4000 & \\
+\hline
+Bias     &       0.173&       0.096&       0.050&       0.026&      -0.040&      -0.008&       0.003&       0.003\\
+Sim SE         &       0.268&       0.171&       0.118&       0.084&       0.443&       0.314&       0.219&       0.153\\
+Mean GLS SE      &1.9e7&       0.830&       0.401&       0.084&7.3e7 &       1.876&       4.259&       0.156\\
+Median GLS SE     &       0.495&       0.215&       0.123&       0.083&       1.037&       0.429&       0.225&       0.152\\
+CR95\%        &       0.988&       0.980&       0.958&       0.948&       0.991&       0.977&       0.967&       0.952\\
+Mean Rbst SE     &       0.224&       0.159&       0.112&       0.080&       0.353&       0.269&       0.199&       0.144\\
+CR95\%       &       0.892&       0.928&       0.939&       0.932&       0.875&       0.904&       0.927&       0.936\\
+\hline 
+%Mean CLS SE    &       0.235&       0.162&       0.112&       0.079&       0.372&       0.274&       0.199&       0.143\\
+%CR95\%       &       0.907&       0.930&       0.932&       0.930&       0.892&       0.905&       0.925&       0.932\\    
+\end{tabular}
+
+}
+
+\end{table}%
+
+When we consider the presence of Intra-Cluster correlation,
+Table~\ref{tbl-sim3}, we still observe similar problems with the GLS-SE,
+albeit with high coverage rates. While Robust and Clustered Standard
+errors are in average smaller than the Simulated Standard errors,
+coverage rates are above 90\%. Clustered standard errors perform the
+best only when the sample size is large, with Robust standard error
+producing low Standard errors estimates.
+
+\begin{table}
+
+\caption{\label{tbl-sim3}95\% Coverage Ratio, and Standard Error
+Estimation: With Intra-cluster Correlation}
+
+\centering{
+
+\begin{tabular}[hbt!]{l*{10}{c}cccccccccccccccccccc}
+    \hline 
+             &      \multicolumn{4}{c}{Q25}   &      \multicolumn{4}{c}{Q75}   &\\
+             N        &  =500& =1000 & =2000     &    =4000 &  =500& =1000 & =2000     &   =4000 & \\
+   \hline
+    Bias    &       0.180&       0.091&       0.053&       0.027&      -0.022&      -0.008&       0.003&       0.003\\
+    Sim SE         &       0.299&       0.200&       0.141&       0.100&       0.503&       0.352&       0.253&       0.182\\
+    Mean GLS SE      &1.5e7&       1.053&       0.190&       0.093&6.0e7 &       1.332&       0.309&       0.167\\
+    Median GLS SE      &       0.476&       0.215&       0.133&       0.092&       0.913&       0.384&       0.236&       0.165\\
+    CR95\%      &       0.984&       0.963&       0.939&       0.928&       0.986&       0.963&       0.940&       0.925\\
+    Mean Rbst SE    &       0.253&       0.179&       0.126&       0.089&       0.402&       0.303&       0.222&       0.160\\
+    CR95\%       &       0.896&       0.916&       0.917&       0.915&       0.880&       0.905&       0.917&       0.906\\
+    Mean CLS SE    &       0.252&       0.180&       0.130&       0.096&       0.397&       0.304&       0.228&       0.172\\
+    CR95\       &       0.892&       0.915&       0.923&       0.935&       0.875&       0.902&       0.919&       0.928\\
+    \hline 
+\end{tabular}
+
+}
+
+\end{table}%
+
+Overall, the simulation study shows that using GLS-SE estimator may be
+appropriate when the sample is relatively large. When there is suspected
+presence of intra-cluster correlation, the use of clustered standard
+errors is recommended in larger samples. However, when the sample is
+small, the use of robust standard errors may be appropriate if GLS
+standard errors when there is the risk of near-zero predictions from the
+scale model.
 
@@
 
+May be worth noting that the GLS SE are almost twice as large as the
+robust and clustered standard errors. This is consistent with the
+results from the simulation study. Examining the predictions of the
+scale model, we find that there are 9 observations with a negative
+predicted scale, and 9 observations that could be considered outliers.
+This may be the reason for the large GLS standard errors.
+
 \begin{longtable}[]{@{}
@@
 
-Furthermore, we have assessed the impact of misspecified
-heteroskedasticity and intracluster correlation on the performance of
-standard error estimations. Our findings emphasize the importance of
-using appropriate standard error estimators to ensure accurate
-inference. In particular, we find that GLS standard errors are biased
-when the model heteroskedasticity is misspecified and that robust and
-clustered standard errors perform better in these cases. This may also
-suggest a venue for future research, in which the validity of the
-location-scale model assumption is tested.
+Furthermore, we have assessed the impact of intracluster correlation on
+the performance of standard error estimations. Our findings emphasize
+the importance of using appropriate standard error estimators to ensure
+accurate inference. In particular, we find that GLS standard errors are
+biased when when the scale model predictions are close to zero or
+negative, and that Robust and clustered standard errors are more stable
+in those scenarios. Clustered Standard errors perform the best in the
+presence of intra-cluster correlation, but the advantage is only evident
+when the sample size is large.
+
+Finally, we have illustrated the application of our extended methodology
+using data from \citet{persson_economic_2005}. Our results are
+consistent with those reported in \citet{mss2019}, and we are able to
+provide robust and clustered standard errors for the location and scale
+coefficients. We find that the GLS standard errors are almost twice as
+large as the robust and clustered standard errors, which is consistent
+with the results from our simulation study. Nevertheless, there is no
+drastic change in the original conclusions.
 
@@
 \item
-  \texttt{mmqreg} in Stata: `net install mmqreg,
-  from(https://friosavila.github.io/stpackages)
+  \texttt{mmqreg} in Stata:
+  \texttt{net\ install\ mmqreg,\ from(https://friosavila.github.io/stpackages)}
 \item
-  \texttt{mmqreg} in R: Program available in mmqreg repository on GitHub
+  \texttt{mmqreg} in R: Available on GitHub
   (https://github.com/friosavila/mmqreg)
-\item
-  \texttt{mmqreg} in Python:
-\item
-  \texttt{mmqreg} in Julia:
 \end{itemize}

### 2024-02-08 article/OLD.qmd
s
s

--- 2023-11-13 article/article_old.qmd
@@
 [^10]: There are two possible reasons that may explain the differences in the GLS standard errors.
-On the one hand, in our derivation, the influence function of the standardized $\tau_{th}$ quantile (see #eq-infs) does not have the same leading term as the one reported in MSS (see theorem 3, and the definition of $W$).
+On the one hand, in our derivation, the influence function of the standardized $\tau_{th}$ quantile (see #eq-ifs) does not have the same leading term as the one reported in MSS (see theorem 3, and the definition of $W$).
 

### 2024-02-08 article/alt_article.qmd
s
s

--- 2024-02-07 article/article.qmd
@@
 ---
-title: Estimating Quantile Regressions with Multiple Fixed Effects through Method of Moments \tnoteref{t1,t2}
+title: Estimating Quantile Regressions with Multiple Fixed Effects through Method of Moments 
 author:
@@
           country: USA
-    attributes:
-        corresponding: true
+
   - name: Leonardo Siles
@@
 format:
-  elsevier-pdf:
-    keep-tex: true
-    journal:
-      formatting: review
-      model: 1p
-      cite-style: authoryear
-      number-depth: 2
-include-in-header: 
-      text: |
-        \tnotetext[t1]{The opinions expressed in this paper are those of the authors and do not necessarily reflect the views of the World Bank, its Board of Directors, or the countries it represents.}
-        \tnotetext[t2]{The authors would like to thank Enrique Pinzon an Joao Santos-Silva for their helpful comments and suggestions.}
+  pdf: 
+    toc-depth: 2
+    number-sections: true
+    documentclass: article
+    margin-bottom: 1in
+    margin-top: 1in
+    margin-left: 1in
+    margin-right: 1in
+    thanks: |
+      The opinions expressed in this paper are those of the authors and do not necessarily reflect the views of the World Bank, its Board of Directors, or the countries it represents.
+
+      The authors would like to thank Enrique Pinzon an Joao Santos-Silva for their helpful comments and suggestions.
+
+    fontsize: 11pt
+    cite-method: natbib
 
@@
 -->
+{{< pagebreak >}}
 
@@
 
-[^10]: The differences in the GLS standard errors may be due that in our derivation the influence function of the standardized $\tau_{th}$ quantile (see #eq-infs) does not have the same leading term as the one reported in MSS (see Theorem 3, and the definition of $W$).
+[^10]: The differences in the GLS standard errors may be due that in our derivation the influence function of the standardized $\tau_{th}$ quantile (see #eq-ifs) does not have the same leading term as the one reported in MSS (see Theorem 3, and the definition of $W$).
 

### 2024-02-08 article/article.tex
s
s

@@
   be due that in our derivation the influence function of the
-  standardized \(\tau_{th}\) quantile (see \#eq-infs) does not have the
+  standardized \(\tau_{th}\) quantile (see \#eq-ifs) does not have the
   same leading term as the one reported in MSS (see Theorem 3, and the

### 2024-02-11 article/alt_article.qmd
Update alt_article.qmd
ss
s

@@
     fontsize: 11pt
-    cite-method: natbib
-
+    csl: "templates/apa-no-ampersand.csl"
+    template-partials: 
+      - "templates/title.tex"
+      - "templates/before-body.tex"
+      - "templates/_authors.tex"      
 ---
@@
 
-[^10]: The differences in the GLS standard errors may be due that in our derivation the influence function of the standardized $\tau_{th}$ quantile (see #eq-ifs) does not have the same leading term as the one reported in MSS (see Theorem 3, and the definition of $W$).
+[^10]: The differences in the GLS standard errors may be due that in our derivation the influence function of the standardized $\tau_{th}$ quantile (see @eq-ifs) does not have the same leading term as the one reported in MSS (see Theorem 3, and the definition of $W$).
 

### 2024-02-12 article/alt_article.qmd
ssss
sss

@@
           country: USA          
-
+    attributes:
+      corresponding: true 
   - name: Leonardo Siles
@@
           name: Universidad Católica Boliviana
-          city: La Paz
-          country: Bolivia
+          city: La Paz, Bolivia
   - name: Gustavo Canavire-Bacarreza

### 2024-08-08 article/article_edited.qmd
s

[TextBlock(text="<edited_text>\ntitle: Estimating Quantile Regressions with Multiple Fixed Effects through Method of Moments \\tnoteref{t1,t2}\nauthor:\n  - name: Fernando Rios-Avila\n    email: friosavi@levy.org\n    affiliations: \n        - id: levy\n          name: Levy Economics Institute of Bard College\n          city: Annandale-on-Hudson, NY\n          country: USA          \n    attributes:\n        corresponding: true\n  - name: Leonardo Siles\n    email: leonardo.siles@ucb.edu.bo\n    affiliations:\n        - id: ucb\n          name: Universidad Católica Boliviana\n          city: La Paz\n          country: Bolivia\n  - name: Gustavo Canavire-Bacarreza\n    email: gcanavire@worldbank.org\n    affiliations:\n        - id: wb\n          name: The World Bank                 \n          city: Washington, D.C.\n          country: USA\nabstract: |\n  This paper proposes a new method to estimate quantile regressions with multiple fixed effects. The method, which expands on the strategy proposed by @mss2019, allows for the inclusion of multiple fixed effects and provides various alternatives for the estimation of standard errors. We provide Monte Carlo simulations to show the finite sample properties of the proposed method in the presence of two sets of fixed effects. Finally, we apply the proposed method to estimate the determinants of the surplus of government as a share of GDP, allowing for both time and country fixed effects.\n  \nkeywords: \n  - Fixed effects\n  - Linear heteroskedasticity\n  - Location-scale model\n  - Quantile regression\n\ndate: last-modified\nbibliography: bibliography.bib\nformat:\n  elsevier-pdf:\n    keep-tex: true\n    journal:\n      formatting: review\n      model: 1p\n      cite-style: authoryear\n      number-depth: 2\ninclude-in-header: \n      text: |\n        \\tnotetext[t1]{The opinions expressed in this paper are those of the authors and do not necessarily reflect the views of the World Bank, its Board of Directors, or the countries it represents.}    \n        \\tnotetext[t2]{The authors would like to thank Enrique Pinzon and Joao Santos-Silva for their helpful comments and suggestions.}   \n\n---\n\n<!--\nHow to Render this? Lik this:\nquarto render article.qmd --to elsevier-pdf \n\n --> \n\n # Introduction\n\n Quantile regression (QR), introduced by @koenkerbasset1978, is an estimation strategy used for modeling the relationships between explanatory variables X and the conditional quantiles of the dependent variable $Q_y (\\tau|x)$. Using QR one can obtain richer characterizations of the relationships between dependent and independent variables, by exploring how the variables relate along the entire conditional distribution. \n\n A relatively recent development in the literature has focused on extending quantile regressions analysis to include individual fixed effects in the framework of panel data. However, as described in @neymanscott1948 and @lancaster2000, when individual fixed effects are included in quantile regression analysis, an incidental parameter problem is generated. While many strategies have been proposed for estimating this type of model (see @galvao2017quantile for a brief review), neither has become standard because of their restrictive assumptions regarding the inclusion of individual and multiple fixed effects, the computational complexity, and implementation. \n\n More recently, @mss2019 (MSS hereafter) proposed a methodology based on a conditional location-scale model, similar to the one described in @he1997 and @zhao2000, for the estimation of quantile regressions models for panel data via a method of moments. This method allows individual fixed effects to have heterogeneous effects on the entire conditional distribution of the outcome, rather than constraining their effect to be a location shift only, as in @canay2011, @koenker2004, and @lamarche2010. \n\n In principle, under the assumption that the data-generating process behind the data is based on a multiplicative heteroskedastic process that is linear in parameters [@mss2019, @he1997, @zhao2000, @cameron2005], the effect of a variable $X$ on the $q_{th}$ quantile can be derived as the combination of a location effect and a scale effect moderated by the quantile of an underlying i.i.d. error. For statistical inference, MSS derives the asymptotic distribution of the estimator, suggesting the use of bootstrap standard errors, as well. \n\n This methodology is not meant to substitute for the use of standard quantile regression analysis. That said, given the assumptions required for the identification of the model, it provides a simple and fast alternative for the estimation of quantile regression models with individual fixed effects. \n\n In this framework, our paper expands on @mss2019 in two ways. First, making use of the properties of generalized method of moments (GMM) estimators, we derive various alternatives for the estimation of standard errors based on the empirical influence functions of the estimators. Even if the model is correctly specified, robust standard errors perform better than GLS standard errors due to small violations of the model assumptions due to sampling variability. Furthermore, clustered standard errors may help to further account for typically unobserved correlations across observations. Second, we reconsider the application of Frisch-Waugh-Lovell (FWL) theorem [@frishwaugh1933 and @lovell1963] to extend the MSS estimator and allow for the inclusion of multiple fixed effects. This extension may be useful for empirical analysis, as it is common to control for multiple fixed effects such as individual and time fixed effects.  \n\n The rest of the paper is structured as follows: section 2 presents the basic setup of the location-scale model described in @he1997 and @zhao2000, tying the relationship between the standard quantile regression model and the location-scale model. It also revisits the methodology of MSS, proposing alternative estimators for the standard errors based on the properties of GMM estimators and the empirical influence functions. It also shows that the FWL theorem can be used to control for multiple fixed effects. Section 3 presents the results of a small simulation study, and section 4 illustrates the application of the proposed methods with one empirical example. Section 5 concludes.\n\n # Methodology {#sec-method}\n\n ## Quantile Regression: Location-Scale model {#sec-betas}\n\n Quantile regressions are used to identify relationships between the explanatory variables $X$ and the conditional quantiles of the dependent variable $Q_y(\\tau|X)$. This relationship is commonly assumed to follow a linear functional form: \n\n $$Q_y(\\tau|X) =X\\beta(\\tau)\n$$ {#eq-eq1}\n\n This allows for a linear effect of $X$ on $Y$, but that could vary across values of $\\tau$.  \n\n An alternative formulation of quantile regressions is the location-scale model. This approach assumes that the conditional quantile of $Y$ given $X$ and $\\tau$ can be expressed as a combination of two models: the location model, which describes the central tendency of the conditional distribution; and the scale model, which describes deviations from the central tendency: \n\n $$Q_y(\\tau|X) =X\\beta+X\\gamma(\\tau)\n$$ {#eq-eq2}\n\n Here, the location parameters $\\beta$ are typically identified using a linear regression model (as in @mss2019) or a median regression (as in @he1997 and @zhao2000) and the scale parameters $\\gamma(\\tau)$ can be estimated using standard approaches. \n\n Both the standard quantile regression (@eq-eq1) and the location-scale specification (@eq-eq2) can be estimated as the solution to a weighted minimization problem: \n\n $$\\hat{\\beta}(\\tau) = \\underset{\\beta}{\\operatorname{argmin}}\n\\left( \\sum_{i\\in y_i\\geq x_i'\\beta} \\tau (y_i - x_i'\\beta) - \\sum_{i\\in y_i<x_i'\\beta} (1-\\tau)(y_i - x_i'\\beta) \\right)\n$$ {#eq-eq3}\n\n One characteristic of this estimator is that the $\\beta(\\tau)$ coefficients are identified locally and thus the estimated quantile coefficients will exhibit considerable variation when analyzed across $\\tau$. It is also implicit that if one requires an analysis of the entire distribution, it would be necessary to estimate the model for each quantile.[^1] \n\n [^1]: There are other estimators that provide smoother estimates for the quantile regression coefficients using a kernel local weighted approach [@kaplan2017], as well as identifying the full set of quantile coefficients while simultaneously assuming some parametric functional forms [@frumentobotai2016].\n\n One insightful extension to the location-scale parameterizations suggested by @he1997, @zhao2000, @cameron2005, and @mss2019 is to assume that the data-generating process (DGP) can be written as a linear model with a multiplicative heteroskedastic process that is linear in parameters.[^2] \n\n [^2]: @mss2019 also discuss a model where heteroskedasticity can be an arbitrary nonlinear function $\\sigma(x_i'\\gamma)$, but develop the estimator for the linear case, i.e., when $\\sigma()$ is the identity function.\n\n $$\\begin{aligned}\ny_i &=x_i'\\beta+\\nu_i \\\\\n\\nu_i &=\\varepsilon_i \\times x_i'\\gamma \n\\end{aligned}\n$$ {#eq-eq4}\n\n Under the assumption that $\\varepsilon$ is an i.i.d. unobserved random variable that is independent of $X$, the conditional quantile of $Y$ given $X$ and $\\tau$ can be written as \n\n $$Q_y(\\tau|X) =X\\beta+Q_\\varepsilon(\\tau) \\times X\\gamma \n$$ {#eq-eq5}\n\n In this setup, the traditional quantile coefficients are identified as the location model coefficients plus the scale model coefficients moderated by the $\\tau_{th}$ unconditional quantile of the standardized error $\\varepsilon$. For simplicity, we will use $q_\\tau$ to denote $Q_\\varepsilon(\\tau)$ in the rest of the paper. \n\n $$\\beta(\\tau) = \\beta + q_\\tau \\times \\gamma \n$$ {#eq-eq6}\n\n While this specification imposes a strong assumption on the DGP, it has two advantages over the standard quantile regression model. First, because the location-scale model can be identified globally, with only a single parameter ($q_\\tau$) requiring local estimation, this estimation approach will be more efficient than the standard quantile regression model [@zhao2000]. Second, under the assumption that $X\\gamma$ is strictly positive, the model will produce quantile coefficients that do not cross [@he1997].  \n\n Following MSS, the quantile regression model defined by @eq-eq5 can be estimated using a generalized method of moments approach. And while it is possible to identify all coefficients ($\\beta,\\gamma, q_\\tau$) simultaneously, we describe and use the implementation approach advocated by MSS, which identifies each set of coefficients separately. \n\n First, the location model can be estimated using a standard linear regression model, where the dependent variable is the outcome $Y$ and the independent variables are the explanatory variables $X$ (including a constant) with an error $u$, which is by definition heteroskedastic. In this case, the location-model coefficients are identified under the following condition: \n\n $$\\begin{aligned}\n      y_i &=x_i'\\beta+\\nu_i \\\\\n      E\\big[ x_i \\nu_i\\big] &=0\n      \\end{aligned}\n$$ {#eq-eq7}\n\n Second, after the location model is estimated, the scale coefficients can be identified by modeling heteroskedasticity as a linear function of characteristics $X$. For this, we use the absolute value of the errors from the location model $u$ as the dependent variable, which allows us to estimate the conditional standard deviation (rather than conditional variance) of the errors. In this case, the coefficients are identified under the following condition: \n\n $$\\begin{aligned}\n  |\\nu_i| &=x_i'\\gamma+\\omega_i \\\\\n   E\\big[ x_i (|\\nu_i| -x_i'\\gamma ) \\big] &=0\n  \\end{aligned}\n$$ {#eq-eq8}\n\n It should be noticed that the estimation of the standard errors (next section) requires that the Scale component prediction $x_i'\\gamma$ is strictly positive, because it represents the conditional standard deviation of the error $\\nu_i$. Because this component is identified using a linear model, some values for $x_i'\\gamma$ may be negative, which will affect the estimation of the standard errors, as shown in the simulation study. \n\n Third, given the location and scale coefficients, the $\\tau_{th}$ quantile of the error $\\varepsilon$ can be estimated using the following condition: \n\n $$\\begin{aligned}\n  E\\left[  \\mathbb{1}\\left(x_i' (\\beta +   \\gamma q_\\tau) \\geq y_i \\right) - \\tau \\right] &=0  \\\\\n  E\\left[  \\mathbb{1}\\left(   q_\\tau \\geq \\frac{y_i-x_i'\\beta}{x_i'\\gamma} \\right) - \\tau \\right] &=0  \\\\\n  \\end{aligned}\n$$ {#eq-eq9}\n\n where one identifies the quantile of the error $\\varepsilon$ using standardized errors $\\frac{y_i-x_i'\\beta}{x_i'\\gamma}$ or by finding the values that identify the overall quantile coefficients $\\beta(\\tau)=\\beta + \\gamma q_\\tau$. Afterwards, the conditional quantile coefficients are simply defined as the combination of the location and scale coefficients. \n\n\n\n ## Standard Errors: GLS, Robust, Clustered {#sec-se}\n\n As discussed in the previous section, the estimation of quantile regression coefficients using the location-scale model with heteroskedastic linear errors can be estimated using a the following set of moments, which fits within the GMM framework: \n\n $$\\begin{aligned}\n  E[x_i \\nu_i  ] &= E[h_{1,i}]=0 \\\\\n  E[x_i  (|\\nu_i|-x_i \\gamma) ] &=E[h_{2,i}]=0 \\\\\n  E\\left[  \\mathbb{1}\\left(   q_\\tau\\geq \\frac{y_i-x_i'\\beta}{x_i'\\gamma} \\right) - \\tau \\right]  &=E[h_{3,i}]=0 \n  \\end{aligned}\n$${#eq-eq10}\n\n Under the conditions described in @newey_chapter_1994 (see section 7), @cameron2005 (see chapter 6.3.9), or as shown in @mss2019, the location, scale, and residual quantile coefficients are asymptotically normal.[^3] \n\n [^3]: @zhao2000 also shows that the quantile coefficients for the location-scale model follow a normal distribution, but uses the assumption that the location model is derived using a least absolute deviation approach (median regression).\n\n Call $\\theta=[ \\beta' \\ \\ \\gamma' \\ \\ q_\\tau ]'$ the set of coefficients that are identified by the moment conditions in @eq-eq10, a just identified model, and the function $h_i$ is a vector function that stacks all the moments described in @eq-eq10 at the individual level. Then $\\hat\\theta$ follows a normal distribution with mean $\\theta$ and variance-covariance matrix $V(\\theta)$ that is estimated as \n\n $$\n\\hat{V}(\\hat\\theta)=\\frac{1}{N} \n\\bar G(\\hat\\theta)^{-1} \n\\left( \\frac{1}{N} \\sum_{i=1}^N h_i h_i'  \\Big|_{\\theta=\\hat\\theta} \\right) \n\\bar G(\\hat\\theta)^{-1} \n$$\n\n which is equivalent to the Eicker-White heteroskedasticity-consistent estimator for least-squares estimators. \n\n Here, the inner product is the moment covariance matrix and $\\bar{G}(\\theta)$", type='text')]

\nIn the case of unbalanced setups with multiple groups, the estimation involves iterative processes for which various approaches have been suggested and implemented (see, for example, @correia_feasible_nodate, @gaure2013, @rios2015, among others).\n\nWhen applying the partialing-out approach, some modifications to the approach described in @sec-betas are needed.\n\nFirst, for all dependent and independent variables in the model ($w=y,x$), we partial out the group fixed effects and obtain the centered-residualized variables:\n\n$$\\begin{aligned}\nw_{i} &= \\delta_{g1}^w + \\delta_{g2}^w + u_{i}^w \\\\\nw_{i}^{rc} &= E(w_{i}) + \\hat{u}_{i}^w\n\\end{aligned}$$\n\nAfterward, we estimate the location model using the centered-residualized variables:[^8]\n\n[^8]: Using centered-residualized variables allows us to include a constant in the model specification, which simplifies the derivation of the influence functions. However, as with other fixed effects models, the constant is not identified and thus should not be interpreted.\n\n$$y_{i}^{rc} = x_{i}^{rc'} \\beta + \\nu_{i}$$\n\nBecause $|\\hat \\nu_i|$ is the dependent variable for the scale model, we apply the partialing out and recentering to this expression ($|\\hat \\nu_i|^{rc}$), and use that to estimate the following model:\n\n$$|\\hat\\nu_{i}|^{rc} = x_{i}^{rc'} \\gamma + \\omega_{i}$$\n\nFinally, the standardized residuals $\\varepsilon_i$ can be obtained as follows:\n\n$$\\hat{\\varepsilon}_{i} = \\frac{\\nu_{i}}{|\\hat\\nu_{i}|- \\hat \\omega_{i}}$$\n\nwhere $|\\hat\\nu_{i}|- \\hat \\omega_{i}$ is the prediction for the conditional standard deviation $\\sigma(x_i)=x_{i}' \\gamma + \\zeta_{g1} + \\zeta_{g2}$\n\nThe $\\tau_{th}$ quantile of the error $\\varepsilon$ can be estimated as usual, and the variance-covariance matrices obtained in the same way as before (see @sec-se) by using $x_{i}^{rc}$ instead of $x_{i}$ when estimating the influence functions for all estimated coefficients.\n\n# Simulation Evidence\n\nTo show the performance of the extended strategy, we implement a small simulation study. We consider a simple model with a single explanatory variable $x$. In contrast with MSS, we consider a two-way fixed effect structure. For this exercise, we consider the following data-generating process:\n\n$$y_i = \\alpha_{1i} + \\alpha_{2i} + x_i + (2+x_i + \\alpha_{1i} + \\alpha_{2i} ) \\varepsilon_i$$\n\nwhere $\\alpha_{1i}\\sim \\chi^2(1)$, $\\alpha_{2i} \\sim \\chi^2(1)$, and $x_i = 0.5 * (\\chi_i +0.5(\\alpha_{1i}+\\alpha_{2i}))$, with $\\chi_i \\sim \\chi^2(1)$. We only consider the case when the error term $\\varepsilon_i$ is assumed to follow a centered $\\chi^2$ distribution.[^99]\n\n[^99]: Specifically, we assume $\\varepsilon=\\frac{r_i}{5}-1$, where $r_i$ follows a chi-squared distribution such that $r_i \\sim \\chi^2(5)$. Simulations under the assumption of normal errors are available upon request.\n\nWe assume that there are 50 mutually exclusive groups for each set of fixed effects. Observations are assigned to each subgroup randomly using a uniform distribution between 1 and 50.\n\nTo assess the alternative standard error estimators, we consider a second data-generating process where the error term is correlated within clusters. For this, we assume observations are assigned randomly to 100 mutually exclusive groups, which are independent from the fixed effect groups. In this setup, the data-generating process is:\n\n$$\\begin{aligned}\ny_i &= \\alpha_{1i} + \\alpha_{2i} + x_i + (2+x_i + \\alpha_{1i} + \\alpha_{2i} )*\\kappa_i \\\\\n\\kappa_i &= inv-\\chi^2_5(r_{i})/5-1 \\\\\nr_i &= \\Phi((\\sqrt{.25}*s_{i}+\\sqrt{.75}*s_{g}))\n\\end{aligned}$$\n\nwhere $s_{i}\\sim N(0,1)$ and $s_{g}\\sim N(0,1)$, are errors that vary across individuals $i$ or across clusters $g$. $\\Phi()$ is the cumulative distribution function of a normal distribution, and $inv-\\chi^2_5()$ is the inverse function for a Chi-2 distribution with 5 degrees of freedom. With this setup, we generate an error structure with a strong intra-cluster correlation, but without affecting the model specification assumption.[^9]\n\n[^9]: For the implementation, we first estimate the model using the full sample, then randomly assign each observation into one of two groups, and finally reestimate the quantile coefficients for each group. The bias-corrected estimator is then obtained as $\\hat\\beta(\\tau)_{jkc}=2*\\hat\\beta(\\tau)_{full}-0.5*\\big(\\hat\\beta(\\tau)_{s1}+\\hat\\beta(\\tau)_{s2}\\big)$.\n\n[^88: This is also consistent with simulations with a single fixed effect]\n\nWe consider sample sizes of 500, 1000, 2000, and 4000 observations, which implies an average of 10, 20, 40, and 80 observations per group. The model is estimated using the location-scale model with heteroskedastic linear errors, and we report the coefficients for the 25th and 75th quantiles. We run this exercise 5000 times. @tbl-sim1 reports the bias, simulated standard error, and mean squared error, using the first data generation structure only. We also report the results obtained using an adaptation bias-corrected estimator based on the split-panel jackknife estimator proposed by @dhaene2015.\n\nSimilar to the findings in MSS, we find that while the estimator presents a substantial bias when the sample is small ($N=500$), this bias shrinks as the sample size increases. As MSS describes, the bias seems to be proportional to the sample size, or more precisely to the average number of observations per sub-group. Interestingly, the bias-corrected estimator presents an almost 0 bias for the 25th percentile, even when the samples are small. In contrast, when considering the 75th percentile, the simple estimator shows smaller bias than the Jacknife estimator. In either case, despite the bias reduction obtained using the JKC estimator, the standard errors are larger than without correction. For the 25th quantile, the reduction in bias is large enough to produce a smaller Mean Squared Error (MSE) than the simple estimator. This is similar to the results of MSS.\n\nTo evaluate the performance of the different standard errors, we present bias, 95% coverage of the bias-corrected estimates, as well as the simulated standard errors, average and median of the standard errors obtained using the GLS, robust SE, and clustered standard SE. @tbl-sim2 considers the d.g.p. without intra-cluster correlation, while @tbl-sim3 considers the d.g.p. that induces intra-cluster correlations. All simulations consider 5000 repetitions.\n\nThe bias magnitude in @tbl-sim2 and @tbl-sim3 is comparable to those observed in @tbl-sim1, with simulated standard errors that show to be slightly larger when we allow for intra-cluster correlations, just as expected. When assuming there is no need to cluster standard errors (@tbl-sim2), the coverage associated with GLS standard errors is above 95% when the samples are small, but it approximates to 95% as the sample size increases. On the other hand, the coverage rates associated with Robust Standard errors are closer to 90%, albeit increasing slightly for larger samples.\n\nOne of the main reasons that the GLS-Standard errors achieve higher than expected rates of coverage may be related to the fact that the standard error estimator is very sensitive to near-zero predictions from the scale model. As shown in @tbl-sim2, average and median GLS-SE are considerably larger than the simulated standard errors when the samples are small. While robust standard errors are less sensitive to this problem, producing more stable results, they tend to underestimate the magnitude of the true standard errors in small samples. This translates into the lower coverage rates.\n\nWhen we consider the presence of Intra-Cluster correlation, @tbl-sim3, we still observe similar problems with the GLS-SE, albeit with high coverage rates. While Robust and Clustered Standard errors are on average smaller than the Simulated Standard errors, coverage rates are above 90%. Clustered standard errors perform the best only when the sample size is large, with Robust standard errors producing low Standard error estimates.\n\nOverall, the simulation study shows that using the GLS-SE estimator may be appropriate when the sample is relatively large. When there is suspected presence of intra-cluster correlation, the use of clustered standard errors is recommended in larger samples. However, when the sample is small, the use of robust standard errors may be appropriate if GLS standard errors when there is the risk of near-zero predictions from the scale model.\n

\nFurthermore, we have assessed the impact of intracluster correlation on the performance of standard error estimations. Our findings emphasize the importance of using appropriate standard error estimators to ensure accurate inference. In particular, we find that GLS standard errors are biased when the scale model predictions are close to zero or negative, and that Robust and clustered standard errors are more stable in those scenarios. Clustered standard errors perform the best in the presence of intra-cluster correlation, but the advantage is only evident when the sample size is large.\n\nFinally, we have illustrated the application of our extended methodology using data from @persson_economic_2005. Our results are consistent with those reported in @mss2019, and we are able to provide robust and clustered standard errors for the location and scale coefficients. We find that the GLS standard errors are almost twice as large as the robust and clustered standard errors, which is consistent with the results from our simulation study. Nevertheless, there is no drastic change in the original conclusions.\n

### 2024-09-10 article/_extensions/sim-art2/_authors.tex
Update Paper
WIth Comments from GJ

$-- You can use as many custom partials as you need. Convention is to prefix name with '_'
$-- It can be useful to use such template to split some template parts in smaller pieces, which is easier to reuse. 
$-- This '_custom.tex' is used on 'title.tex' as example.
$-- See other existing format in quarto-journals/ organisation.
$-- %%%% TODO %%%%%
$-- Use it if you need to insert content at this specific place of the main Pandoc's template. Otherwise, remove it.
$-- Here we are using it to format the authors part of the template.
$-- %%%%%%%%%%%%%%%

$it.name.literal$
\thanks{
  $for(it.affiliations)$
    $it.name$$sep$, $it.city$
  $endfor$
  $if(it.email)$
    \href{mailto:$it.email$}{Email: $it.email$}
  $endif$
}

### 2024-09-10 article/alt_article.qmd
Update Paper
WIth Comments from GJ

@@
 
-keywords: 
-  - Fixed effects
-  - Linear heteroskedasticity
-  - Location-scale model
-  - Quantile regression
-
-date: last-modified
-bibliography: bibliography.bib
-format:
-  pdf: 
-    toc-depth: 2
-    number-sections: true
-    documentclass: article
-    margin-bottom: 1in
-    margin-top: 1in
-    margin-left: 1in
-    margin-right: 1in
 thanks: |
@@
 
-    fontsize: 11pt
-    csl: "templates/apa-no-ampersand.csl"
-    template-partials: 
-      - "templates/title.tex"
-      - "templates/before-body.tex"
-      - "templates/_authors.tex"      
+keywords: [Fixed effects, Linear heteroskedasticity, Location-scale model, Quantile regression]
+jelcode: [C21, C22, C23]
+
+date: last-modified
+bibliography: bibliography.bib
+format:
+  sim-art2-pdf:
+    keep-tex: true
+
 ---
 
-<!--
-How to Render this?
-Lik this:
-quarto render article.qmd --to elsevier-pdf
-
--->
 {{< pagebreak >}}
@@
 
-::: {#tbl-sim1}
+::: {#tbl-sim1 tbl-pos="H"}
 
@@
 
-::: {#tbl-sim2}
+::: {#tbl-sim2 tbl-pos="H"}
 
@@
 
-::: {#tbl-sim3}
+::: {#tbl-sim3 tbl-pos="H"}
 
@@
 
-# Illustrative application
+# Illustrative applications
+
+## Determinants of government surpluses
 
@@
 
-|          | polityt |  lyp   | trade | p1564 |  p65   |  lspl  | oil_im | oil_ex |  ygap  |
-|----------|:-------:|:------:|:-----:|:-----:|:------:|:------:|:------:|:------:|:------:|
-| Location |         |        |       |       |        |        |        |        |        |
-|  coeff   |  0.116  | -0.715 | 0.030 | 0.121 | 0.028  | 0.691  | -0.047 | -0.006 | 0.010  |
-|  se_gls  |  0.046  | 0.540  | 0.008 | 0.033 | 0.070  | 0.035  | 0.008  | 0.022  | 0.028  |
-|  se_r    |  0.047  | 0.597  | 0.008 | 0.031 | 0.070  | 0.037  | 0.007  | 0.017  | 0.021  |
-|  se_cl   |  0.046  | 0.465  | 0.007 | 0.032 | 0.071  | 0.035  | 0.010  | 0.020  | 0.023  |
-| Scale    |         |        |       |       |        |        |        |        |        |
-|  coeff   | -0.097  | -0.616 | 0.003 | 0.036 | 0.087  | -0.085 | 0.013  | 0.016  | -0.004 |
-|  se_gls  |  0.032  | 0.371  | 0.005 | 0.023 | 0.048  | 0.024  | 0.006  | 0.015  | 0.019  |
-|  se_r    |  0.031  | 0.398  | 0.005 | 0.020 | 0.049  | 0.025  | 0.005  | 0.010  | 0.015  |
-|  se_cl   |  0.048  | 0.800  | 0.008 | 0.031 | 0.067  | 0.029  | 0.004  | 0.010  | 0.012  |
-| Q25      |         |        |       |       |        |        |        |        |        |
-|  coeff   |  0.191  | -0.239 | 0.028 | 0.093 | -0.039 | 0.756  | -0.057 | -0.018 | 0.013  |
-|  se_gls  |  0.059  | 0.684  | 0.010 | 0.042 | 0.088  | 0.045  | 0.010  | 0.027  | 0.035  |
-|  se_r    |  0.056  | 0.656  | 0.008 | 0.036 | 0.086  | 0.040  | 0.010  | 0.020  | 0.025  |
-|  se_cl   |  0.073  | 0.687  | 0.006 | 0.041 | 0.098  | 0.023  | 0.010  | 0.021  | 0.029  |
-| Q50      |         |        |       |       |        |        |        |        |        |
-|  coeff   |  0.108  | -0.765 | 0.030 | 0.124 | 0.035  | 0.684  | -0.046 | -0.005 | 0.009  |
-|  se_gls  |  0.046  | 0.535  | 0.007 | 0.033 | 0.069  | 0.035  | 0.008  | 0.022  | 0.027  |
-|  se_r    |  0.046  | 0.593  | 0.008 | 0.031 | 0.069  | 0.036  | 0.007  | 0.017  | 0.021  |
-|  se_cl   |  0.043  | 0.484  | 0.008 | 0.032 | 0.070  | 0.036  | 0.010  | 0.020  | 0.023  |
-| Q75      |         |        |       |       |        |        |        |        |        |
-|  coeff   |  0.031  | -1.258 | 0.033 | 0.153 | 0.104  | 0.616  | -0.036 | 0.008  | 0.006  |
-|  se_gls  |  0.048  | 0.551  | 0.008 | 0.034 | 0.071  | 0.036  | 0.008  | 0.022  | 0.028  |
-|  se_r    |  0.049  | 0.696  | 0.009 | 0.034 | 0.075  | 0.043  | 0.007  | 0.018  | 0.023  |
-|  se_cl   |  0.039  | 0.919  | 0.012 | 0.041 | 0.079  | 0.055  | 0.010  | 0.022  | 0.020  |
+::: {#tbl-tb1 tbl-pos="h"}
 
-: Determinants of Government Surpluses: Individual Fixed Effects {#tbl-tb1}
+{{< include tbl4.tex >}}
+
+Determinants of Government Surpluses: Individual Fixed Effects
+
+:::
 
@@
 
-|          | polity |  lyp   | trade | prop1564 | prop65 |  lspl  |  ygap  |
-|----------|:------:|:------:|:-----:|:--------:|:------:|:------:|:------:|
-| Location |        |        |       |          |        |        |        |
-|  coeff   | 0.126  | -0.418 | 0.028 |  0.108   | 0.042  | 0.693  | -0.014 |
-|  se_gls  | 0.087  | 1.157  | 0.015 |  0.072   | 0.136  | 0.066  | 0.053  |
-|  se_r    | 0.047  | 0.703  | 0.008 |  0.038   | 0.068  | 0.038  | 0.022  |
-|  se_cl   | 0.048  | 0.506  | 0.008 |  0.044   | 0.077  | 0.037  | 0.022  |
-| Scale    |        |        |       |          |        |        |        |
-|  coeff   | -0.095 | -1.255 | 0.005 |  0.033   | 0.040  | -0.081 | 0.008  |
-|  se_gls  | 0.081  | 1.073  | 0.014 |  0.067   | 0.126  | 0.061  | 0.049  |
-|  se_r    | 0.031  | 0.452  | 0.005 |  0.025   | 0.045  | 0.025  | 0.017  |
-|  se_cl   | 0.041  | 0.848  | 0.006 |  0.030   | 0.048  | 0.033  | 0.013  |
-| Q25      |        |        |       |          |        |        |        |
-|  coeff   | 0.201  | 0.576  | 0.025 |  0.082   | 0.010  | 0.757  | -0.020 |
-|  se_gls  | 0.154  | 2.070  | 0.024 |  0.118   | 0.219  | 0.121  | 0.085  |
-|  se_r    | 0.058  | 0.751  | 0.008 |  0.049   | 0.080  | 0.040  | 0.026  |
-|  se_cl   | 0.073  | 0.761  | 0.006 |  0.052   | 0.087  | 0.023  | 0.027  |
-| Q50      |        |        |       |          |        |        |        |
-|  coeff   | 0.119  | -0.512 | 0.029 |  0.111   | 0.045  | 0.687  | -0.013 |
-|  se_gls  | 0.091  | 1.230  | 0.014 |  0.070   | 0.130  | 0.072  | 0.051  |
-|  se_r    | 0.046  | 0.695  | 0.008 |  0.037   | 0.068  | 0.038  | 0.022  |
-|  se_cl   | 0.045  | 0.529  | 0.008 |  0.044   | 0.077  | 0.039  | 0.021  |
-| Q75      |        |        |       |          |        |        |        |
-|  coeff   | 0.041  | -1.555 | 0.033 |  0.138   | 0.078  | 0.619  | -0.007 |
-|  se_gls  | 0.067  | 0.898  | 0.011 |  0.053   | 0.098  | 0.052  | 0.038  |
-|  se_r    | 0.048  | 0.827  | 0.009 |  0.037   | 0.075  | 0.046  | 0.026  |
-|  se_cl   | 0.038  | 0.980  | 0.012 |  0.050   | 0.086  | 0.063  | 0.020  |
+:::{#tbl-tb2 tbl-pos="h"}
 
-: The Determinants of Government Surpluses: Individual and Time Fixed Effects {#tbl-tb2}
+{{< include tbl5.tex >}}
+
+The Determinants of Government Surpluses: Individual and Time Fixed Effects
+
+:::
+
+## The Effect of Criminal Activities on Labor Incomes{#sec-crime}
+
+In this section, we investigate the effects of criminal activities on labor incomes using a quantile regression approach to discover whether crime has different impacts on the distribution of interest.
+We use data from the ENEMDU labor survey from Ecuador and combine it with administrative records of crime reports by Ecuadorian Cantons.
+
+The combined data set covers the period 2019-2022.
+For the sake of brevity, we will only present here the results of quantile regressions of the log of total labor income on the log of annual reported murders (LMURDERS) and other covariates displayed in Table 1.
+However, our findings are robust to alternative specifications of the model where the dependent variable is either the log of per-capita household income or the log of total labor income from main occupation, both of which are displayed in @sec-app-crime.
+
+:::{#tbl-ecuador tbl-pos="htbp"}
+
+{{< include tbl6.tex >}}
+
+The Effect of Crime on Labor Income: Canton, Activity Sector and Time Fixed Effects
+
+:::
+
+The findings in @tbl-ecuador support the idea that the effect of murders diminishes as we move forward in the distribution from low to high incomes: in the lowest decile, a 1% increase in reported murders is associated with a 3.08% reduction in total labor income; instead, for the top 10% labor income earners, murders are seen to have little effect on the dependent variable and, in addition, the coefficient is not significant at conventional levels.
+Quantile regression estimates are thus really useful to discover relationships between dependent and explanatory variables that are not seen in standard (mean) regression analysis.
+For this application, we have found a monotonic decreasing effect of the log of reported crimes on total labor income.
+
+While the capability of estimating distinct coefficients of explanatory variables for each quantile is a feature present since @koenkerbasset1978, the method of moments approach allows us to include not one but multiple sets of fixed effects so that one can account for unobserved heterogeneity at different levels.
+Regarding this application, we have included in the estimation fixed effects for Canton, Activity Sector of the income earner and Year as is shown in @tbl-ecuador.
+Given that LMURDERS is measured at the Canton level, it may be important to control for unobserved factors affecting both crime and income earnings in the Cantons of Ecuador.
+
+Finally, our approach also allows us to obtain clustered standard errors for estimated coefficients so that statistical inference can be performed properly.
+@tbl-ecuador presents clustered standard errors at the Canton level, the rationale being the same as described above for the inclusion of Canton fixed effects in the specification.
+Had we not taken into account the correlated nature of our standard errors, we would have computed misleading (and smaller) estimates.
+For example, robust standard errors in this specification are, on average, 2.5 times smaller than clustered standard errors.
+It is important, however, to remark that the effects of murders on labor income at the lower half of the distribution are still statistically different from zero when clustering at the Canton level.
 
@@
 Nevertheless, there is no drastic change in the original conclusions.
+
+Our example using data to analyze the impact of Crime on labor income in Ecuador also suggests the relevance of using clustered standard errors in the presence of unobserved heterogeneity at different levels.
+We find that the effect of murders on labor income diminishes as we move forward in the distribution from low to high incomes, which is a result that would not have been possible without the use of quantile regression.
 
@@
 
+# Complementary analysis of @sec-crime{#sec-app-crime}
+
+In this appendix, we present the quantile regressions of both (log) per-capita household income and the (log) of labor income from main occupation on the (log) of annual reported murders.
+While in the first specification the coefficients of interest are not significant at conventional levels because of clustered standard errors (see @tbl-acrime1), the same pattern of decreasing association between murders and measurements of well-being as we move to the right of the distribution is revealed using our proposed method.
+
+However, in @tbl-acrime2 we get significant (at the 1% level) associations between reported murders and a slightly different measurement of labor income that only takes into account the main occupation of the individual.
+Compared to total labor income, the coefficients displayed in @tbl-acrime2 are smaller in magnitude: for the lowest decile of the distribution, we find a 1 percentage point difference in the coefficient of interest between the two alternative specifications, where the largest effect corresponds to total labor income.
+Nevertheless, and once again, the decreasing pattern of reported murders across quantiles is documented for this specification.
+What is even more interesting, compared to our estimations in @tbl-ecuador, is that crime is no longer statistically meaningful from the median of the distribution onwards.
+
+:::{#tbl-acrime1 tbl-pos="H"}
+
+{{< include tbla1.tex >}}
+
+The Effect of Crime on Per Capita Household Income: Canton and Time Fixed Effects
+:::
+
+:::{#tbl-acrime2 tbl-pos="H"}
+
+{{< include tbla2.tex >}}
+
+The Effect of Crime on Labor Income in Main Occupation: Canton, Activity
+Sector and Time FE
+:::
+
 # Implementation

### 2024-09-10 article/alt_article.tex
Update Paper
WIth Comments from GJ

--- 2024-02-08 article/article.tex
@@
 \documentclass[
-  authoryear,
-  review,
-  1p]{elsarticle}
+  12pt,
+  oneside]{article}
 
@@
 \usepackage{xcolor}
+\usepackage[lmargin=1.1in,rmargin=1.1in,tmargin=1in,bmargin=1.2in]{geometry}
 \setlength{\emergencystretch}{3em} % prevent overfull lines
@@
 % Make \paragraph and \subparagraph free-standing
+\makeatletter
 \ifx\paragraph\undefined\else
   \let\oldparagraph\paragraph
-  \renewcommand{\paragraph}[1]{\oldparagraph{#1}\mbox{}}
+  \renewcommand{\paragraph}{
+    \@ifstar
+      \xxxParagraphStar
+      \xxxParagraphNoStar
+  }
+  \newcommand{\xxxParagraphStar}[1]{\oldparagraph*{#1}\mbox{}}
+  \newcommand{\xxxParagraphNoStar}[1]{\oldparagraph{#1}\mbox{}}
 \fi
@@
   \let\oldsubparagraph\subparagraph
-  \renewcommand{\subparagraph}[1]{\oldsubparagraph{#1}\mbox{}}
+  \renewcommand{\subparagraph}{
+    \@ifstar
+      \xxxSubParagraphStar
+      \xxxSubParagraphNoStar
+  }
+  \newcommand{\xxxSubParagraphStar}[1]{\oldsubparagraph*{#1}\mbox{}}
+  \newcommand{\xxxSubParagraphNoStar}[1]{\oldsubparagraph{#1}\mbox{}}
 \fi
+\makeatother
 
@@
 
-\tnotetext[t1]{The opinions expressed in this paper are those of the authors and do not necessarily reflect the views of the World Bank, its Board of Directors, or the countries it represents.}
-\tnotetext[t2]{The authors would like to thank Enrique Pinzon an Joao Santos-Silva for their helpful comments and suggestions.}
+% TODO: Add custom LaTeX header directives here
 \makeatletter
@@
 \makeatother
+
 \ifLuaTeX
@@
 \usepackage[]{natbib}
-\bibliographystyle{elsarticle-harv}
+\bibliographystyle{chicago}
 \usepackage{bookmark}
@@
 \hypersetup{
-  pdftitle={Estimating Quantile Regressions with Multiple Fixed Effects through Method of Moments },
+  pdftitle={Estimating Quantile Regressions with Multiple Fixed Effects through Method of Moments},
   pdfauthor={Fernando Rios-Avila; Leonardo Siles; Gustavo Canavire-Bacarreza},
@@
 
-\setlength{\parindent}{6pt}
+\definecolor{ahjcolor}{rgb}{0.0, 0.13, 0.82}
+\PassOptionsToPackage{colorlinks=true, linkcolor=ahjcolor, urlcolor=ahjcolor, citecolor=ahjcolor}{hyperref}
+
+% --- Packages ---
+% Layout and spacing
+\usepackage{setspace}
+\usepackage{enumitem}
+
+% Math and symbols
+\usepackage{amsmath, amssymb, amsthm, amsbsy, amsfonts, mathrsfs, mathtools, bm, dsfont}
+
+% Graphics and tables
+\usepackage{graphicx, float, caption, subcaption}
+\usepackage{longtable, array, multirow, booktabs, threeparttable}
+\usepackage{lscape}
+
+% Text formatting
+\usepackage{color, xcolor, soul}
+\usepackage{titlesec}
+
+% Additional features
+\usepackage{authblk} % Author and affiliation
+\usepackage{appendix} % Appendix support
+
+% Hyperlinks
+\usepackage{hyperref}
+
+% Math Operators
+\DeclareMathOperator*{\argmin}{arg\,min}
+\DeclareMathOperator*{\argmax}{arg\,max}
+\DeclareMathOperator*{\sign}{sign}
+\DeclareMathOperator*{\tr}{Tr}
+\DeclareMathOperator*{\p}{Pr}
+\DeclareMathOperator*{\Var}{Var}
+\DeclareMathOperator*{\rank}{rank}
+\DeclareMathOperator*{\diag}{diag}
+
+% Theorem Environments
+\newtheorem{thm}{Theorem}
+\newtheorem{cor}{Corollary}
+\newtheorem{lemma}{Lemma}
+\newtheorem{prop}{Proposition}
+\newtheorem{ass}{Assumption}
+\newtheorem{exm}{Example}
+
+% Affiliation formatting
+\renewcommand\Affilfont{\itshape\small}
+
+% LaTeX tweaks
+\setcounter{MaxMatrixCols}{10}
+\makeatletter
+\makeatother
+
+% Page settings
+\onehalfspacing
+\setlength{\parskip}{0.5em}
+\setlist{nolistsep}
+% title
+
+\title{\textbf{\Large Estimating Quantile Regressions with Multiple
+Fixed Effects through Method of Moments}\thanks{The opinions expressed
+in this paper are those of the authors and do not necessarily reflect
+the views of the World Bank, its Board of Directors, or the countries it
+represents.
+
+The authors would like to thank Enrique Pinzon an Joao Santos-Silva for
+their helpful comments and suggestions.}}
+
+\author{
+Fernando Rios-Avila
+\thanks{
+      Levy Economics Institute of Bard
+College      \href{mailto:friosavi@levy.org}{Email: friosavi@levy.org}
+  } \hspace{0.25 cm} 
+Leonardo Siles
+\thanks{
+      Universidad Católica
+Boliviana      \href{mailto:leonardo.siles@ucb.edu.bo}{Email: leonardo.siles@ucb.edu.bo}
+  } \hspace{0.25 cm} 
+Gustavo Canavire-Bacarreza
+\thanks{
+      The World
+Bank      \href{mailto:gcanavire@worldbank.org}{Email: gcanavire@worldbank.org}
+  }}
+
 \begin{document}
-
-\begin{frontmatter}
-\title{Estimating Quantile Regressions with Multiple Fixed Effects
-through Method of Moments \tnoteref{t1,t2}}
-\author[1]{Fernando Rios-Avila%
-\corref{cor1}%
-}
- \ead{friosavi@levy.org} 
-\author[2]{Leonardo Siles%
-%
-}
- \ead{leonardo.siles@ucb.edu.bo} 
-\author[3]{Gustavo Canavire-Bacarreza%
-%
-}
- \ead{gcanavire@worldbank.org}
-
-\affiliation[1]{organization={Levy Economics Institute of Bard
-College},city={Annandale-on-Hudson,
-NY},country={USA},countrysep={,},postcodesep={}}
-\affiliation[2]{organization={Universidad Católica Boliviana},city={La
-Paz},country={Bolivia},countrysep={,},postcodesep={}}
-\affiliation[3]{organization={The World Bank},city={Washington,
-D.C.},country={USA},countrysep={,},postcodesep={}}
-
-\cortext[cor1]{Corresponding author}
-
+\maketitle
 \begin{abstract}
-This paper proposes a new method to estimate quantile regressions with
-multiple fixed effects. The method, which expands on the strategy
+
+    This paper proposes a new method to estimate quantile regressions
+with multiple fixed effects. The method, which expands on the strategy
 proposed by \citet{mss2019}, allows for the inclusion of multiple fixed
@@
 determinants of the surplus of government as a share of GDP, allowing
-for both time and country fixed effects.
+for both time and country fixed effects. \\ \\
+
+    \noindent \textbf{Keywords:} Fixed effectsLinear
+heteroskedasticityLocation-scale modelQuantile regression \\
+    \noindent \textbf{JEL Codes:} C21C22C23
+
     \end{abstract}
 
-\begin{keyword}
-    Fixed effects \sep Linear heteroskedasticity \sep Location-scale
-model \sep 
-    Quantile regression
-\end{keyword}
-\end{frontmatter}
+    \newpage
+
+\newpage{}
 
@@
 the data is based on a multiplicative heteroskedastic process that is
-linear in parameters \citep[\citet{he1997}, \citet{zhao2000},
-\citet{cameron2005}]{mss2019}, the effect of a variable \(X\) on the
-\(q_{th}\) quantile can be derived as the combination of a location
-effect, and scale effect moderated by the quantile of an underlying
-i.i.d. error. For statistical inference, MSS derives the asymptotic
-distribution of the estimator, suggesting the use of bootstrap standard
-errors, as well.
+linear in parameters \citep[@he1997, @zhao2000, @cameron2005]{mss2019},
+the effect of a variable \(X\) on the \(q_{th}\) quantile can be derived
+as the combination of a location effect, and scale effect moderated by
+the quantile of an underlying i.i.d. error. For statistical inference,
+MSS derives the asymptotic distribution of the estimator, suggesting the
+use of bootstrap standard errors, as well.
 
@@
 
-\begin{table}
+\begin{table}[H]
 
@@
 
-\section{Illustrative application}\label{illustrative-application}
+\section{Illustrative applications}\label{illustrative-applications}
+
+\subsection{Determinants of government
+surpluses}\label{determinants-of-government-surpluses}
 
@@
 
-\begin{longtable}[]{@{}
-  >{\raggedright\arraybackslash}p{(\columnwidth - 18\tabcolsep) * \real{0.1235}}
-  >{\centering\arraybackslash}p{(\columnwidth - 18\tabcolsep) * \real{0.1111}}
-  >{\centering\arraybackslash}p{(\columnwidth - 18\tabcolsep) * \real{0.0988}}
-  >{\centering\arraybackslash}p{(\columnwidth - 18\tabcolsep) * \real{0.0864}}
-  >{\centering\arraybackslash}p{(\columnwidth - 18\tabcolsep) * \real{0.0864}}
-  >{\centering\arraybackslash}p{(\columnwidth - 18\tabcolsep) * \real{0.0988}}
-  >{\centering\arraybackslash}p{(\columnwidth - 18\tabcolsep) * \real{0.0988}}
-  >{\centering\arraybackslash}p{(\columnwidth - 18\tabcolsep) * \real{0.0988}}
-  >{\centering\arraybackslash}p{(\columnwidth - 18\tabcolsep) * \real{0.0988}}
-  >{\centering\arraybackslash}p{(\columnwidth - 18\tabcolsep) * \real{0.0988}}@{}}
-\caption{Determinants of Government Surpluses: Individual Fixed
-Effects}\label{tbl-tb1}\tabularnewline
-\toprule\noalign{}
-\begin{minipage}[b]{\linewidth}\raggedright
-\end{minipage} & \begin{minipage}[b]{\linewidth}\centering
-polityt
-\end{minipage} & \begin{minipage}[b]{\linewidth}\centering
-lyp
-\end{minipage} & \begin{minipage}[b]{\linewidth}\centering
-trade
-\end{minipage} & \begin{minipage}[b]{\linewidth}\centering
-p1564
-\end{minipage} & \begin{minipage}[b]{\linewidth}\centering
-p65
-\end{minipage} & \begin{minipage}[b]{\linewidth}\centering
-lspl
-\end{minipage} & \begin{minipage}[b]{\linewidth}\centering
-oil\_im
-\end{minipage} & \begin{minipage}[b]{\linewidth}\centering
-oil\_ex
-\end{minipage} & \begin{minipage}[b]{\linewidth}\centering
-ygap
-\end{minipage} \\
-\midrule\noalign{}
-\endfirsthead
-\toprule\noalign{}
-\begin{minipage}[b]{\linewidth}\raggedright
-\end{minipage} & \begin{minipage}[b]{\linewidth}\centering
-polityt
-\end{minipage} & \begin{minipage}[b]{\linewidth}\centering
-lyp
-\end{minipage} & \begin{minipage}[b]{\linewidth}\centering
-trade
-\end{minipage} & \begin{minipage}[b]{\linewidth}\centering
-p1564
-\end{minipage} & \begin{minipage}[b]{\linewidth}\centering
-p65
-\end{minipage} & \begin{minipage}[b]{\linewidth}\centering
-lspl
-\end{minipage} & \begin{minipage}[b]{\linewidth}\centering
-oil\_im
-\end{minipage} & \begin{minipage}[b]{\linewidth}\centering
-oil\_ex
-\end{minipage} & \begin{minipage}[b]{\linewidth}\centering
-ygap
-\end{minipage} \\
-\midrule\noalign{}
-\endhead
-\bottomrule\noalign{}
-\endlastfoot
-Location & & & & & & & & & \\
-~coeff & 0.116 & -0.715 & 0.030 & 0.121 & 0.028 & 0.691 & -0.047 &
--0.006 & 0.010 \\
-~se\_gls & 0.046 & 0.540 & 0.008 & 0.033 & 0.070 & 0.035 & 0.008 & 0.022
-& 0.028 \\
-~se\_r & 0.047 & 0.597 & 0.008 & 0.031 & 0.070 & 0.037 & 0.007 & 0.017 &
-0.021 \\
-~se\_cl & 0.046 & 0.465 & 0.007 & 0.032 & 0.071 & 0.035 & 0.010 & 0.020
-& 0.023 \\
-Scale & & & & & & & & & \\
-~coeff & -0.097 & -0.616 & 0.003 & 0.036 & 0.087 & -0.085 & 0.013 &
-0.016 & -0.004 \\
-~se\_gls & 0.032 & 0.371 & 0.005 & 0.023 & 0.048 & 0.024 & 0.006 & 0.015
-& 0.019 \\
-~se\_r & 0.031 & 0.398 & 0.005 & 0.020 & 0.049 & 0.025 & 0.005 & 0.010 &
-0.015 \\
-~se\_cl & 0.048 & 0.800 & 0.008 & 0.031 & 0.067 & 0.029 & 0.004 & 0.010
-& 0.012 \\
-Q25 & & & & & & & & & \\
-~coeff & 0.191 & -0.239 & 0.028 & 0.093 & -0.039 & 0.756 & -0.057 &
--0.018 & 0.013 \\
-~se\_gls & 0.059 & 0.684 & 0.010 & 0.042 & 0.088 & 0.045 & 0.010 & 0.027
-& 0.035 \\
-~se\_r & 0.056 & 0.656 & 0.008 & 0.036 & 0.086 & 0.040 & 0.010 & 0.020 &
-0.025 \\
-~se\_cl & 0.073 & 0.687 & 0.006 & 0.041 & 0.098 & 0.023 & 0.010 & 0.021
-& 0.029 \\
-Q50 & & & & & & & & & \\
-~coeff & 0.108 & -0.765 & 0.030 & 0.124 & 0.035 & 0.684 & -0.046 &
--0.005 & 0.009 \\
-~se\_gls & 0.046 & 0.535 & 0.007 & 0.033 & 0.069 & 0.035 & 0.008 & 0.022
-& 0.027 \\
-~se\_r & 0.046 & 0.593 & 0.008 & 0.031 & 0.069 & 0.036 & 0.007 & 0.017 &
-0.021 \\
-~se\_cl & 0.043 & 0.484 & 0.008 & 0.032 & 0.070 & 0.036 & 0.010 & 0.020
-& 0.023 \\
-Q75 & & & & & & & & & \\
-~coeff & 0.031 & -1.258 & 0.033 & 0.153 & 0.104 & 0.616 & -0.036 & 0.008
-& 0.006 \\
-~se\_gls & 0.048 & 0.551 & 0.008 & 0.034 & 0.071 & 0.036 & 0.008 & 0.022
-& 0.028 \\
-~se\_r & 0.049 & 0.696 & 0.009 & 0.034 & 0.075 & 0.043 & 0.007 & 0.018 &
-0.023 \\
-~se\_cl & 0.039 & 0.919 & 0.012 & 0.041 & 0.079 & 0.055 & 0.010 & 0.022
-& 0.020 \\
-\end{longtable}
+\begin{table}[h]
+
+\caption{\label{tbl-tb1}Determinants of Government Surpluses: Individual
+Fixed Effects}
+
+\centering{
+
+    \centering
+    \begin{tabular}{lccccccccc}
+    \toprule
+              & polityt &  lyp   & trade & p1564 &  p65   &  lspl  & oil-im & oil-ex &  ygap  \\
+    \midrule
+    \multicolumn{8}{l}{\textbf{Location}} \\
+    \ \ \ coeff     &  0.116  & -0.715 & 0.030 & 0.121 & 0.028  & 0.691  & -0.047 & -0.006 & 0.010  \\
+    \ \ \ se-gls   &  0.046  & 0.540  & 0.008 & 0.033 & 0.070  & 0.035  & 0.008  & 0.022  & 0.028  \\
+    \ \ \ se-r     &  0.047  & 0.597  & 0.008 & 0.031 & 0.070  & 0.037  & 0.007  & 0.017  & 0.021  \\
+    \ \ \ se-cl    &  0.046  & 0.465  & 0.007 & 0.032 & 0.071  & 0.035  & 0.010  & 0.020  & 0.023  \\
+    \hline
+    \multicolumn{8}{l}{\textbf{Scale}} \\
+    \ \ \ coeff     & -0.097  & -0.616 & 0.003 & 0.036 & 0.087  & -0.085 & 0.013  & 0.016  & -0.004 \\
+    \ \ \ se-gls   &  0.032  & 0.371  & 0.005 & 0.023 & 0.048  & 0.024  & 0.006  & 0.015  & 0.019  \\
+    \ \ \ se-r     &  0.031  & 0.398  & 0.005 & 0.020 & 0.049  & 0.025  & 0.005  & 0.010  & 0.015  \\
+    \ \ \ se-cl    &  0.048  & 0.800  & 0.008 & 0.031 & 0.067  & 0.029  & 0.004  & 0.010  & 0.012  \\
+    \hline
+    \multicolumn{8}{l}{\textbf{Q25}} \\
+    \ \ \ coeff     &  0.191  & -0.239 & 0.028 & 0.093 & -0.039 & 0.756  & -0.057 & -0.018 & 0.013  \\
+    \ \ \ se-gls   &  0.059  & 0.684  & 0.010 & 0.042 & 0.088  & 0.045  & 0.010  & 0.027  & 0.035  \\
+    \ \ \ se-r     &  0.056  & 0.656  & 0.008 & 0.036 & 0.086  & 0.040  & 0.010  & 0.020  & 0.025  \\
+    \ \ \ se-cl    &  0.073  & 0.687  & 0.006 & 0.041 & 0.098  & 0.023  & 0.010  & 0.021  & 0.029  \\
+    \hline
+    \multicolumn{8}{l}{\textbf{Q50}} \\
+    \ \ \ coeff     &  0.108  & -0.765 & 0.030 & 0.124 & 0.035  & 0.684  & -0.046 & -0.005 & 0.009  \\
+    \ \ \ se-gls   &  0.046  & 0.535  & 0.007 & 0.033 & 0.069  & 0.035  & 0.008  & 0.022  & 0.027  \\
+    \ \ \ se-r     &  0.046  & 0.593  & 0.008 & 0.031 & 0.069  & 0.036  & 0.007  & 0.017  & 0.021  \\
+    \ \ \ se-cl    &  0.043  & 0.484  & 0.008 & 0.032 & 0.070  & 0.036  & 0.010  & 0.020  & 0.023  \\
+    \hline
+    \multicolumn{8}{l}{\textbf{Q75}} \\
+    \ \ \ coeff     &  0.031  & -1.258 & 0.033 & 0.153 & 0.104  & 0.616  & -0.036 & 0.008  & 0.006  \\
+    \ \ \ se-gls   &  0.048  & 0.551  & 0.008 & 0.034 & 0.071  & 0.036  & 0.008  & 0.022  & 0.028  \\
+    \ \ \ se-r     &  0.049  & 0.696  & 0.009 & 0.034 & 0.075  & 0.043  & 0.007  & 0.018  & 0.023  \\
+    \ \ \ se-cl    &  0.039  & 0.919  & 0.012 & 0.041 & 0.079  & 0.055  & 0.010  & 0.022  & 0.020  \\
+    \bottomrule
+    \end{tabular}
+
+}
+
+\end{table}%
 
@@
   be due that in our derivation the influence function of the
-  standardized \(\tau_{th}\) quantile (see \#eq-ifs) does not have the
-  same leading term as the one reported in MSS (see Theorem 3, and the
-  definition of \(W\)).}
+  standardized \(\tau_{th}\) quantile (see Equation~\ref{eq-ifs}) does
+  not have the same leading term as the one reported in MSS (see Theorem
+  3, and the definition of \(W\)).}
 
@@
 
-\begin{longtable}[]{@{}
-  >{\raggedright\arraybackslash}p{(\columnwidth - 14\tabcolsep) * \real{0.1493}}
-  >{\centering\arraybackslash}p{(\columnwidth - 14\tabcolsep) * \real{0.1194}}
-  >{\centering\arraybackslash}p{(\columnwidth - 14\tabcolsep) * \real{0.1194}}
-  >{\centering\arraybackslash}p{(\columnwidth - 14\tabcolsep) * \real{0.1045}}
-  >{\centering\arraybackslash}p{(\columnwidth - 14\tabcolsep) * \real{0.1493}}
-  >{\centering\arraybackslash}p{(\columnwidth - 14\tabcolsep) * \real{0.1194}}
-  >{\centering\arraybackslash}p{(\columnwidth - 14\tabcolsep) * \real{0.1194}}
-  >{\centering\arraybackslash}p{(\columnwidth - 14\tabcolsep) * \real{0.1194}}@{}}
-\caption{The Determinants of Government Surpluses: Individual and Time
-Fixed Effects}\label{tbl-tb2}\tabularnewline
-\toprule\noalign{}
-\begin{minipage}[b]{\linewidth}\raggedright
-\end{minipage} & \begin{minipage}[b]{\linewidth}\centering
-polity
-\end{minipage} & \begin{minipage}[b]{\linewidth}\centering
-lyp
-\end{minipage} & \begin{minipage}[b]{\linewidth}\centering
-trade
-\end{minipage} & \begin{minipage}[b]{\linewidth}\centering
-prop1564
-\end{minipage} & \begin{minipage}[b]{\linewidth}\centering
-prop65
-\end{minipage} & \begin{minipage}[b]{\linewidth}\centering
-lspl
-\end{minipage} & \begin{minipage}[b]{\linewidth}\centering
-ygap
-\end{minipage} \\
-\midrule\noalign{}
-\endfirsthead
-\toprule\noalign{}
-\begin{minipage}[b]{\linewidth}\raggedright
-\end{minipage} & \begin{minipage}[b]{\linewidth}\centering
-polity
-\end{minipage} & \begin{minipage}[b]{\linewidth}\centering
-lyp
-\end{minipage} & \begin{minipage}[b]{\linewidth}\centering
-trade
-\end{minipage} & \begin{minipage}[b]{\linewidth}\centering
-prop1564
-\end{minipage} & \begin{minipage}[b]{\linewidth}\centering
-prop65
-\end{minipage} & \begin{minipage}[b]{\linewidth}\centering
-lspl
-\end{minipage} & \begin{minipage}[b]{\linewidth}\centering
-ygap
-\end{minipage} \\
-\midrule\noalign{}
-\endhead
-\bottomrule\noalign{}
-\endlastfoot
-Location & & & & & & & \\
-~coeff & 0.126 & -0.418 & 0.028 & 0.108 & 0.042 & 0.693 & -0.014 \\
-~se\_gls & 0.087 & 1.157 & 0.015 & 0.072 & 0.136 & 0.066 & 0.053 \\
-~se\_r & 0.047 & 0.703 & 0.008 & 0.038 & 0.068 & 0.038 & 0.022 \\
-~se\_cl & 0.048 & 0.506 & 0.008 & 0.044 & 0.077 & 0.037 & 0.022 \\
-Scale & & & & & & & \\
-~coeff & -0.095 & -1.255 & 0.005 & 0.033 & 0.040 & -0.081 & 0.008 \\
-~se\_gls & 0.081 & 1.073 & 0.014 & 0.067 & 0.126 & 0.061 & 0.049 \\
-~se\_r & 0.031 & 0.452 & 0.005 & 0.025 & 0.045 & 0.025 & 0.017 \\
-~se\_cl & 0.041 & 0.848 & 0.006 & 0.030 & 0.048 & 0.033 & 0.013 \\
-Q25 & & & & & & & \\
-~coeff & 0.201 & 0.576 & 0.025 & 0.082 & 0.010 & 0.757 & -0.020 \\
-~se\_gls & 0.154 & 2.070 & 0.024 & 0.118 & 0.219 & 0.121 & 0.085 \\
-~se\_r & 0.058 & 0.751 & 0.008 & 0.049 & 0.080 & 0.040 & 0.026 \\
-~se\_cl & 0.073 & 0.761 & 0.006 & 0.052 & 0.087 & 0.023 & 0.027 \\
-Q50 & & & & & & & \\
-~coeff & 0.119 & -0.512 & 0.029 & 0.111 & 0.045 & 0.687 & -0.013 \\
-~se\_gls & 0.091 & 1.230 & 0.014 & 0.070 & 0.130 & 0.072 & 0.051 \\
-~se\_r & 0.046 & 0.695 & 0.008 & 0.037 & 0.068 & 0.038 & 0.022 \\
-~se\_cl & 0.045 & 0.529 & 0.008 & 0.044 & 0.077 & 0.039 & 0.021 \\
-Q75 & & & & & & & \\
-~coeff & 0.041 & -1.555 & 0.033 & 0.138 & 0.078 & 0.619 & -0.007 \\
-~se\_gls & 0.067 & 0.898 & 0.011 & 0.053 & 0.098 & 0.052 & 0.038 \\
-~se\_r & 0.048 & 0.827 & 0.009 & 0.037 & 0.075 & 0.046 & 0.026 \\
-~se\_cl & 0.038 & 0.980 & 0.012 & 0.050 & 0.086 & 0.063 & 0.020 \\
-\end{longtable}
+\begin{table}[h]
+
+\caption{\label{tbl-tb2}The Determinants of Government Surpluses:
+Individual and Time Fixed Effects}
+
+\centering{
+
+    \centering
+    \begin{tabular}{lccccccc}
+    \hline
+     & polity & lyp & trade & prop1564 & prop65 & lspl & ygap \\
+    \hline
+    \multicolumn{8}{l}{\textbf{Location}} \\
+    \ \ \ coeff & 0.126 & -0.418 & 0.028 & 0.108 & 0.042 & 0.693 & -0.014 \\
+    \ \ \ se-gls & 0.087 & 1.157 & 0.015 & 0.072 & 0.136 & 0.066 & 0.053 \\
+    \ \ \ se-r & 0.047 & 0.703 & 0.008 & 0.038 & 0.068 & 0.038 & 0.022 \\
+    \ \ \ se-cl & 0.048 & 0.506 & 0.008 & 0.044 & 0.077 & 0.037 & 0.022 \\
+    \hline
+    \multicolumn{8}{l}{\textbf{Scale}} \\
+    \ \ \ coeff & -0.095 & -1.255 & 0.005 & 0.033 & 0.040 & -0.081 & 0.008 \\
+    \ \ \ se-gls & 0.081 & 1.073 & 0.014 & 0.067 & 0.126 & 0.061 & 0.049 \\
+    \ \ \ se-r & 0.031 & 0.452 & 0.005 & 0.025 & 0.045 & 0.025 & 0.017 \\
+    \ \ \ se-cl & 0.041 & 0.848 & 0.006 & 0.030 & 0.048 & 0.033 & 0.013 \\
+    \hline
+    \multicolumn{8}{l}{\textbf{Q25}} \\
+    \ \ \ coeff & 0.201 & 0.576 & 0.025 & 0.082 & 0.010 & 0.757 & -0.020 \\
+    \ \ \ se-gls & 0.154 & 2.070 & 0.024 & 0.118 & 0.219 & 0.121 & 0.085 \\
+    \ \ \ se-r & 0.058 & 0.751 & 0.008 & 0.049 & 0.080 & 0.040 & 0.026 \\
+    \ \ \ se-cl & 0.073 & 0.761 & 0.006 & 0.052 & 0.087 & 0.023 & 0.027 \\
+    \hline
+    \multicolumn{8}{l}{\textbf{Q50}} \\
+    \ \ \ coeff & 0.119 & -0.512 & 0.029 & 0.111 & 0.045 & 0.687 & -0.013 \\
+    \ \ \ se-gls & 0.091 & 1.230 & 0.014 & 0.070 & 0.130 & 0.072 & 0.051 \\
+    \ \ \ se-r & 0.046 & 0.695 & 0.008 & 0.037 & 0.068 & 0.038 & 0.022 \\
+    \ \ \ se-cl & 0.045 & 0.529 & 0.008 & 0.044 & 0.077 & 0.039 & 0.021 \\
+    \hline
+    \multicolumn{8}{l}{\textbf{Q75}} \\
+    \ \ \ coeff & 0.041 & -1.555 & 0.033 & 0.138 & 0.078 & 0.619 & -0.007 \\
+    \ \ \ se-gls & 0.067 & 0.898 & 0.011 & 0.053 & 0.098 & 0.052 & 0.038 \\
+    \ \ \ se-r & 0.048 & 0.827 & 0.009 & 0.037 & 0.075 & 0.046 & 0.026 \\
+    \ \ \ se-cl & 0.038 & 0.980 & 0.012 & 0.050 & 0.086 & 0.063 & 0.020 \\
+    \hline
+    \end{tabular}
+
+}
+
+\end{table}%
+
+\subsection{The Effect of Criminal Activities on Labor
+Incomes}\label{sec-crime}
+
+In this section, we investigate the effects of criminal activities on
+labor incomes using a quantile regression approach to discover whether
+crime has different impacts on the distribution of interest. We use data
+from the ENEMDU labor survey from Ecuador and combine it with
+administrative records of crime reports by Ecuadorian Cantons.
+
+The combined data set covers the period 2019-2022. For the sake of
+brevity, we will only present here the results of quantile regressions
+of the log of total labor income on the log of annual reported murders
+(LMURDERS) and other covariates displayed in Table 1. However, our
+findings are robust to alternative specifications of the model where the
+dependent variable is either the log of per-capita household income or
+the log of total labor income from main occupation, both of which are
+displayed in Section~\ref{sec-app-crime}.
+
+\begin{table}[htbp]
+
+\caption{\label{tbl-ecuador}The Effect of Crime on Labor Income: Canton,
+Activity Sector and Time Fixed Effects}
+
+\centering{
+
+    \centering
+    \begin{tabular}{lccccc}
+    \toprule
+    VARIABLES & q10 & q25 & q50 & q75 & q90 \\ \hline
+     &  &  &  &  &  \\
+    lmurders & -0.031* & -0.022* & -0.014* & -0.007 & -0.002 \\
+     & (0.016) & (0.012) & (0.008) & (0.006) & (0.006) \\
+    age & 0.062*** & 0.058*** & 0.054*** & 0.050*** & 0.047*** \\
+     & (0.002) & (0.002) & (0.002) & (0.002) & (0.002) \\
+    age$^2$ & -0.001*** & -0.001*** & -0.001*** & -0.001*** & -0.001*** \\
+     & (0.000) & (0.000) & (0.000) & (0.000) & (0.000) \\
+    male & 0.526*** & 0.435*** & 0.353*** & 0.284*** & 0.225*** \\
+     & (0.049) & (0.037) & (0.027) & (0.020) & (0.017) \\
+    informal & -0.841*** & -0.723*** & -0.617*** & -0.528*** & -0.451*** \\
+     & (0.040) & (0.028) & (0.019) & (0.014) & (0.014) \\
+    urban & -0.104*** & -0.102*** & -0.101*** & -0.100*** & -0.099*** \\
+     & (0.014) & (0.012) & (0.011) & (0.012) & (0.013) \\
+    married & 0.085*** & 0.094*** & 0.102*** & 0.108*** & 0.114*** \\
+     & (0.013) & (0.010) & (0.007) & (0.006) & (0.005) \\
+    educ & 0.026*** & 0.035*** & 0.042*** & 0.048*** & 0.053*** \\
+     & (0.002) & (0.002) & (0.003) & (0.003) & (0.004) \\
+    tenure & 0.010*** & 0.008*** & 0.007*** & 0.006*** & 0.005*** \\
+     & (0.001) & (0.001) & (0.001) & (0.001) & (0.001) \\
+    Constant & 3.715*** & 4.130*** & 4.500*** & 4.813*** & 5.082*** \\
+     & (0.058) & (0.046) & (0.043) & (0.046) & (0.052) \\
+     &  &  &  &  &  \\
+    \bottomrule
+    Observations & 445,521 & 445,521 & 445,521 & 445,521 & 445,521 \\
+    Canton FE & Yes & Yes & Yes & Yes & Yes \\
+    Activity Sector FE & Yes & Yes & Yes & Yes & Yes \\
+    Year FE & Yes & Yes & Yes & Yes & Yes \\ 
+    \bottomrule
+    \multicolumn{6}{c}{ Clustered standard errors at Canton Level in parentheses} \\
+    \multicolumn{6}{c}{ *** p$<$0.01, ** p$<$0.05, * p$<$0.1} \\
+    \end{tabular}
+
+}
+
+\end{table}%
+
+The findings in Table~\ref{tbl-ecuador} support the idea that the effect
+of murders diminishes as we move forward in the distribution from low to
+high incomes: in the lowest decile, a 1\% increase in reported murders
+is associated with a 3.08\% reduction in total labor income; instead,
+for the top 10\% labor income earners, murders are seen to have little
+effect on the dependent variable and, in addition, the coefficient is
+not significant at conventional levels. Quantile regression estimates
+are thus really useful to discover relationships between dependent and
+explanatory variables that are not seen in standard (mean) regression
+analysis. For this application, we have found a monotonic decreasing
+effect of the log of reported crimes on total labor income.
+
+While the capability of estimating distinct coefficients of explanatory
+variables for each quantile is a feature present since
+\citet{koenkerbasset1978}, the method of moments approach allows us to
+include not one but multiple sets of fixed effects so that one can
+account for unobserved heterogeneity at different levels. Regarding this
+application, we have included in the estimation fixed effects for
+Canton, Activity Sector of the income earner and Year as is shown in
+Table~\ref{tbl-ecuador}. Given that LMURDERS is measured at the Canton
+level, it may be important to control for unobserved factors affecting
+both crime and income earnings in the Cantons of Ecuador.
+
+Finally, our approach also allows us to obtain clustered standard errors
+for estimated coefficients so that statistical inference can be
+performed properly. Table~\ref{tbl-ecuador} presents clustered standard
+errors at the Canton level, the rationale being the same as described
+above for the inclusion of Canton fixed effects in the specification.
+Had we not taken into account the correlated nature of our standard
+errors, we would have computed misleading (and smaller) estimates. For
+example, robust standard errors in this specification are, on average,
+2.5 times smaller than clustered standard errors. It is important,
+however, to remark that the effects of murders on labor income at the
+lower half of the distribution are still statistically different from
+zero when clustering at the Canton level.
 
@@
 drastic change in the original conclusions.
+
+Our example using data to analyze the impact of Crime on labor income in
+Ecuador also suggests the relevance of using clustered standard errors
+in the presence of unobserved heterogeneity at different levels. We find
+that the effect of murders on labor income diminishes as we move forward
+in the distribution from low to high incomes, which is a result that
+would not have been possible without the use of quantile regression.
 
@@
 
+\section{\texorpdfstring{Complementary analysis of
+Section~\ref{sec-crime}}{Complementary analysis of Section~}}\label{sec-app-crime}
+
+In this appendix, we present the quantile regressions of both (log)
+per-capita household income and the (log) of labor income from main
+occupation on the (log) of annual reported murders. While in the first
+specification the coefficients of interest are not significant at
+conventional levels because of clustered standard errors (see
+Table~\ref{tbl-acrime1}), the same pattern of decreasing association
+between murders and measurements of well-being as we move to the right
+of the distribution is revealed using our proposed method.
+
+However, in Table~\ref{tbl-acrime2} we get significant (at the 1\%
+level) associations between reported murders and a slightly different
+measurement of labor income that only takes into account the main
+occupation of the individual. Compared to total labor income, the
+coefficients displayed in Table~\ref{tbl-acrime2} are smaller in
+magnitude: for the lowest decile of the distribution, we find a 1
+percentage point difference in the coefficient of interest between the
+two alternative specifications, where the largest effect corresponds to
+total labor income. Nevertheless, and once again, the decreasing pattern
+of reported murders across quantiles is documented for this
+specification. What is even more interesting, compared to our
+estimations in Table~\ref{tbl-ecuador}, is that crime is no longer
+statistically meaningful from the median of the distribution onwards.
+
+\begin{table}[H]
+
+\caption{\label{tbl-acrime1}The Effect of Crime on Per Capita Household
+Income: Canton and Time Fixed Effects}
+
+\centering{
+
+    \centering
+    \begin{tabular}{lccccc}
+    \toprule
+    VARIABLES & q10 & q25 & q50 & q75 & q90 \\ \hline
+     &  &  &  &  &  \\
+    lmurders & -0.026 & -0.022 & -0.019 & -0.015 & -0.012 \\
+     & (0.019) & (0.015) & (0.012) & (0.009) & (0.008) \\
+    age & 0.005*** & 0.005*** & 0.005*** & 0.006*** & 0.006*** \\
+     & (0.001) & (0.001) & (0.001) & (0.001) & (0.001) \\
+    age$^2$ & 0.000 & 0.000 & 0.000** & 0.000** & 0.000** \\
+     & (0.000) & (0.000) & (0.000) & (0.000) & (0.000) \\
+    male & -0.014** & -0.010** & -0.006 & -0.003 & 0.000 \\
+     & (0.006) & (0.005) & (0.004) & (0.004) & (0.004) \\
+    informal & -0.428*** & -0.377*** & -0.326*** & -0.279*** & -0.237*** \\
+     & (0.029) & (0.024) & (0.018) & (0.014) & (0.011) \\
+    urban & 0.136*** & 0.128*** & 0.119*** & 0.112*** & 0.105*** \\
+     & (0.033) & (0.030) & (0.028) & (0.026) & (0.025) \\
+    Constant & 5.046*** & 5.377*** & 5.707*** & 6.014*** & 6.282*** \\
+     & (0.079) & (0.068) & (0.061) & (0.058) & (0.059) \\
+     &  &  &  &  &  \\ \hline
+    Observations & 566,127 & 566,127 & 566,127 & 566,127 & 566,127 \\
+    Canton FE & Yes & Yes & Yes & Yes & Yes \\
+    Year FE & Yes & Yes & Yes & Yes & Yes \\ \hline
+    \multicolumn{6}{c}{\footnotesize Clustered standard errors at Canton Level in parentheses} \\
+    \multicolumn{6}{c}{\footnotesize *** p$<$0.01, ** p$<$0.05, * p$<$0.1} \\
+    \multicolumn{6}{c}{\footnotesize Coefficients for marital status, education attainment and household size not shown.} \\
+\end{tabular}
+
+}
+
+\end{table}%
+
+\begin{table}[H]
+
+\caption{\label{tbl-acrime2}The Effect of Crime on Labor Income in Main
+Occupation: Canton, Activity Sector and Time FE}
+
+\centering{
+
+    \centering
+    \begin{tabular}{lccccc}
+    \toprule
+    VARIABLES & q10 & q25 & q50 & q75 & q90 \\ \hline
+     &  &  &  &  &  \\
+    lmurders & -0.021*** & -0.014** & -0.007 & -0.002 & 0.004 \\
+     & (0.008) & (0.006) & (0.005) & (0.006) & (0.007) \\
+    age & 0.061*** & 0.053*** & 0.046*** & 0.040*** & 0.034*** \\
+     & (0.003) & (0.002) & (0.002) & (0.001) & (0.001) \\
+    age$^2$ & -0.001*** & -0.001*** & -0.000*** & -0.000*** & -0.000*** \\
+     & (0.000) & (0.000) & (0.000) & (0.000) & (0.000) \\
+    male & 0.158*** & 0.149*** & 0.141*** & 0.133*** & 0.126*** \\
+     & (0.018) & (0.015) & (0.012) & (0.010) & (0.010) \\
+    informal & -0.515*** & -0.460*** & -0.410*** & -0.363*** & -0.321*** \\
+     & (0.018) & (0.015) & (0.013) & (0.012) & (0.012) \\
+    urban & -0.091*** & -0.098*** & -0.105*** & -0.111*** & -0.116*** \\
+     & (0.012) & (0.011) & (0.010) & (0.010) & (0.011) \\
+    married & 0.099*** & 0.093*** & 0.087*** & 0.082*** & 0.077*** \\
+     & (0.007) & (0.005) & (0.004) & (0.004) & (0.004) \\
+    educ & 0.042*** & 0.046*** & 0.050*** & 0.053*** & 0.056*** \\
+     & (0.001) & (0.002) & (0.003) & (0.004) & (0.005) \\
+    tenure & 0.007*** & 0.006*** & 0.005*** & 0.005*** & 0.004*** \\
+     & (0.001) & (0.001) & (0.001) & (0.001) & (0.001) \\
+    Constant & 3.882*** & 4.279*** & 4.649*** & 4.987*** & 5.294*** \\
+     & (0.064) & (0.045) & (0.047) & (0.057) & (0.068) \\
+     &  &  &  &  &  \\ \hline
+    Observations & 249,993 & 249,993 & 249,993 & 249,993 & 249,993 \\
+    Canton FE & Yes & Yes & Yes & Yes & Yes \\
+    Activity Sector FE & Yes & Yes & Yes & Yes & Yes \\
+    Year FE & Yes & Yes & Yes & Yes & Yes \\ \hline
+    \multicolumn{6}{c}{ Clustered standard errors at Canton Level in parentheses} \\
+    \multicolumn{6}{c}{ *** p$<$0.01, ** p$<$0.05, * p$<$0.1} \\
+    \end{tabular}
+
+}
+
+\end{table}%
+
 \section{Implementation}\label{implementation}

### 2024-09-11 article/alt_article.qmd
s
Update alt_article.qmd

@@
 
-keywords: [Fixed effects, Linear heteroskedasticity, Location-scale model, Quantile regression]
-jelcode: [C21, C22, C23]
+keywords: Fixed effects, Linear heteroskedasticity, Location-scale model, Quantile regression
+jelcode: C21, C22, C23
 
@@
 It also shows that the FWL theorem can be used to control for multiple fixed effects.
-Section 3 presents the results of a small simulation study and section 4 illustrates the application of the proposed methods with one empirical example.
+Section 3 presents the results of a small simulation study and section 4 illustrates the application of the proposed methods with two empirical example.
 Section 5 concludes.

### 2024-09-18 article/ThingsToChange.qmd
Create ThingsToChange.qmd

--- 2024-09-11 article/alt_article.qmd
@@
+to be changed
+
 ---
@@
           name: Levy Economics Institute of Bard College
-          city: Annandale-on-Hudson, NY
+          city: Annandale-on-Hudson
           country: USA          
@@
   - name: Leonardo Siles
-    email: leonardo.siles@ucb.edu.bo
+    email: lsiles@fen.uchile.cl
     affiliations:
-        - id: ucb
-          name: Universidad Católica Boliviana
-          city: La Paz, Bolivia
+        - id: fen
+          name: Facultad de Economia y Negocios, Universidad de Chile
+          city: Santiago
+          country: Chile
   - name: Gustavo Canavire-Bacarreza
-    email: gcanavire@worldbank.org
+    email: gcanavire@gmail.com
     affiliations:
-        - id: wb
-          name: The World Bank                 
-          city: Washington, D.C.
-          country: USA
+        - id: upb
+          name: Universidad Privada Boliviana and World Bank, Poverty and Equity Global Practice
 abstract: |
   This paper proposes a new method to estimate quantile regressions with multiple fixed effects.
-The method, which expands on the strategy proposed by @mss2019, allows for the inclusion of multiple fixed effects and provides various alternatives for the estimation of standard errors.
+The method, which expands on the strategy proposed by @mss2019, allows for the inclusion of multiple fixed effects and provides various alternatives for estimating standard errors.
 We provide Monte Carlo simulations to show the finite sample properties of the proposed method in the presence of two sets of fixed effects.
-Finally, we apply the proposed method to estimate the determinants of the surplus of government as a share of GDP, allowing for both time and country fixed effects.
+Finally, we apply the proposed method to two different examples using macroeconomic and microeconomic data and allowing for multiple fixed effects with robust results.
 
-thanks: |
-  The opinions expressed in this paper are those of the authors and do not necessarily reflect the views of the World Bank, its Board of Directors, or the countries it represents.
-
-  The authors would like to thank Enrique Pinzon an Joao Santos-Silva for their helpful comments and suggestions.
-
-keywords: Fixed effects, Linear heteroskedasticity, Location-scale model, Quantile regression
-jelcode: C21, C22, C23
+keywords: 
+  - Fixed effects
+  - Linear heteroskedasticity
+  - Location-scale model
 
@@
 format:
-  sim-art2-pdf:
-    keep-tex: true
+  pdf: 
+    toc-depth: 2
+    number-sections: true
+    documentclass: article
+    margin-bottom: 1.2in
+    margin-top: 1in
+    margin-left: 1.1in
+    margin-right: 1.1in
+    thanks: |
+      The opinions expressed in this paper are those of the authors and do not necessarily reflect the views of the World Bank, its Board of Directors, or the countries it represents.
 
+      The authors would like to thank Enrique Pinzon and Joao Santos-Silva for their helpful comments and suggestions. All remaining errors are our own.
+
+    fontsize: 12pt
+    csl: "templates/apa-no-ampersand.csl"
+    template-partials: 
+      - "templates/title.tex"
+      - "templates/before-body.tex"
+      - "templates/_authors.tex"      
 ---
-
-{{< pagebreak >}}
 
@@
 
-Quantile regression (QR), introduced by @koenkerbasset1978, is an estimation strategy used for modeling the relationships between explanatory variables X and the conditional quantiles of the dependent variable $Q_y (\tau|x)$.
-Using QR one can obtain richer characterizations of the relationships between dependent and independent variables, by exploring how the variables relate along the entire conditional distribution.
-
-A relatively recent development in the literature has focused on extending quantile regressions analysis to include individual fixed effects in the framework of panel data.
-However, as described in @neymanscott1948, and @lancaster2000,  when individual fixed effects are included in quantile regression analysis an incidental parameter problem is generated.
-While many strategies have been proposed for estimating this type of model (see @galvao2017quantile for a brief review), neither has become standard because of their restrictive assumptions in regard to the inclusion of individual and multiple fixed effects, the computational complexity, and implementation.
-
-More recently, @mss2019 (MSS hereafter) proposed a methodology based on a conditional location-scale model, similar to the one described in @he1997 and @zhao2000, for the estimation of quantile regressions models for panel data via a method of moments.
-This method allows individual fixed effects to have heterogeneous effects on the entire conditional distribution of the outcome, rather than constraining their effect to be a location shift only, as in @canay2011, @koenker2004, and @lamarche2010.
-
-In principle, under the assumption that data-generating process behind the data is based on a multiplicative heteroskedastic process that is linear in parameters [@mss2019, @he1997, @zhao2000, @cameron2005], the effect of a variable $X$ on the $q_{th}$ quantile can be derived as the combination of a location effect, and scale effect moderated by the quantile of an underlying i.i.d.
-error.
-For statistical inference, MSS derives the asymptotic distribution of the estimator, suggesting the use of bootstrap standard errors, as well.
-
-This methodology is not meant to substitute for the use of standard quantile regression analysis.
-That said, given the assumptions required for the identification of the model, it provides a simple and fast alternative for the estimation of quantile regression models with individual fixed effects.
-
-In this framework, our paper expands on @mss2019 in two ways.
-First, making use of the properties of generalized method of moments (GMM) estimators, we derive various alternatives for the estimation of standard errors based on the empirical influence functions of the estimators.
-Even if the model is correctly specified, robust standard errors perform better than GLS standard errors due small violations of the model assumptions due to sampling variability.
-Furthermore, clustered standard errors may help to further account for typically unobserved correlations across observations.
-Second, we reconsider the application of Frisch-Waugh-Lovell (FWL) theorem [@frishwaugh1933 and @lovell1963] to extend the MSS estimator and allow for the inclusion of multiple fixed effects.
-This extension may be useful for empirical analysis, as it is common to control for multiple fixed effects such as individual and time fixed effects.
-
-The rest of the paper is structured as follows: section 2 presents the basic setup of the location-scale model described in @he1997 and @zhao2000, tying the relationship between the standard quantile regression model and the location-scale model.
-It also revisits the methodology of MSS, proposing alternative estimators for the standard errors based on the properties of GMM estimators and the empirical influence functions.
-It also shows that the FWL theorem can be used to control for multiple fixed effects.
-Section 3 presents the results of a small simulation study and section 4 illustrates the application of the proposed methods with two empirical example.
-Section 5 concludes.
+[No changes to this section]
 
@@
 
-## Quantile Regression: Location-Scale model {#sec-betas}
-
-Quantile regressions are used to identify relationships between the explanatory variables $X$ and the conditional quantiles of the dependent variable $Q_y(\tau|X)$.
-This relationship is commonly assumed to follow a linear functional form:
-
-$$Q_y(\tau|X) =X\beta(\tau)
-$$ {#eq-eq1}
-
-This allows for a linear effect of $X$ on $Y$, but that could vary across values of $\tau$.
-
-An alternative formulation of quantile regressions is the location-scale model.
-This approach assumes that the conditional quantile of $Y$ given $X$ and $\tau$ can be expressed as a combination of two models: the location model, which describes the central tendency of the conditional distribution; and the scale model, which describes deviations from the central tendency:
-
-$$Q_y(\tau|X) =X\beta+X\gamma(\tau)
-$$ {#eq-eq2}
-
-Here, the location parameters $\beta$ are typically identified using a linear regression model (as in @mss2019) or a median regression (as in @he1997 and @zhao2000) and the scale parameters $\gamma(\tau)$ can be estimated using standard approaches.
-
-Both the standard quantile regression (@eq-eq1) and the location-scale specification (@eq-eq2) can be estimated as the solution to a weighted minimization problem:
-
-$$\hat{\beta}(\tau) = \underset{\beta}{\operatorname{argmin}}
-\left( \sum_{i\in y_i\geq x_i'\beta} \tau (y_i - x_i'\beta) - \sum_{i\in y_i<x_i'\beta} (1-\tau)(y_i - x_i'\beta) \right)
-$$ {#eq-eq3}
-
-One characteristic of this estimator is that the $\beta(\tau)$ coefficients are identified locally and thus the estimated quantile coefficients will exhibit considerable variation when analyzed across $\tau$.
-It is also implicit that if one requires an analysis of the entire distribution, it would be necessary to estimate the model for each quantile.[^1]
-
-[^1]: There are other estimators that provide smoother estimates for the quantile regression coefficients using a kernel local weighted approach [@kaplan2017], as well as identifying the full set of quantile coefficients while simultaneously assuming some parametric functional forms [@frumentobotai2016].
-
-One insightful extension to the location-scale parameterizations suggested by @he1997, @zhao2000, @cameron2005, and @mss2019 is to assume that the data-generating process (DGP) can be written as a linear model with a multiplicative heteroskedastic process that is linear in parameters.[^2]
-
-[^2]: @mss2019 also discuss a model where heteroskedasticity can be an arbitrary nonlinear function $\sigma(x_i'\gamma)$, but develop the estimator for the linear case, i.e., when $\sigma()$ is the identity function.
-
-$$\begin{aligned}
-y_i &=x_i'\beta+\nu_i \\
-\nu_i &=\varepsilon_i \times x_i'\gamma 
-\end{aligned}
-$$ {#eq-eq4}
-
-Under the assumption that $\varepsilon$ is an i.i.d. unobserved random variable that is independent of $X$, the conditional quantile of $Y$ given $X$ and $\tau$ can be written as
-
-$$Q_y(\tau|X) =X\beta+Q_\varepsilon(\tau) \times X\gamma 
-$$ {#eq-eq5}
-
-In this setup, the traditional quantile coefficients are identified as the location model coefficients plus the scale model coefficients moderated by the $\tau_{th}$ unconditional quantile of the standardized error $\varepsilon$.
-For simplicity we will use $q_\tau$ to denote $Q_\varepsilon(\tau)$ in the rest of the paper.
-
-$$\beta(\tau) = \beta + q_\tau \times \gamma 
-$$ {#eq-eq6}
-
-While this specification imposes a strong assumption on the DGP, it has two advantages over the standard quantile regression model.
-First, because the location-scale model can be identified globally, with only a single parameter ($q_\tau$) requiring local estimation, this estimation approach will be more efficient than the standard quantile regression model [@zhao2000].
-Second, under the assumption that $X\gamma$ is strictly positive, the model will produce quantile coefficients that do not cross [@he1997].
-
-Following MSS, the quantile regression model defined by @eq-eq5 can be estimated using a generalized method of moments approach.
-And while it is possible to identify all coefficients ($\beta,\gamma, q_\tau$) simultaneously, we describe and use the implementation approach advocated by MSS, which identifies each set of coefficients separately.
-
-First, the location model can be estimated using a standard linear regression model, where the dependent variable is the outcome $Y$ and the independent variables are the explanatory variables $X$ (including a constant) with an error $u$, which is by definition heteroskedastic.
-In this case, the location-model coefficients are identified under the following condition:
-
-$$\begin{aligned}
-      y_i &=x_i'\beta+\nu_i \\
-      E\big[ x_i \nu_i\big] &=0
-      \end{aligned}
-$$ {#eq-eq7}
-
-Second, after the location model is estimated, the scale coefficients can be identified by modeling heteroskedasticity as a linear function of characteristics $X$.
-For this we use the absolute value of the errors from the location model $u$ as dependent variable, which allows us to estimate the conditional standard deviation (rather than conditional variance) of the errors.
-In this case, the coefficients are identified under the following condition:
-
-$$\begin{aligned}
-  |\nu_i| &=x_i'\gamma+\omega_i \\
-   E\big[ x_i (|\nu_i| -x_i'\gamma ) \big] &=0
-  \end{aligned}
-$$ {#eq-eq8}
-
-It should be noticed that the estimation of the standard errors (next section) requires that the Scale component prediction $x_i'\gamma$ is strictly positive, because it represents the conditional standard deviation of the error $\nu_i$.
-Because this component is identified using a linear model, some values for $x_i'\gamma$ may be negative, which will affect the estimation of the standard errors, as shown in the simulation study.
-
-Third, given the location and scale coefficients, the $\tau_{th}$ quantile of the error $\varepsilon$ can be estimated using the following condition:
-
-$$\begin{aligned}
-  E\left[  \mathbb{1}\left(x_i' (\beta +   \gamma q_\tau) \geq y_i \right) - \tau \right] &=0  \\
-  E\left[  \mathbb{1}\left(   q_\tau \geq \frac{y_i-x_i'\beta}{x_i'\gamma} \right) - \tau \right] &=0  \\
-  \end{aligned}
-$$ {#eq-eq9}
-
-where one identifies the quantile of the error $\varepsilon$ using standardized errors $\frac{y_i-x_i'\beta}{x_i'\gamma}$ or by finding the values that identify the overall quantile coefficients $\beta(\tau)=\beta + \gamma q_\tau$.
-Afterwards, the conditional quantile coefficients are simply defined as the combination of the location and scale coefficients.
-
-## Standard Errors: GLS, Robust, Clustered {#sec-se}
-
-As discussed in the previous section, the estimation of quantile regression coefficients using the location-scale model with heteroskedastic linear errors can be estimated using a the following set of moments, which fits within the GMM framework:
-
-$$\begin{aligned}
-  E[x_i \nu_i  ] &= E[h_{1,i}]=0 \\
-  E[x_i  (|\nu_i|-x_i \gamma) ] &=E[h_{2,i}]=0 \\
-  E\left[  \mathbb{1}\left(   q_\tau\geq \frac{y_i-x_i'\beta}{x_i'\gamma} \right) - \tau \right]  &=E[h_{3,i}]=0 
-  \end{aligned}
-$${#eq-eq10}
-
-Under the conditions described in @newey_chapter_1994 (see section 7), @cameron2005 (see chapter 6.3.9), or as shown in @mss2019, the location, scale, and residual quantile coefficients are asymptotically normal.[^3]
-
-[^3]: @zhao2000 also shows that the quantile coefficients for the location-scale model follow a normal distribution, but uses the assumption that the location model is derived using a least absolute deviation approach (median regression).
-
-Call $\theta=[ \beta' \ \ \gamma' \ \ q_\tau ]'$ the set of coefficients that are identified by the moment conditions in @eq-eq10, a just identified model, and the function $h_i$ is a vector function that stacks all the moments described in @eq-eq10 at the individual level.
-Then $\hat\theta$ follows a normal distribution with mean $\theta$ and variance-covariance matrix $V(\theta)$ that is estimated as
-
-$$
-\hat{V}(\hat\theta)=\frac{1}{N} 
-\bar G(\hat\theta)^{-1} 
-\left( \frac{1}{N} \sum_{i=1}^N h_i h_i'  \Big|_{\theta=\hat\theta} \right) 
-\bar G(\hat\theta)^{-1} 
-$$
-
-which is equivalent to the Eicker-White heteroskedasticity-consistent estimator for least-squares estimators.
-
-Here, the inner product is the moment covariance matrix and $\bar{G}(\theta)$ is the Jacobian matrix of the moment equations evaluated at $\hat\theta$.
-
-$$\bar{G}(\theta) =-\frac{1}{N} \sum_{i=1} \frac{\partial h_i}{\partial \theta'} \Big|_{\theta=\hat\theta}$$
-
-In this framework, the quantile regression coefficients, a combination of the location-scale-quantile estimates, will follow a normal distribution with mean $\beta(\tau) = \beta+\gamma q_\tau$ and variance-covariance matrix equal to
-
-$$\hat{V}(\beta(\tau)) = \Xi \hat{V}(\hat\theta) \Xi'
-$$
-
-where $\Xi$ is a $k \times (2k+1)$ matrix defined as
-
-$$\Xi = [ I(k), \hat q_\tau \times I(k), \hat \gamma ]
-$${#eq-eqqtile}
-
-with $I(k)$ being an identity matrix of dimension $k$ (number of explanatory variables in $X$ including the constant).
-
-While it is possible to estimate the variance-covariance matrix using simultaneous model estimation for a just identified model, it is more efficient to estimate each set of coefficients separately.
-Afterward, the variance-covariance matrix can be estimated using the empirical influence functions of the estimators (see @jann_2020 for an overview of the application and @hampel2005 for an in-depth review).
-
-Specifically, given an arbitrary vector of empirical influence functions $\lambda_i(\theta)$, the variance-covariance matrix can be estimated as
-
-$$\hat{V}(\theta) = \frac{1}{N^2} \sum_{i=1}^N \lambda_i(\theta) \lambda_i(\theta)'
-$$ {#eq-eqvcv}
-
-where the influence functions are defined as:
-
-$$\lambda_i(\theta) = \bar G(\theta)^{-1} h_i(\theta)$$
-
-For the specific case of quantile regressions via moments, the influence functions for the location, scale, and quantile coefficients are[^4]
-
-[^4]: The derivation of the influence functions can be found in the appendix.
-
-$$\begin{aligned}
-\lambda_i(\theta)&=
-  \begin{bmatrix}
-  \lambda_{i}(\beta) \\
-  \lambda_{i}(\gamma) \\
-  \lambda_{i}(q_\tau) 
-  \end{bmatrix} \\
-\lambda_{i}(\beta)&=N (X'X)^{-1}  x_i ( x_i'\gamma) \times \varepsilon_i \\
-\lambda_{i}(\gamma)&= N(X'X)^{-1} x_i ( x_i' \gamma ) \times (\tilde \varepsilon_i -1\big)\\
-\lambda_{i}(q_\tau)&=\frac{\tau-\mathbb{1}\big( q_\tau  \geq \varepsilon_i  \big) }{f_{\varepsilon}(q_\tau)}
-- \frac{ x_i'\gamma \times \varepsilon_i }{\bar x_i'\gamma} 
--  q_\tau \frac{  x_i' \gamma  \times (\tilde \varepsilon_i -1\big)}{\bar x_i'\gamma}
-\end{aligned}
-$$ {#eq-ifs}
-
-The different types of standard errors estimation thus depend on the assumptions imposed for the estimation of $V(\theta)$.
-
-### Robust Standard Errors
-
-The first and most natural standard error estimator is given by equation @eq-eqvcv.
-This is equivalent to the Eicker-White heteroskedasticity-consistent estimator for least-squares estimators.
-Considering the location-scale model, the variance-covariance matrix for the quantile coefficients can be estimated as
-
-$$\hat{V}_{robust}
-  \begin{pmatrix}
-  \hat\beta \\
-  \hat\gamma \\
-  \hat q_\tau
-  \end{pmatrix}
- = \frac{1}{N^2} 
- \begin{pmatrix}
- \sum \lambda_i(\beta) \lambda_i(\beta)' & \sum \lambda_i(\beta) \lambda_i(\gamma)' & \sum \lambda_i(\beta) \lambda_i(q_\tau)' \\
- \sum \lambda_i(\gamma) \lambda_i(\beta)' & \sum \lambda_i(\gamma) \lambda_i(\gamma)' & \sum \lambda_i(\gamma) \lambda_i(q_\tau)' \\
- \sum \lambda_i(q_\tau) \lambda_i(\beta)' & \sum \lambda_i(q_\tau)\lambda_i(\gamma)' & \sum \lambda_i(q_\tau) \lambda_i(q_\tau)' 
-  \end{pmatrix}
-$$
-
-### Clustered Standard Errors
-
-Because one of the typical applications of quantile regressions is the analysis of panel data, allowing for clustered standard errors at the individual level is important.
-If the unobserved error $\varepsilon$ is correlated within clusters, generalized least squares (GLS) standard errors could be severely biased.
-The standard recommendation has been to report block-bootstrap standard errors, clustered at the individual level.
-
-Because we have access to the influence functions, it is straightforward to estimate one-way clustered standard errors.
-
-Let $N_G$ be the total number of clusters $g$, where $g=1\dots N_G$. The clustered variance covariance matrix is given by[^5]
-
-[^5]: It should be noted that one could just as well apply the insights of @cameron_robust_2011, allowing for multiway clustering.
-
-$$\hat{V}_{clustered}
-  \begin{pmatrix}
-  \hat\beta \\
-  \hat\gamma \\
-  \hat q_\tau
-  \end{pmatrix}
- = \frac{1}{N^2} 
- \begin{pmatrix}
- \sum_{g=1}^{N_G} S\lambda_i(\theta) S\lambda_i(\theta)'
-  \end{pmatrix}
-$$
-
-where $S\lambda_i(\theta)$ is the sum of the influence functions over all observations within a given cluster $g$.
-
-$$S\lambda_i(\theta) = \sum_{i\in g} \lambda_i(\theta)
-$$
-
-### GLS Standard Errors {#sec-gls}
-
-The standard errors proposed by MSS can be understood as an application of GLS, which will be valid as long as the model for heteroskedasticity is correctly specified.[^6] To estimate the GLS standard errors, we make use of the following property:
-
-[^6]: As discussed in most econometric textbooks, for example @cameron2005, one approach to correct for heteroskedasticity, when the heteroskedasticity functional form is known or can be estimated, is to use weighted least squares.
-While feasible this approach would defeat the purpose of identifying quantile effects exploiting the heteroskedasticity of the model.
-
-Consider the influence functions and robust variance-covariance matrix for the location coefficients:
-
-$$\begin{aligned}
-\hat V(\hat \beta) &= \frac{1}{N} \sum_i^N \lambda_{i}(\beta) \lambda_{i}(\beta)' \\
-&= \frac{1}{N}  (X'X)^{-1}  \sum_i^N x_i x_i' ( x_i'\gamma \times \varepsilon_i)^2 (X'X)^{-1} \\
-\end{aligned}
-$$
-
-Under the assumption that the model for heteroskedasticity is correctly specified, we can apply the law of iterated expectations and rewrite the variance-covariance matrix as
-
-$$\begin{aligned}
-\hat V(\hat \beta) &= \frac{1}{N} \sum_i^N \lambda_{i}(\beta) \lambda_{i}(\beta)' \\
-&= E(\varepsilon_i^2) \frac{1}{N}  (X'X)^{-1}  \sum_i^N x_i x_i' ( x_i'\gamma)^2 (X'X)^{-1} \\
-&= \sigma^2_{\varepsilon} \frac{1}{N}  (X'X)^{-1}  \hat\Omega_{\beta\beta} (X'X)^{-1}  
-\end{aligned}
-$$
-
-This standard error estimator is an application of GLS that accounts for the heteroskedasticity the model uses to identify the quantile coefficients.
-We can apply the same principle to find the GLS standard errors for the system of location-scale and quantile coefficients.
-To do this, we define the following modified influence functions:
-
-$$\begin{aligned}
-\tilde \lambda_{1,i}&=\tilde \lambda_{2,i}=N (X'X)^{-1}  x_i ( x_i'\gamma) \\  
-\tilde \lambda_{3,i}&=x_i' \gamma  \\
- \psi_{i,1} &= \varepsilon_i \\
- \psi_{i,2} &= \tilde \varepsilon_i -1 \\
- \psi_{i,3} &= \frac{1}{ x_i' \gamma }\frac{\tau-\mathbb{1}\big( q_\tau  \geq \varepsilon_i  \big) }{ f_{\varepsilon}(q_\tau)} - \frac{\varepsilon_i }{\bar x_i'\gamma} 
--  q_\tau \frac{(\tilde \varepsilon_i -1\big)}{\bar x_i'\gamma}
-\end{aligned}
-$$
-
-Then, the GLS standard errors for the location-scale and quantile coefficients can be estimated as
-
-$$\hat{V}_{gls}
-  \begin{pmatrix}
-  \hat\beta \\
-  \hat\gamma \\
-  \hat q_\tau
-  \end{pmatrix}
- = \frac{1}{N^2} 
- \begin{pmatrix}
- \hat\sigma_{11} \hat\Omega_{11} & \hat\sigma_{12} \hat\Omega_{12} & \hat\sigma_{13} \hat\Omega_{13} \\
- \hat\sigma_{12} \hat\Omega_{12} & \hat\sigma_{22} \hat\Omega_{22} & \hat\sigma_{23} \hat\Omega_{23} \\
- \hat\sigma_{13} \hat\Omega_{13} & \hat\sigma_{23} \hat\Omega_{23} & \hat\sigma_{33} \hat\Omega_{33}
-  \end{pmatrix}
-$$
-
-where
-
-$$\begin{aligned}
-\hat\Omega_{jk} &= \frac{1}{N} \sum_{i=1}^N \tilde \lambda_{i,j}(\theta) \tilde \lambda_{i,k}(\theta)' \\
-\hat\sigma_{jk} &= \frac{1}{N} \sum_{i=1}^N \psi_{i,j} \psi_{i,k}
-\end{aligned}
-$$
-
-This estimator of standard errors is equivalent to the one derived by MSS using Theorem 3.
-Empirically, the simulation study shows that this estimator may be very sensitive to predictions of the scale model.
-In the simulation study, we show that when the sample small, and the likelihood of predicting zero or negative values for the scale model is high, the GLS standard errors may be unreasonably large.
-
-## Multiple Fixed Effects: Expanding on @mss2019
-
-Using the setup described in the previous section, MSS proposes an extension to the model proposed by @he1997 that enables the estimation of quantile regression models with panel data, allowing for the inclusion of individual fixed effects.
-However, the methodology can also be generalized to allow for the inclusion of multiple fixed effects.
-This type of analysis can be useful when considering data such as employer-employee linked data [@abowed2006] or teacher-student linked data [@harrissass2011].
-Or, in the most common case, allowing to control for both individual and time fixed effects.
-
-We return to the original model and now assume there are sets of unobserved heterogeneity that are constant across observations, if they belong to common groups.
-Without loss of generality, we can assume that the data-generating process is as follows:
-
-$$\begin{aligned}
-  y_{i} &= x_{i}' \beta + \delta_{g1} + \delta_{g2} + \nu_i \\
-  \nu_i &= \varepsilon_i \times (x_{i}' \gamma + \zeta_{g1} + \zeta_{g2})   
-  \end{aligned}
-$$
-
-where we assume $x_{i}$ vary across groups $g_1$ and $g_2$ (and thus are not collinear) and that $\delta's$ and $\zeta's$ are the location and scale effects associated with the groups fixed effects.[^7]
-
-[^7]: We could just as well consider multiple sets of fixed effects.
-
-If the dimension of groups $g_k$ is low, this model could be estimated using a dummy inclusion approach following @sec-betas, and the standard errors obtained as discussed in @sec-se.
-However, if the dimensionality of $g_k$ is high, the dummy inclusion approach may not be computationally feasible.
-A more feasible approach is to apply the FWL theorem and partial out the impact of the group fixed effects on the control variables $x_{i}$, and the outcome of interest $y_{i}$, and using a similar approach for the identification of $\sigma(x)$.
-In the case of unbalanced setups with multiple groups, the estimation involves iterative processes for which various approaches have been suggested and implemented (see for example, @correia_feasible_nodate, @gaure2013, @rios2015, among others).
-
-When applying the partialing-out approach, some modifications to the approach described in @sec-betas are needed.
-
-First, for all dependent and independent variables in the model ($w=y,x$), we partial out the group fixed effects and obtain the centered-residualized variables:
-
-$$\begin{aligned}
-w_{i} &= \delta_{g1}^w + \delta_{g2}^w + u_{i}^w \\
-w_{i}^{rc} &= E(w_{i}) + \hat{u}_{i}^w
-\end{aligned}
-$$
-
-Afterward, we estimate the location model using the centered-residualized variables:[^8]
-
-[^8]: Using centered-residualized variables allows us to include a constant in the model specification, which simplifies the derivation of the influence functions.
-However, as with other fixed effects models, the constant is not identified and thus should not be interpreted.
-
-$$y_{i}^{rc} = x_{i}^{rc'} \beta + \nu_{i}
-$$
-
-Because $|\hat \nu_i|$ is the dependent variable for the scale model, we apply the partialing out and recentering to this expression ($|\hat \nu_i|^{rc}$), and use that to estimate the following model:
-
-$$|\hat\nu_{i}|^{rc} = x_{i}^{rc'} \gamma + \omega_{i}$$
-
-Finally, the standardized residuals $\varepsilon_i$ can be obtained as follows:
-
-$$\hat{\varepsilon}_{i} = \frac{\nu_{i}}{|\hat\nu_{i}|- \hat \omega_{i}}$$
-
-where $|\hat\nu_{i}|- \hat \omega_{i}$ is the prediction for the conditional standard deviation $\sigma(x_i)=x_{i}' \gamma + \zeta_{g1} + \zeta_{g2}$
-
-The $\tau_{th}$ quantile of the error $\varepsilon$ can be estimated as usual and the variance-covariance matrices obtained in the same way as before (see @sec-se) by using $x_{i}^{rc}$ instead of $x_{i}$ when estimating the influence functions for all estimated coefficients.
+[No changes to this section]
 
@@
 
-To show the performance of the extended strategy, we implement a small simulation study.
-We consider a simple model with a single explanatory variable $x$.
-In contrast with MSS, we consider a two-way fixed effect structure.
-For this exercise, we consider the following data-generating process:
+[No changes to this section]
 
-$$y_i = \alpha_{1i} + \alpha_{2i} + x_i + (2+x_i + \alpha_{1i} + \alpha_{2i} ) \varepsilon_i
-$$
+# Application: Determinants of government surpluses
 
-where $\alpha_{1i}\sim \chi^2(1)$, $\alpha_{2i} \sim \chi^2(1)$, and $x_i = 0.5 * (\chi_i +0.5(\alpha_{1i}+\alpha_{2i}))$, with $\chi_i \sim \chi^2(1)$.
-We only consider the case when the error term $\varepsilon_i$ is assumed to follow a centered $\chi^2$ distribution.[^99] We assume that there are 50 mutually exclusive groups for each set of fixed effects.
-Observations are assigned to each subgroup randomly using a uniform distribution between 1 and 50.
-
-To assess the alternative Standard error estimators, we consider a second data-generating process where the error term is correlated within clusters.
-For this, we assume observations are assigned ramdomly to 100 mutually exclusive groups, which are independent from the fixed effect groups.
-In this setup the data-generating process is:
-
-$$\begin{aligned}
-y_i &= \alpha_{1i} + \alpha_{2i} + x_i + (2+x_i + \alpha_{1i} + \alpha_{2i} )*\kappa_i \\
-\kappa_i &= inv-\chi^2_5(r_{i})/5-1 \\
-r_i &= \Phi((\sqrt{.25}*s_{i}+\sqrt{.75}*s_{g}))
-\end{aligned}
-$$
-
-where $s_{i}\sim N(0,1)$ and $s_{g}\sim N(0,1)$, are errors that vary across individuals $i$ or across clusters $g$.
-$\Phi()$ is the cumulative distribution function of a normal distribution, and $inv-\chi^2_5()$ is the inverse function for a Chi-2 distribution with 5 degrees of freedom.
-With this setup, we generate an error structure with a strong intra-cluster correlation, but without affecting the model specification assumption.^[We do not consider the case of misspecification of the scale model because that change would not only have an impact on the standard errors, but also affect the bias of the estimated coefficients]
-
-We consider sample sizes of 500, 1000, 2000, and 4000 observations, which implies an average of 10, 20, 40, and 80 observations per group.
-The model is estimated using the location-scale model with heteroskedastic linear errors and we report the coefficients for the 25th and 75th quantiles.
-We run this excercise 5000 times.
-@tbl-sim1 reports the bias, simulated standard error, and mean squared error, using the first data generation structure only.
-We also report the results obtained using an adaptation bias-corrected estimator based on the split-panel jackknife estimator proposed by @dhaene2015.[^9] These results are labeled JKC.
-
-[^99]: Specifically we assume $\varepsilon=\frac{r_i}{5}-1$, where $r_i$ follows a chi-squared distribution such that $r_i \sim \chi^2(5)$.
-Simulations under the assumption of normal errors are available upon request.
-
-[^9]: For the implementation, we first estimate the model using the full sample, then randomly assign each observation into one of two groups, and finally reestimate the quantile coefficients for each group.
-The bias-corrected estimator is then obtained as $\hat\beta(\tau)_{jkc}=2*\hat\beta(\tau)_{full}-0.5*\big(\hat\beta(\tau)_{s1}+\hat\beta(\tau)_{s2}\big)$.
-
-Similar to the findings in MSS, we find that while the estimator presents a substantial bias when the sample is small ($N=500$), this bias shrinks as the sample size increases.
-As MSS describes, the bias seems to be proportional to the sample size, or more precisely to the average number of observations per sub-group.
-Interestingly, the bias-corrected estimator presents an almost 0 bias for the 25th percentile, even when the samples are small.
-In contrast, when considering the 75th percentile, the simple estimator shows smaller bias than the Jacknife estimator.[^88: This is also consistent with simulations with a single fixed effect] In either case, despite the bias reduction obtained using the JKC estimator, the standard errors are larger than without correction.
-For the 25th quantile, the reduction in bias is large enough to produce a smaller Mean Squared Error (MSE) than the simple estimator.
-This is similar to the results of MSS.
-
-::: {#tbl-sim1 tbl-pos="H"}
-
-{{< include tb1.tex >}}
-
-Bias, Simulated Standard error, and Mean Squared Error 
-:::
-
-To evaluate the performance of the different standard errors, we present bias, 95% coverage of the biased corrected estimates, as well as the simulated standard errors, average and median of the standard errors obtained using the GLS, robust SE, and clustered standard SE.
-@tbl-sim2 considers the d.g.p.
-without intra-cluster correlation, while @tbl-sim3 considers the d.g.p.
-that induces intra-cluster correlations.
-All simulations consider 5000 repetitions.
-
-The bias magnitude in @tbl-sim2 and @tbl-sim3 is comparable to those observed in @tbl-sim1, with simulated standard errors that show to be slighly larger when we allow for intra-cluster correlations, just as expected.
-When assuming there is no need to clustered standard errors (@tbl-sim2), the coverage associated to GLS standard errors is above 95% when the samples are small, but it approximates to 95% as the sample size increases.
-On the other and, the coverage rates associated to Robust Standard errors are closer to 90%, albeit increasing slighly for larger samples.
-
-One of the main reason that the GLS-Standard errors achieve higher than expected rates of coverage may be related to the fact that the Standard error estimator is very sensitive to near zero predictions from the scale model.
-As shown in @tbl-sim2, average and median GLS-SE are considerably larger than the simulated standard errors when the sample are small.
-While robust standard errors are less sensitive to this problem, producing more stable results, they tend to underestimate the magnitude of the true standard errors in small samples.
-This translates into the lower coverage rates.
-
-::: {#tbl-sim2 tbl-pos="H"}
-
-{{< include tb2.tex >}}
-
-95% Coverage Ratio, and Standard Error Estimation: No Intra-cluster Correlation
-:::
-
-When we consider the presence of Intra-Cluster correlation, @tbl-sim3, we still observe similar problems with the GLS-SE, albeit with high coverage rates.
-While Robust and Clustered Standard errors are in average smaller than the Simulated Standard errors, coverage rates are above 90%.
-Clustered standard errors perform the best only when the sample size is large, with Robust standard error producing low Standard errors estimates.
-
-::: {#tbl-sim3 tbl-pos="H"}
-
-{{< include tb3.tex >}}
-
-95% Coverage Ratio, and Standard Error Estimation: With Intra-cluster Correlation
-:::
-
-Overall, the simulation study shows that using GLS-SE estimator may be appropriate when the sample is relatively large.
-When there is suspected presence of intra-cluster correlation, the use of clustered standard errors is recommended in larger samples.
-However, when the sample is small, the use of robust standard errors may be appropriate if GLS standard errors when there is the risk of near-zero predictions from the scale model.
-
-# Illustrative applications
-
-## Determinants of government surpluses
+[This section has been expanded. Replace the existing section with the following:]
 
 In this section we replicate one of the exercises from MSS, allowing for time and individual fixed effects as well as for different standard errors estimations.
-We use data from @persson_economic_2005, to estimate the relationship between surplus of government as share of GDP, and a measure of quality of democracy (POLITY); log of real income per capita (LYP); trade volume as share of GDP (TRADE); share of population between 15 and 65 years of age (P1564); the share of the population 65 years and older (P65); one-year lag of the dependent variable (LSP); oil prices in US dollars, differntiating between importer and exporter countries (OILIM and OILEX); and the output gap (YGAP).
+We use data from @persson_economic_2005, to estimate the relationship between surplus of government as share of GDP, and a measure of quality of democracy (POLITY); log of real income per capita (LYP); trade volume as share of GDP (TRADE); share of population between 15 and 65 years of age (P1564); the share of the population 65 years and older (P65); one-year lag of the dependent variable (LSP); oil prices in US dollars, differentiating between importer and exporter countries (OILIM and OILEX); and the output gap (YGAP).
 In addition to country fixed effects (as illustrated in MSS), we show results allowing for time fixed effects.
@@
 
-::: {#tbl-tb1 tbl-pos="h"}
-
-{{< include tbl4.tex >}}
-
-Determinants of Government Surpluses: Individual Fixed Effects
-
-:::
+[Insert @tbl-tb1 and @tbl-tb2 here]
 
@@
 
-:::{#tbl-tb2 tbl-pos="h"}
+# Application: Labor incomes and crime in Ecuador
 
-{{< include tbl5.tex >}}
+[This is a new section. Add it after the previous section:]
 
-The Determinants of Government Surpluses: Individual and Time Fixed Effects
-
-:::
-
-## The Effect of Criminal Activities on Labor Incomes{#sec-crime}
-
-In this section, we investigate the effects of criminal activities on labor incomes using a quantile regression approach to discover whether crime has different impacts on the distribution of interest.
+In this section we investigate the effects of criminal activities on labor incomes using a quantile regression approach in order to discover whether crime has different impacts on the distribution of interest.
 We use data from the ENEMDU labor survey from Ecuador and combine it with administrative records of crime reports by Ecuadorian Cantons.
@@
 The combined data set covers the period 2019-2022.
-For the sake of brevity, we will only present here the results of quantile regressions of the log of total labor income on the log of annual reported murders (LMURDERS) and other covariates displayed in Table 1.
-However, our findings are robust to alternative specifications of the model where the dependent variable is either the log of per-capita household income or the log of total labor income from main occupation, both of which are displayed in @sec-app-crime.
+For the sake of brevity, we will only present here the results of quantile regressions of the log of total labor income on the log of annual reported murders (LMURDERS) and other covariates displayed in @tbl-ecucrime_clustered.
+However, our findings are robust to alternative specifications of the model where the dependent variable is either the log of per-capita household income or the log of total labor income from main occupation, both of which are displayed in Appendix B.
 
-:::{#tbl-ecuador tbl-pos="htbp"}
+[Insert @tbl-ecucrime_clustered here]
 
-{{< include tbl6.tex >}}
-
-The Effect of Crime on Labor Income: Canton, Activity Sector and Time Fixed Effects
-
-:::
-
-The findings in @tbl-ecuador support the idea that the effect of murders diminishes as we move forward in the distribution from low to high incomes: in the lowest decile, a 1% increase in reported murders is associated with a 3.08% reduction in total labor income; instead, for the top 10% labor income earners, murders are seen to have little effect on the dependent variable and, in addition, the coefficient is not significant at conventional levels.
+The findings in @tbl-ecucrime_clustered support the idea that the effect of murders diminishes as we move forward in the distribution from low to high incomes: in the lowest decile, an 1% increase in reported murders is associated with a 3.08% reduction in total labor income; instead, for the top 10% labor income earners, murders are seen to have a little effect on the dependent variable and, in addition, the coefficient is not significant at conventional levels.
 Quantile regression estimates are thus really useful to discover relationships between dependent and explanatory variables that are not seen in standard (mean) regression analysis.
@@
 
-While the capability of estimating distinct coefficients of explanatory variables for each quantile is a feature present since @koenkerbasset1978, the method of moments approach allows us to include not one but multiple sets of fixed effects so that one can account for unobserved heterogeneity at different levels.
-Regarding this application, we have included in the estimation fixed effects for Canton, Activity Sector of the income earner and Year as is shown in @tbl-ecuador.
+While the capability of estimating distinct coefficients of explanatory variables for each quantile is a feature present since @koenkerbasset1978, our method of moments approach allows us to include multiple not one but multiple sets of fixed effects so that one can account for unobserved heterogeneity at different levels.
+Regarding this application, we have included in the estimation fixed effects for Canton, Activity Sector of the income earner and Year as is shown in @tbl-ecucrime_clustered.
 Given that LMURDERS is measured at the Canton level, it may be important to control for unobserved factors affecting both crime and income earnings in the Cantons of Ecuador.
 
-Finally, our approach also allows us to obtain clustered standard errors for estimated coefficients so that statistical inference can be performed properly.
-@tbl-ecuador presents clustered standard errors at the Canton level, the rationale being the same as described above for the inclusion of Canton fixed effects in the specification.
+Finally our approach also allows to obtain clustered standard errors for estimated coefficients so that statistical inference can be performed properly.
+@tbl-ecucrime_clustered presents clustered standard errors at the Canton level, the rationale being the same as described above for the inclusion of Canton fixed effects in the specification.
 Had we not taken into account the correlated nature of our standard errors, we would have computed misleading (and smaller) estimates.
@@
 
-In this paper, we have extended the methodology proposed by @mss2019 in order to estimate quantile regression models with multiple sets of fixed effects as well as with alternative standard errrors.
+[Replace the existing Conclusions section with the following:]
+
+In this paper, we have extended the methodology proposed by @mss2019 in order to estimate quantile regression models with multiple sets of fixed effects as well as with alternative standard errors.
 This methodology will allow researchers to implement more-comprehensive analyses of data sets characterized by complex hierarchies and unobserved heterogeneity.
@@
 
-Our example using data to analyze the impact of Crime on labor income in Ecuador also suggests the relevance of using clustered standard errors in the presence of unobserved heterogeneity at different levels.
-We find that the effect of murders on labor income diminishes as we move forward in the distribution from low to high incomes, which is a result that would not have been possible without the use of quantile regression.
-
 # References {.unnumbered}
@@
 
-{{< pagebreak >}}
-
 \appendix
@@
 
-## Model Identification
+[No changes to this section]
 
-The estimation of quantile regression via moments assumes that the DGP is linear in parameters, with an heteroskedastic error term that is also a linear function of parameters:
+# Complimentary analysis of Section 5
 
-$$\begin{aligned}
-y_i = x_i'\beta + \nu_i \\
-\nu_i = \varepsilon_i \times x_i'\gamma
-\end{aligned}
-$$
-
-where $\varepsilon$ is an unobserved i.i.d. random variable that is independent of $x$ and such that $x\gamma$ is larger than 0 for any $x$.
-
-In this case, the $\tau_{th}$ conditional quantile model can be written as
-
-$$Q_y(\tau|X) = x'(\beta +Q_\varepsilon(\tau)  \times \gamma)$$
-
-This model is identified under the following conditions:
-
-$$\begin{aligned}
-  E[(y_i-x_i'\beta)x_i ]  &= E[h_{1,i}]=0 \\
-  E[ (|y_i-x_i'\beta|-x_i' \gamma) x_i ] &=E[h_{2,i}]=0 \\
-  E\left[  \mathbb{1}\left( Q_\varepsilon(\tau) x_i'\gamma +x_i'\beta\geq  y_i  \right) - \tau \right] 
-   &=E[h_{3,i}]=0 
-\end{aligned}
-$$
-
-For simplicity, the rest of the appendix uses $q_\tau$ to represent  $Q_\varepsilon(\tau)$.
-
-## Estimation of the Variance-Covariance Matrix
-
-In this model, to estimate the variance-covariance matrix the set of coefficients $\theta'=[\beta' \ \gamma' \ q_\tau]$, we need to obtain the influence functions of all coefficients, which are defined as
-
-$$\lambda_i = \bar G(\theta)^{-1}
-\begin{bmatrix}
-h_{1,i} \\
-h_{2,i} \\
-h_{3,i}
-\end{bmatrix}
-$$
-
-where the Jacobian matrix $\bar G(\theta)$ is defined as
-
-$$\bar G(\theta) = \begin{bmatrix}
-\bar G_{11} & \bar G_{12} & \bar G_{13} \\
-\bar G_{21} & \bar G_{22} & \bar G_{23} \\
-\bar G_{31} & \bar G_{32} & \bar G_{13} \\
-\end{bmatrix}
-$$
-
-with
-
-$$\bar G_{j,k} = - \frac 1 N \sum_{i=1}^N \frac{\partial h_{j,i}}{\partial \theta_k'} \ \forall j,k \in 1,2,3
-$$
-
-First Moment Condition: Location Model
-
-$$h_{1,i}=x_i(y_i-x_i'\beta)$$
-
-$$\begin{aligned}
-\bar G_{1,1} &=- \frac{1}{N} \sum_{i=1}^N \frac{\partial h_{1,i}}{\partial \beta'} \\
-             &=- \frac{1}{N} \sum_{i=1}^N (-x_i x_i') \\
-             &= N^{-1} X'X
-\end{aligned}
-$$
-
-$$
-\bar G_{1,2} = \bar G_{1,3} = 0
-$$
-
-Second Moment Condition: Scale model
-
-$$h_{2,i}=x_i(|y_i-x_i'\beta|-x_i'\gamma)$$
-
-$$\begin{aligned}
-\bar G_{2,1} &= -\frac{1}{N} \sum \frac{\partial h_{2,i}}{\partial \beta'} \\
-             &=  \frac{1}{N} \sum x_i x_i' \frac{y_i-x_i'\beta}{|y_i-x_i'\beta|} \\
-\frac{y_i-x_i'\beta}{|y_i-x_i'\beta|} &= sign(y_i-x_i'\beta) \\            
-\end{aligned}
-$$
-
-Under the assumption $\varepsilon_i \times x\gamma$, or in this case $y_i-x_i'\beta$, is uncorrelated with $x$, we can simplify the expression as
-
-$$\begin{aligned}
-\bar G_{2,1} &= N^{-1} \left(N^{-1}\sum sign(y_i-x_i'\beta)\right) \sum x_i x_i' \\
-&= N^{-1} E[sign(y_i-x_i'\beta)] X'X
-\end{aligned}
-$$
-
-$$\begin{aligned}
-\bar G_{2,2} &= -\frac{1}{N} \sum \frac{\partial h_{2,i}}{\partial \gamma'} \\
-             &=  \frac{1}{N} \sum x_i x_i' \\
-             &= N^{-1} X'X
-\end{aligned}
-$$
-
-$$\bar G_{2,3}=0$$
-
-Third Moment Condition: Quantile of Standardized Residual
-
-$$\begin{aligned}
-h_{3,i} &= \mathbb{1}\left( q_\tau  x_i'\gamma +x_i'\beta - y_i \geq 0 \right) - \tau \text{ or}\\
-h_{3,i} &= \mathbb{1}\left( q_\tau  \geq \frac{y_i- x_i'\beta}{x_i'\gamma}  \right) - \tau = \mathbb{1}\big( q_\tau \geq \varepsilon  \big) - \tau \\
-\end{aligned}
-$$
-
-Because the indicator function $\mathbb{1}()$ is not differentiable, we borrow from the nonparametric literature to approximate this function with a kernel function.
-Call $k()$ a well behaved kernel function that is symetric around 0, and $K()$ its integral, with range between 0 and 1.
-With an arbirarily small bandwidth $h$, we can use the function $K()$ to approximate the indicator function:
-
-$$
-\lim_{h\rightarrow 0} K\left(\frac{z}{h}\right) \approx \mathbb{1}(z\geq 0)
-$$
-
-Thus the function $h_{3,i}$ can be approximated as
-
-$$h_{3,i} \approx K\left( \frac{1}{h} \Big( q_\tau x_i'\gamma +x_i'\beta - y_i  \Big) \right) - \tau
-$$
-
-Now, we can obtain the Jacobian matrix $\bar G_{3,1}$ as:
-
-$$\begin{aligned}
-\bar G_{3,1} &= -\frac{1}{N} \sum \frac{\partial h_{3,i}}{\partial \beta'} \\
-             &= -N^{-1} \sum \frac{1}{h} k\left( \frac{1}{h} \Big( q_\tau x_i'\gamma +x_i'\beta - y_i  \Big) \right) x_i' \\ 
-             &= -N^{-1} \sum \frac{1}{h} k\left( \frac{1}{h} \big( q_\tau x_i'\gamma - \nu_i \big)   \right) x_i'  \\
-             &= -N^{-1} \sum \frac{1}{h} k\left( \frac{1}{h} ( q_\tau - \varepsilon_i ) x_i'\gamma  \right) x_i'  
-\end{aligned}
-$$
-
-If we condition on $X$, use the law of iterated expectations, and assume that $\varepsilon_i$ is homoskedastic, we can obtain:
-
-$$\begin{aligned}
-\bar G_{3,1} &= -N^{-1} \sum \frac{1}{h} k\left( \frac{1}{h} ( q_\tau - \varepsilon_i ) x_i'\gamma  \right) x_i'  \\
-             &= -N^{-1} \sum \frac{1}{h} k\left( \frac{q_\tau - \varepsilon_i}{h}  \right)  \frac{x_i'}{x_i'\gamma}  \\
-             &= -N^{-1} f_\varepsilon (q_\tau) \sum  \frac{x_i'}{x_i'\gamma}  
-\end{aligned}
-$$
-
-Finally, this simplifies to:
-$$\begin{aligned}
-\bar G_{3,1} &\simeq -  f_\varepsilon (q_\tau) \frac{\bar x_i'}{ \bar x_i' \gamma} 
-\end{aligned}
-$$
-
-where we use the fact that asymptotically, the expression $\frac{1}{N}\sum \frac{a_i}{b_i}$ can be approximated using Taylor expansions by $\frac{\bar a}{\bar b}$.
-[^11] Thus, we can rewrite the last term as
-
-[^11]: This approximation will be useful when we consider the estimation of the influence functions.
-
-The Jacobian for the second matrix $\bar G_{3,2}$ can be derived similarly:
-
-$$\begin{aligned}
-\bar G_{3,2} &= -\frac{1}{N} \sum \frac{\partial h_{3,i}}{\partial \gamma'} \\
-             &= -N^{-1} \sum \frac{1}{h} k\left( \frac{1}{h} ( q_\tau - \varepsilon_i ) x_i'\gamma  \right) q_\tau x_i'  \\
-             &= -N^{-1} \sum \frac{1}{h} k\left( \frac{q_\tau - \varepsilon_i}{h}    \right) q_\tau \frac{x_i'}{x_i'\gamma}  \\
-             &\simeq  -  f(q_\tau)  q_\tau \frac{\bar x'}{\bar x'\gamma}
-\end{aligned}
-$$
-
-and the Jacobian for the third matrix $\bar G_{3,3}$ is
-
-$$\begin{aligned}
-\bar G_{3,3} &= -\frac{1}{N} \sum \frac{\partial h_{3,i}}{\partial q_\tau} \\
-             &= -N^{-1} \sum \frac{1}{h} k\left( \frac{1}{h} ( q_\tau - \varepsilon_i ) x_i'\gamma  \right) x_i'\gamma  \\
-             &= -N^{-1} \sum \frac{1}{h} k\left( \frac{q_\tau - \varepsilon_i}{h}   \right) \frac{x_i'\gamma}{x_i'\gamma}  \\
-             &\simeq  -  f(q_\tau)  
-\end{aligned}
-$$
-
-## Influence Functions
-
-Location Coefficients
-
-$$\lambda_i(\beta) = \bar G^{-1}_{1,1} h_{1,i} = N (X'X)^{-1}(x_i (y_i-x_i'\beta)) = N (X'X)^{-1}(x_i \nu_i)
-$$
-
-which can also be written as a function of the standardized residuals:
-
-$$\lambda_i(\beta) = \bar G^{-1}_{1,1} h_{1,i} = N (X'X)^{-1}(x_i (y_i-x_i'\beta)) = N (X'X)^{-1}(x_i ( x_i'\gamma \times \varepsilon))
-$$
-
-Scale Coefficients
-
-$$\begin{aligned}
-\lambda_i(\gamma)&=\bar G_{2,2}^{-1}\Big(h_{2,i}-\bar G_{2,1} \lambda_i(\beta)\Big) \\
-&=N (X'X)^{-1} \Big(x_i(|\nu_i|-x_i' \gamma) 
-- N^{-1} E[sign(\nu_i)] X'X \big[ N (X'X)^{-1}(x_i \nu_i) \big] \Big) \\
-&=N (X'X)^{-1} \Big(x_i(|\nu_i|-x_i' \gamma) - E[sign(\nu_i)] (x_i \nu_i)  \Big) \\
-&=N (X'X)^{-1} x_i \Big( |\nu_i| - E[sign(\nu_i)] \nu_i -x_i' \gamma \Big) 
-\end{aligned}
-$$
-
-However,
-
-$$\begin{aligned}
-|\nu_i| &= \nu_i \times \mathbb{1}(\nu_i \geq 0) - \nu_i \times \mathbb{1}(\nu_i < 0) \\
-|\nu_i| &= \nu_i \times \mathbb{1}(\nu_i \geq 0) - \nu_i \times [1-\mathbb{1}(\nu_i \geq 0)] \\
-|\nu_i| &= 2 \nu_i \times \mathbb{1}(\nu_i \geq 0) - \nu_i  
-\end{aligned}
-$$
-
-and
-
-$$\begin{aligned}
-E[sign(\nu_i)] &= E[\mathbb{1}(\nu_i \geq 0)] - E[\mathbb{1}(\nu_i < 0)] \\
-E[sign(\nu_i)] &= E[\mathbb{1}(\nu_i \geq 0)] - E[(1-\mathbb{1}(\nu_i \geq 0))] \\
-E[sign(\nu_i)] &= 2 E[\mathbb{1}(\nu_i \geq 0)] - 1
-\end{aligned}
-$$
-
-Thus,
-
-$$\begin{aligned}
-\lambda_i(\gamma) &= N(X'X)^{-1} x_i   \Big( 2 \nu_i \times \mathbb{1}(\nu_i \geq 0) - \nu_i  - ( 2 E[\mathbb{1}(\nu_i \geq 0)] - 1) \nu_i -x_i' \gamma \Big) \\
-  &= N(X'X)^{-1} x_i   \Big( 2 \nu_i \times \mathbb{1}(\nu_i \geq 0) -  2 E[\mathbb{1}(\nu_i \geq 0)] \nu_i -x_i' \gamma \Big) \\
-  &= N(X'X)^{-1} x_i   \Big( 2 \nu_i \times \big[ \mathbb{1}(\nu_i \geq 0) -  E[\mathbb{1}(\nu_i \geq 0)] \big] -x_i'\gamma \Big) \\
-  &= N(X'X)^{-1} x_i   \Big( \tilde \nu_i -x_i' 
-  \gamma \Big)
-\end{aligned}
-$$
-
-This last expression is the equivalent simplification used in @mss2019 and @im2000.
-If the scale function is strictly positive, it also follows that $\mathbb{1}(\nu_i \geq 0)= \mathbb{1}(\varepsilon_i \geq 0)$.
-Thus, it can be simplified as
-
-$$\begin{aligned}
-\lambda_i(\gamma) &= N(X'X)^{-1} x_i ( x_i' \gamma ) \times (\tilde \varepsilon_i -1\big)
-\end{aligned}
-$$
-
-Quantile of Standardized Residual
-
-$$\begin{aligned}
-\lambda_i(q_\tau)&=\bar G_{3,3}^{-1}
-\Big(
- h_{3,i}-\bar G_{3,1} \lambda_i(\beta)-\bar G_{3,2} \lambda_i(\gamma)
-\Big) \\
-&=-\frac{1}{f_{\varepsilon}(q_\tau)} \times \Bigg( \Big(\mathbb{1} ( q_\tau  \geq \varepsilon  ) - \tau \Big)  \\
-&+ f_{\varepsilon} (q_\tau) \frac{\bar x_i'}{\bar x_i'\gamma} 
-N (X'X)^{-1} x_i  ( x_i'\gamma \times \varepsilon) \\
-&+ f_{\varepsilon}(q_\tau) q_\tau \frac{\bar x_i'}{\bar x_i'\gamma} N(X'X)^{-1} x_i   \big( \tilde \nu_i -x_i' 
-  \gamma \big) 
-\Bigg) \\
-&=\frac{\tau-\mathbb{1}\big( q_\tau  \geq \varepsilon  \big) }{f_{\varepsilon}(q_\tau)}
-- \frac{ x_i'\gamma \times \varepsilon_i }{\bar x_i'\gamma} 
--  q_\tau \frac{ \tilde \nu_i -x_i' 
-  \gamma }{\bar x_i'\gamma} 
-\end{aligned}
-$$
-
-# Complementary analysis of @sec-crime{#sec-app-crime}
+[This is a new appendix. Add it after the previous appendix:]
 
 In this appendix, we present the quantile regressions of both (log) per-capita household income and the (log) of labor income from main occupation on the (log) of annual reported murders.
-While in the first specification the coefficients of interest are not significant at conventional levels because of clustered standard errors (see @tbl-acrime1), the same pattern of decreasing association between murders and measurements of well-being as we move to the right of the distribution is revealed using our proposed method.
+While in the first specification the coefficients of interest are not significant at conventional levels because of clustered standard errors (see table @tbl-ecucrime_percapitaincome), the same pattern of decreasing association between murders and measurements of well-being as we move to the right of the distribution is revealed using our proposed method.
 
-However, in @tbl-acrime2 we get significant (at the 1% level) associations between reported murders and a slightly different measurement of labor income that only takes into account the main occupation of the individual.
-Compared to total labor income, the coefficients displayed in @tbl-acrime2 are smaller in magnitude: for the lowest decile of the distribution, we find a 1 percentage point difference in the coefficient of interest between the two alternative specifications, where the largest effect corresponds to total labor income.
+However, in table @tbl-ecucrime_mainlaborinc we get significant (at the 1% level) associations between reported murders and a slightly different measurement of labor income that only takes into account the main occupation of the individual.
+Compared to total labor income, the coefficients displayed in table @tbl-ecucrime_mainlaborinc are smaller in magnitude: for the lowest decile of the distribution, we find a 1 percentage point difference in the coefficient of interest between the two alternative specifications, where the largest effect corresponds to total labor income.
 Nevertheless, and once again, the decreasing pattern of reported murders across quantiles is documented for this specification.
-What is even more interesting, compared to our estimations in @tbl-ecuador, is that crime is no longer statistically meaningful from the median of the distribution onwards.
+What is even more interesting, compared to our estimations in table @tbl-ecucrime_clustered, is that crime is no longer statistically meaningful from the median of the distribution onwards.
 
-:::{#tbl-acrime1 tbl-pos="H"}
-
-{{< include tbla1.tex >}}
-
-The Effect of Crime on Per Capita Household Income: Canton and Time Fixed Effects
-:::
-
-:::{#tbl-acrime2 tbl-pos="H"}
-
-{{< include tbla2.tex >}}
-
-The Effect of Crime on Labor Income in Main Occupation: Canton, Activity
-Sector and Time FE
-:::
+[Insert @tbl-ecucrime_percapitaincome and @tbl-ecucrime_mainlaborinc here]
 
@@
 
-The method described here can be implemented using any of the following packages:
-
--   `mmqreg` in Stata: `net install mmqreg, from(https://friosavila.github.io/stpackages)`
--   `mmqreg` in R: Available on GitHub (https://github.com/friosavila/mmqreg)
+[No changes to this section]
